### 2019-12-20 MS.tex
Imported overleaf version

\documentclass{article}

\usepackage{graphicx}
%\pagestyle{empty}
\usepackage{dsfont}
\usepackage{textcomp}
\usepackage{amsmath}
\usepackage{courier}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\graphicspath{{images/}}
\usepackage{amsthm}
\usepackage{eucal}
\usepackage{amssymb}
%\usepackage{mdsymbol}
\usepackage{mathrsfs}
\usepackage{dsfont}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{caption}
\usepackage{tikz}
\usepackage{tikz-cd}
\usepackage{wrapfig,lipsum,booktabs}
\usepackage{caption}
\usepackage[square, longnamesfirst,numbers]{natbib}
\usepackage[ruled,linesnumbered]{algorithm2e}

%\usepackage{hyperref}
\usepackage{amstext} % for \text macro
\usepackage{array}   % for \newcolumntype macro
\usepackage[unicode]{hyperref}
\usepackage{verbatim}
\usepackage{makecell}
\usepackage{float}

\newcolumntype{C}{>{$}c<{$}} % math-mode version of "l" column type

\newcommand{\den}{\mathop{\mathgroup\symoperators den}\nolimits}
\newcommand{\ggd}{\mathop{\mathgroup\symoperators ggd}\nolimits}
\newcommand{\des}{\text{d.e.s.d.a.\ }}
%\newcommand{\opg}{\text{d.e.s.d.a.\ }}
\newcommand{\blokje}{\hfill $\Box$\\}
%Om je bewijs of je antwoord af te sluiten.
\newcommand{\header}[1]{\vspace{0.5cm}\framebox[\linewidth]{\textsc{Exercise #1}}\\}
\newcommand{\deel}[1]{\textbf{#1)}\ }
\newcommand{\macht}[1]{\mathcal{P}(#1)}
\newcommand{\entier}[1]{\left\lfloor #1 \right\rfloor}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\renewcommand{\C}{\mathbb{C}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\Lcal}{\mathcal{L}}
\renewcommand{\O}{\mathcal{O}}
\renewcommand{\P}{\mathbb{P}}
\newcommand{\Pcal}{\mathcal{P}}
\newcommand{\NP}{\mathcal{NP}}
\newcommand{\NPC}{\mathcal{NPC}}
\newcommand{\F}{\mathbb{F}}
\renewcommand{\angle}[1]{\hspace{-2pt}\left\langle #1 \right\rangle}
\newcommand{\rad}{\text{rad}}
\newcommand{\x}{x}
\newcommand{\tensor}{\otimes}
\newcommand{\Ring}{\textbf{Rings}}
\newcommand{\Sets}{\textbf{Sets}}

\DeclareMathOperator{\mon}{mon}
\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\Gal}{Gal}
\DeclareMathOperator{\End}{End}
\DeclareMathOperator{\sgn}{sgn}
\DeclareMathOperator{\trdeg}{trdeg}
\DeclareMathOperator{\rk}{rk}
\DeclareMathOperator{\Fun}{Fun}
\DeclareMathOperator{\im}{im}
\DeclareMathOperator{\Spec}{Spec}
\DeclareMathOperator{\sep}{sep}
\DeclareMathOperator{\Ann}{Ann}
\let\S\undefined
\DeclareMathOperator{\S}{S}
\DeclareMathOperator{\A}{A}

\frenchspacing

\begingroup
\makeatletter
\@for\theoremstyle:=definition,remark,plain\do{%
	\expandafter\g@addto@macro\csname th@\theoremstyle\endcsname{%
		\addtolength{\thm@preskip}{5pt}
		\setlength{\thm@postskip}{10pt}
	}%
}
\endgroup %Zorgt voor mooie enters voor claims

\title{A geometric approach to linear and quadratic Chabauty}
\author{Pim Spelier}
\date{November 2015}

%\newtheoremstyle{mytheoremstyle}{5pt}{-15pt}{\itshape}{}{\bfseries}{.}{.5em}{}

\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section] % reset theorem numbering for each section
\newtheorem{lem}[thm]{Lemma} % same for lemma's
\newtheorem{conj}[thm]{Conjecture} % same for vermoedens
\newtheorem{cor}[thm]{Corollary} % same for vermoedens
\newtheorem{prop}[thm]{Proposition} % same for vermoedens
\newtheorem{algo}[thm]{Algorithm} % same for vermoedens

\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition} % definition numbers are dependent on theorem numbers
\newtheorem{exmp}[thm]{Example} % same for example numbers

\theoremstyle{remark}
\newtheorem{rem}[thm]{Remark} % remark numbers are dependent on theorem numbers

\usepackage{chngcntr}
\counterwithin{table}{section}

\newcommand{\overbar}[1]{\overline{#1}}

%\setlength{\parindent}{0pt}
%\setlength{\parskip}{\baselineskip}

\newcommand\legendre[2]{
  \genfrac(){}{}{#1}{#2}
}

\newcommand{\ord}{\operatorname{ord}}

\begin{document}
%\nocite{*}

\vspace*{1em}

\begin{center}

{\Large\bf 
P.\ Spelier
}

\vspace{1em}

{\LARGE\bf 
A geometric approach to linear and quadratic Chabauty
}

\vspace{10em}

{\large\bf 
Master thesis
}

\vspace{1em}

{\large\bf 
\today
}

\vspace{10em}

{\large\bf
\begin{tabular}{ll}
Thesis supervisor: & prof. dr. S.J. Edixhoven\\
\end{tabular}
}

\vfill

\includegraphics{ulzegel_blauw}\\

\vspace{2em}

{\large\bf 
Leiden University\\
Mathematical Institute\\
}

\end{center}
\thispagestyle{empty}
\newpage

\tableofcontents
\newpage

%-----------------------------------------------------------------------------------------------------------------------

\section{Introduction}
\label{section:intro}
Say something about the problem, Faltings, et cetera

Say something about Chabauty's general idea

Mention Flyn, Coleman, Balakrishnan et al. and their way of doing quadratic quickly

Say something about linear Chabauty geometric style

Say something about quadratic Chabauty geometric style.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{Linear Chabauty}
Let $p>2$ be a prime, and $C$ be a scheme over $\Z$, proper, flat, regular with $C$ smooth over $\Z_{(p)}$ and $C_\Q$ of dimension $1$ and geometrically connected, of genus $g \geq 1$ and Mordell-Weil rank $r < g$. Assume we have a $\Q$-point $b$ in $C$, or equivalently a $\Z$-point. Let $J$ be the Jacobian of $C$; we view $C$ as a subscheme of $J$, using the map $Q \mapsto Q - b$ on points. Let $P \in C(\F_p)$ be a point such that $t := P - b \in J(\F_p)$ lies in the image of $J(\Z)$.

\begin{defn}
Let $S$ be a scheme, $T \to U$ a morphism of schemes and $x : T \to S$ an $T$-point. We define $S(U)_x$ as the morphisms from $U$ to $S$ that, after precomposing with $T \to U$, give $x$.
\end{defn}

We want to find an upper bound for the cardinality of $C(\Z)_P$

% Say something about smooth schemes over Z_p, and their Z_p points
\subsection{Points on a smooth scheme over \texorpdfstring{$\Z_p$}{Z\_p}}
\label{subs:smoothzppoints}
Let $X/\Z_p$ be a smooth scheme of dimension $d$, and let $x \in X(\F_p)$ be a point. Then $X(\Z_p)_x$ is in bijection with $\Z_p^d$. This bijection is given by choosing parameters at $x$; evaluating at $X(\Z_p)_x$ gives a bijection with $(p\Z_p)^d$, and then we divide by $p$. For putting up a nice framework to work in, we start with blowing up $X$ at $x$.
%TODO: give proof and define $\Z_p\angle{z_1,...,z_r}$ as the $p$-adic completion of $\Z_p[z_1,...,z_r]$, i.e. powerseries which are polynomials modulo every power of $p$.

% Blow up X at x, and look at the part where p generates the maximal ideal
Assume, by looking at a neighborhood of $x$, that $X = \Spec A$ is affine and that $p,t_1,\dots,t_d$ generate $O_{X,x}$ with $t_1,\dots,t_d$ regular on $X$. By shrinking $X$ even more, we may assume that $t = (t_1,\dots,t_d): X \to \A^d_{\Z_p}$ is smooth and hence \'etale. Let $\Tilde{X}_x$ be the blowup of $X$ at $x$. Now consider the blowup $\Tilde{X}_x \to X$ of $X$ at $x$, and let $\Tilde{X}_x^p$ be the part where $p$ generates the maximal ideal. As $t$ is \'etale, the ideal of $X$ defining $x$ is the pullback along $t$ of the ideal of $\A^d_{\Z_p}$ defining the origin $a$ over $\F_p$. That means that the blowup $\Tilde{X}_x \to X$ is the pullback of the blowup $\Tilde{\A}^d_{\Z_p,a} \to \A^d$. Then the part $\Tilde{X}_x^p$ is the pullback of the corresponding part of $\Tilde{\A}^d_{\Z_p,a}$, i.e. $\Spec \Z_p[x_1/p,...,x_d/p]$ with the morphism $\Z_p[x_1,...,x_d] \to \Z_p[x_1/p,...,x_d/p]$ being the inclusion. That implies that $\Tilde{X}_x^p$ is $\Spec A[]$

Conclude that $\Tilde{X}_x^p(Z_p)$ is in bijection with $X(Z_p)_x$

Talk about the coordinate ring and its p-adic completion

Say something about functoriality

\subsection{From \texorpdfstring{$J(\Z)$}{J(Z)} to \texorpdfstring{$J(\Z_p)$}{J(Z\_p)}}
For $p > 2$, we know that the torsion of $J(\Z)$ injects into $J(\F_p)$, by Proposition 2.3 of \cite{pierre2000}. Hence for $0 \in J(\F_p)$, we know $J(\Z)_0$ is as a group isomorphic to $\Z^r$ with $r$ the Mordell-Weil rank. By assumption, we also know $J(\Z)_t$ is in bijection with $J(\Z)_0$. By Subsection \ref{subs:smoothzppoints} we know $J(\Z_p)_t$ is in bijection with $\Z_p^{g}$, with the bijection given by evaluating parameters and dividing by $p$. Let $\kappa: \Z^r \to \Z_p^g$ be the map resulting from the inclusion $J(\Z)_t \to J(\Z_p)_t$. Then $\kappa$ turns out to have a special property.

\begin{thm}
\label{thm:kappanice}
There are uniquely determined $\kappa_1,...,\kappa_g \in \Z_p\angle{z_1,...,z_r}$ such that for all $x \in \Z^r$ we have $\kappa(x) = (\kappa_1(x),...,\kappa_g(x))$ and the image $\overline{\kappa_i}$ of $\kappa_i$ in $\F_p[z_1,...,z_r]$ has degree at most $1$.
\end{thm}
TODO: give proof

\begin{cor}
\label{cor:closurejac}
The map $\kappa$ extends uniquely to a continuous map $\kappa: \Z_p^r \to \Z_p^g$, given by the same power series, and the closure $\overline{J(\Z)_t} \subset J(\Z_p)_t$ is given by the image of $\Z_p^r$ under $\kappa$.
\end{cor}
TODO: give proof

\subsection{From \texorpdfstring{$C(\Z_p)$}{C(Z\_p)} to \texorpdfstring{$J(\Z_p)$}{J(Z\_p)}}
By Subsection \ref{subs:smoothzppoints}, we also know that $C(\Z_p)_P$ is in bijection with $\Z_p$, again with the bijection given by evaluating a parameter and dividing by $p$. Apparently the resulting function $\Z_p \to \Z_p^g$ is linear modulo $p$, i.e. there are power series $f_1,...,f_{g-1} \in \Z_p\angle{z_1,...,z_g}$ such that the image of $C(\Z_p)_P$ is exactly given by $V(f_1,...,f_{g-1})$, and all $f_i$ are linear modulo $p$. Another way to think of this, is as $C(\Z/p^2\Z)_P$ being an affine line inside $J(\Z/p^2\Z)_t$.
TODO: give proof
% Say something about the f_i defining C(Z_p) in J(Z_p)

\subsection{Finding \texorpdfstring{$C(\Z)$}{C(Z)}}
Clearly, as subsets of $J(\Z_p)_t$, we have the inclusion $C(\Z)_P \subset C(\Z_p)_P \cap \overline{J(\Z)_t}$. Let $\kappa^*f_1,...,\kappa^*f_{g-1}$ be the pullbacks along $\kappa$ of the $f_i$, and let $I$ be the ideal they generate inside $A := \Z_p\angle{z_1,...,z_r}$. Then $C(\Z_p)_P \cap \overline{J(\Z)_t}$ is in bijection with $\Hom(A/I,\Z_p)$. By Theorem 4.2 of Edixhoven-Lido, we just need to check whether $\overline{A}/\overline{I}$ is finite. As all $\overline{\kappa^* f_i}$ are linear, in fact, $\overline{A}/\overline{I}$ is always of the form $0$ or $\F_p[w_1,...,w_s]$ for some $s \leq r$, and $s = 0$ iff the system of linear equations $\overline{\kappa^* f_i} = 0, i \in \{1,...,g-1\}$ has a unique solution. In general, we may expect an upper bound for $|C(\Z)_P|$ of $1$ if $r \leq g-1$.
TODO: give proof of Theorem 4.2.
% Pull back the f_i along kappa for the final theorem

\subsection{Calculations modulo \texorpdfstring{$p^2$}{p\^2}}
Say something about how, for the right set of points $\{p_1,...,p_g\}$, the map $C^{g} \to J$ is etale at that set of points. Then say something about what that implies about $J(\Z_p)_0$ (equal to $\sum q_i - p_i$ where $q_i \in C(\Z_p)_{p_i}$), and $J(\Z/p^2\Z)_0$, which becomes isomorphic as vector spaces to $\F_p^g$, and how we can find $\kappa$ by expressing elements of $J(\Z)_0$ in that basis, and similarly $f_1,...,f_{g-1}$ by finding $P_1 - P_2$ in that basis for some $Q_1,Q_2 \in C(\Z/p^2\Z)_P$ not equal.

An important part of this, is that there is a parametrisation $P_\mu, \mu \in \F_p$ of the points in $C(\Z/p^2\Z)_P$ such that $P_\mu + P_\nu = P_{\mu + \nu} + P_0$ as Cartier divisors.

\section{Implementations of linear Chabauty and an explicit example}
We now assume that $C$ is hyperelliptic, i.e. given by the degree $2g+2$ homogenisation of an equation of the form
\[
y^2 = f(x)
\]
inside $\P(1,g+1,1)$ where $f$ is a monic polynomial of degree $2g+1$ or $2g+2$. An alternative way of defining such a curve, and the one we will be using mainly, is as a glueing of two affine charts: $y^2 = f(x)$, and $w^2 = f^{r}(v)$, where $f^{r}(v)$ is the polynomial $v^{2g + 2} f(1/v)$, and a birational map between them is given by $(x,y) \mapsto (\frac{1}{x},\frac{y}{x^{-g-1}})$. We also have the coordinates $X,Y,Z$ of $\P(1,g+1,1)$, with $x = X/Z, y = Y/Z^{g+1}, v = Z/X, w = Y/X^{g+1}$, but beware; these coordinates do not behave nicely on the origin of the patch $D(Y)$. We mainly use the first chart; we call any point that lies on it an affine point of $C$. We will treat the case that $f$ has degree $2g+2$ (this can be done by translating $f$ until the constant coefficient is non-zero, and then looking at $f^r$). In that case, writing , the line at infinity $C$ looks like $Y^2 = X^{2g+2}$, i.e. $(Y-X^{g+1})(Y+X^{g+1}) = 0$, and we see there are two points $\infty_+ = (1:1:0)$ and $\infty_- = (1:-1:0)$. Finally, we note that there is an involution on $C$ given by $\sigma(x,y) = (x,-y)$ and $\sigma(v,w) = (v,-w)$.

\subsection{Makdisis algorithms}
Say something about how Makdisis algorithms work (i.e., give an introduction to the terminology) \cite{makdisi2004}.

As we are using and adding on an implementation by Mascot \cite{mascot2018}, we briefly introduce his notation. This is a summary of section 2.1 in \cite{mascot2018}.

We first look at representing $J(k)$ where $k$ is a field. Given a divisor $D$ on $C$, denote
\[
\Lcal(D) = \{f \in k(C)^\times : \div(f) + D \geq 0 \} \sqcup \{0\}.
\]
We pick $D_0$ an effective divisor of degree $d_0 \geq 2g+1$; in the case of hyperelliptic curves, this will be $(g+1)(\infty_+ + \infty_-)$. We set $V_n = \Lcal(nD_0)$. We let $n_Z$ be an integer $\geq 5d_0 + 1$, and assume, if necessary passing to an extension of $k$, that we have a set $Z$ of size $n_Z$ of distinct points in $C(k)$ outside the support of $D_0$; in fact, this will consist of affine points in our case. We have an evaluation map $V_5 \to k^Z$, evaluating a rational function at $Z$. By our choice of $n_Z$, this is an injective map, i.e. we can represent rational functions in $V_5$ by their values in $k^Z$. In this representation, we can even add, subtract, or multiply rational function, by respectively adding, subtracting or multiplying the correspondig vectors in $k^Z$. It is now also possible to represent subspaces of $V_5$ by giving a basis in $k^Z$.

We now explain the representation of $J(k)$. Note that for any $x \in J(k)$, we have that $x + D_0$ is of degree at least $2g+1$ and hence is equivalent to an effective divisor $E \geq 0$. Then we represent $x$ by $\Lcal(2D_0 - E)$ inside $V_2$; by Riemann-Roch this is a $d_W$-dimensional subspace of $V_2$ where $d_W = d_0 + 1 - g$, and in particular we can represent it as a $n_z \times d_W$ matrix, itself representing a subspace of $k^Z$. This representation is nowhere near unique; there are many different effective divisors $E$ equivalent to $x + D_0$, and many bases for a subspace of $k^Z$.

As explained in Mascots article, using this representation one can do all relevant computations in $J(k)$; adding, subtracting, finding the zero element, and most importantly: checking equality.

\subsubsection{Going from \texorpdfstring{$\F_p$}{Fp} to \texorpdfstring{$\Z/p^e\Z$}{Z/peZ}}
We now know how to compute in $J(k)$ for $k$ a field such that $C(k)$ is big enough. In practice, if we want to calculate in $J(\F_p)$, this means passing to $J(\F_q)$ for some $q = p^a$ with $a$ large enough; by the Hasse-Weil bound this will work. However, for Chabauty we want to compute inside $J(\Z/p^e\Z)$. Luckily, Mascots code takes care of this too, by passing from vector spaces over $\F_p$ to free $R$-submodules of $R^n$ with $R = Z/p^e\Z$; in fact, all submodules of $R^n$ we will be seeing are free. That means all these submodules will have good reduction, i.e. the rank remains the same when passing to $\F_p$. If the maps between such modules also have good reduction, then all kernels, images, et cetera will also have these properties, and can be calculated by Hensel lifting the kernels, images, et cetera of these maps modulo $p$.

Explain Howell modules, good subspaces of free modules over $\Z/p^e\Z$, and extensions of $\Z/p^e\Z$ (similar to $\F_q / \F_p$).

\subsection{Implementing the Abel-Jacobi map}
Say something about implementing the Abel-Jacobi map $C \to J, Q \mapsto Q - \infty_+$. Right now, information about this (the implementation and why it works) can be found in Hyper2RR.gp.

Now that we can do computations with elements in the Jacobian over $\Z/p^2\Z$, it only remains to construct elements in the Jacobian. Explicitly, we want to go from a degree zero divisor to an element in Mascots representation. Since we can add elements in the Jacobian, for this it is enough to compute the Abel-Jacobi embedding
\begin{align*}
j_{\infty_+}: C &\to J \\
              P &\mapsto P-\infty_+.
\end{align*}
We will only need $j_{\infty_+}(P)$ and $j_{\infty_-}(P)$ for affine points $P$; as the calculation of $j_{\infty_-}(P)$ is entirely similar to $j_{\infty_+}(P)$, we only focus on $j_{\infty_+}(P)$. For this, we present the following algorithm:

\begin{algorithm}[H]
\label{alg:abeljacobi}
 \KwData{$C,J$, an affine point $P \in C(R)$ where $R = \Z/p^e\Z)$}
 \KwResult{A space of the form $\Lcal(2D_0 - E)$ where $E-D_0 = P - \infty_+$ as divisors and $E \geq 0$}
 $Z' \leftarrow Z \sqcup \{P\}$\;
 $B = (b_1,\dots,b_{g+3}) \leftarrow$ a basis of $\Lcal(D_0)$\; \label{alg:abeljacobi:basisLD0}
 \eIf{$(f^r)'(0) \not= 0$}{
   $b_{g+4} \leftarrow \frac{X(X^{g+1} + Y)}{Z^{g+2}}$\;
   }{
   $b_{g+4} \leftarrow \frac{X(X^{g+1} + Y + XZ^{g})}{Z^{g+2}}$\;
  }
 $b_{g+4} \leftarrow xF$\;
 $W \leftarrow$ a $(n_Z + 1)\times (g+4)$ matrix with rows being the evaluations of $B\sqcup{b_{g + 4}}$ on a point in $Z'$.\;
 $V \leftarrow \ker(\im W \subset R^{n_Z + 1} \to R)$, the projection on the last coordinate.\;
 %Calculate $\Lcal(D_0 + \infty_+ - P)$\;
 $U \leftarrow \im(R^{g+4} \xrightarrow{\cdot V} R^{n_Z + 1} \to R^{n_Z})$, where the last map is the projection on the first coordinates.\;
 $F \leftarrow \frac{X^{g+1} - Y}{Z^{g+1}}$ evaluated on $\Z$\;
 %Evaluate the special function $F$ (see Hyper2RR.gp) on $Z$\;
 Return $U\cdot F$\;
 \caption{The Abel-Jacobi embedding}
\end{algorithm}

\begin{prop}
\label{prop:abeljacobia}
Algorithm~\ref{alg:abeljacobi} gives correct output.
\end{prop}
Before this proof, we start with a quick lemma.
\begin{lem}
\label{lem:poles2d0i+}
The poles of $b_{g+4}$ are exactly $(g+1)(\infty_+ + \infty_-) + \infty_+$. 
\end{lem}
\begin{proof}
We start by recalling that at the other affine patch, the curve $C$ is given by $w^2 = f^r(v)$ and by the assumption that $f$ is monic of degree $2g+2$ we have $f^r(0) = 1$. The points $\infty_\pm$ correspond to $(v,w) = (0,\pm 1)$ in this patch. Letting $g^r(v)$ be the polynomial $(f^r(v)-1)/v$, we can rewrite the equation for $C$ to $(w-1)(w+1) = vg^r(v)$. As the derivative of $(w-1)(w+1)$ to $w$ doesn't vanish at both of $\infty_\pm$, we see that $v$ is a uniformiser at both these points. That means that $v_{\infty_\pm}(x)$, the order of $x$ at $\infty_\pm$, is equal to $-1$.

Now, if $g^r(0)$ is non-zero, then $w- \pm 1$ is also a uniformiser at $\infty_\pm$ and non-zero at $\infty_\mp$, so \[(w+1)/v^{g+2} = \frac{X(X^{g+1} - Y)}{Z^{g+2}}\] has poles exactly $(g+2)(\infty_+ + \infty_-) - \infty_-$ as we wanted to show.
And if $g^r(0)$ is zero, then $v_{\infty_\pm}(w-\pm1)$ is at least $2$ so $w-\pm 1 + v$ is a uniformiser at $\infty_\pm$ and non-zero at $\infty_\mp$, so \[(w+1+v)/v^{g+2} = \frac{X(X^{g+1} + Y + XZ^g)}{Z^{g+2}}\] again has the right poles.
\end{proof}

\begin{proof}[Proof of Proposition \ref{prop:abeljacobia}]
First note that by Riemann-Roch, the dimension of $\Lcal(D_0)$ is $g + 3$, and we also have by the proof of the previous lemma that $1,x,\dots,x^{g+1},y$ all lie in $\Lcal(D_0)$ and hence form a basis, so we can indeed find $B$ as in line~\ref{alg:abeljacobi:basisLD0}. Note that by Lemma~\ref{lem:poles2d0i+} the element $b_{g+4}$ lies in $\Lcal(D_0 + \infty_+)$ but not in $\Lcal(D_0)$, so as $\deg D_0 \geq 2g-1$, we have by a dimensional argument that $b_1,\dots,b_{g+4}$ is a basis for $\Lcal(D_0 + \infty_+)$.

Evaluating $\Lcal(D_0 + \infty_+)$ on $P$ gives a linear map $\Lcal(D_0 + \infty_+) \to R$, and the kernel is exactly $\Lcal(D_0 + \infty_+ - P)$. Finally, note that the poles of $F$ are, again by the previous lemma, $g(\infty_+ + \infty_-) + \infty_-$. 
\end{proof}

Say something about how with just this map and Mascots code, one can already find the $\overline{\kappa^* f_i} $ and compute an upper bound for $C(\Z)_P$ using brute force.

\subsection{Speeding up the calculations}
Say something about how one express an element in $J(\Z/p^2\Z)_0$ on the basis in something like $O(g)$ hopefully (ignoring the time for adding,multiplying, et cetera in the Jacobian), instead of the bruteforce $O(p^g)$. This is currently done using code from Mascot. Say what the final complexity is.

\subsection{An explicit example}
Treat the example in ExChabauty.gp.

\section{The Poincare torsor}
Define and cite theorems about the Poincare Torsor

\section{Quadratic Chabauty using the Poincare torsor}
Explain how to do Chabauty in the case $r < g + \rho - 1$, where $\rho$ is the N\'eron-Severirank.

\section{Implementations of quadratic Chabauty and an explicit example}
Explain something about implementing quadratic Chabauty.

\newpage
\bibliographystyle{alpha}
\addcontentsline{toc}{section}{References}
\bibliography{ref}

\end{document}

### 2019-12-20 MS.tex
Corrected a few errors

@@
 
-Mention Flyn, Coleman, Balakrishnan et al. and their way of doing quadratic quickly
+Mention Flynn, Coleman, Kim, Balakrishnan et al. and their way of doing quadratic Chabauty
 
@@
 Assume we have a $\Q$-point $b$ in $C$, or equivalently a $\Z$-point.
-Let $J$ be the Jacobian of $C$; we view $C$ as a subscheme of $J$, using the map $Q \mapsto Q - b$ on points.
+Let $J$ be the Jacobian of $C_\Q$; we view $C_\Q$ as a subscheme of $J$, using the map $Q \mapsto Q - b$ on points.
 Let $P \in C(\F_p)$ be a point such that $t := P - b \in J(\F_p)$ lies in the image of $J(\Z)$.
@@
 \begin{defn}
-Let $S$ be a scheme, $T \to U$ a morphism of schemes and $x : T \to S$ an $T$-point. We define $S(U)_x$ as the morphisms from $U$ to $S$ that, after precomposing with $T \to U$, give $x$.
+Let $S$ be a scheme, $T \to U$ a morphism of schemes and $x : T \to S$ a $T$-point. We define $S(U)_x$ as the morphisms from $U$ to $S$ that, after precomposing with $T \to U$, give $x$.
 \end{defn}
@@
 \label{subs:smoothzppoints}
-Let $X/\Z_p$ be a smooth scheme of dimension $d$, and let $x \in X(\F_p)$ be a point.
+Let $X/\Z_p$ be a smooth scheme of relative dimension $d$, and let $x \in X(\F_p)$ be a point.
 Then $X(\Z_p)_x$ is in bijection with $\Z_p^d$.
@@
 % Blow up X at x, and look at the part where p generates the maximal ideal
-Assume, by looking at a neighborhood of $x$, that $X = \Spec A$ is affine and that $p,t_1,\dots,t_d$ generate $O_{X,x}$ with $t_1,\dots,t_d$ regular on $X$.
-By shrinking $X$ even more, we may assume that $t = (t_1,\dots,t_d): X \to \A^d_{\Z_p}$ is smooth and hence \'etale.
-Let $\Tilde{X}_x$ be the blowup of $X$ at $x$.
+Assume, by looking at a neighborhood of $x$, that $X = \Spec A$ is affine and that $p,t_1,\dots,t_d$ generate the maximal ideal of $O_{X,x}$ with $t_1,\dots,t_d$ elements of $O_X(X)$.
+By shrinking $X$ even more, we may assume that $t = (t_1,\dots,t_d): X \to \A^d_{\Z_p}$ is \'etale.
 Now consider the blowup $\Tilde{X}_x \to X$ of $X$ at $x$, and let $\Tilde{X}_x^p$ be the part where $p$ generates the maximal ideal.
@@
 Then the part $\Tilde{X}_x^p$ is the pullback of the corresponding part of $\Tilde{\A}^d_{\Z_p,a}$, i.e.
-$\Spec \Z_p[x_1/p,...,x_d/p]$ with the morphism $\Z_p[x_1,...,x_d] \to \Z_p[x_1/p,...,x_d/p]$ being the inclusion.
-That implies that $\Tilde{X}_x^p$ is $\Spec A[]$
+$\Spec \Z_p[x_1/p,\dots,x_d/p]$ with the morphism $\Z_p[x_1,\dots,x_d] \to \Z_p[x_1/p,\dots,x_d/p]$ being the inclusion.
+That implies that $\Tilde{X}_x^p$ is $\Spec A[t_1/p,\dots,t_d/p]$.
 
@@
 By Subsection \ref{subs:smoothzppoints}, we also know that $C(\Z_p)_P$ is in bijection with $\Z_p$, again with the bijection given by evaluating a parameter and dividing by $p$.
-Apparently the resulting function $\Z_p \to \Z_p^g$ is linear modulo $p$, i.e.
+The resulting function $\Z_p \to \Z_p^g$ is linear and non-constant modulo $p$, i.e.
 there are power series $f_1,...,f_{g-1} \in \Z_p\angle{z_1,...,z_g}$ such that the image of $C(\Z_p)_P$ is exactly given by $V(f_1,...,f_{g-1})$, and all $f_i$ are linear modulo $p$.
@@
  \eIf{$(f^r)'(0) \not= 0$}{
-   $b_{g+4} \leftarrow \frac{X(X^{g+1} + Y)}{Z^{g+2}}$\;
+   $F \leftarrow x^{g+1} + y$\;\label{alg:abeljacobi:defF1}
    }{
-   $b_{g+4} \leftarrow \frac{X(X^{g+1} + Y + XZ^{g})}{Z^{g+2}}$\;
+   $b_{g+4} \leftarrow x^{g+1} + x^g +  y$\;\label{alg:abeljacobi:defF2}
   }
@@
  $W \leftarrow$ a $(n_Z + 1)\times (g+4)$ matrix with rows being the evaluations of $B\sqcup{b_{g + 4}}$ on a point in $Z'$.\;
- $V \leftarrow \ker(\im W \subset R^{n_Z + 1} \to R)$, the projection on the last coordinate.\;
+ $V \leftarrow \ker(\im W \subset R^{n_Z + 1} \to R)$, the projection on the last coordinate.\; \label{alg:abeljacobi:kerp}
  %Calculate $\Lcal(D_0 + \infty_+ - P)$\;
  $U \leftarrow \im(R^{g+4} \xrightarrow{\cdot V} R^{n_Z + 1} \to R^{n_Z})$, where the last map is the projection on the first coordinates.\;
- $F \leftarrow \frac{X^{g+1} - Y}{Z^{g+1}}$ evaluated on $\Z$\;
- %Evaluate the special function $F$ (see Hyper2RR.gp) on $Z$\;
- Return $U\cdot F$\;
+ %$F \leftarrow \frac{X^{g+1} - Y}{Z^{g+1}}$ evaluated on $\Z$\;
+ Evaluate the special function $F$ (see Hyper2RR.gp) on $Z$\;
+ Return $U\cdot \sigma(F)$\;
  \caption{The Abel-Jacobi embedding}
@@
 \begin{prop}
-\label{prop:abeljacobia}
+\label{prop:abeljacobi}
 Algorithm~\ref{alg:abeljacobi} gives correct output.
@@
 \label{lem:poles2d0i+}
-The poles of $b_{g+4}$ are exactly $(g+1)(\infty_+ + \infty_-) + \infty_+$. 
+The poles of $F$, as defined in line~\ref{alg:abeljacobi:defF1} or \ref{alg:abeljacobi:defF2}, are exactly $g(\infty_+ + \infty_-) + \infty_+$. 
 \end{lem}
@@
 
-Now, if $g^r(0)$ is non-zero, then $w- \pm 1$ is also a uniformiser at $\infty_\pm$ and non-zero at $\infty_\mp$, so \[(w+1)/v^{g+2} = \frac{X(X^{g+1} - Y)}{Z^{g+2}}\] has poles exactly $(g+2)(\infty_+ + \infty_-) - \infty_-$ as we wanted to show.
-And if $g^r(0)$ is zero, then $v_{\infty_\pm}(w-\pm1)$ is at least $2$ so $w-\pm 1 + v$ is a uniformiser at $\infty_\pm$ and non-zero at $\infty_\mp$, so \[(w+1+v)/v^{g+2} = \frac{X(X^{g+1} + Y + XZ^g)}{Z^{g+2}}\] again has the right poles.
+Now, if $g^r(0)$ is non-zero, then $w- \pm 1$ is also a uniformiser at $\infty_\pm$ and non-zero at $\infty_\mp$, so \[(w+1)/v^{g+1} = y + x^{g+1}\] has poles exactly $(g+1)(\infty_+ + \infty_-) - \infty_-$ as we wanted to show.
+And if $g^r(0)$ is zero, then $v_{\infty_\pm}(w-\pm1)$ is at least $2$ so $w-\pm 1 + v$ is a uniformiser at $\infty_\pm$ and non-zero at $\infty_\mp$, so \[(w+1+v)/v^{g+1} = y + x^{g+1} + x^{g}\] again has the right poles.
 \end{proof}
@@
 First note that by Riemann-Roch, the dimension of $\Lcal(D_0)$ is $g + 3$, and we also have by the proof of the previous lemma that $1,x,\dots,x^{g+1},y$ all lie in $\Lcal(D_0)$ and hence form a basis, so we can indeed find $B$ as in line~\ref{alg:abeljacobi:basisLD0}.
-Note that by Lemma~\ref{lem:poles2d0i+} the element $b_{g+4}$ lies in $\Lcal(D_0 + \infty_+)$ but not in $\Lcal(D_0)$, so as $\deg D_0 \geq 2g-1$, we have by a dimensional argument that $b_1,\dots,b_{g+4}$ is a basis for $\Lcal(D_0 + \infty_+)$.
+Note that by Lemma~\ref{lem:poles2d0i+} the element $b_{g+4}$ lies in $\Lcal(D_0 + \infty_+)$ but not in $\Lcal(D_0)$, so as $\deg D_0 \geq 2g-1$, we have by a dimensional argument that $b_1,\dots,b_{g+4}$ is a basis for $\Lcal(D_0 + \infty_+)$; that it is in fact a basis is evident as this argument tells us it is a basis when tensored with $\F_p$.
 
-Evaluating $\Lcal(D_0 + \infty_+)$ on $P$ gives a linear map $\Lcal(D_0 + \infty_+) \to R$, and the kernel is exactly $\Lcal(D_0 + \infty_+ - P)$.
-Finally, note that the poles of $F$ are, again by the previous lemma, $g(\infty_+ + \infty_-) + \infty_-$.
+Evaluating $\Lcal(D_0 + \infty_+)$ on $P$ gives a linear map $\Lcal(D_0 + \infty_+) \to R$, and the kernel is exactly $\Lcal(D_0 + \infty_+ - P)$; this is the resulting $V$ in line~\ref{alg:abeljacobi:kerp}.
+Then.
+Finally, note that the poles of $\sigma(F)$ are, again by the previous lemma, $g(\infty_+ + \infty_-) + \infty_+$; write $E$ for the divisor of zeroes of $F$; we see it has degree $2g+1$.
+Then we have the equality \[\Lcal(D_0 + \infty_+-P) \cdot F = \Lcal(2D_0 - E - P).\]
+This last term is in fact in Mascots representation, and trivially $P-\infty_+ = P + E - D_0$, so this represents $P-\infty_+$ in the Jacobian.
 \end{proof}

### 2020-01-15 MS.tex
Updates Abel-Jacobi algorithm

@@
 Hence for $0 \in J(\F_p)$, we know $J(\Z)_0$ is as a group isomorphic to $\Z^r$ with $r$ the Mordell-Weil rank.
-By assumption, we also know $J(\Z)_t$ is in bijection with $J(\Z)_0$.
+By assumption, we also know $J(\Z)_t$ is in bijection with $J(\Z)_0$, with the bijection giving by translating with a lift of $t$.
 By Subsection \ref{subs:smoothzppoints} we know $J(\Z_p)_t$ is in bijection with $\Z_p^{g}$, with the bijection given by evaluating parameters and dividing by $p$.
@@
 \end{thm}
-TODO: give proof
+TODO: give proof. Use formal group scheme by looking to 0.
 
@@
    }{
-   $b_{g+4} \leftarrow x^{g+1} + x^g +  y$\;\label{alg:abeljacobi:defF2}
+   $F \leftarrow x^{g+1} + x^g +  y$\;\label{alg:abeljacobi:defF2}
   }

### 2020-01-15 MS.tex
More about Zp points on smooth scheme and compile script

@@
 
+Say how much is borrowed from the article by Bas and Guido, but with a focus on the linear part, and more explanations.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 % Blow up X at x, and look at the part where p generates the maximal ideal
-Assume, by looking at a neighborhood of $x$, that $X = \Spec A$ is affine and that $p,t_1,\dots,t_d$ generate the maximal ideal of $O_{X,x}$ with $t_1,\dots,t_d$ elements of $O_X(X)$.
-By shrinking $X$ even more, we may assume that $t = (t_1,\dots,t_d): X \to \A^d_{\Z_p}$ is \'etale.
+Assume, by looking at a neighborhood of $x$, that $X = \Spec A$ is affine and that $p,t_1,\dots,t_d$ generate the maximal ideal of $O_{X,x}$ with $t_1,\dots,t_d$ elements of $O_X(X) = A$, also called \textit{parameters} at $x$.
+By shrinking $X$ even more, we may assume as $X$ is smooth that $t = (t_1,\dots,t_d): X \to \A^d_{\Z_p}$ is \'etale.
 Now consider the blowup $\Tilde{X}_x \to X$ of $X$ at $x$, and let $\Tilde{X}_x^p$ be the part where $p$ generates the maximal ideal.
+Equivalently, that is the part where $t_1,\dots,t_d$ are multiples of $p$, so informally it consists of the points that reduce to $x$ modulo $p$.
+
 As $t$ is \'etale, the ideal of $X$ defining $x$ is the pullback along $t$ of the ideal of $\A^d_{\Z_p}$ defining the origin $a$ over $\F_p$.
@@
 Then the part $\Tilde{X}_x^p$ is the pullback of the corresponding part of $\Tilde{\A}^d_{\Z_p,a}$, i.e.
-$\Spec \Z_p[x_1/p,\dots,x_d/p]$ with the morphism $\Z_p[x_1,\dots,x_d] \to \Z_p[x_1/p,\dots,x_d/p]$ being the inclusion.
-That implies that $\Tilde{X}_x^p$ is $\Spec A[t_1/p,\dots,t_d/p]$.
+$\Spec \Z_p[\Tilde{x_1},\dots,\Tilde{x_d/p}] = \Spec \Z_p[x_1/p,\dots,x_d/p]$ with the morphism $\Z_p[x_1,\dots,x_d] \to \Z_p[\Tilde{x_1},\dots,\tilde{x_p}]$ given by $x_i \mapsto p\Tilde{x_i}$.
+That implies that $\Tilde{X}_x^p$ is $\Spec A[t_1/p,\dots,t_d/p]$, with the map $\Tilde{X}_x^p \to X$ given by the inclusion $A \to \Spec A[t_1/p,\dots,t_d/p]$ (remember that the $t_i$ are elements of $O_X(X) = A$).
+If furthermore $f$ is locally of finite type, then by (IV,17.6.3) of \cite{ega} we have an isomorphism between the $p$-adic completion $O(\Tilde{X}_x^p)$ and the completion $\Z_p\angle{\Tilde{x_1},\dots, \Tilde{x_d}}$ of $\Z_p[\Tilde{x_1},...,\Tilde{x_d}]$, with the latter completion being the ring of convergent power series, i.e.
+\[
+\Z_p\angle{\Tilde{x_1},\dots, \Tilde{x_d}} = \left\{f \in \Z_p[[\Tilde{x_1},\dots,\Tilde{x_d}]] \mid \forall n \geq 0, f + (p^n) \in \Z/p^n\Z[\Tilde{x_1},\dots,\tilde{X_d}] + (p^n) \right\}.
+\]
 
@@
 That means all these submodules will have good reduction, i.e.
-the rank remains the same when passing to $\F_p$.
+the rank remains the same when tensoring with $\F_p$.
 If the maps between such modules also have good reduction, then all kernels, images, et cetera will also have these properties, and can be calculated by Hensel lifting the kernels, images, et cetera of these maps modulo $p$.
 
-Explain Howell modules, good subspaces of free modules over $\Z/p^e\Z$, and extensions of $\Z/p^e\Z$ (similar to $\F_q / \F_p$).
+The final trick we need is extensions of $\Z/p^e\Z$.
+As said before, we need $n_Z$ affine points that are distinct modulo $p$, so we passed from $\F_p$ to an extension of $\F_q$.
+The corresponding notion of an extension of $\Z/p^e\Z$ is given by taking an irreducible polynomial $\overline{T} \in \F_p[t]$ with $\F_q \cong \F_p[t]/\overline{T}$, arbitrarily lifting $\overline{T}$ to a polynomial $T \in \Z/p^e\Z$, and looking at $R = \Z/p^e\Z[t]/T$.
+Again, we will only be looking at free submodules of $R^n$, so we can again do normal linear algebra over $R \tensor \F_p = \F_q$, and using Hensel to lift.
 
@@
 \addcontentsline{toc}{section}{References}
-\bibliography{ref}
+\bibliography{ref.bib}
 

### 2020-01-15 compile.sh

@@ -1,0 +1,4 @@
+pdflatex MS.tex
+bibtex MS.aux
+pdflatex MS.tex
+pdflatex MS.tex

### 2020-01-17 MS.tex
Cleaned up section smooth points

@@
 That implies that $\Tilde{X}_x^p$ is $\Spec A[t_1/p,\dots,t_d/p]$, with the map $\Tilde{X}_x^p \to X$ given by the inclusion $A \to \Spec A[t_1/p,\dots,t_d/p]$ (remember that the $t_i$ are elements of $O_X(X) = A$).
-If furthermore $f$ is locally of finite type, then by (IV,17.6.3) of \cite{ega} we have an isomorphism between the $p$-adic completion $O(\Tilde{X}_x^p)$ and the completion $\Z_p\angle{\Tilde{x_1},\dots, \Tilde{x_d}}$ of $\Z_p[\Tilde{x_1},...,\Tilde{x_d}]$, with the latter completion being the ring of convergent power series, i.e.
+If furthermore $t$ is locally of finite type, then by (IV,17.6.3) of \cite{ega} we have an isomorphism between the $p$-adic completion $O(\Tilde{X}_x^p)$ and the completion $\Z_p\angle{\Tilde{x_1},\dots, \Tilde{x_d}}$ of $\Z_p[\Tilde{x_1},...,\Tilde{x_d}]$, with the latter completion being the ring of convergent power series, i.e.
 \[
@@
 \]
+
+Note that this construction is functorial, as in the following lemma:
+\begin{lem}
+Given two smooth schemes $X,Y$ over $\Z_p$, two $\F_p$-point $x\in X(\F_p), y\in Y(\F_p)$, there is a natural bijection between maps $f: Y \to X$ satisfying $f(y) = x$, and morphisms $\Tilde{Y}_y^p \to \Tilde{X}_Y^p$.
+\end{lem}
+\begin{proof}
+
+\end{proof}
+
+Applying this lemma with $Y = \Spec \Z_p$ and $y$ the origin over $\F_p$, we get a natural bijection between $X(\Z_p)_x$ and $\Hom(O(\Tilde{x}_Y^p),\Z_p)$.
+As $\Z_p$ is $p$-adically complete, the map $t$ gives an isomorphism between $\Hom(O(\Tilde{x}_Y^p),\Z_p)$ and $\Hom(\Z_p\angle{\Tilde{x_1},\dots, \Tilde{x_d}},\Z_p) \cong \Z_p^d$.
 

### 2020-01-21 MS.tex
Added Cartier divisors on curve

--- 2020-01-15 MS.tex
@@
 Then the part $\Tilde{X}_x^p$ is the pullback of the corresponding part of $\Tilde{\A}^d_{\Z_p,a}$, i.e.
-$\Spec \Z_p[\Tilde{x_1},\dots,\Tilde{x_d/p}] = \Spec \Z_p[x_1/p,\dots,x_d/p]$ with the morphism $\Z_p[x_1,\dots,x_d] \to \Z_p[\Tilde{x_1},\dots,\tilde{x_p}]$ given by $x_i \mapsto p\Tilde{x_i}$.
+$\Spec \Z_p[\Tilde{x_1},\dots,\Tilde{x_d}] = \Spec \Z_p[x_1/p,\dots,x_d/p]$ with the morphism $\Z_p[x_1,\dots,x_d] \to \Z_p[\Tilde{x_1},\dots,\tilde{x_p}]$ given by $x_i \mapsto p\Tilde{x_i}$.
 That implies that $\Tilde{X}_x^p$ is $\Spec A[t_1/p,\dots,t_d/p]$, with the map $\Tilde{X}_x^p \to X$ given by the inclusion $A \to \Spec A[t_1/p,\dots,t_d/p]$ (remember that the $t_i$ are elements of $O_X(X) = A$).
-If furthermore $f$ is locally of finite type, then by (IV,17.6.3) of \cite{ega} we have an isomorphism between the $p$-adic completion $O(\Tilde{X}_x^p)$ and the completion $\Z_p\angle{\Tilde{x_1},\dots, \Tilde{x_d}}$ of $\Z_p[\Tilde{x_1},...,\Tilde{x_d}]$, with the latter completion being the ring of convergent power series, i.e.
+
+This now enables us to characterise explicitly the $\Z_p$-points above $x$, as in the following two lemmas.
+
+\begin{lem}
+With $X$ as above, there is a natural bijection $X(\Z_p)_x \to \Tilde{X}_x^p(\Z_p)$,
+\end{lem}
+\begin{proof}
+Note that by (I,2.4.4) of \cite{ega}, a $\Z_p$ point of a scheme $S$ is just an $\F_p$-point $s$ together with a local morphism $\O_{S,s} \to \Z_p$.
+In our case, we find that $X(\Z_p)_x$ is naturally in bijection with $\Hom_{\text{local}}(A_x,\Z_p)$.
+As the maximal ideal of $A_x$ is generated by $p,t_1,\dots,t_d$, the locality property just means that the images of $t_1,\dots,t_d$ are divisible by $p$, i.e.
+exactly those morphisms that extend to a morphism $A[t_1/p,\dots,t_d/p] \to \Z_p$, i.e.
+a $\Z_p$-point of $\Tilde{X}_x^p$.
+Hence we find the natural bijection.
+\end{proof}
+
+\begin{lem}
+With $X$ as above and furthermore $t$ locally of finite type, evaluating $t$ at $X(\Z_p)_x$ gives a bijection to $(p\Z_p)^d$.
+\end{lem}
+\begin{proof}
+As $t$ is locally of finite type, by (IV,17.6.3) of \cite{ega} we have an isomorphism between the $p$-adic completion $O(\Tilde{X}_x^p)^{\wedge p}$ and the completion $\Z_p\angle{\Tilde{x_1},\dots, \Tilde{x_d}}$ of $\Z_p[\Tilde{x_1},...,\Tilde{x_d}]$, with the latter completion being the ring of convergent power series, i.e.
 \[
@@
 \]
+By the universal property of completions, as $t$ induces the isomorphism between completion, $t$ also induces a bijection $$\Hom(O(X(\Z_p)_x), \Z_p) \to \Hom(O(X(\Z_p)_x)^{\wedge p}, \Z_p) = \Hom(\Z_p\angle{\Tilde{x_1},\dots,\Tilde{x_d}},\Z_p) = \Z_p^d$$.
+Following all the bijections, we indeed get the bijection we wanted.
+\end{proof}
 
-Conclude that $\Tilde{X}_x^p(Z_p)$ is in bijection with $X(Z_p)_x$
+Note that this construction is functorial, as in the following lemma:
+\begin{lem}
+Given two smooth schemes $X,Y$ over $\Z_p$, two $\F_p$-point $x\in X(\F_p), y\in Y(\F_p)$, there is a natural bijection between maps $f: Y \to X$ satisfying $f(y) = x$, and morphisms $\Tilde{Y}_y^p \to \Tilde{X}_Y^p$.
+\end{lem}
+\begin{proof}
+TODO
+Is this even necessary?
+\end{proof}
 
-Talk about the coordinate ring and its p-adic completion
-
-Say something about functoriality
+Finally, we look at the specific case of $X$ being of relative dimension $1$ over $\Z_p$.
+It then turns out that there is additionally a free faithful $\F_p$-action on $X(\Z/p^2\Z)_0$.
+We can parametrise $X(\Z/p^2\Z)_0$ by $t = t_1 : X(\Z/p^2\Z)_0 \to p\Z/p^2\Z$; write $P_{\lambda}$ for the point with $t$-value $\lambda p$.
+Then as Cartier divisor, the point $P_{\lambda}$ is defined by $t - \mu p \in O(X_{\Z/p^2\Z})_x$, so $P_{\lambda} + P_{\mu}$ is defined by $(t-\lambda p)(t-\mu p) = t^2 - (\lambda + \mu)tp$, which defines the same Cartier divisor as $P_{\lambda'} + P_{\mu'}$ if and only if $\lambda + \mu = \lambda' + \mu'$.
+So as a Cartier divisor, $P(\lambda) + P_{\mu}$ is in fact equal to $P_{\lambda'} + P_{\mu'}$.
 

### 2020-01-21 MS.tex
[Introduction] mentioned Dogra

@@
 
-Mention Flynn, Coleman, Kim, Balakrishnan et al. and their way of doing quadratic Chabauty
+Mention Flynn, Coleman, Kim, Balakrishnan, Dogra, and other mentionable people. and their way of doing (quadratic) Chabauty
 
-Say something about linear Chabauty geometric style
+Say something about linear Chabauty geometric style.
 

### 2020-01-27 MS.tex
Group schemes to formal groups

@@
 \DeclareMathOperator{\Spec}{Spec}
+\DeclareMathOperator{\Spf}{Spf}
 \DeclareMathOperator{\sep}{sep}
@@
 \begin{lem}
-With $X$ as above and furthermore $t$ locally of finite type, evaluating $t$ at $X(\Z_p)_x$ gives a bijection to $(p\Z_p)^d$.
+With $X$ as above, evaluating $t$ at $X(\Z_p)_x$ gives a bijection to $(p\Z_p)^d$.
 \end{lem}
@@
 \label{thm:kappanice}
-There are uniquely determined $\kappa_1,...,\kappa_g \in \Z_p\angle{z_1,...,z_r}$ such that for all $x \in \Z^r$ we have $\kappa(x) = (\kappa_1(x),...,\kappa_g(x))$ and the image $\overline{\kappa_i}$ of $\kappa_i$ in $\F_p[z_1,...,z_r]$ has degree at most $1$.
+There are uniquely determined $\kappa_1,\dots,\kappa_g \in \Z_p\angle{z_1,...,z_r}$ such that for all $x \in \Z^r$ we have $\kappa(x) = (\kappa_1(x),\dots,\kappa_g(x))$ and the image $\overline{\kappa_i}$ of $\kappa_i$ in $\F_p[z_1,...,z_r]$ has degree at most $1$.
 \end{thm}
-TODO: give proof. Use formal group scheme by looking to 0.
+
+We will prove this using results about formal group as defined in \citep{honda70}.
+To be able to use this theory, we first give some results about going from a group scheme over $\Z_p$ to a formal group.
+
+\subsubsection{From group schemes to formal groups}
+We first recall the definition of a formal group.
+\begin{defn}
+\label{defn:formalgroup}
+Let $R$ be a ring, and $n$ be a non-negative integer.
+Let $x,y,z$ be vectors of $n$ variables.
+An $n$-dimensional formal group is an element $F = (F_1,\dots,F_n) \in R[[x,y]]^n$ satisfying $F \equiv x + y \mod (x,y)^2$ and $F(F(x,y),z) = F(x,F(y,z))$.
+If furthermore $F(x,y) = F(y,x)$, this formal group is said to be commutative.
+\end{defn}
+\begin{exmp}
+\label{exmp:gmformalgroup}
+Take $n=1$ and $F(x,y) = x + y + xy = (1+x)(1+y)-1$, also known as the multiplicative formal group. This satisfies associativity as $F(F(x,y),z) = (1+x)(1+y)(1+z)-1 = F(x,F(y,z))$.
+\end{exmp}
+%For such a formal group, by Hensels lemma it turns out that there is a unique $i_F \in R[[x]]^n$ with $F(x,i_F(x)) = F(i_F(x),x) = 0$ and then by the associativity we find $F(x,0) = F(0,x)$.
+Such a formal group gives rise to a coproduct $\mu: R[[x]] \to R[[x,y]]$, by sending $x_j to F_j(x,y)$ and extending continously for the $(x)$-adic topology; this works exactly because the constant term of the $F_j$ are all $0$.
+This coproduct, together with the antipode given by extending $x_j \mapsto i_{F,j}$ continuously and the counit $R[[x]] \to R$ sending $x$ to 0, turns $R[[x]]$ into a group object in the category consisting of $(A,I)$ where $A$ is an $R$-algebra, $I$ is an ideal of $A$ and $A$ is $I$-adically complete as in the following way.
+
+Given a smooth scheme $G$ over $\Z_p$ of relative dimension $d$, we can look at the completion along the zero section $\Hat{O}_{G,e}$.
+By smoothness, this is isomorphic as topological $\Z_p$-algebras to the ring of power series $\Z_p[[x_1,\dots,x_d]]$.
+This completion naturally gives rise to a formal scheme denoted $\Spf \Hat{O}_{G,e}$; in a categorical notion, this is a functor on finite $\Z_p$-algebras sending $A$ to $\Hom_{\text{cont}}(\Hat{O}_{G,e},A)$, but we can also think of it as a locally ringed space with $\Spec \Z_p$ as topological space, and sheaf of rings $\Hat{O}_{G,e}$.
+
+If furthermore $G$ is a group scheme over $\Z_p$, then this formal scheme promotes to a formal group scheme, i.e.
+for every finite $\Z_p$-algebra $A$ the set $\Hom_{\text{cont}}(\Hat{O}_{G,e},A)$ gets a group structure, functorially in $A$.
+By functoriality, this is the same [TODO: why exactly?] as an continuous coproduct $\mu: \Hat{O}_{G,e} \to \left(\Hat{O}_{G,e}\right)^{\tensor 2}$.
+After choosing an isomorphism between $\Hat{O}_{G,e}$ and $\Z_p[[x_1,\dots,x_d]]$, let $F_j \in \Z_p[x,y]$ denote $\mu(x_i)$.
+Then it is clear that $F = (F_1,\dots,F_d)$ is a $d$-dimensional formal group scheme, and commutative if $G$ was commutative.
+\begin{exmp}
+\label{exmp:gmtoformal} %TODO: nicely LaTeX Example bla, continued
+Take $G = \G_m$ over $\Z_p$, i.e.
+$\Z_p[u,u^{-1}]$.
+Then the zero section $e$ is the map sending $u$ to $1$, and we can identify the completion $\Hat{O}_{G,e}$ with the power series ring $\Z_p[[u-1]] \cong \Z_p[[x]]$, sending $u-1$ to $x$.
+The group structure on $G$ then gives rise to the coproduct $\Z_p[[u-1]] \to \Z_p[[u-1,v-1]], u \mapsto uv$ so the coproduct on $\Z_p[[x]]$ sends $x$ to $uv-1 = (x+1)(y+1) -1 = x + y + xy$.
+Hence the formal group corresponding to this group scheme is exactly the multiplicative formal group from Example~\ref{exmp:gmformalgroup}.
+\end{exmp}
 

### 2020-01-27 MS.tex
Added TODO for formal groups

@@
 \newcommand{\Z}{\mathbb{Z}}
+\renewcommand{\G}{\mathbb{G}}
 \renewcommand{\C}{\mathbb{C}}
@@
 Given a smooth scheme $G$ over $\Z_p$ of relative dimension $d$, we can look at the completion along the zero section $\Hat{O}_{G,e}$.
-By smoothness, this is isomorphic as topological $\Z_p$-algebras to the ring of power series $\Z_p[[x_1,\dots,x_d]]$.
+By smoothness, after picking parameters, this is isomorphic as topological $\Z_p$-algebras to the ring of power series $\Z_p[[x_1,\dots,x_d]]$.
 This completion naturally gives rise to a formal scheme denoted $\Spf \Hat{O}_{G,e}$; in a categorical notion, this is a functor on finite $\Z_p$-algebras sending $A$ to $\Hom_{\text{cont}}(\Hat{O}_{G,e},A)$, but we can also think of it as a locally ringed space with $\Spec \Z_p$ as topological space, and sheaf of rings $\Hat{O}_{G,e}$.
@@
 \end{exmp}
+
+TODO: explain that the formal group gives the group law on $J(\Z_p)_0$. Explain the logarithm. Prove Theorem~\ref{thm:kappanice}.
 

### 2020-01-28 MS.tex
Added start using Honda

@@
 
-TODO: explain that the formal group gives the group law on $J(\Z_p)_0$. Explain the logarithm. Prove Theorem~\ref{thm:kappanice}.
+This formal group tells us exactly how multiplication works on $G(\Z/p^e\Z)_0$; if we let $t = (t_1,\dots,t_d)$ denote the formal parameters giving the isomorphism $\Hat{O}_{G,e} \to \Z_p[[x_1,\dots,x_d]]$, and we represent a point $P$ in $G(\Z/p^e\Z)_0$ by their parameter values $t(P) \in p\Z/p^e\Z$, then the multiplication $p\Z/p^e\Z \times p\Z/p^e\Z \to p\Z/p^e\Z$ is exactly $F$.
+By taking limits, $F$ also gives the multiplication on $G(\Z_p)_0$.
+
+Now we will look at the theory of formal groups, and how that will help us.  over a $\Q$-algebra, Theorem~1 of \citep{honda70} gives the existence of
 

### 2020-01-29 MS.tex
Added log/exp

@@
 \end{exmp}
+\begin{exmp}
+\label{exmp:ganformalgroup}
+For any $n$, we can take $F(x,y) = x+ y$, also known as the $n$-dimensional additive formal group.
+\end{exmp}
 %For such a formal group, by Hensels lemma it turns out that there is a unique $i_F \in R[[x]]^n$ with $F(x,i_F(x)) = F(i_F(x),x) = 0$ and then by the associativity we find $F(x,0) = F(0,x)$.
@@
 After choosing an isomorphism between $\Hat{O}_{G,e}$ and $\Z_p[[x_1,\dots,x_d]]$, let $F_j \in \Z_p[x,y]$ denote $\mu(x_i)$.
-Then it is clear that $F = (F_1,\dots,F_d)$ is a $d$-dimensional formal group scheme, and commutative if $G$ was commutative.
+Then it is clear that $F_G = (F_1,\dots,F_d)$ is a $d$-dimensional formal group scheme, and commutative if $G$ was commutative.
 \begin{exmp}
@@
 The group structure on $G$ then gives rise to the coproduct $\Z_p[[u-1]] \to \Z_p[[u-1,v-1]], u \mapsto uv$ so the coproduct on $\Z_p[[x]]$ sends $x$ to $uv-1 = (x+1)(y+1) -1 = x + y + xy$.
-Hence the formal group corresponding to this group scheme is exactly the multiplicative formal group from Example~\ref{exmp:gmformalgroup}.
+Hence the formal group $F_{\G_m}$ corresponding to this group scheme is exactly the multiplicative formal group from Example~\ref{exmp:gmformalgroup}.
 \end{exmp}
@@
 
-Now we will look at the theory of formal groups, and how that will help us.  over a $\Q$-algebra, Theorem~1 of \citep{honda70} gives the existence of
+Now we will look at the theory of formal groups, and how that will help us.
+For a $n$-dimensional formal group $F$ over a ring $R$, Proposition~1.1 of \citep{honda70} gives us a canonical $R$-basis $\omega_1,\dots,\omega_n$ of the right invariant differentials; these are elements of $\bigoplus_{j=1}^n R[[x]] \d x_j$.
+If the formal group is furthermore commutative, then by Proposition~1.3 of \citep{honda70} these are closed, i.e.
+$d\omega_j = 0$.
+A $1$-form $d\omega = \sum_{i=1}^n f_i dx_i$ being closed means exactly that $\frac{\partial f_i}{\partial x_j} = \frac{\partial f_j}{\partial x_i}$ for all $i,j$, and then, if $R$ has no torsion, we can formally integrate $\omega$, i.e.
+write it as $df$ where $f \in (\Q\tensor R)[[x]]$.
+We make this unique by demanding that $f(0) = 0$.
+Writing this $f$ as $\sum_{I \in \N^n} a_I x^I$ with $I$ denoting a multi index and $a_I \in \Q\tensor R$, we see that $a_I$, although itself not necessarily lying in $R$, is close: writing $I = (I_1,\dots,I_n)$ we see that for all $j$ we must have $I_j a_I \in R$ as $f_j = \frac{\partial f}{\partial x_j} \in R[[x]]$.
+
+In particular, we write $\log_i$ for the unique element of $(\Q\tensor R)[[x]]$ such that $d\log_i = \omega_i$.
+Together, these $\log_i$ give an element $\log \in R[[x]]^n$, and by Theorem~1 of \citep{honda70}, this logarithm satisfies $\log(x) = x \mod (x)^2$, and $\log(F(x,y)) = \log(x)+\log(y)$.
+By the first result, $\log$ has an inverse which we will call $\exp$, also given by powerseries in $(\Q\tensor R)[[x]])$, and also satisfying $\exp(x) = x \mod (x)^2$.
+\begin{exmp} %TODO: nicely LaTeX Example bla, continued
+Taking $F$ the multiplicative group as in Example~\ref{exmp:gmformalgroup}, Proposition~1.1 of \citep{honda70} gives us $\omega = \frac{1}{x+1}dx$; as a power series this is $\sum_{j \geq 0} (-x)^j$.
+The formal anti-derivative of this is $\log = \sum_{j \geq 1} \frac{-(-x)^j}{j}$, and Theorem $1$ will tell us what we already know in the context of analysis $\log(x + y + xy) = \log(x)+\log(y)$.
+Then analysis will also explicitly tell us
+\end{exmp}
 

### 2020-01-30 MS.tex
Added skeleton log map lemma

@@
 \usepackage{float}
+\usepackage{mathtools}
 
@@
 \renewcommand{\angle}[1]{\hspace{-2pt}\left\langle #1 \right\rangle}
+\newcommand*\diff{\mathop{}\!\mathrm{d}}
 \newcommand{\rad}{\text{rad}}
@@
 \begin{lem}
+\ref{lem:smoothpointfunc}
 Given two smooth schemes $X,Y$ over $\Z_p$, two $\F_p$-point $x\in X(\F_p), y\in Y(\F_p)$, there is a natural bijection between maps $f: Y \to X$ satisfying $f(y) = x$, and morphisms $\Tilde{Y}_y^p \to \Tilde{X}_Y^p$.
@@
 \end{exmp}
+[TODO: add lemma about composites of power series]
 %For such a formal group, by Hensels lemma it turns out that there is a unique $i_F \in R[[x]]^n$ with $F(x,i_F(x)) = F(i_F(x),x) = 0$ and then by the associativity we find $F(x,0) = F(0,x)$.
@@
 Now we will look at the theory of formal groups, and how that will help us.
-For a $n$-dimensional formal group $F$ over a ring $R$, Proposition~1.1 of \citep{honda70} gives us a canonical $R$-basis $\omega_1,\dots,\omega_n$ of the right invariant differentials; these are elements of $\bigoplus_{j=1}^n R[[x]] \d x_j$.
+For a $n$-dimensional formal group $F$ over a ring $R$, Proposition~1.1 of \citep{honda70} gives us a canonical $R$-basis $\omega_1,\dots,\omega_n$ of the right invariant differentials; these are elements of $\bigoplus_{j=1}^n R[[x]] \diff x_j$.
 If the formal group is furthermore commutative, then by Proposition~1.3 of \citep{honda70} these are closed, i.e.
 $d\omega_j = 0$.
-A $1$-form $d\omega = \sum_{i=1}^n f_i dx_i$ being closed means exactly that $\frac{\partial f_i}{\partial x_j} = \frac{\partial f_j}{\partial x_i}$ for all $i,j$, and then, if $R$ has no torsion, we can formally integrate $\omega$, i.e.
+A $1$-form $d\omega = \sum_{i=1}^n f_i \diff x_i$ being closed means exactly that $\frac{\partial f_i}{\partial x_j} = \frac{\partial f_j}{\partial x_i}$ for all $i,j$, and then, if $R$ has no torsion, we can formally integrate $\omega$, i.e.
 write it as $df$ where $f \in (\Q\tensor R)[[x]]$.
@@
 The formal anti-derivative of this is $\log = \sum_{j \geq 1} \frac{-(-x)^j}{j}$, and Theorem $1$ will tell us what we already know in the context of analysis $\log(x + y + xy) = \log(x)+\log(y)$.
-Then analysis will also explicitly tell us
+Then analysis will also explicitly tell us what $\exp$ looks like: namely, $\exp(x) = \sum_{j \geq 1} \frac{x^j}{j!}$.
 \end{exmp}
+
+Now we will see how we can use this formal logarithm in our case of the formal group $F_G$ stemming from a $d$-dimensional smooth group scheme $G/\Z_p$.
+Recall that we have a bijection $G(\Z_p)_0 \to p\Z_p^d \to \Z_p^d$ given by evaluating at parameters $t = (t_1,\dots,t_d)$ and then dividing by $p$; furthermore, recall that the group structure on $G(\Z_p)_0$ is the same as the group structure defined by $F_G$ on $p\Z_p^d$.
+Let $\log \in \Z_p[[x]]^d$ denote the logarithm corresponding to $F_G$, and let $\log_p$ denote the power series $\log(px)/p = (\log_1(px)/p,\dots,\log_d(px)/p)$.
+We then have the following little lemma to bridge the gap between power series and maps.
+\begin{lem}
+With notation as above, we have the following statements about $\log_p$:
+\begin{enumerate}
+	\item $\log_p$ lies in $\Z_p\angle{x_1,\dots,x_d}^d$, the ring of convergent power series, and hence defines a map $\log_p: \Z_p^d \to \Z_p^d$.
+	\item Letting $\oplus$ denote the group structure on $\Z_p^d$ coming from the bijection $G(\Z_p)_0 \to p\Z_p^d \to \Z_p^d$, the map $\log_p$ is a group morphism from $(\Z_p^d,\oplus)$ to $(\Z_p^d,+)$.
+	\item If $p > 2$, the map $\log_{p,i}$ reduces to $x_i$ modulo $p$ and hence $\log_p$ has an inverse $\exp_p$, which is also an element of $\Z_p\angle{x_1,\dots,x_d}$.
+Then this $\exp_p$ is a two-sided inverse of $\log_p$, and hence $\log_p: \Z_p^d \to \Z_p^d$ is a bijection.
+\end{enumerate} 
+\end{lem}
+\begin{proof}
+Write $\log_{i} = \sum_{I} a_{i,I} x^I$ and $log_{p,i} = \sum_I a_{i,I} p^{|I|-1} x^I$ where $I$ ranges over the multi indices.
+Recall that $a_{i,0} = 0$.
+Also, recall that although a priori the coefficients $a_I$ lie in $\Q_p$, we have $I_j a_{i,I} \in \Z_p$ for all $I$ and $i,j$.
+For purposes of easy estimation, this also means $|I|a_{i,I} \in \Z_p$.
+As we have, with no constraint on $p$, for all $n\geq $ that $c_n\coloneqq p^{n-1}/n$ lies in $\Z_p$ and converges to $0$, this means that \[ \log_{p,i} = \sum_I a_{i,I} p^{|I|-1} x^I = \sum_I |I|a_{i,I} c_{|I|} x^I\] is indeed an element of $\Z_p\angle{x_1,\dots,x_d}^n$, and hence defines a map $\Z_p^d \to \Z_p$.
+Hence all the $\log_{p,i}$ together give a map $\Z_p^d \to \Z_p^d$
+
+[TODO: explain why group morphism]
+
+To study $\log_p$ modulo $p$, we note that if $n\geq 3$, then $p$ actually divides $c_n$, and for $p > 2$ we even have $p|c_2$.
+As $\log_{p,i} = x_i \mod (x)^2$, this means that for $p > 2$ we have \[\log_{p,i} \equiv \sum_{|I| = 1} |I|a_{i,I}c_|I| x^I \equiv x_i \bmod p.\]
+[TODO: explain how the lemma gives $\exp_p \in \Z_p[[x]]^d$, and how the construction hopefully shows it is indeed a convergent power series]
+\end{proof}
+
+[TODO: proof of Theorem~\ref{thm:kappanice}, should be easy now].
 
@@
 \end{cor}
-TODO: give proof
+TODO: give proof. This is easy now.
 
@@
 Another way to think of this, is as $C(\Z/p^2\Z)_P$ being an affine line inside $J(\Z/p^2\Z)_t$.
-TODO: give proof
+TODO: give proof.
+This uses the functoriality of smooth $\Z_p$-points reducing to a point.
+That $C(\Z/p^2\Z)_P$ is an affine line inside $J(\Z/p^2\Z)_t$ can also be seen more easily, using Lemma~\ref{lem:smoothpointsfunc}.
 % Say something about the f_i defining C(Z_p) in J(Z_p)

### 2020-02-05 MS.tex
Finished first draft JZ0 -> JZp0

@@
 \newcommand{\x}{x}
+\newcommand{\m}{\mathfrak{m}}
 \newcommand{\tensor}{\otimes}
@@
 \DeclareMathOperator{\Ann}{Ann}
+\DeclareMathOperator{\GL}{GL}
 \let\S\undefined
@@
 To be able to use this theory, we first give some results about going from a group scheme over $\Z_p$ to a formal group.
+[TODO: introduce the "subscript zero" notation for power series with no constant term; $R[[x]]_0 = \{f: f \equiv 0 \mod x\}$].
+First we introduce some notation that will be used in this section.
+Let $R$ be a commutative ring, and $x = (x_1,\dots,x_n)$ and sometimes $y,z$ are vectors of variables.
+Then $R[[x]]$ denotes as usual the powerseries in the $x_i$, and $R[[x]]_0$ denotes those power series with constant term $0$.
+With $x = (x_1,\dots,x_n)$ and $y = (y,_1,\dots,y_m$), let $f \in R[[x]]^m$ and assume $f(0) = 0$.
+Then for $g \in R[[y]]^k$ for some $k\in\Z_{\geq 0}$, we can compose $g$ and $f$ to get $g\circ f := (g_1(f(x)),\dots,g_k(f(x)))\in R[[x]]]^k$.
+This definition makes sense because $f^i$ converges to $0$, so for any $a \in R^{\Z_{\geq 0}} $ the sum $\sum_i a_i f^i$ always converges.
 
 \subsubsection{From group schemes to formal groups}
-We first recall the definition of a formal group.
+We first recall the definition of a formal group. For this entire section, $R$ is a ring, and $x,y,z$ are vectors of variables.
 \begin{defn}
 \label{defn:formalgroup}
-Let $R$ be a ring, and $n$ be a non-negative integer.
+Let $n$ be a non-negative integer.
 Let $x,y,z$ be vectors of $n$ variables.
-An $n$-dimensional formal group is an element $F = (F_1,\dots,F_n) \in R[[x,y]]^n$ satisfying $F \equiv x + y \mod (x,y)^2$ and $F(F(x,y),z) = F(x,F(y,z))$.
+An $n$-dimensional formal group is an element $F = (F_1,\dots,F_n) \in R[[x,y]]_0^n$ satisfying $F \equiv x + y \mod (x,y)^2$ and $F(F(x,y),z) = F(x,F(y,z))$.
 If furthermore $F(x,y) = F(y,x)$, this formal group is said to be commutative.
@@
 \end{exmp}
-[TODO: add lemma about composites of power series]
-%For such a formal group, by Hensels lemma it turns out that there is a unique $i_F \in R[[x]]^n$ with $F(x,i_F(x)) = F(i_F(x),x) = 0$ and then by the associativity we find $F(x,0) = F(0,x)$.
-Such a formal group gives rise to a coproduct $\mu: R[[x]] \to R[[x,y]]$, by sending $x_j to F_j(x,y)$ and extending continously for the $(x)$-adic topology; this works exactly because the constant term of the $F_j$ are all $0$.
-This coproduct, together with the antipode given by extending $x_j \mapsto i_{F,j}$ continuously and the counit $R[[x]] \to R$ sending $x$ to 0, turns $R[[x]]$ into a group object in the category consisting of $(A,I)$ where $A$ is an $R$-algebra, $I$ is an ideal of $A$ and $A$ is $I$-adically complete as in the following way.
+[TODO: add text explaining the following lemma]
+Note there is no mention of an inverse, but the following lemma, a formal version of the implicit function theorem, tells us that the inverse follows automatically from the definitions.
+\begin{lem}
+\label{lem:implicitfunction}
+Let $x,y$ have length $n$. Let $F \in R[[x,y]]_0^n$ such that $F \equiv Ax + By \bmod (x,y)^2$ with $B \in \GL_n(R)$. Then there's a unique $\iota \in R[[x]]_0^n$ such that $F(x,\iota(x)) = 0$. 
+\end{lem}
+\begin{proof}
+If $F$ is a polynomial, this is a special case of a multivariate version of Hensel's lemma, as in Corrolaire~2 of \cite[III,4.5]{BourbakiCA}, over $R[[x]]$ with maximal ideal $\m = (x)$, as the derivative matrix of $F(x,\iota)$ with respect to $\iota$ is $B$, which is invertible, and $\iota = 0$ gives a solution modulo $\m$.
+Now for $F$ any power series, let $F_j$ be the polynomial consisting of all terms in $F$ of degree at most $j$, and let $\iota_j$ be the unique power series in $R[[x]]_0^n$such that $F_j(x,\iota_j) = 0$.
+Note that both $\iota_j$ and $\iota_{j+1}$ are solutions to $F_j(x,\iota) \equiv 0 \mod \m^j$, so by the uniquess guaranteed by Hensel's lemma used over $R[[x]]/\m^j$, these must be equal.
+Hence they converge to $\iota \in R[[x]]_0^n$, which is the unique solution of $F(x,\iota(x)) = 0$.
+\end{proof}
+This has the following corollary about the inverse of a power series.
+\begin{cor}
+\label{lem:formalinverse}
+Let $x$ have length $n$. Let $a \in R[[x]]_0^n$ with $a \equiv Px \mod x$ for some matrix $A\in \GL_n(R)$. Then there is a unique $b \in R[[x]]_0^n$ such that $a \circ b = b \circ a = x$.
+\end{cor}
+\begin{proof}
+Let $F(x,y) = x - a(x)$.
+This satisfies the constraints of Lemma~\ref{lem:implicitfunction}, so we find a unique $b$ such that $a \circ b = x$.
+Applying Lemma~\ref{lem:implicitfunction} again gives a unique $c$ such that $b \circ c = x$.
+But then $a = a \circ (b \circ c) = (a \circ b) \circ c = c$ shows $a = c$ and hence we are done.
+\end{proof}
+So a formal group $F$ does by Lemma~\ref{lem:implicitfunction} indeed have a right inverse $\iota_F$.
+Also, by $F(0,0) = 0$ we have that $F(x,F(\iota_f,0)) = 0$ so $F(\iota_f,0)$ is in fact equal to $\iota_F$; as $\iota_F \equiv -x \mod (x)^2$, it has a formal inverse and hence $F(x,0) = x$, so $0$ is indeed a right unit.
+A standard argument now shows that $\iota_F$ is also a left inverse and $0$ is also a right unit, so $F$ gives $R[[x]]$ the structure of a group object in the category of topological rings; for two continuous morphisms $f_1,f_2$ from $R[[x]]$ to some ring $A$, given by sending $x$ to $a_1,a_2$ respectively, we define $(f_1 \oplus f_2)(x) = F(a_1,a_2)$, and by our considerations this makes $\Hom_{\text{cont}}{R,A}$ into a group, functorially in $A$.
 
@@
 \begin{lem}
+\label{lem:formallog}
 With notation as above, we have the following statements about $\log_p$:
@@
 As we have, with no constraint on $p$, for all $n\geq $ that $c_n\coloneqq p^{n-1}/n$ lies in $\Z_p$ and converges to $0$, this means that \[ \log_{p,i} = \sum_I a_{i,I} p^{|I|-1} x^I = \sum_I |I|a_{i,I} c_{|I|} x^I\] is indeed an element of $\Z_p\angle{x_1,\dots,x_d}^n$, and hence defines a map $\Z_p^d \to \Z_p$.
-Hence all the $\log_{p,i}$ together give a map $\Z_p^d \to \Z_p^d$
-
-[TODO: explain why group morphism]
+Hence all the $\log_{p,i}$ together give a map $\Z_p^d \to \Z_p^d$.
+By the equality of power series $\log(F(x,y)) = \log(x)+\log(y)$ from the definition of the logarithm, and the fact that all these powerseries converge on $p\Z_p^d$, this $\log_{p,i}$ is indeed a group morphism from $(\Z_p^d,\oplus)$ to $(\Z_p^d,+)$
 
@@
 As $\log_{p,i} = x_i \mod (x)^2$, this means that for $p > 2$ we have \[\log_{p,i} \equiv \sum_{|I| = 1} |I|a_{i,I}c_|I| x^I \equiv x_i \bmod p.\]
-[TODO: explain how the lemma gives $\exp_p \in \Z_p[[x]]^d$, and how the construction hopefully shows it is indeed a convergent power series]
+Note that as $\log_p \equiv x \mod (x)^2$, by Lemma~\ref{lem:formalinverse} it has an inverse $\exp_p \in \Z_p[[x]]_0^n$.
+Modulo $p$, this $\exp_p$ must be $x$, which lies in $\Z_p\angle{x}_0^n$; as $\Z_p\angle{x}$ is $p$-adically complete, using Hensel this shows $\exp_p$ is indeed in $\Z_p\angle{x}_0^n$.
+\end{proof}
+[TODO: I'd like to study what happens modulo higher powers of $p$; for example, if $\log_p$ is at most quadratic mod $p^2$, then so is $\exp_p$; and similar for $\log_p$ at most cubic mod $p^3$.
+Even in general, if $\log_p$ has degree at most $d$ modulo $p^k$, then $\exp_p$ has degree at most $f = f(d,k)$ (seen most easily by working in a ``universal'' ring $\Z[p]/(p^k)$).
+
+This lemma makes the proof of Theorem~\ref{thm:kappanice} relatively easy. 
+\begin{proof}[Proof of Theorem~\ref{thm:kappanice}]
+Write $\log_p$ for the logarithm corresponding to the formal group corresponding to the The map $\kappa: \Z^d \to \Z_p^g$ given by the inclusion $J(\Z)_0$ to $J(\Z_p)_0$ is a group morphism with the group structure on $\Z^d$ being addition and the group structure on $\Z_p^g$, denoted by $\oplus$, given by the bijection with $J(\Z_p)_0$ induced by choosing parameters at $0$.
+Then by Lemma~\ref{lem:formallog} the map factors as in the diagram of groups
+%\[
+% https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBpiBdUkANwEMAbAVxiRAAoAdTgLQD0opANQBKEAF9S6TLnyEUAJnJVajFmy68A+mj4BzUtwhpmcMZOnY8BIgEZStlfWatEHbjx37h5lTCh68ESgAGYAThAAtkhkIDgQSPYgDHQARjAMAAoy1vLJMCE4INTO6m7cANZ0aGh0ElIg4VEx1PFISqoubNwMEHo6AATcAMZYYcNDnFU1dRaNEdGIHW2ISaWuINwwAB5oOhIU4kA
+\begin{tikzcd}
+{(\Z^d,+)} \arrow[rr, "\kappa"] \arrow[rd, "\log_p \circ \kappa"] &                                   & {(\Z_p^g,\oplus)} \\
+                                                                  & {(\Z_p^g,+)} \arrow[ru, "\exp_p"] &                  
+\end{tikzcd}
+%\]
+Then the arrow $\log_p \circ \kappa$ is just a linear map, and $\exp_p$ is a convergent power series that is linear modulo $p$, so their composite $\kappa$ is also a convergent power series linear modulo $p$.
 \end{proof}
 
-[TODO: proof of Theorem~\ref{thm:kappanice}, should be easy now].
-
+This immediately gives rise to the following corollary.
 \begin{cor}
@@
 \end{cor}
-TODO: give proof. This is easy now.
 
@@
 In general, we may expect an upper bound for $|C(\Z)_P|$ of $1$ if $r \leq g-1$.
-TODO: give proof of Theorem 4.2.
+TODO: give proof of Theorem 4.12.
 % Pull back the f_i along kappa for the final theorem

### 2020-02-05 MS.tex
Processed part of Bas annotations

@@
 \DeclareMathOperator{\A}{A}
+\let\div\undefined
+\DeclareMathOperator{\div}{div}
 
@@
 \section{Linear Chabauty}
-Let $p>2$ be a prime, and $C$ be a scheme over $\Z$, proper, flat, regular with $C$ smooth over $\Z_{(p)}$ and $C_\Q$ of dimension $1$ and geometrically connected, of genus $g \geq 1$ and Mordell-Weil rank $r < g$.
+Let $p>2$ be a prime, and $C$ be a scheme over $\Z$, proper, flat, regular with $C$ smooth over $\Z_{(p)}$ and $C_\Q$ of dimension $1$ and geometrically connected, of genus $g \geq 1$ and with the Jacobian $J$ of $C_\Q$ having Mordell-Weil rank $r < g$.
 Assume we have a $\Q$-point $b$ in $C$, or equivalently a $\Z$-point.
-Let $J$ be the Jacobian of $C_\Q$; we view $C_\Q$ as a subscheme of $J$, using the map $Q \mapsto Q - b$ on points.
+We view $C_\Q$ as a subscheme of $J$, using the map $Q \mapsto Q - b$ on points.
 Let $P \in C(\F_p)$ be a point such that $t := P - b \in J(\F_p)$ lies in the image of $J(\Z)$.
@@
 By shrinking $X$ even more, we may assume as $X$ is smooth that $t = (t_1,\dots,t_d): X \to \A^d_{\Z_p}$ is \'etale.
-Now consider the blowup $\Tilde{X}_x \to X$ of $X$ at $x$, and let $\Tilde{X}_x^p$ be the part where $p$ generates the maximal ideal.
+Now consider the blowup $\Tilde{X}_x \to X$ of $X$ at $x$, and let $\Tilde{X}_x^p$ be the part where $p$ generates the inverse image of the maximal ideal of $O_{X,x}$.
 Equivalently, that is the part where $t_1,\dots,t_d$ are multiples of $p$, so informally it consists of the points that reduce to $x$ modulo $p$.
 
-As $t$ is \'etale, the ideal of $X$ defining $x$ is the pullback along $t$ of the ideal of $\A^d_{\Z_p}$ defining the origin $a$ over $\F_p$.
-That means that the blowup $\Tilde{X}_x \to X$ is the pullback of the blowup $\Tilde{\A}^d_{\Z_p,a} \to \A^d$.
+There is an explicit description of the map $\Tilde{X}_x^p \to X$; as $t$ is \'etale, the ideal of $X$ defining $x$ is the pullback along $t$ of the ideal of $\A^d_{\Z_p}$ defining the origin $a$ over $\F_p$.
+That means that the blowup $\Tilde{X}_x \to X$ is the pullback of the blowup $\Tilde{\A}^d_{\Z_p,a} \to \A_{\Z_p}^d$.
 Then the part $\Tilde{X}_x^p$ is the pullback of the corresponding part of $\Tilde{\A}^d_{\Z_p,a}$, i.e.
-$\Spec \Z_p[\Tilde{x_1},\dots,\Tilde{x_d}] = \Spec \Z_p[x_1/p,\dots,x_d/p]$ with the morphism $\Z_p[x_1,\dots,x_d] \to \Z_p[\Tilde{x_1},\dots,\tilde{x_p}]$ given by $x_i \mapsto p\Tilde{x_i}$.
+$\Spec \Z_p[\Tilde{x_1},\dots,\Tilde{x_d}] = \Spec \Z_p[x_1/p,\dots,x_d/p]$ with the morphism $\Z_p[x_1,\dots,x_d] \to \Z_p[\Tilde{x_1},\dots,\tilde{x_d}]$ given by $x_i \mapsto p\Tilde{x_i}$.
 That implies that $\Tilde{X}_x^p$ is $\Spec A[t_1/p,\dots,t_d/p]$, with the map $\Tilde{X}_x^p \to X$ given by the inclusion $A \to \Spec A[t_1/p,\dots,t_d/p]$ (remember that the $t_i$ are elements of $O_X(X) = A$).
@@
 \[
-\Z_p\angle{\Tilde{x_1},\dots, \Tilde{x_d}} = \left\{f \in \Z_p[[\Tilde{x_1},\dots,\Tilde{x_d}]] \mid \forall n \geq 0, f + (p^n) \in \Z/p^n\Z[\Tilde{x_1},\dots,\tilde{X_d}] + (p^n) \right\}.
+\Z_p\angle{\Tilde{x_1},\dots, \Tilde{x_d}} = \left\{f \in \Z_p[[\Tilde{x_1},\dots,\Tilde{x_d}]] \mid \forall n \geq 0, f + (p^n) \in \Z/p^n\Z[\Tilde{x_1},\dots,\tilde{x_d}] + (p^n) \right\}.
 \]
-By the universal property of completions, as $t$ induces the isomorphism between completion, $t$ also induces a bijection $$\Hom(O(X(\Z_p)_x), \Z_p) \to \Hom(O(X(\Z_p)_x)^{\wedge p}, \Z_p) = \Hom(\Z_p\angle{\Tilde{x_1},\dots,\Tilde{x_d}},\Z_p) = \Z_p^d$$.
-Following all the bijections, we indeed get the bijection we wanted.
+By the universal property of completions, as $t$ induces the isomorphism between completion, $t$ also induces a bijection $$\Hom(O(X(\Z_p)_x), \Z_p) \to \Hom(O(X(\Z_p)_x)^{\wedge p}, \Z_p) = \Hom(\Z_p\angle{\Tilde{x_1},\dots,\Tilde{x_d}},\Z_p) = \Z_p^d.$$ Following all the bijections, we indeed get the bijection we wanted.
 \end{proof}
@@
 \ref{lem:smoothpointfunc}
-Given two smooth schemes $X,Y$ over $\Z_p$, two $\F_p$-point $x\in X(\F_p), y\in Y(\F_p)$, there is a natural bijection between maps $f: Y \to X$ satisfying $f(y) = x$, and morphisms $\Tilde{Y}_y^p \to \Tilde{X}_Y^p$.
+Given two smooth schemes $X,Y$ over $\Z_p$ and two $\F_p$-points $x\in X(\F_p), y\in Y(\F_p)$, a map $f: Y \to X$ satisfying $f(y) = x$ gives rise to a morphism $\Tilde{Y}_y^p \to \Tilde{X}_x^p$.
 \end{lem}
 \begin{proof}
-TODO
-Is this even necessary?
+TODO: give proof.
 \end{proof}
 
+[TODO: add that the map $\Tilde{Y}_y^p(\Z_p) \to \Tilde{X}_x^p(\Z_p)$ is, after choosing parameters, given by convergent power series; are these in general linear modulo $p$?
+And what happens modulo higher powers?]
+
 Finally, we look at the specific case of $X$ being of relative dimension $1$ over $\Z_p$.
-It then turns out that there is additionally a free faithful $\F_p$-action on $X(\Z/p^2\Z)_0$.
+It then turns out that there is additionally a free transitive $\F_p$-action on $X(\Z/p^2\Z)_0$.
+[TODO: maybe replace this by an action of the tangent space of $X_{\F_p}$ at $x$].
 We can parametrise $X(\Z/p^2\Z)_0$ by $t = t_1 : X(\Z/p^2\Z)_0 \to p\Z/p^2\Z$; write $P_{\lambda}$ for the point with $t$-value $\lambda p$.
-Then as Cartier divisor, the point $P_{\lambda}$ is defined by $t - \mu p \in O(X_{\Z/p^2\Z})_x$, so $P_{\lambda} + P_{\mu}$ is defined by $(t-\lambda p)(t-\mu p) = t^2 - (\lambda + \mu)tp$, which defines the same Cartier divisor as $P_{\lambda'} + P_{\mu'}$ if and only if $\lambda + \mu = \lambda' + \mu'$.
-So as a Cartier divisor, $P(\lambda) + P_{\mu}$ is in fact equal to $P_{\lambda'} + P_{\mu'}$.
+Then as Cartier divisor, the point $P_{\lambda}$ is defined by $t - \lambda p \in O(X_{\Z/p^2\Z})_x$, so $P_{\lambda} + P_{\mu}$ is defined by $(t-\lambda p)(t-\mu p) = t^2 - (\lambda + \mu)tp$, which defines the same Cartier divisor as $P_{\lambda'} + P_{\mu'}$ if and only if $\lambda + \mu = \lambda' + \mu'$.
+So as a Cartier divisor, $P_{\lambda} + P_{\mu}$ is in fact equal to $P_{\lambda'} + P_{\mu'}$.
 
@@
 To be able to use this theory, we first give some results about going from a group scheme over $\Z_p$ to a formal group.
-[TODO: introduce the "subscript zero" notation for power series with no constant term; $R[[x]]_0 = \{f: f \equiv 0 \mod x\}$].
 First we introduce some notation that will be used in this section.
@@
 
-Given a smooth scheme $G$ over $\Z_p$ of relative dimension $d$, we can look at the completion along the zero section $\Hat{O}_{G,e}$.
+Given a smooth scheme $G$ over $\Z_p$ of relative dimension $d$, together with a $\Z_p$-point $e$, we can look at the completion $\Hat{O}_{G,e}$ along the section $e$.
 By smoothness, after picking parameters, this is isomorphic as topological $\Z_p$-algebras to the ring of power series $\Z_p[[x_1,\dots,x_d]]$.
-This completion naturally gives rise to a formal scheme denoted $\Spf \Hat{O}_{G,e}$; in a categorical notion, this is a functor on finite $\Z_p$-algebras sending $A$ to $\Hom_{\text{cont}}(\Hat{O}_{G,e},A)$, but we can also think of it as a locally ringed space with $\Spec \Z_p$ as topological space, and sheaf of rings $\Hat{O}_{G,e}$.
+This completion naturally gives rise to a formal scheme denoted $\Spf \Hat{O}_{G,e}$; in a categorical notion, this is a functor on finite length $\Z_p$-algebras sending $A$ to $\Hom_{\text{cont}}(\Hat{O}_{G,e},A)$, but we can also think of it as a locally ringed space with $\Spec \Z_p$ as topological space, and sheaf of rings $\Hat{O}_{G,e}$.
 
@@
 for every finite $\Z_p$-algebra $A$ the set $\Hom_{\text{cont}}(\Hat{O}_{G,e},A)$ gets a group structure, functorially in $A$.
-By functoriality, this is the same [TODO: why exactly?] as an continuous coproduct $\mu: \Hat{O}_{G,e} \to \left(\Hat{O}_{G,e}\right)^{\tensor 2}$.
-After choosing an isomorphism between $\Hat{O}_{G,e}$ and $\Z_p[[x_1,\dots,x_d]]$, let $F_j \in \Z_p[x,y]$ denote $\mu(x_i)$.
+By functoriality, this is the same [TODO: why exactly?] as an continuous coproduct $\mu: \Hat{O}_{G,e} \to \left(\Hat{O}_{G,e}\right)^{\Hat{\tensor} 2}$.
+After choosing an isomorphism between $\Hat{O}_{G,e}$ and $\Z_p[[x_1,\dots,x_d]]$, let $F_j \in \Z_p[[x,y]]$ denote $\mu(x_i)$.
 Then it is clear that $F_G = (F_1,\dots,F_d)$ is a $d$-dimensional formal group scheme, and commutative if $G$ was commutative.
@@
 
+[TODO: in general, generators of the Mordell-Weil group are computationally out of reach.
+But, if we only generate a subgroup of $J(\Z)_0$ of index finite and coprime to $p$, then the closure of this in $J(\Z_p)_0$ will be the same.
+This happens in particular if we generate a subgroup of $J(\Z)$ of index finite and coprime to $p|J(\F_p)|$.]
+
 \subsection{From \texorpdfstring{$C(\Z_p)$}{C(Z\_p)} to \texorpdfstring{$J(\Z_p)$}{J(Z\_p)}}
@@
 By Theorem 4.2 of Edixhoven-Lido, we just need to check whether $\overline{A}/\overline{I}$ is finite.
-As all $\overline{\kappa^* f_i}$ are linear, in fact, $\overline{A}/\overline{I}$ is always of the form $0$ or $\F_p[w_1,...,w_s]$ for some $s \leq r$, and $s = 0$ iff the system of linear equations $\overline{\kappa^* f_i} = 0, i \in \{1,...,g-1\}$ has a unique solution.
-In general, we may expect an upper bound for $|C(\Z)_P|$ of $1$ if $r \leq g-1$.
+As all $\overline{\kappa^* f_i}$ are linear, in fact, $\overline{A}/\overline{I}$ is always of the form $0$ (meaning no solutions) or $\F_p[w_1,...,w_s]$ for some $s \leq r$, and $s = 0$ iff the system of linear equations $\overline{\kappa^* f_i} = 0, i \in \{1,...,g-1\}$ has a unique solution.
+In general, we may hope an upper bound for $|C(\Z)_P|$ of $1$ if $r \leq g-1$.
 TODO: give proof of Theorem 4.12.
@@
 \section{Implementations of linear Chabauty and an explicit example}
+[TODO: make sure I clearly differentiate divisors and divisor classes]
 We now assume that $C$ is hyperelliptic, i.e. given by the degree $2g+2$ homogenisation of an equation of the form
@@
 We will treat the case that $f$ has degree $2g+2$ (this can be done by translating $f$ until the constant coefficient is non-zero, and then looking at $f^r$).
-In that case, writing , the line at infinity $C$ looks like $Y^2 = X^{2g+2}$, i.e.
+In that case, near the line at infinity $C$ looks like $Y^2 = X^{2g+2}$, i.e.
 $(Y-X^{g+1})(Y+X^{g+1}) = 0$, and we see there are two points $\infty_+ = (1:1:0)$ and $\infty_- = (1:-1:0)$.
@@
 we can represent rational functions in $V_5$ by their values in $k^Z$.
-In this representation, we can even add, subtract, or multiply rational function, by respectively adding, subtracting or multiplying the correspondig vectors in $k^Z$.
+In this representation, we can add, subtract, or, if the degree at infinity is not too large, even multiply rational functions, by respectively adding, subtracting or multiplying the correspondig vectors in $k^Z$.
 It is now also possible to represent subspaces of $V_5$ by giving a basis in $k^Z$.
+(Instead of passing to an extension of $k$, one could also evaluate functions on infinitesemal neighborhoods of $k$-points, i.e.
+compute Taylor expansions near those points.)
 
 We now explain the representation of $J(k)$.
-Note that for any $x \in J(k)$, we have that $x + D_0$ is of degree at least $2g+1$ and hence is equivalent to an effective divisor $E \geq 0$.
+Note that for any $x \in J(k)$, we have that $x + [D_0]$ is a divisor class of degree at least $2g+1$ and hence is equivalent to an effective divisor $E \geq 0$ of degree $d_0$.
 Then we represent $x$ by $\Lcal(2D_0 - E)$ inside $V_2$; by Riemann-Roch this is a $d_W$-dimensional subspace of $V_2$ where $d_W = d_0 + 1 - g$, and in particular we can represent it as a $n_z \times d_W$ matrix, itself representing a subspace of $k^Z$.
@@
 
-As explained in Mascots article, using this representation one can do all relevant computations in $J(k)$; adding, subtracting, finding the zero element, and most importantly: checking equality.
+As explained in Mascot's article, using this representation one can do all relevant computations in $J(k)$; adding, subtracting, finding the zero element, and most importantly: checking equality.
 
@@
 However, for Chabauty we want to compute inside $J(\Z/p^e\Z)$.
-Luckily, Mascots code takes care of this too, by passing from vector spaces over $\F_p$ to free $R$-submodules of $R^n$ with $R = Z/p^e\Z$; in fact, all submodules of $R^n$ we will be seeing are free.
+Luckily, Mascots code takes care of this too, by passing from vector spaces over $\F_p$ to free $R$-submodules of $R^n$ with $R = \Z/p^e\Z$; in fact, all submodules of $R^n$ we will be seeing are free.
 That means all these submodules will have good reduction, i.e.
-the rank remains the same when tensoring with $\F_p$.
-If the maps between such modules also have good reduction, then all kernels, images, et cetera will also have these properties, and can be calculated by Hensel lifting the kernels, images, et cetera of these maps modulo $p$.
+they will remain free and of the same rank after tensoring with $\F_p$.
+If the maps between such modules also have good reduction, then all kernels, images, et cetera will also have these properties, and can first be calculated modulo $p$ using linear algebra and then by Hensel lifting modulo higher powers of $p$.
 
@@
 Explicitly, we want to go from a degree zero divisor to an element in Mascots representation.
-Since we can add elements in the Jacobian, for this it is enough to compute the Abel-Jacobi embedding
+In our case, we will only need this in cases where divisors are sums of points, and since we can add elements in the Jacobian, for this it is enough to compute the Abel-Jacobi embedding
 \begin{align*}
@@
 \end{align*}
+If the degree zero divisor is not a sum of points, one can pass to an extension, knowing that the result at the end will be defined over the ring we started with.
 We will only need $j_{\infty_+}(P)$ and $j_{\infty_-}(P)$ for affine points $P$; as the calculation of $j_{\infty_-}(P)$ is entirely similar to $j_{\infty_+}(P)$, we only focus on $j_{\infty_+}(P)$.
@@
  \KwData{$C,J$, an affine point $P \in C(R)$ where $R = \Z/p^e\Z)$}
- \KwResult{A space of the form $\Lcal(2D_0 - E)$ where $E-D_0 = P - \infty_+$ as divisors and $E \geq 0$}
+ \KwResult{A space of the form $\Lcal(2D_0 - E)$ where $[E-D_0] = [P - \infty_+]$ as divisors and $E \geq 0$}
  $Z' \leftarrow Z \sqcup \{P\}$\;

### 2020-02-06 MS.tex
Added last comments of Bas from 30-01

@@
 \newcolumntype{C}{>{$}c<{$}} % math-mode version of "l" column type
+
+\relpenalty=10000
+\binoppenalty=10000
 
@@
 Then by Lemma~\ref{lem:formallog} the map factors as in the diagram of groups
-%\[
+\[
 % https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBpiBdUkANwEMAbAVxiRAAoAdTgLQD0opANQBKEAF9S6TLnyEUAJnJVajFmy68A+mj4BzUtwhpmcMZOnY8BIgEZStlfWatEHbjx37h5lTCh68ESgAGYAThAAtkhkIDgQSPYgDHQARjAMAAoy1vLJMCE4INTO6m7cANZ0aGh0ElIg4VEx1PFISqoubNwMEHo6AATcAMZYYcNDnFU1dRaNEdGIHW2ISaWuINwwAB5oOhIU4kA
@@
 \end{tikzcd}
-%\]
+\]
 Then the arrow $\log_p \circ \kappa$ is just a linear map, and $\exp_p$ is a convergent power series that is linear modulo $p$, so their composite $\kappa$ is also a convergent power series linear modulo $p$.
@@
 Explicitly, we want to go from a degree zero divisor to an element in Mascots representation.
-In our case, we will only need this in cases where divisors are sums of points, and since we can add elements in the Jacobian, for this it is enough to compute the Abel-Jacobi embedding
+Generally these divisors are not always sums of points over the ring we are working with, but if $J(\Z)$ is generated by $C(\Z)$, then we only need this in cases where divisors are sums of points.
+Since we can add elements in the Jacobian, for this it is enough to compute the Abel-Jacobi embedding
 \begin{align*}
@@
 \end{align*}
-If the degree zero divisor is not a sum of points, one can pass to an extension, knowing that the result at the end will be defined over the ring we started with.
+If the degree zero divisor is not a sum of points, one can temporarily pass to an extension, knowing that the result at the end will be defined over the ring we started with.
 We will only need $j_{\infty_+}(P)$ and $j_{\infty_-}(P)$ for affine points $P$; as the calculation of $j_{\infty_-}(P)$ is entirely similar to $j_{\infty_+}(P)$, we only focus on $j_{\infty_+}(P)$.
@@
  \KwData{$C,J$, an affine point $P \in C(R)$ where $R = \Z/p^e\Z)$}
- \KwResult{A space of the form $\Lcal(2D_0 - E)$ where $[E-D_0] = [P - \infty_+]$ as divisors and $E \geq 0$}
+ \KwResult{A space of the form $\Lcal(2D_0 - E)$ where $E-D_0 = P - \infty_+$ as divisors and $E \geq 0$}
  $Z' \leftarrow Z \sqcup \{P\}$\;
@@
  %Calculate $\Lcal(D_0 + \infty_+ - P)$\;
- $U \leftarrow \im(R^{g+4} \xrightarrow{\cdot V} R^{n_Z + 1} \to R^{n_Z})$, where the last map is the projection on the first coordinates.\;
- %$F \leftarrow \frac{X^{g+1} - Y}{Z^{g+1}}$ evaluated on $\Z$\;
- Evaluate the special function $F$ (see Hyper2RR.gp) on $Z$\;
- Return $U\cdot \sigma(F)$\;
+ $U \leftarrow \im(V \to R^{n_Z})$, where the last map is the projection on the first coordinates.\;
+ Return $U$\;
  \caption{The Abel-Jacobi embedding}
@@
 First note that by Riemann-Roch, the dimension of $\Lcal(D_0)$ is $g + 3$, and we also have by the proof of the previous lemma that $1,x,\dots,x^{g+1},y$ all lie in $\Lcal(D_0)$ and hence form a basis, so we can indeed find $B$ as in line~\ref{alg:abeljacobi:basisLD0}.
-Note that by Lemma~\ref{lem:poles2d0i+} the element $b_{g+4}$ lies in $\Lcal(D_0 + \infty_+)$ but not in $\Lcal(D_0)$, so as $\deg D_0 \geq 2g-1$, we have by a dimensional argument that $b_1,\dots,b_{g+4}$ is a basis for $\Lcal(D_0 + \infty_+)$; that it is in fact a basis is evident as this argument tells us it is a basis when tensored with $\F_p$.
+Note that by Lemma~\ref{lem:poles2d0i+} the element $b_{g+4}$ lies in $\Lcal(D_0 + \infty_+)$ but not in $\Lcal(D_0)$, so as adding a point to a divisor causes the the dimension to increase by at most $1$, we have by that $b_1,\dots,b_{g+4}$ is a basis for $\Lcal(D_0 + \infty_+)$; that it is in fact a basis is evident as this argument tells us it is a basis when tensored with $\F_p$.
 
-Evaluating $\Lcal(D_0 + \infty_+)$ on $P$ gives a linear map $\Lcal(D_0 + \infty_+) \to R$, and the kernel is exactly $\Lcal(D_0 + \infty_+ - P)$; this is the resulting $V$ in line~\ref{alg:abeljacobi:kerp}.
-Then.
-Finally, note that the poles of $\sigma(F)$ are, again by the previous lemma, $g(\infty_+ + \infty_-) + \infty_+$; write $E$ for the divisor of zeroes of $F$; we see it has degree $2g+1$.
-Then we have the equality \[\Lcal(D_0 + \infty_+-P) \cdot F = \Lcal(2D_0 - E - P).\]
-This last term is in fact in Mascots representation, and trivially $P-\infty_+ = P + E - D_0$, so this represents $P-\infty_+$ in the Jacobian.
+Evaluating $\Lcal(D_0 + \infty_+)$ on $P$ gives a linear map $\Lcal(D_0 + \infty_+) \to R$, and the kernel is exactly $\Lcal(D_0 + \infty_+ - P)$; this is the resulting $U$ in line~\ref{alg:abeljacobi:kerp}.
+Furthermore we have the equality of divisors $P-\infty_+ = E - D_0$ where $E = P + D_0 - \infty_+ \geq 0$, so $\Lcal(D_0 + \infty_+ - P)$ is as a subspace of $V_2$ equal to $\Lcal(2D_0 - E)$.
+This last term is in fact in Mascots representation, so this represents $P-\infty_+$ in the Jacobian.
 \end{proof}
@@
 \subsection{Speeding up the calculations}
-Say something about how one express an element in $J(\Z/p^2\Z)_0$ on the basis in something like $O(g)$ hopefully (ignoring the time for adding,multiplying, et cetera in the Jacobian), instead of the bruteforce $O(p^g)$.
+Say something about how one express an element in $J(\Z/p^2\Z)_0$ on the basis in something like $O(g)$ hopefully (ignoring the time for adding,multiplying, et cetera in the Jacobian), identify $J(Z/p^2)_0$ with $F_p^g$ using $g$ generators of the ideal of the zero section of $J_{Z/p^2}$, then the group structure that $J$ induces on $F_p^g$ is the usual addition.
 This is currently done using code from Mascot.

### 2020-02-11 MS.tex
Added small comment on source saturation Jacobian
Added todo's
Started proof log/exp mod p^m

@@
 Then this $\exp_p$ is a two-sided inverse of $\log_p$, and hence $\log_p: \Z_p^d \to \Z_p^d$ is a bijection.
+	\item Let $m \in \Z_{>0}$. For $p > m+1$, the map $\log_p$ and $\exp_p$ are of degree at most $m$ modulo $p^m$.
 \end{enumerate} 
@@
 Modulo $p$, this $\exp_p$ must be $x$, which lies in $\Z_p\angle{x}_0^n$; as $\Z_p\angle{x}$ is $p$-adically complete, using Hensel this shows $\exp_p$ is indeed in $\Z_p\angle{x}_0^n$.
+
+As $c_n$ has $p$-adic valuation $n-1$ for $...$
 \end{proof}
@@
 But, if we only generate a subgroup of $J(\Z)_0$ of index finite and coprime to $p$, then the closure of this in $J(\Z_p)_0$ will be the same.
-This happens in particular if we generate a subgroup of $J(\Z)$ of index finite and coprime to $p|J(\F_p)|$.]
+This happens in particular if we generate a subgroup of $J(\Z)$ of index finite and coprime to $p|J(\F_p)|$.
+Preferably, find a source for this?
+]
 
@@
 In general, we may hope an upper bound for $|C(\Z)_P|$ of $1$ if $r \leq g-1$.
-TODO: give proof of Theorem 4.12.
+
 % Pull back the f_i along kappa for the final theorem

### 2020-02-12 MS.tex
Worked on deg exp_p mod p^m

@@
 
-As $c_n$ has $p$-adic valuation $n-1$ for $...$
+Finally, let $m \in \Z_{>0}$ with $p > m+1$.
+As $c_n$ has $p$-adic valuation $n-1$ for $n < p$, and $p$-adic valuation at least $p-2 \geq m$ for $n \geq p$, indeed $\log_p$ has degree at most $m$ modulo $p^m$.
+Then the statement that $\exp_p$ has degree at most $m$ modulo $p^m$ is easily proven by the formula in $\Z/p^m\Z[x,\varepsilon]$ that $\log_p(g(x) -\varepsilon)+\varepsilon$
 \end{proof}

### 2020-02-13 MS.tex
Confront C(Z_p) with J(Z)

@@
 \section{Linear Chabauty}
+\label{section:linchab}
 Let $p>2$ be a prime, and $C$ be a scheme over $\Z$, proper, flat, regular with $C$ smooth over $\Z_{(p)}$ and $C_\Q$ of dimension $1$ and geometrically connected, of genus $g \geq 1$ and with the Jacobian $J$ of $C_\Q$ having Mordell-Weil rank $r < g$.
@@
 \label{thm:kappanice}
-There are uniquely determined $\kappa_1,\dots,\kappa_g \in \Z_p\angle{z_1,...,z_r}$ such that for all $x \in \Z^r$ we have $\kappa(x) = (\kappa_1(x),\dots,\kappa_g(x))$ and the image $\overline{\kappa_i}$ of $\kappa_i$ in $\F_p[z_1,...,z_r]$ has degree at most $1$.
+There are uniquely determined $\kappa_1,\dots,\kappa_g \in \Z_p\angle{z_1,...,z_r}$ such that for all $x \in \Z^r$ we have $\kappa(x) = (\kappa_1(x),\dots,\kappa_g(x))$ and the image $\overline{\kappa_i}$ of $\kappa_i$ in $\F_p[z_1,...,z_r]$ has degree at most $1$; furthermore, for $m \in \Z_{>0}$ with $m<p-1$, these $\kappa$ are also of degree at most $m$ modulo $p^m$.
 \end{thm}
@@
 To study $\log_p$ modulo $p$, we note that if $n\geq 3$, then $p$ actually divides $c_n$, and for $p > 2$ we even have $p|c_2$.
-As $\log_{p,i} = x_i \mod (x)^2$, this means that for $p > 2$ we have \[\log_{p,i} \equiv \sum_{|I| = 1} |I|a_{i,I}c_|I| x^I \equiv x_i \bmod p.\]
+As $\log_{p,i} = x_i \mod (x)^2$, this means that for $p > 2$ we have \[\log_{p,i} \equiv \sum_{|I| = 1} |I|a_{i,I}c_{|I|} x^I \equiv x_i \bmod p.\]
 Note that as $\log_p \equiv x \mod (x)^2$, by Lemma~\ref{lem:formalinverse} it has an inverse $\exp_p \in \Z_p[[x]]_0^n$.
@@
 As $c_n$ has $p$-adic valuation $n-1$ for $n < p$, and $p$-adic valuation at least $p-2 \geq m$ for $n \geq p$, indeed $\log_p$ has degree at most $m$ modulo $p^m$.
-Then the statement that $\exp_p$ has degree at most $m$ modulo $p^m$ is easily proven by the formula in $\Z/p^m\Z[x,\varepsilon]$ that $\log_p(g(x) -\varepsilon)+\varepsilon$
+Then we use induction to prove that $\exp_p$ has degree at most $m$ modulo $p^m$.
+This will follow immediately from the following considerations; firstly, for $f,g,g_m \in \Z/p^m\Z[x]_0^d$ satisfying $f(g(x)) = x \bmod p^{m-1}$, with $f,g$ linear modulo $p$ and $f,g$ having as derivative at $0$ invertible $d\times d$-matrices $C_f,C_g$ we have the formula
+\[
+f(g(x) + p^{m-1}g_m(x))+p^{m-1}f_m(g(x)) = f(g(x)) + p^{m-1}(C_f g_m(x))x^m
+\]
+and as $C_f$ is invertible, there is a unique value of $p^{m-1}g_m$ such that $f((g+p^{m-1}g_m)(x)) = x$, and then $p^{m-1}g_m$ has degree at most $\deg f(g(x))$.
+Secondly, if furthermore we can write $f,g$ in the forms $f = \sum_{i=1}^m p^{i-1}a_i x^i,g = \sum_{i=1}^{m-1} p^{i-1}b_i x^i$ with $p^{i-1}\mid a_i,b_i$, then we have
+\begin{align*}
+%f(g(x)) &= \sum_{i=1}^m p^{i-1} a_i g^i \\
+%        &= \sum_{i=1}^m p^{i-1} a_i \sum_{I_1,\dots,I_{i}} \prod_{j=1}^i p^{I_j-1} b_{I_j} x^{I_j} \\
+%        &= \sum_{i=1}^m \sum_n p^{n-1} x^n \left(\sum_{I_1 + \cdots +I_{i} = n} a_i \prod_{j=1}^i b_{I_j}\right) \\
+\end{align*}
+which is clearly of degree at most $m$.
+In total, there is a unique $\tilde{g} \in \Z/p^m\Z[x]_0^d$ satisfying $\tilde{g} \equiv g \bmod p^{m-1}$ and $f(\tilde{g}(x))=x$, and this $\tilde{g}$ has degree at most $m$.
+This finishes the proof.
+[TODO: This is clearly a Hensel like proof, and I would prefer to just outright use Hensels lemma in some way.
+Is this doable?
+I think so...
+Maybe multiply $g$ by $p$ and divide coefficients of $f$ by powers of $p$, and use that $\Z_p[[px]]$ is $p$-adically complete.
+Also, try to get rid of the calculation at the end.]
 \end{proof}
-[TODO: I'd like to study what happens modulo higher powers of $p$; for example, if $\log_p$ is at most quadratic mod $p^2$, then so is $\exp_p$; and similar for $\log_p$ at most cubic mod $p^3$.
-Even in general, if $\log_p$ has degree at most $d$ modulo $p^k$, then $\exp_p$ has degree at most $f = f(d,k)$ (seen most easily by working in a ``universal'' ring $\Z[p]/(p^k)$).
 
@@
 \]
-Then the arrow $\log_p \circ \kappa$ is just a linear map, and $\exp_p$ is a convergent power series that is linear modulo $p$, so their composite $\kappa$ is also a convergent power series linear modulo $p$.
+Then the arrow $\log_p \circ \kappa$ is just a linear map, and $\exp_p$ is a convergent power series that is of degree at most $m$ modulo $p^m$ for $m < p-1$, so their composite $\kappa$ is also a convergent power series of degree at most $m$ modulo $p^m$ for $m < p-1$
 \end{proof}
@@
 \subsection{From \texorpdfstring{$C(\Z_p)$}{C(Z\_p)} to \texorpdfstring{$J(\Z_p)$}{J(Z\_p)}}
+\label{subsection:czptojzp}
 By Subsection \ref{subs:smoothzppoints}, we also know that $C(\Z_p)_P$ is in bijection with $\Z_p$, again with the bijection given by evaluating a parameter and dividing by $p$.
 The resulting function $\Z_p \to \Z_p^g$ is linear and non-constant modulo $p$, i.e.
-there are power series $f_1,...,f_{g-1} \in \Z_p\angle{z_1,...,z_g}$ such that the image of $C(\Z_p)_P$ is exactly given by $V(f_1,...,f_{g-1})$, and all $f_i$ are linear modulo $p$.
+there are power series $f_1,\dots,f_{g-1} \in \Z_p\angle{z_1,...,z_g}$ such that the image of $C(\Z_p)_P$ is exactly given by $V(f_1,...,f_{g-1})$, and all $f_i$ are linear modulo $p$.
 Another way to think of this, is as $C(\Z/p^2\Z)_P$ being an affine line inside $J(\Z/p^2\Z)_t$.
@@
 
+\begin{rem}
+\label{rem:fislinear}
+We can pick our parameters right such that $C(\Z_p)_P \to J(\Z_p)_t$ is given by $\Z_p \to \Z_p^g$, mapping $\Z_p$ to the last coordinate.
+Then $f_1,\dots,f_{g-1}$ are just the other parameters at $t$, so they are linear.
+\end{rem}
+
 \subsection{Finding \texorpdfstring{$C(\Z)$}{C(Z)}}
 Clearly, as subsets of $J(\Z_p)_t$, we have the inclusion $C(\Z)_P \subset C(\Z_p)_P \cap \overline{J(\Z)_t}$.
-Let $\kappa^*f_1,...,\kappa^*f_{g-1}$ be the pullbacks along $\kappa$ of the $f_i$, and let $I$ be the ideal they generate inside $A := \Z_p\angle{z_1,...,z_r}$.
-Then $C(\Z_p)_P \cap \overline{J(\Z)_t}$ is in bijection with $\Hom(A/I,\Z_p)$.
-By Theorem 4.2 of Edixhoven-Lido, we just need to check whether $\overline{A}/\overline{I}$ is finite.
+The theory we have built so far enables the following method, which is in sharp contrast with Colemans method; instead of pulling back equations for $\overline{J(\Z)_t}$ to $C(\Z_p)_P$, we pull back equations for $C(\Z_p)_P$ to $\overline{J(\Z)_t}$ to arrive at the following theorem.
+\begin{thm}
+Let $C,J,p,P,t$ be as in Section~\ref{section:linchab}, let $\kappa$ be as in Theorem~\ref{thm:kappanice} and let $f_1,\cdots,f_{g-1}$ be as in Subsection~\ref{subsection:czptojzp}.
+Define $\lambda_1 = \kappa^*f_1,\dots,\lambda_{g-1} = \kappa^*f_{g-1}$ to be the pullbacks along $\kappa$ of the $f_i$.
+Then $\kappa$ induces a surjection from $Z(\lambda_1,\dots,\lambda_{g-1})$ to $C(\Z_p)_P \cap \overline{J(\Z)_t}$.
+\end{thm}
+
+The $\lambda_i$ are in general not computationally available, as they are power series, but we can approximate them modulo powers of $p$.
+For example, we know that the $\lambda_i$ are linear modulo $p$.
+And in particular, if $f_1,\dots,f_{g-1}$ are as in Remark~\ref{rem:fislinear}, then $\lambda_i = \kappa_i$ for $i \leq g-1$, so they are also of degree at most $m$ modulo $p^m$ for $m < p-1$.
+Knowing this, we can compute $\lambda_i$ modulo powers of $p$.
+[TODO: explain]
+
+[TODO: explain how to use these power series. Explain 4.12, $(I : p^\infty)$ and Newton polygons.]
+By Theorem 4.12 of Edixhoven-Lido, we just need to check whether $\overline{A}/\overline{I}$ is finite.
 As all $\overline{\kappa^* f_i}$ are linear, in fact, $\overline{A}/\overline{I}$ is always of the form $0$ (meaning no solutions) or $\F_p[w_1,...,w_s]$ for some $s \leq r$, and $s = 0$ iff the system of linear equations $\overline{\kappa^* f_i} = 0, i \in \{1,...,g-1\}$ has a unique solution.
@@
 
-% Pull back the f_i along kappa for the final theorem
+\subsection{Complications and improvements}
+$\overline{J(\Z)_0}$ open in $J(\Z_p)_0$.
+
+Calculations in $J(\Z)$.
+
+According to McCallum\&Poonen, it can be that $J(\Z)_0$ and $C(\Z)_P$ are tangent as $p$-adic manifolds and then finite-precision calculations will never be enough.
+I don't see what's happening there.
+Maybe give an example?
+
+It is possible that $C(\Z_p)_P \cap \overline{J(\Z)_t}$ is bigger than $C(\Z)_P$; give an example. Refer to \citep{Balakrishnan19}.
+
+Explain Mordell-Weil sieve
 
@@
 \subsection{Implementing the Abel-Jacobi map}
-Say something about implementing the Abel-Jacobi map $C \to J, Q \mapsto Q - \infty_+$. Right now, information about this (the implementation and why it works) can be found in Hyper2RR.gp.
-
 Now that we can do computations with elements in the Jacobian over $\Z/p^2\Z$, it only remains to construct elements in the Jacobian.

### 2020-02-19 MS.tex
Added mumford rep and params at J

@@
 \usepackage[ruled,linesnumbered]{algorithm2e}
+\usepackage{todonotes}
 
@@
 \newpage
-
+\listoftodos
 \tableofcontents
@@
 \label{section:intro}
+In mathematics a fundamental problem is solving polynomial equations over the rationals, dating back to Diophantus.
+An important special case in algebraic geometry is that of curves.
+The behavior of the rational points of curves depends enormously on the \textit{genus} of the curve, a numerical invariant of a curve.
+For $g = 0$, there are either no or infinitely many solutions, and their behavior is well understood.
 Say something about the problem, Faltings, et cetera
@@
 Say how much is borrowed from the article by Bas and Guido, but with a focus on the linear part, and more explanations.
+It is meant as a full guide to linear Chabauty, including both theoretical and practical components, focussing partly on explicit computations.
 
@@
 \begin{align*}
-%f(g(x)) &= \sum_{i=1}^m p^{i-1} a_i g^i \\
-%        &= \sum_{i=1}^m p^{i-1} a_i \sum_{I_1,\dots,I_{i}} \prod_{j=1}^i p^{I_j-1} b_{I_j} x^{I_j} \\
-%        &= \sum_{i=1}^m \sum_n p^{n-1} x^n \left(\sum_{I_1 + \cdots +I_{i} = n} a_i \prod_{j=1}^i b_{I_j}\right) \\
+f(g(x)) &= \sum_{i=1}^m p^{i-1} a_i g^i \\
+        &= \sum_{i=1}^m p^{i-1} a_i \sum_{I_1,\dots,I_{i}} \prod_{j=1}^i p^{I_j-1} b_{I_j} x^{I_j} \\
+        &= \sum_{i=1}^m \sum_n p^{n-1} x^n \left(\sum_{I_1 + \cdots +I_{i} = n} a_i \prod_{j=1}^i b_{I_j}\right) \\
 \end{align*}
@@
 \begin{proof}[Proof of Theorem~\ref{thm:kappanice}]
-Write $\log_p$ for the logarithm corresponding to the formal group corresponding to the The map $\kappa: \Z^d \to \Z_p^g$ given by the inclusion $J(\Z)_0$ to $J(\Z_p)_0$ is a group morphism with the group structure on $\Z^d$ being addition and the group structure on $\Z_p^g$, denoted by $\oplus$, given by the bijection with $J(\Z_p)_0$ induced by choosing parameters at $0$.
-Then by Lemma~\ref{lem:formallog} the map factors as in the diagram of groups
+Write $\log_p$ for the logarithm corresponding to the formal group corresponding to the The map $\kappa_0: \Z^d \to \Z_p^g$ given by the inclusion $J(\Z)_0$ to $J(\Z_p)_0$ is a group morphism with the group structure on $\Z^d$ being addition and the group structure on $\Z_p^g$, denoted by $\oplus$, given by the bijection with $J(\Z_p)_0$ induced by choosing parameters at $0$, and $\kappa$ is $\kappa_0 \oplus t$.
+Then by Lemma~\ref{lem:formallog} the map $\kappa$ factors as in the diagram of groups
 \[
@@
 \end{cor}
-
-[TODO: in general, generators of the Mordell-Weil group are computationally out of reach.
-But, if we only generate a subgroup of $J(\Z)_0$ of index finite and coprime to $p$, then the closure of this in $J(\Z_p)_0$ will be the same.
-This happens in particular if we generate a subgroup of $J(\Z)$ of index finite and coprime to $p|J(\F_p)|$.
-Preferably, find a source for this?
-]
 
@@
 And in particular, if $f_1,\dots,f_{g-1}$ are as in Remark~\ref{rem:fislinear}, then $\lambda_i = \kappa_i$ for $i \leq g-1$, so they are also of degree at most $m$ modulo $p^m$ for $m < p-1$.
-Knowing this, we can compute $\lambda_i$ modulo powers of $p$.
-[TODO: explain]
+Knowing this, we can compute $\lambda_i$ modulo powers of $p$ by extrapolation, and the following lemma, an immediate consequence of Lagrange interpolation, tells us how.
+\begin{lem}
+\label{lem:interpolate}
+Let $R$ be a ring, and assume operations in $R$ are $O(1)$, $f \in R[x]$ with $x = (x_1,\dots,x_n)$ a polynomial of degree at most $m$, and $S$ a subset of $R$ with $S-S \subset \{0\} \cup R^*$ and $|S| > m$.
+Then $f$ is uniquely determinable in $O(nm^{n+1})$ by its values on $S^n$.
+\end{lem} %complexity easily 
+\begin{proof}
+Both uniqueness and construction follow from the case with $n=1$; uniqueness from the fact that the ideals $\{(x-s) \mid s \in S\}$ are pairwise coprime, and the construction is Lagrange interpolation.
+The complexity follows easily from induction on $n$ and the formula for Lagrange interpolation.
+\end{proof}
+
+Note that evaluating $\lambda_i$ at a point in $J(\Z)_t$ comes down to calculating the value of a parameter at that point. More about this can be found in Section~\ref{subs:paramj}
 
@@
 
-\subsection{Complications and improvements}
-$\overline{J(\Z)_0}$ open in $J(\Z_p)_0$.
-
-Calculations in $J(\Z)$.
-
-According to McCallum\&Poonen, it can be that $J(\Z)_0$ and $C(\Z)_P$ are tangent as $p$-adic manifolds and then finite-precision calculations will never be enough.
+\section{Complications and improvements}
+\begin{itemize}
+\item $\overline{J(\Z)_0}$ open in $J(\Z_p)_0$.
+\item Calculations in $J(\Z)$.
+\item According to McCallum\&Poonen, it can be that $J(\Z)_0$ and $C(\Z)_P$ are tangent as $p$-adic manifolds and then finite-precision calculations will never be enough.
 I don't see what's happening there.
 Maybe give an example?
-
-It is possible that $C(\Z_p)_P \cap \overline{J(\Z)_t}$ is bigger than $C(\Z)_P$; give an example. Refer to \citep{Balakrishnan19}.
-
-Explain Mordell-Weil sieve
+\item It is possible that $C(\Z_p)_P \cap \overline{J(\Z)_t}$ is bigger than $C(\Z)_P$; give an example. Refer to \citep{Balakrishnan19}.
+\item Explain Mordell-Weil sieve. Maybe "The Mordell-Weil sieve: Proving non-existence of rational points on curves" for a short explanation? Nice to also treat this in the final example.
+\item in general, generators of the Mordell-Weil group are computationally out of reach.
+But, if we only generate a subgroup of $J(\Z)_0$ of index finite and coprime to $p$, then the closure of this in $J(\Z_p)_0$ will be the same.
+This happens in particular if we generate a subgroup of $J(\Z)$ of index finite and coprime to $p|J(\F_p)|$.
+Preferably, find a source for this?
+\end{itemize}
 
@@
 
-\subsection{Implementing the Abel-Jacobi map}
+\subsection{Implementing the Abel-Jacobi map and Mumford representations}
 Now that we can do computations with elements in the Jacobian over $\Z/p^2\Z$, it only remains to construct elements in the Jacobian.
 Explicitly, we want to go from a degree zero divisor to an element in Mascots representation.
-Generally these divisors are not always sums of points over the ring we are working with, but if $J(\Z)$ is generated by $C(\Z)$, then we only need this in cases where divisors are sums of points.
-Since we can add elements in the Jacobian, for this it is enough to compute the Abel-Jacobi embedding
+Most of the times these divisors are sums of points over the ring we are working with, but sometimes they are given as a Mumford representation.
+\begin{defn}
+Let $C$ be any (hyper)elliptic curve given by $y^2 = f(x)$ with $f$ of degree $2g+2$ where $g$ is the genus of $C$.
+A Mumford representation is a pair $(a,b)$ with $a,b$ polynomials in $x$, representing the degree $0$ divisor $D(a,b)$ on $C$, given on the first affine chart by the equation $a(x) = 0, y = b(x)$ and on the line at infinity by $-\deg a\infty_+$.
+Such a pair $a,b$ is required to satisfy that
+\begin{enumerate}
+\item the polynomial $b$ is of degree at most $\deg a -1$;
+\item the polynomial $a$ is monic of degree at most $g+1$;
+\item the polynomial $a$ divides $f - h^2$.
+\end{enumerate}
+\end{defn}
+\begin{rem}
+If $b$ does not satisfy the first condition, we can reduce $b$ modulo $a$. If $a$ does not satisfy the second condition, we can use the formula that on the first affine chart, we have
+\[
+D(a,b) + D(\frac{f-b^2}{a},b) = (y-h)
+\]
+meaning that with additional calculations of the behaviour of $(y-h)$ at infinity we can express $[D(a,b)]$ in the Jacobian in terms of $D(\frac{f-b^2}{a},b)$, and if $\deg a$ is strictly bigger than $g+1$, the degree of $\frac{f-b^2}{a}$ is at most $\deg a -2$.
+\end{rem}
+
+We will treat both how to explicitly compute the Abel-Jacobi embedding and divisors in Mumford represenation in Makdisi's representation for the Jacobian. We start with the Abel-Jacobi embedding 
 \begin{align*}
@@
 \end{align*}
-If the degree zero divisor is not a sum of points, one can temporarily pass to an extension, knowing that the result at the end will be defined over the ring we started with.
 We will only need $j_{\infty_+}(P)$ and $j_{\infty_-}(P)$ for affine points $P$; as the calculation of $j_{\infty_-}(P)$ is entirely similar to $j_{\infty_+}(P)$, we only focus on $j_{\infty_+}(P)$.
@@
 
+Now we move on to the Mumford representation.
+We present a way to go from the Mumford representation of a divisor to a Makdisi representation for the corresponding point on the Jacobian.
+This is based on private correspondence between Mascot and the author.
+\begin{proof}[Algorithm/proof]
+Let $(a,b)$ be the Mumford representation of a divisor $D = D(a,b)$.
+Let $\deg a = d \leq g$, and denote $D_{\text{aff}}$ for the affine part of $D$.
+Note that $E-D_0 = D$ for $E = D_0 - D_{\text{aff}} + d\infty_+$ an effective divisor, so $\Lcal(2D_0 - E) = \Lcal(D_0 - D)$ is a Makdisi representation for $[D]$.
+
+Of course, we can rewrite $\Lcal(D_0 -D)$ as 
+\[
+\Lcal((g+1)\infty_- + (g+1+d)\infty_+ - D_{\text{aff}}) = \Lcal(2D_0 - D_{\text{aff}} ) \cap \Lcal((g+1)\infty_- + (g+1+d)\infty_+).
+\]
+
+We first calculate $\Lcal(2D_0 - D_{\text{aff}})$. Note that \todo{Compute this, currently talking with Mascot about this.}
+
+For $\Lcal((g+1)\infty_- + (g+1+d)\infty_+)$, we first inductively calculate $W_n := \Lcal(2D_0 - n\infty_-)$.
+For $W_1$ we have a basis $1,x,\dots,x^{2g+1},y,xy,\dots,x^g y, x^{g+1}y+x^{2g+2}$, and for $n \geq 0$ we have by a simple use of Lemma 2.2 of \citep{makdisi04} that for $1 \leq n \leq g+1$ we have $W_{n} = \{s \in \Lcal(2D_0) \mid s\Lcal(2D_0) \in W_1 \cdot W_{n-1}\}$.
+This is a purely linear constraint, hence simple linear algebra allows us to calculate all $W_n$ for $n \leq g+1$.
+Finally, we have
+\[
+\Lcal((g+1)\infty_- + (g+1+d)\infty_+) = \{ s \in \Lcal((g+1+d)(\infty_+ + \infty_-)) \mid sx^{g+1-d} \in W_d).
+\] 
+Once again noting that we can write down an explicit basis for $\Lcal((g+1+d)(\infty_+ + \infty_-))$, this allows us to calculate $\Lcal((g+1)\infty_- + (g+1+d)\infty_+)$ and to finish the computation.
+\end{proof}
+
+\subsection{Parameters at $J$}
+\label{subs:paramj}
+Being able to calculate in the Jacobian, we can move on to the final ingredient for explicit computations: parameters at points of $J$.
+For any nice curve $C$ over $\Z$, smooth over $\Z_{(p)}$, with a $\Z$-point $b$, we have a birational map from $C^{(g)}$, the $g$-fold symmetric product of $C$, to $J$, given on points by sending $[(P_1,\dots,P_g)]$ to $[\sum P_i - gb]$.
+This map is \'etale at $[(P_1,\dots,P_g)]$ if $H^0(P_1 + \cdots + P_g)$ has dimension $1$ \todo{find a reference for this}, and if all $P_i$ are distinct, then the map $C^g \to C^{(g)}$ is \'etale at $P_1,\dots,P_g$ as well.
+Then finding parameters at $x := \sum P_i - gb$ just comes down to finding parameters at each of the $P_i$.
+In our case of a hyperellptic curve, this is just an easy computation.
+
+Tell about how $J(\Z_p)_x$ is now parametrised as the product of $C(\Z_p)_{P_i}$, \todo{what this means for mod $p^2$}
+
 Say something about how with just this map and Mascots code, one can already find the $\overline{\kappa^* f_i} $ and compute an upper bound for $C(\Z)_P$ using brute force.
 
-\subsection{Speeding up the calculations}
 Say something about how one express an element in $J(\Z/p^2\Z)_0$ on the basis in something like $O(g)$ hopefully (ignoring the time for adding,multiplying, et cetera in the Jacobian), identify $J(Z/p^2)_0$ with $F_p^g$ using $g$ generators of the ideal of the zero section of $J_{Z/p^2}$, then the group structure that $J$ induces on $F_p^g$ is the usual addition.
@@
 
-\subsection{An explicit example}
+\section{An explicit example}
 Treat the example in ExChabauty.gp.
 
-\section{The Poincare torsor}
-Define and cite theorems about the Poincare Torsor
-
-\section{Quadratic Chabauty using the Poincare torsor}
-Explain how to do Chabauty in the case $r < g + \rho - 1$, where $\rho$ is the N\'eron-Severirank.
-
-\section{Implementations of quadratic Chabauty and an explicit example}
-Explain something about implementing quadratic Chabauty.
+\section{Quadratic Chabauty}
+Maybe treat how the Poincare torsor fits into this context; perhaps give an overview?
+Not sure if I can say enough while keeping it interesting.
+I would like to give a simpler introduction to \citep{edixhoven20}, saying a few things about the similarities and differences with linear Chabauty.
+I am not going to go in much detail, and am not going to do an example.
 

### 2020-02-25 MS.tex
Added introduction

@@
-\documentclass{article}
+\documentclass[12pt]{article}
 
@@
 An important special case in algebraic geometry is that of curves.
-The behavior of the rational points of curves depends enormously on the \textit{genus} of the curve, a numerical invariant of a curve.
+The behavior of the rational points of curves depends enormously on the \textit{genus} $g$ of the curve $C$, a numerical invariant of a curve.
 For $g = 0$, there are either no or infinitely many solutions, and their behavior is well understood.
-Say something about the problem, Faltings, et cetera
+For $g = 1$, we get an elliptic curve, whose set of rational points forms an often infinite group.
 
-Say something about Chabauty's general idea
+In this thesis, we look only at the case $g > 1$, It turns out that there are always finitely many points; this result was originally conjectured by Mordell in 1922 and finally proven by Faltings in 1983.
 
-Mention Flynn, Coleman, Kim, Balakrishnan, Dogra, and other mentionable people. and their way of doing (quadratic) Chabauty
+Before it was proven, one of the major partial results was a theorem from Chabauty in 1941, phrased in terms of the rank $r$ of the group of rational points on the Jacobian $J$ of the curve, also called the Mordell-Weil rank.
+Chabauty proved, using $p$-adic methods, that if $r$ is strictly smaller than the genus $g$, then $C$ has finitely many points.
+Loosely said, this proof and all Chabauty related theorems, rely on choosing a prime $p$ for which $C$ has good reduction, and intersecting $J(\Z)$ with $C(\Z_p)$ inside the bigger $p$-adic manifold $J(\Z_p)$; by properties of $\Z_p$, the subgroup $J(\Z_p)$, generated by $r$ elements, lies within a $p$-adic manifold of dimension at most $r$, and $C(\Z_p)$ is a $1$-dimensional $p$-adic manifold, and hence their intersection is expected to be discrete and -- as $J(\Z_p)$ is compact -- finite.
 
-Say something about linear Chabauty geometric style.
+This was later made into an effective argument by Coleman in 1985.
+This was done by finding explicitly, as a power series, a differential form $\omega$ on $J_{\Z_p}$ whose Coleman integral vanishes on $J(\Z)$.
+Pulling $\omega$ back to $C_{\Z_p}$ and looking at the fibre of reduction to a single $\F_p$-point $P$, one can in certain cases give an upper bound for the number of points in $C(\Z)$ reducing to $P$ based only on finite-precision calculations of $\omega$.
 
-Say something about quadratic Chabauty geometric style.
+This Coleman-Chabauty method has been greatly generalised by Kim to so called non-abelian Chabauty.
+He interprets working in the Jacobian as dealing with the abelianised fundamental group of the curve $C$, and works with larger, non-abelian quotients of the fundamental group.
+Using quadratic Chabauty, a special case of non-abelian Chabauty, Balakrishnan, Dogra, M\"uller, Tuitman and Vonk famously calculated in May of 2019 all rational points of the ``cursed curve'', the modular curve $X_s(13)$.
+They use an endomorphism of the Jacobian, and do $p$-adic analysis on $p$-adic local height to accomplish this fact.
+\todo{Bas, is dit de goede samenvatting?
+Voornamelijk mijn vraag: is het nog steeds een specifiek geval van Coleman-Chabauty?}
 
-Say how much is borrowed from the article by Bas and Guido, but with a focus on the linear part, and more explanations.
-It is meant as a full guide to linear Chabauty, including both theoretical and practical components, focussing partly on explicit computations.
+Very recently, Edixhoven and Lido made available a preprint of their article ``Geometric quadratic Chabauty''.
+Their goal in this article is to make a more geometric approach to quadratic Chabauty, by working in a pullback $T$ of the Poincar\'e torsor of the Jacobian.
+They also abandon the Coleman method for Chabauty; instead they parametrise the map $T(\Z) \to T(\Z_p)$ with power series, and pull back equations for the curve along this map.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-\section{Linear Chabauty}
-\label{section:linchab}
+The purpose of this thesis is to make the work bij Edixhoven and Lido more accessible by applying geometric Chabauty to the linear case, i.e.
+when working with $J(\Z)$ and $J(\Z_p)$.
+In this thesis, we go into more detail of what is happening throughout the process, including both theoretical and practical components.
+We hope to provide the reader with a clear overview of geometric Chabauty, and a new way to do explicit computations.
+
+\subsection{Overview}
+We first present the context in which we will perform Chabauty.
 Let $p>2$ be a prime, and $C$ be a scheme over $\Z$, proper, flat, regular with $C$ smooth over $\Z_{(p)}$ and $C_\Q$ of dimension $1$ and geometrically connected, of genus $g \geq 1$ and with the Jacobian $J$ of $C_\Q$ having Mordell-Weil rank $r < g$.
@@
 
-We want to find an upper bound for the cardinality of $C(\Z)_P$
+We want to find an upper bound for the cardinality of $C(\Z)_P$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\section{Linear Chabauty}
+\label{section:linchab}
 

### 2020-02-27 MS.tex
Overview added and moved stuff

@@
 \usepackage{todonotes}
+\usepackage[all]{nowidow}
 
@@
 {\LARGE\bf 
-A geometric approach to linear and quadratic Chabauty
+A geometric approach to linear Chabauty
 }
@@
 He interprets working in the Jacobian as dealing with the abelianised fundamental group of the curve $C$, and works with larger, non-abelian quotients of the fundamental group.
-Using quadratic Chabauty, a special case of non-abelian Chabauty, Balakrishnan, Dogra, M\"uller, Tuitman and Vonk famously calculated in May of 2019 all rational points of the ``cursed curve'', the modular curve $X_s(13)$.
-They use an endomorphism of the Jacobian, and do $p$-adic analysis on $p$-adic local height to accomplish this fact.
+Using quadratic Chabauty, a special case of non-abelian Chabauty, Balakrishnan, Dogra, M\"uller, Tuitman and Vonk famously mcalculated in May of 2019 all rational points of the ``cursed curve'', the modular curve $X_s(13)$.
+They use an endomorphism of the Jacobian, and do $p$-adic analysis on $p$-adic local heights to make non-abelian Chabauty explicit.
 \todo{Bas, is dit de goede samenvatting?
@@
 Very recently, Edixhoven and Lido made available a preprint of their article ``Geometric quadratic Chabauty''.
-Their goal in this article is to make a more geometric approach to quadratic Chabauty, by working in a pullback $T$ of the Poincar\'e torsor of the Jacobian.
+Their goal in this article is to make a more geometric approach to effective quadratic Chabauty, by working in a pullback $T$ of the Poincar\'e torsor of the Jacobian.
 They also abandon the Coleman method for Chabauty; instead they parametrise the map $T(\Z) \to T(\Z_p)$ with power series, and pull back equations for the curve along this map.
@@
 \end{defn}
+\begin{exmp}
+If we have a projective variety $X$ over $\Z$, then $X(\Z)$ is in bijection with $X(\Q)$.
+The natural map $X(\Z) \to X(\F_p)$ reduces a point modulo $p$ and for $x \in X(\F_p)$, the set $X(\Z)_x$ consists of the $\Z$-points reducing to $x$.
+\end{exmp}
 
-We want to find an upper bound for the cardinality of $C(\Z)_P$.
+Geometric chabauty works by finding an upper bound for the cardinality of $C(\Z)_P$. For this, we use the following diagram.
+\[
+\begin{tikzcd}
+C(\Z)_P \arrow[d] \arrow[r, "a"] & J(\Z)_t \arrow[d] \\
+C(\Z_p)_P \arrow[r]              & J(\Z_p)_t        
+\end{tikzcd}
+\]
+where the two vertical maps are inclusions, and the two horizontal maps are subtraction of $b$.
+We will in fact compute upper bounds for the larger set $C(\Z_p)_P \cup \overline{J(\Z)_t}$, where $\overline{J(\Z)_t}$ is the closure of $J(\Z)_t$ in $J(\Z_p)_t$.
+
+In Section~\ref{section:smoothzppoints}, we treat the structure of $C(\Z_p)_P$ and $J(\Z_p)_t$; we will show that, after choosing parameters, they are canonically in bijection with respectively $\Z_p$ and $\Z_p^g$.
+We also discuss the resulting map $\Z_p \to \Z_p^g$.
+
+In Section~\ref{section:kappa} we further look at the map $J(\Z)_t \to J(\Z_p)_t$.
+This is a translation of the group morphism $J(\Z)_0 \to J(\Z_p)_0$ between kernels of reduction; it turns out that for our choice of $p$, the subgroup $J(\Z)_0$ is free of rank $r$.
+We study the properties of the resulting map $\Z^r \to \Z_p^g$, using the theory of formal groups to determine the group structure on $\Z_p^g$ induced by the bijection $J(\Z_p)_t \to \Z_p^g$.
+
+In Section~\ref{section:intersection}, we put all of this information together, culminating in several methods to compute upper bounds on $\left|C(\Z_p)_P \cup \overline{J(\Z)_t}\right|$ with finite precision calculations.
+
+These methods are not always guaranteed to prove finiteness of $C(\Z)_P$.
+In Section~\ref{section:remarks} we treat several possible complications and improvements, partially with explicit examples.
+We also look at the specific case of calculations modulo $p$, i.e.
+in $J(\Z/p^2\Z)_t$, in which the theory simplifies.
+\todo{Bas, wat vind je van het bestaan van dit hoofdstuk?}
+
+Next, in Section~\ref{section:explicit} we focus on how to perform these calculations happening in the Jacobian.
+Here, we use Makdisi's approach of representing a divisor by a subspace of a large Riemann-Roch space.
+We partially follow the article \citep{mascot2018} by Mascot, and also give an original algorithm for explicitly computing the map $C(\Z_p)_P \to J(\Z_p)_t$ in Makdisi's representation.
+
+We end with an explicit example in Section~\ref{section:example}, a genus $2$ curve whose Jacobian has Mordell-Weil rank $1$.
+We use both Magma and Pari/GP to do our calculations, and end up with a complete list of all rational points of the curve.
 
@@
 \newpage
-\section{Linear Chabauty}
-\label{section:linchab}
-
 % Say something about smooth schemes over Z_p, and their Z_p points
-\subsection{Points on a smooth scheme over \texorpdfstring{$\Z_p$}{Z\_p}}
-\label{subs:smoothzppoints}
+\section{Points on a smooth scheme over \texorpdfstring{$\Z_p$}{Z\_p}}
+\label{section:smoothzppoints}
 Let $X/\Z_p$ be a smooth scheme of relative dimension $d$, and let $x \in X(\F_p)$ be a point.
@@
 
-\subsection{From \texorpdfstring{$J(\Z)$}{J(Z)} to \texorpdfstring{$J(\Z_p)$}{J(Z\_p)}}
+\subsection{From \texorpdfstring{$C(\Z_p)$}{C(Z\_p)} to \texorpdfstring{$J(\Z_p)$}{J(Z\_p)}}
+\label{subsection:czptojzp}
+We know that $C(\Z_p)_P$ is in bijection with $\Z_p$, again with the bijection given by evaluating a parameter and dividing by $p$.
+The resulting function $\Z_p \to \Z_p^g$ is linear and non-constant modulo $p$, i.e.
+there are power series $f_1,\dots,f_{g-1} \in \Z_p\angle{z_1,...,z_g}$ such that the image of $C(\Z_p)_P$ is exactly given by $V(f_1,...,f_{g-1})$, and all $f_i$ are linear modulo $p$.
+Another way to think of this, is as $C(\Z/p^2\Z)_P$ being an affine line inside $J(\Z/p^2\Z)_t$.
+TODO: give proof.
+This uses the functoriality of smooth $\Z_p$-points reducing to a point.
+That $C(\Z/p^2\Z)_P$ is an affine line inside $J(\Z/p^2\Z)_t$ can also be seen more easily, using Lemma~\ref{lem:smoothpointsfunc}.
+% Say something about the f_i defining C(Z_p) in J(Z_p)
+
+\begin{rem}
+\label{rem:fislinear}
+We can pick our parameters right such that $C(\Z_p)_P \to J(\Z_p)_t$ is given by $\Z_p \to \Z_p^g$, mapping $\Z_p$ to the last coordinate.
+Then $f_1,\dots,f_{g-1}$ are just the other parameters at $t$, so they are linear.
+\end{rem}
+
+\section{From \texorpdfstring{$J(\Z)$}{J(Z)} to \texorpdfstring{$J(\Z_p)$}{J(Z\_p)}}
+\label{section:kappa}
 For $p > 2$, we know that the torsion of $J(\Z)$ injects into $J(\F_p)$, by Proposition 2.3 of \cite{pierre2000}.
@@
 By assumption, we also know $J(\Z)_t$ is in bijection with $J(\Z)_0$, with the bijection giving by translating with a lift of $t$.
-By Subsection \ref{subs:smoothzppoints} we know $J(\Z_p)_t$ is in bijection with $\Z_p^{g}$, with the bijection given by evaluating parameters and dividing by $p$.
+By Subsection \ref{section:smoothzppoints} we know $J(\Z_p)_t$ is in bijection with $\Z_p^{g}$, with the bijection given by evaluating parameters and dividing by $p$.
 Let $\kappa: \Z^r \to \Z_p^g$ be the map resulting from the inclusion $J(\Z)_t \to J(\Z_p)_t$.
@@
 
-\subsubsection{From group schemes to formal groups}
+\subsection{From group schemes to formal groups}
 We first recall the definition of a formal group. For this entire section, $R$ is a ring, and $x,y,z$ are vectors of variables.
@@
 
-\subsection{From \texorpdfstring{$C(\Z_p)$}{C(Z\_p)} to \texorpdfstring{$J(\Z_p)$}{J(Z\_p)}}
-\label{subsection:czptojzp}
-By Subsection \ref{subs:smoothzppoints}, we also know that $C(\Z_p)_P$ is in bijection with $\Z_p$, again with the bijection given by evaluating a parameter and dividing by $p$.
-The resulting function $\Z_p \to \Z_p^g$ is linear and non-constant modulo $p$, i.e.
-there are power series $f_1,\dots,f_{g-1} \in \Z_p\angle{z_1,...,z_g}$ such that the image of $C(\Z_p)_P$ is exactly given by $V(f_1,...,f_{g-1})$, and all $f_i$ are linear modulo $p$.
-Another way to think of this, is as $C(\Z/p^2\Z)_P$ being an affine line inside $J(\Z/p^2\Z)_t$.
-TODO: give proof.
-This uses the functoriality of smooth $\Z_p$-points reducing to a point.
-That $C(\Z/p^2\Z)_P$ is an affine line inside $J(\Z/p^2\Z)_t$ can also be seen more easily, using Lemma~\ref{lem:smoothpointsfunc}.
-% Say something about the f_i defining C(Z_p) in J(Z_p)
-
-\begin{rem}
-\label{rem:fislinear}
-We can pick our parameters right such that $C(\Z_p)_P \to J(\Z_p)_t$ is given by $\Z_p \to \Z_p^g$, mapping $\Z_p$ to the last coordinate.
-Then $f_1,\dots,f_{g-1}$ are just the other parameters at $t$, so they are linear.
-\end{rem}
-
-\subsection{Finding \texorpdfstring{$C(\Z)$}{C(Z)}}
+\section{Computing the intersection}
+\label{section:intersection}
 Clearly, as subsets of $J(\Z_p)_t$, we have the inclusion $C(\Z)_P \subset C(\Z_p)_P \cap \overline{J(\Z)_t}$.
@@
 \begin{thm}
-Let $C,J,p,P,t$ be as in Section~\ref{section:linchab}, let $\kappa$ be as in Theorem~\ref{thm:kappanice} and let $f_1,\cdots,f_{g-1}$ be as in Subsection~\ref{subsection:czptojzp}.
+Let $C,J,p,P,t$ be as in the overview, let $\kappa$ be as in Theorem~\ref{thm:kappanice} and let $f_1,\cdots,f_{g-1}$ be as in Subsection~\ref{subsection:czptojzp}.
 Define $\lambda_1 = \kappa^*f_1,\dots,\lambda_{g-1} = \kappa^*f_{g-1}$ to be the pullbacks along $\kappa$ of the $f_i$.
@@
 Then $f$ is uniquely determinable in $O(nm^{n+1})$ by its values on $S^n$.
-\end{lem} %complexity easily 
+\end{lem}
 \begin{proof}
@@
 \section{Complications and improvements}
+\label{section:remarks}
 \begin{itemize}
@@
 Preferably, find a source for this?
+Bas, do you have a reference for the complexity of such calculations?
 \end{itemize}
 
-\subsection{Calculations modulo \texorpdfstring{$p^2$}{p\^2}}
-Say something about how, for the right set of points $\{p_1,...,p_g\}$, the map $C^{g} \to J$ is etale at that set of points.
-Then say something about what that implies about $J(\Z_p)_0$ (equal to $\sum q_i - p_i$ where $q_i \in C(\Z_p)_{p_i}$), and $J(\Z/p^2\Z)_0$, which becomes isomorphic as vector spaces to $\F_p^g$, and how we can find $\kappa$ by expressing elements of $J(\Z)_0$ in that basis, and similarly $f_1,...,f_{g-1}$ by finding $P_1 - P_2$ in that basis for some $Q_1,Q_2 \in C(\Z/p^2\Z)_P$ not equal.
-
-An important part of this, is that there is a parametrisation $P_\mu, \mu \in \F_p$ of the points in $C(\Z/p^2\Z)_P$ such that $P_\mu + P_\nu = P_{\mu + \nu} + P_0$ as Cartier divisors.
-
-\section{Implementations of linear Chabauty and an explicit example}
-[TODO: make sure I clearly differentiate divisors and divisor classes]
+\section{Implementations of linear Chabauty}
 We now assume that $C$ is hyperelliptic, i.e. given by the degree $2g+2$ homogenisation of an equation of the form
@@
 
-We first calculate $\Lcal(2D_0 - D_{\text{aff}})$. Note that \todo{Compute this, currently talking with Mascot about this.}
+We first calculate $\Lcal(2D_0 - D_{\text{aff}})$. Both over $\Q_p$ and over $\F_p$ we have the equality
+\[
+\Lcal(2D_0 - D_{\text{aff}) = a(x)\Lcal((2g+2-d)(\infty_- + \infty_+)) + (y-b(x))\Lcal((g+1)(\infty_- + \infty_+))
+\]
+and then it should follow over $\Z_p$ so over $\Z/p^k\Z$. \todo{Give more details, currently talking with Mascot about this.}
 
@@
 This map is \'etale at $[(P_1,\dots,P_g)]$ if $H^0(P_1 + \cdots + P_g)$ has dimension $1$ \todo{find a reference for this}, and if all $P_i$ are distinct, then the map $C^g \to C^{(g)}$ is \'etale at $P_1,\dots,P_g$ as well.
-Then finding parameters at $x := \sum P_i - gb$ just comes down to finding parameters at each of the $P_i$.
-In our case of a hyperellptic curve, this is just an easy computation.
+Then finding parameters $t_1,\dots,t_g$ at $Q := [\sum_{i=1}^g P_i - gb]$ just comes down to finding parameters at each of the $P_i$.
+In our case of a hyperellptic curve, this is just an easy computation; for a point $(a,b)$ on the first affine chart, we can take $x-a$ if $b$ is non-zero and $y$ if $a$ is zero.
 
-Tell about how $J(\Z_p)_x$ is now parametrised as the product of $C(\Z_p)_{P_i}$, \todo{what this means for mod $p^2$}
+This now means $J(\Z_p)_Q$ is parametrised as the product of $C(\Z_p)_{P_i}$. In particular, we have a bijection
+\[
+\prod_{i=1}^g C(\Z/p^k\Z)_{P_i} \to J(\Z/p^k\Z)_{Q}.
+\] As we are able to explicitly compute this map using the Abel-Jacobi map, and we are able to test equality in $J(\Z/p^k\Z)$, we can compute the map $(t_1,\dots,t_g): J(\Z/p^k\Z)_Q \to (\Z/p^{k-1}\Z)^g$.
+
+\todo{what this means for mod $p^2$}
 
@@
 
-Say something about how one express an element in $J(\Z/p^2\Z)_0$ on the basis in something like $O(g)$ hopefully (ignoring the time for adding,multiplying, et cetera in the Jacobian), identify $J(Z/p^2)_0$ with $F_p^g$ using $g$ generators of the ideal of the zero section of $J_{Z/p^2}$, then the group structure that $J$ induces on $F_p^g$ is the usual addition.
+Say something about how one express an element in $J(\Z/p^2\Z)_0$ on the basis in something like $O(g)$ hopefully (ignoring the time for adding,multiplying, et cetera in the Jacobian), identify $J(\Z/p^2)_0$ with $\F_p^g$ using $g$ generators of the ideal of the zero section of $J_{\Z/p^2}$, then the group structure that $J$ induces on $\F_p^g$ is the usual addition.
 This is currently done using code from Mascot.
+
+\subsection{Complexity}
 Say what the final complexity is.
@@
 \section{An explicit example}
-Treat the example in ExChabauty.gp.
+\label{section:example}
+Treat the example in ExChabauty.gp. Bas, what do I do with my code? Do I just paste it in at the end, give a link to the github page, or just not give it all?
 
@@
 I am not going to go in much detail, and am not going to do an example.
+Bas, do you think this would be useful?
 

### 2020-02-27 MS.tex
Finished theoretical chapter

@@
 Another way to think of this, is as $C(\Z/p^2\Z)_P$ being an affine line inside $J(\Z/p^2\Z)_t$.
-TODO: give proof.
+\todo{give proof}.
 This uses the functoriality of smooth $\Z_p$-points reducing to a point.
@@
 \begin{thm}
+\label{thm:final}
 Let $C,J,p,P,t$ be as in the overview, let $\kappa$ be as in Theorem~\ref{thm:kappanice} and let $f_1,\cdots,f_{g-1}$ be as in Subsection~\ref{subsection:czptojzp}.
 Define $\lambda_1 = \kappa^*f_1,\dots,\lambda_{g-1} = \kappa^*f_{g-1}$ to be the pullbacks along $\kappa$ of the $f_i$.
-Then $\kappa$ induces a surjection from $Z(\lambda_1,\dots,\lambda_{g-1})$ to $C(\Z_p)_P \cap \overline{J(\Z)_t}$.
+Then $\kappa$ induces a surjection from $Z(\lambda_1,\dots,\lambda_{g-1}) \subset \Z_p^r$ to $C(\Z_p)_P \cap \overline{J(\Z)_t}$.
 \end{thm}
 
-The $\lambda_i$ are in general not computationally available, as they are power series, but we can approximate them modulo powers of $p$.
-For example, we know that the $\lambda_i$ are linear modulo $p$.
-And in particular, if $f_1,\dots,f_{g-1}$ are as in Remark~\ref{rem:fislinear}, then $\lambda_i = \kappa_i$ for $i \leq g-1$, so they are also of degree at most $m$ modulo $p^m$ for $m < p-1$.
-Knowing this, we can compute $\lambda_i$ modulo powers of $p$ by extrapolation, and the following lemma, an immediate consequence of Lagrange interpolation, tells us how.
-\begin{lem}
-\label{lem:interpolate}
-Let $R$ be a ring, and assume operations in $R$ are $O(1)$, $f \in R[x]$ with $x = (x_1,\dots,x_n)$ a polynomial of degree at most $m$, and $S$ a subset of $R$ with $S-S \subset \{0\} \cup R^*$ and $|S| > m$.
-Then $f$ is uniquely determinable in $O(nm^{n+1})$ by its values on $S^n$.
-\end{lem}
+Hence if we find an upper bound for the cardinality of $Z(\lambda_1,\dots,\lambda_{g-1})$, this is also an upper bound for $C(\Z_p)_P$.
+There are several, sometimes ad hoc, ways of proving finiteness.
+We let $A$ denote $\Z_p\angle{x_1,\dots,x_r}$ and $I$ the ideal generated by $\lambda_1,\dots,\lambda_{g-1}$.
+Noting that $Z(\lambda_1,\dots,\lambda_{g-1}) = \Hom_{\Z_p}(A/I,\Z_p)$, we can use the following theorem.
+
+\begin{prop}
+\label{prop:finedix}
+Let $\overline{A} = A/pA$ and $\overline{I} = I\overline{A}$. Assume $\overline{A}/\overline{I}$ is finite. Then ...% $A$ is the product $\prod_{m \in \MaxSpec(A)} A_m$ and $$\Hom(A/I,\Z_p)$
+\end{prop}
 \begin{proof}
-Both uniqueness and construction follow from the case with $n=1$; uniqueness from the fact that the ideals $\{(x-s) \mid s \in S\}$ are pairwise coprime, and the construction is Lagrange interpolation.
-The complexity follows easily from induction on $n$ and the formula for Lagrange interpolation.
+\todo{give exact statement and proof}
 \end{proof}
 
-Note that evaluating $\lambda_i$ at a point in $J(\Z)_t$ comes down to calculating the value of a parameter at that point. More about this can be found in Section~\ref{subs:paramj}
+To utilise this theorem, we only need to calculate the $\lambda_i$ modulo $p$. In our case, of all $\kappa_i$ and $f_i$ being linear modulo $p$, we get as special case the following corrollary.
+\begin{cor}
+\label{cor:finedixlinear}
+If the system of equations $\forall i: \lambda_i \equiv 0 \bmod p$ has respectively no or one solution, there is respectively none or at most one point in $C(\Z)_P$.
+\end{cor}
 
-[TODO: explain how to use these power series. Explain 4.12, $(I : p^\infty)$ and Newton polygons.]
-By Theorem 4.12 of Edixhoven-Lido, we just need to check whether $\overline{A}/\overline{I}$ is finite.
-As all $\overline{\kappa^* f_i}$ are linear, in fact, $\overline{A}/\overline{I}$ is always of the form $0$ (meaning no solutions) or $\F_p[w_1,...,w_s]$ for some $s \leq r$, and $s = 0$ iff the system of linear equations $\overline{\kappa^* f_i} = 0, i \in \{1,...,g-1\}$ has a unique solution.
-In general, we may hope an upper bound for $|C(\Z)_P|$ of $1$ if $r \leq g-1$.
+In general, even if $\overline{A}/\overline{I}$ is not finite, we see $\Hom(A/I,\Z_p)$ factors through $A/(I:p)$ where $(I:p) = \{x \in A \mid \exists k \in \Z_{\geq 0} p^kx \in A\}$.
+Then a higher precision calculation of the $\lambda_i$ can still lead to a succesfull application of Proposition~\ref{prop:finedix}.
+
+Another specific case is that of $r = 1$.
+In that case, we can use finite precision approximations of $\lambda_1$ to deduce information about its Newton polygon, and use that to bound the number of zeroes in $\Z_p$.
+We can even adapt this method if $r$ is bigger than $1$; sometimes it might be possible to use the implicit function theorem for powerseries, Lemma~\ref{lem:implicitfunction}, to write one of the variables as a power series in the other variables, and then substitute it in the other equations.
+
+\begin{exmp}
+If $r = g-1 = 2$ and $\lambda_1 \equiv px-py,\lambda_2 \equiv x+y+pxy \bmod p^2$, neither Proposition~\ref{prop:finedix} nor Newton polygons are instantly applicable.
+However, substituting $y = -x +px^2 \bmod p^2$ into the first equation gives $2p(x-x^2) = 0 \bmod p^2$, or $x-x^2 = 0\bmod p$.
+Now both Proposition~\ref{prop:finedix} and Newton polygons give an upper bound of $2$ for $C(\Z)_P$.
+\end{exmp}
 
@@
 \[
-\Lcal(2D_0 - D_{\text{aff}) = a(x)\Lcal((2g+2-d)(\infty_- + \infty_+)) + (y-b(x))\Lcal((g+1)(\infty_- + \infty_+))
+\Lcal(2D_0 - D_{\text{aff}}) = a(x)\Lcal((2g+2-d)(\infty_- + \infty_+)) + (y-b(x))\Lcal((g+1)(\infty_- + \infty_+))
 \]
@@
 In our case of a hyperellptic curve, this is just an easy computation; for a point $(a,b)$ on the first affine chart, we can take $x-a$ if $b$ is non-zero and $y$ if $a$ is zero.
+We can also compute the inverse of the map $C(\Z/p^k\Z)_{P_i} \to p\Z/p^k\Z$; this is just a simple exercise in Hensel lifting.
 
@@
 \prod_{i=1}^g C(\Z/p^k\Z)_{P_i} \to J(\Z/p^k\Z)_{Q}.
-\] As we are able to explicitly compute this map using the Abel-Jacobi map, and we are able to test equality in $J(\Z/p^k\Z)$, we can compute the map $(t_1,\dots,t_g): J(\Z/p^k\Z)_Q \to (\Z/p^{k-1}\Z)^g$.
+\] As we are able to explicitly compute this map using the Abel-Jacobi map, and we are able to test equality in $J(\Z/p^k\Z)$, we can compute the map $(t_1,\dots,t_g): J(\Z/p^k\Z)_Q \to (p\Z/p^{k}\Z)^g$ by first computing its inverse and storing all found values.
+
+\label{}
+The $\lambda_i$ from are in general not computationally available, as they are power series, but we can approximate them modulo powers of $p$.
+For example, we know that the $\lambda_i$ are linear modulo $p$.
+And in particular, if $f_1,\dots,f_{g-1}$ are as in Remark~\ref{rem:fislinear}, then $\lambda_i = \kappa_i$ for $i \leq g-1$, so they are also of degree at most $m$ modulo $p^m$ for $m < p-1$.
+Knowing this, we can compute $\lambda_i$ modulo powers of $p$ by extrapolation, and the following lemma, an immediate consequence of Lagrange interpolation, tells us how.
+\begin{lem}
+\label{lem:interpolate}
+Let $R$ be a ring, and assume operations in $R$ are $O(1)$, $f \in R[x]$ with $x = (x_1,\dots,x_n)$ a polynomial of degree at most $m$, and $S$ a subset of $R$ with $S-S \subset \{0\} \cup R^*$ and $|S| > m$.
+Then $f$ is uniquely determinable in $O(nm^{n+1})$ by its values on $S^n$.
+\end{lem}
+\begin{proof}
+Both uniqueness and construction follow from the case with $n=1$; uniqueness from the fact that the ideals $\{(x-s) \mid s \in S\}$ are pairwise coprime, and the construction is Lagrange interpolation.
+The complexity follows easily from induction on $n$ and the formula for Lagrange interpolation.
+\end{proof}
+
+Note that evaluating $\lambda_i$ at a point in $J(\Z)_t$ comes down to calculating the value of a parameter at that point. More about this can be found in Section~\ref{subs:paramj}
 

### 2020-04-14 MS.tex
Added last chapter

@@
 For $g = 0$, there are either no or infinitely many solutions, and their behavior is well understood.
-For $g = 1$, we get an elliptic curve, whose set of rational points forms an often infinite group.
+For $g = 1$, we get either no point or an elliptic curve, whose set of rational points forms an often infinite group.
 
-In this thesis, we look only at the case $g > 1$, It turns out that there are always finitely many points; this result was originally conjectured by Mordell in 1922 and finally proven by Faltings in 1983.
+In this thesis, we look only at the case $g > 1$, It turns out that there are always only finitely many points; this result was originally conjectured by Mordell in 1922 and finally proven by Faltings in 1983.
 
@@
 
-In Section~\ref{section:intersection}, we put all of this information together, culminating in several methods to compute upper bounds on $\left|C(\Z_p)_P \cup \overline{J(\Z)_t}\right|$ with finite precision calculations.
+In Section~\ref{section:intersection}, we put all of this information together, culminating in several methods to possibly compute upper bounds on $\left|C(\Z_p)_P \cup \overline{J(\Z)_t}\right|$ with finite precision calculations.
 
@@
 For putting up a nice framework to work in, we start with blowing up $X$ at $x$.
-%TODO: give proof and define $\Z_p\angle{z_1,...,z_r}$ as the $p$-adic completion of $\Z_p[z_1,...,z_r]$, i.e. powerseries which are polynomials modulo every power of $p$.
 
@@
 \begin{lem}
-\ref{lem:smoothpointfunc}
+\label{lem:smoothpointsfunc}
 Given two smooth schemes $X,Y$ over $\Z_p$ and two $\F_p$-points $x\in X(\F_p), y\in Y(\F_p)$, a map $f: Y \to X$ satisfying $f(y) = x$ gives rise to a morphism $\Tilde{Y}_y^p \to \Tilde{X}_x^p$.
@@
 \begin{proof}
-TODO: give proof.
+\todo{give proof}
 \end{proof}
@@
 It then turns out that there is additionally a free transitive $\F_p$-action on $X(\Z/p^2\Z)_0$.
-[TODO: maybe replace this by an action of the tangent space of $X_{\F_p}$ at $x$].
+\todo{maybe replace this by an action of the tangent space of $X_{\F_p}$ at $x$}.
 We can parametrise $X(\Z/p^2\Z)_0$ by $t = t_1 : X(\Z/p^2\Z)_0 \to p\Z/p^2\Z$; write $P_{\lambda}$ for the point with $t$-value $\lambda p$.
@@
 \end{exmp}
-[TODO: add text explaining the following lemma]
 Note there is no mention of an inverse, but the following lemma, a formal version of the implicit function theorem, tells us that the inverse follows automatically from the definitions.
@@
 for every finite $\Z_p$-algebra $A$ the set $\Hom_{\text{cont}}(\Hat{O}_{G,e},A)$ gets a group structure, functorially in $A$.
-By functoriality, this is the same [TODO: why exactly?] as an continuous coproduct $\mu: \Hat{O}_{G,e} \to \left(\Hat{O}_{G,e}\right)^{\Hat{\tensor} 2}$.
+By functoriality, this is the same [TODO: figure out why exactly?
+Probably just Yoneda] as an continuous coproduct $\mu: \Hat{O}_{G,e} \to \left(\Hat{O}_{G,e}\right)^{\Hat{\tensor} 2}$.
 After choosing an isomorphism between $\Hat{O}_{G,e}$ and $\Z_p[[x_1,\dots,x_d]]$, let $F_j \in \Z_p[[x,y]]$ denote $\mu(x_i)$.
@@
 \begin{exmp}
-\label{exmp:gmtoformal} %TODO: nicely LaTeX Example bla, continued
+\label{exmp:gmtoformal} \todo{nicely LaTeX Example bla, continued}
 Take $G = \G_m$ over $\Z_p$, i.e.
@@
 By the first result, $\log$ has an inverse which we will call $\exp$, also given by powerseries in $(\Q\tensor R)[[x]])$, and also satisfying $\exp(x) = x \mod (x)^2$.
-\begin{exmp} %TODO: nicely LaTeX Example bla, continued
+\begin{exmp} \todo{nicely LaTeX Example bla, continued}
 Taking $F$ the multiplicative group as in Example~\ref{exmp:gmformalgroup}, Proposition~1.1 of \citep{honda70} gives us $\omega = \frac{1}{x+1}dx$; as a power series this is $\sum_{j \geq 0} (-x)^j$.
@@
 This finishes the proof.
-[TODO: This is clearly a Hensel like proof, and I would prefer to just outright use Hensels lemma in some way.
-Is this doable?
+\todo{TODO This is clearly a Hensel like proof, and I would prefer to just outright use Hensels lemma in some way}.
+[Is this doable?
 I think so...
@@
 \section{Complications and improvements}
-\label{section:remarks}
+\label{section:remarks} \todo{Write everything}
 \begin{itemize} 
@@
 Bas, do you have a reference for the complexity of such calculations?
+\item Fun case: if $J$ splits up to isogeny as the product of an elliptic curve and an abelian surface of Mordell-Weil rank respectively $2$ and $1$, then we only need two elements of $J(\Z)_0$ to generate $\overline{J(\Z)_0}$ I think.
+\item Multivatiate generalisation of Newton Polygons: Tropical stuff by Rabinoff, Park, Mixed volume calculations to bound number of zeroes. Katz-Rabinoff-ZB.
 \end{itemize}
@@
 \section{Implementations of linear Chabauty}
+\label{section:explicit}
 We now assume that $C$ is hyperelliptic, i.e. given by the degree $2g+2$ homogenisation of an equation of the form
@@
 \subsection{Makdisis algorithms}
-Say something about how Makdisis algorithms work (i.e., give an introduction to the terminology) \cite{makdisi2004}.
+Say something about how Makdisis algorithms work (i.e., give an introduction to the terminology) \cite{makdisi04}.
 
@@
 
-\begin{proof}[Proof of Proposition \ref{prop:abeljacobia}]
+\begin{proof}[Proof of Proposition \ref{prop:abeljacobi}]
 First note that by Riemann-Roch, the dimension of $\Lcal(D_0)$ is $g + 3$, and we also have by the proof of the previous lemma that $1,x,\dots,x^{g+1},y$ all lie in $\Lcal(D_0)$ and hence form a basis, so we can indeed find $B$ as in line~\ref{alg:abeljacobi:basisLD0}.
@@
 \] As we are able to explicitly compute this map using the Abel-Jacobi map, and we are able to test equality in $J(\Z/p^k\Z)$, we can compute the map $(t_1,\dots,t_g): J(\Z/p^k\Z)_Q \to (p\Z/p^{k}\Z)^g$ by first computing its inverse and storing all found values.
+This gives an algorithm for computing this map that consists of $O(p^{(k-1)g})$ operations in the Jacobian.
 
-\label{}
+\todo{Explain how this can be improved in complexity}
+
+\subsection{Interpolating polynomials}
+\label{subs:interpolate}
 The $\lambda_i$ from are in general not computationally available, as they are power series, but we can approximate them modulo powers of $p$.
@@
 Then $f$ is uniquely determinable in $O(nm^{n+1})$ by its values on $S^n$.
+\todo{There is a better complexity algorithm I think, at least clearly so for $m=1$}
 \end{lem}
@@
 
-Note that evaluating $\lambda_i$ at a point in $J(\Z)_t$ comes down to calculating the value of a parameter at that point. More about this can be found in Section~\ref{subs:paramj}
-
-\todo{what this means for mod $p^2$}
-
-Say something about how with just this map and Mascots code, one can already find the $\overline{\kappa^* f_i} $ and compute an upper bound for $C(\Z)_P$ using brute force.
-
-Say something about how one express an element in $J(\Z/p^2\Z)_0$ on the basis in something like $O(g)$ hopefully (ignoring the time for adding,multiplying, et cetera in the Jacobian), identify $J(\Z/p^2)_0$ with $\F_p^g$ using $g$ generators of the ideal of the zero section of $J_{\Z/p^2}$, then the group structure that $J$ induces on $\F_p^g$ is the usual addition.
-This is currently done using code from Mascot.
+Note that evaluating $\lambda_i$ at a point in $J(\Z)_t$ comes down to calculating the value of a parameter at that point, and this is something we can do.
+That means we can explicitly compute $\lambda_i$ modulo $p^m$ for $m < p-1$.
+Using Proposition~\ref{prop:finedix} or another way, we can hope to find an upper bound on the number of common zeroes of the $\lambda_i$, and hence an upper bound on $C(\Z)_P$
 
 \subsection{Complexity}
-Say what the final complexity is.
+\todo{Refer back to complexity of calculations on the Jacobian ($J(\Z)$ and so on)}
+
+\todo{Find complexity of operations in the Jacobian performed by Mascots code}
 
@@
 \label{section:example}
-Treat the example in ExChabauty.gp. Bas, what do I do with my code? Do I just paste it in at the end, give a link to the github page, or just not give it all?
+We treat the hyperelliptic curve $C$ with first affine chart given by
+\[
+y^2 = f(x) = x^6+ 8x^5+ 22x^4+ 22x^3+ 5x^2+ 6x+ 1.
+\]
+We denote the standard involution on this curve by $\sigma$.
+It has six known rational points $\infty_+,\infty_- = \sigma(\infty_+)$ and $\theta = (0,1),\sigma(\theta),\eta=(-3,1),\sigma(\eta)$.
+We take $p = 5$.
+It turns out that $C(\F_5)$ has seven points; the reductions of the rational points, and $(1,0)$.
+Again taking the map $C \to J$ to be subtraction of $\infty_+$ on points, all seven points in $C(\F_5)$ lie in the image of $J(\Z)$.
+
+We will first show there is at most one point in the residue disc of $\theta$. \todo{Add computations}
+
+Similarly, it follows that all points in $C(\F_5)$ lift to at most one $\Z$-point.
+Noting that the group generated by $\sigma$ acts on $C(\Z)$ and has no fixed points, this means $|C(\Z)| \leq 6$ so our list of rational points is complete.
+
+Bas, what do I do with my code? Do I just paste it in at the end, give a link to the github page, or just not give it all?
 
 \section{Quadratic Chabauty}
+In this section we attempt to give an introduction to the article~\ref{edixhoven20} aimed to introduce all the players in Chabauty at a slightly slower pace.
+We will omit any proofs.For further reading, see for example \ref{hashimoto20}, an in progress cartoon guide to the article by Edixhoven-Lido.
+
+% Explain all diagrams over Q
+We start with explaining the idea over $\Q$; we let $C_\Q$ be a projective, smooth curve over $\Q$ of genus at least $2$, we let $J_\Q$ be its Jacobian.
+We again assume the existence of a rational point $b \in C(\Q)$, and use it to construct an embedding $j_b : C_\Q \to J_\Q$.
+We wish to set up a similar situation to classic Chabauty, and for that we introduce the Poincar\'e line bundle and Poincar\'e torsor.
+For this we need $J^\wedge$, the dual of $J$.
+This dual parametrised degree 0 line bundles on $J$, and hence we get a universal degree 0 line bundle $P$ on $J \times J^\wedge$, called the Poincar\'e line bundle $P$, which also satisfies that both $P_{0\times J^\wedge}$ and $P_{J \times 0\}$ are trivial.
+
+\begin{example}
+If $C$ is an elliptic curve then, identifying $C,J$ and $J^{\wedge}$, we get $P = O(\Delta-\[0\} \times E - E \times \{0\})$, indeed with the fibres $P|_{c \times E} \cong O(c-0)$ being exactly the degree $0$ line bundles on $C$ up to isomorphism.
+\end{example}
+
+The object we will be working with is the Poincar\'e torsor, the $\G_m$ torsor over $J \times J^\wedge$ defined by \[
+P^\times = \text{Isom}_{J_\Q \times J^\wedge_\Q}(O_{J_\Q \times J^\wedge_\Q},P_\Q);
+\] 
+we can also describe this in terms of its functor of points; for any scheme $S$ over $J_\Q \times J^\wedge_\Q$, we have that $P^\times_\Q(S)$ is the set of isomorphisms betweeen $O_S$ and $(P_\Q)_S$, with a free, transitive action of $O_S(S)^\times$, i.e.
+a torsor of $O_S(S)^\times$ in the traditional group-theoretic sense (note that this torsor can be empty).
+
+I don't want to explain the biextension structure. \todo{Bas, do you agree?}
+
+Instead of doing Chabauty in this Poincar\'e torsor, we will look at a pullback of this torsor to a $\G_m$-torsor over $J_\Q$.
+Our first attempt is pulling back along the map $J_\Q$ to $J_\Q \times J^\wedge_\Q$ given as $(\id,\tr_c \circ f)$ where $f: J_\Q \to J^\wedge_\Q$ is a morphism of group schemes.
+We denote the pullback of $P^\times_\Q$ along this map by $T_\Q$, a $\G_m$-torsor over $J_\Q$.
+This $T$ has dimension $g+1$.
+The general idea of geometric quadratic Chabauty, is to work with the following diagram
+\begin{tikzcd} % https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBoBGAXVJADcBDAGwFcYkQBhAfQB0eBFEAF9S6TLnyEU5CtTpNW7AFK8Bw0SAzY8BIgCZZNBizaIQKvvwAEfPAFt4VpQD0+AdxhQA5jFWCRYtqS+qTEcsaKZgAKrjz28OqBErrSoeEKpiAAKsJynj4IKKAAZgBOEHZIZCA4EEgALEYZ7HxZWIywwABWXABGQokgZRVVNLVIMvIm7D29g8OViJPjiAZTkSAAFHxYUKS2pVwAxjY8R1ilJ8UAlPPli401dUsBQ-cNY88AzK8LSF+fJBrRj0XowRhRcQ6KQgRgwYo4XJCIA
+                                                & T \arrow[d] \arrow[r]                   & P^\times \arrow[d]      \\
+C_\Q \arrow[ru, "\Tilde{j_b}"] \arrow[r, "j_b"] & J_\Q \arrow[r, "{(\id,\tr_c \circ f)}"] & J_\Q \times J^\wedge_\Q
+\end{tikzcd}
+where $\Tilde{j_b}$ is a lift of $j_b$.
+This lift will only exist if $j_b^* T$ is a trivial $\G_m$-torsor over $C$; for that, it turns out that we want $f$ to be an element of $\Hom^+(J_\Q,J^\wedge_\Q)$, the group of self dual homomorphism, of trace 0 (where this trace comes from identification with the N\'eron-Severi group); if we do that, it turns out that $j_b^* T$ will correspond to a degree $0$ line bundle on $C_\Q$, and we only need to translate by a constant to make $j_b^* T$ trivial.
+
+If $f$ itself is already trivial, then $T$ is trivial and this will give no further information, and in general that is the best we can do, as generically, the rank of $\Hom^+(J_\Q,J^\wedge_\Q)$, also called the N\'eron-Severi rank $\rho$, is $1$.\todo{This is true, right?
+Can't find reference} But in many interesting cases, this rank is non-zero.
+A family of examples is given by modular curves, where the Hecke algebra acts on $\Hom^+(J_\Q,J^\wedge_\Q)$, in which case the N\'eron-Severi rank turns out to be equal to the genus.
+We can then pick a basis $f_1,\dots,f_{\rho-1}$ of the trace $0$ subgroup of $\Hom^+(J_\Q,J^\wedge_\Q)$, and take the product of all the resulting pullbacks over $J$, to get a $g+\rho-1$ dimensional scheme over $J_\Q$ that admits a morphism from $C_\Q$.
+
+For ease of exposition, we will look at the case $\rho \geq 2$ and use a single, non-zero, trace $0$ morphism $f \in \Hom^+(J_\Q,J^\wedge_\Q)$.
+We then would like to intersect the rational points of $T_\Q$ with the $p$-adic points of $C_\Q$, mapped to $T_\Q$ under $\tilde{j_b}$, inside the $p$-adic points of $T$.
+As in the case of classic Chabauty, one can conclude that the $p$-adic points of $T$ form a $p$-adic manifold of dimension $g+1$, but there is a problem with the rational points of $T_\Q$; these are in bijection with $\G_m(\Q) \times J_\Q(\Q)$.
+The latter is a finitely generated group of rank $r$, the Mordell-Weil rank, but the former is an infinitely generated group, and hence we cannot easily upper bound the dimension of $\overline{T(\Q)}$ inside $T(\Q_p)$ \todo{Check that there is a underscore-Q everywhere}
+
+% Spread out over Z, explain general process and some difficulties
+To combat this problem, the crucial insight is that while $\Q^\times$ is infinitely generated, $\Z^\times$ is finite, so we set everything to work over $\Z$ instead of over $\Q$.
+Our curve is now a surface $C$, of relative dimension $1$ over $\Z$, proper, flat and regular with generic fiber $C_\Q$.
+We cannot expect $C$ to be smooth over $\Z$, we only ask that $C$ is smooth over $\Z[1/n]$ for some squarefree $n$ consisting of bad primes.
+Hence if we build up the theory correctly, we get that as sets, $T(\Z) = \{\pm1\} \times J(\Q)$, which we might expect to parametrise with $\Z^r$ in some nice way.
+It turns out that this is indeed possible, when restricted to residue discs.
+In sections 4 and 5 of the Edixhoven-Lido paper, they give a rather explicit parametrisation in terms of the structure of $P^\times$.
+
+For
+% Computations, and section 7 of the article (line bundles on C x C)
+
 Maybe treat how the Poincare torsor fits into this context; perhaps give an overview?

### 2020-05-14 MS.tex
Worked through all of Bas's comments

@@
 \newcommand{\entier}[1]{\left\lfloor #1 \right\rfloor}
+\newcommand{\A}{\mathbb{A}}
 \newcommand{\N}{\mathbb{N}}
@@
 \DeclareMathOperator{\im}{im}
+\DeclareMathOperator{\id}{id}
+\DeclareMathOperator{\tr}{tr}
+\DeclareMathOperator{\sm}{sm}
+\DeclareMathOperator{\pr}{pr}
+\DeclareMathOperator{\diag}{diag}
 \DeclareMathOperator{\Spec}{Spec}
+\DeclareMathOperator{\MaxSpec}{MaxSpec}
 \DeclareMathOperator{\Spf}{Spf}
@@
 \DeclareMathOperator{\S}{S}
-\DeclareMathOperator{\A}{A}
 \let\div\undefined
@@
 
-Before it was proven, one of the major partial results was a theorem from Chabauty in 1941, phrased in terms of the rank $r$ of the group of rational points on the Jacobian $J$ of the curve, also called the Mordell-Weil rank.
-Chabauty proved, using $p$-adic methods, that if $r$ is strictly smaller than the genus $g$, then $C$ has finitely many points.
+Before it was proven, one of the major partial results was a theorem from Chabauty in 1941, phrased in terms of the rank $r$ of the group of rational points on the Jacobian $J$ of the curve, also called the Mordell-Weil rank, which is finite by the Mordell-Weil theorem.
+Chabauty proved, using $p$-adic methods, that if $r$ is strictly smaller than the genus $g$, then $C$ has only finitely many points.
 Loosely said, this proof and all Chabauty related theorems, rely on choosing a prime $p$ for which $C$ has good reduction, and intersecting $J(\Z)$ with $C(\Z_p)$ inside the bigger $p$-adic manifold $J(\Z_p)$; by properties of $\Z_p$, the subgroup $J(\Z_p)$, generated by $r$ elements, lies within a $p$-adic manifold of dimension at most $r$, and $C(\Z_p)$ is a $1$-dimensional $p$-adic manifold, and hence their intersection is expected to be discrete and -- as $J(\Z_p)$ is compact -- finite.
@@
 Pulling $\omega$ back to $C_{\Z_p}$ and looking at the fibre of reduction to a single $\F_p$-point $P$, one can in certain cases give an upper bound for the number of points in $C(\Z)$ reducing to $P$ based only on finite-precision calculations of $\omega$.
+Most well known is the generic upper bound $|C(\Q)| \leq |C(\F_p)| + 2g-2$ under the conditions $r < g, p > 2g$, as explained in the introductory article \citep{poonen12}.
 
@@
 He interprets working in the Jacobian as dealing with the abelianised fundamental group of the curve $C$, and works with larger, non-abelian quotients of the fundamental group.
-Using quadratic Chabauty, a special case of non-abelian Chabauty, Balakrishnan, Dogra, M\"uller, Tuitman and Vonk famously mcalculated in May of 2019 all rational points of the ``cursed curve'', the modular curve $X_s(13)$.
-They use an endomorphism of the Jacobian, and do $p$-adic analysis on $p$-adic local heights to make non-abelian Chabauty explicit.
-\todo{Bas, is dit de goede samenvatting?
-Voornamelijk mijn vraag: is het nog steeds een specifiek geval van Coleman-Chabauty?}
+Using quadratic Chabauty, the simplest case of non-abelian Chabauty, Balakrishnan, Dogra, M\"uller, Tuitman and Vonk famously calculated in May of 2019 all rational points of the ``cursed curve'', the modular curve $X_s^+(13)$.
+They use an endomorphism of the Jacobian, and do $p$-adic analysis on $p$-adic local heights to make quadratic Chabauty explicit.
 
-Very recently, Edixhoven and Lido made available a preprint of their article ``Geometric quadratic Chabauty''.
+Very recently, Edixhoven and Lido made available a preprint of their article ``Geometric quadratic Chabauty'' \citep{edixhoven20}.
 Their goal in this article is to make a more geometric approach to effective quadratic Chabauty, by working in a pullback $T$ of the Poincar\'e torsor of the Jacobian.
-They also abandon the Coleman method for Chabauty; instead they parametrise the map $T(\Z) \to T(\Z_p)$ with power series, and pull back equations for the curve along this map.
+They also abandon the Coleman method for Chabauty; instead they parametrise the map $T(\Z) \to T(\Z_p)$ with power series, and pull back equations for the curve inside $T(\Z_p)$ along this map.
 
-The purpose of this thesis is to make the work bij Edixhoven and Lido more accessible by applying geometric Chabauty to the linear case, i.e.
+The purpose of this thesis is to make the work by Edixhoven and Lido more accessible by applying geometric Chabauty to the linear case, i.e.
 when working with $J(\Z)$ and $J(\Z_p)$.
 In this thesis, we go into more detail of what is happening throughout the process, including both theoretical and practical components.
-We hope to provide the reader with a clear overview of geometric Chabauty, and a new way to do explicit computations.
+This new method of applying Chabauty leads to, when working modulo $p$, a conditional upper bound $|C(\Q)| \leq |C(\F_p)|$, as obtained in Proposition~\ref{prop:linchabauty}.
+This upper bound compares favorably with classical Coleman-Chabauty, but unlike classical Coleman-Chabauty, we cannot say in general when the conditions of these propositions hold.
+Heuristics show that generally trying multiple primes $p$ of good reduction will yield good results, and if $r < g-1$ the conditions hold for most primes.
+The methods used to obtain Proposition~\ref{prop:linchabauty} are also amenable to higher precision calculations.
+We also give a hyperelliptic example with $r = 1, g = 2$, where the bound from Proposition~\ref{lin:chabauty} indeed holds.
 
@@
 We first present the context in which we will perform Chabauty.
-Let $p>2$ be a prime, and $C$ be a scheme over $\Z$, proper, flat, regular with $C$ smooth over $\Z_{(p)}$ and $C_\Q$ of dimension $1$ and geometrically connected, of genus $g \geq 1$ and with the Jacobian $J$ of $C_\Q$ having Mordell-Weil rank $r < g$.
+Let $p>2$ be a prime, and $C$ be a scheme over $\Z$, proper, flat, regular with $C$ smooth over $\Z_{(p)}$ and $C_\Q$ of dimension $1$ and geometrically connected, of genus $g \geq 1$ and with the Jacobian $J$ of $C$ having Mordell-Weil rank $r < g$.
 Assume we have a $\Q$-point $b$ in $C$, or equivalently a $\Z$-point.
-We view $C_\Q$ as a subscheme of $J$, using the map $Q \mapsto Q - b$ on points.
+We view $C$ as a subscheme of $J$, using the map $Q \mapsto Q - b$ on points.
 Let $P \in C(\F_p)$ be a point such that $t := P - b \in J(\F_p)$ lies in the image of $J(\Z)$.
@@
 where the two vertical maps are inclusions, and the two horizontal maps are subtraction of $b$.
-We will in fact compute upper bounds for the larger set $C(\Z_p)_P \cup \overline{J(\Z)_t}$, where $\overline{J(\Z)_t}$ is the closure of $J(\Z)_t$ in $J(\Z_p)_t$.
+We will in fact compute upper bounds for the larger set $C(\Z_p)_P \cap \overline{J(\Z)_t}$, where $\overline{J(\Z)_t}$ is the closure of $J(\Z)_t$ in $J(\Z_p)_t$.
 
@@
 
-In Section~\ref{section:intersection}, we put all of this information together, culminating in several methods to possibly compute upper bounds on $\left|C(\Z_p)_P \cup \overline{J(\Z)_t}\right|$ with finite precision calculations.
+In Section~\ref{section:intersection}, we put all of this information together, culminating in several methods to possibly compute upper bounds on $\left|C(\Z_p)_P \cap \overline{J(\Z)_t}\right|$ with finite precision calculations.
 
@@
 
-We end with an explicit example in Section~\ref{section:example}, a genus $2$ curve whose Jacobian has Mordell-Weil rank $1$.
+We end our discussion of linear geometric Chabauty with an explicit example in Section~\ref{section:example}, a genus $2$ curve whose Jacobian has Mordell-Weil rank $1$.
 We use both Magma and Pari/GP to do our calculations, and end up with a complete list of all rational points of the curve.
+
+Finally, we provide an introduction to geometric quadratic Chabauty in Section~\ref{section:quadratic}.
+Here, we aim to introduce all the different objects relevant to geometric quadratic Chabauty; we explain why we have to work over $\Z$ instead of over $\Q$ to make geometric quadratic Chabauty make sense; and we explain some of the problems and solutions that working over $\Z$ gives rise to.
 
@@
 \begin{proof}
-As $t$ is locally of finite type, by (IV,17.6.3) of \cite{ega} we have an isomorphism between the $p$-adic completion $O(\Tilde{X}_x^p)^{\wedge p}$ and the completion $\Z_p\angle{\Tilde{x_1},\dots, \Tilde{x_d}}$ of $\Z_p[\Tilde{x_1},...,\Tilde{x_d}]$, with the latter completion being the ring of convergent power series, i.e.
+As $t$ is locally of finite type, by (IV,17.6.3) of \cite{ega} we have an isomorphism between the $p$-adic completion $O(\Tilde{X}_x^p)^{\wedge p}$ and the completion $\Z_p\angle{\Tilde{x_1},\dots, \Tilde{x_d}}$ of $\Z_p[\Tilde{x_1},\dots,\Tilde{x_d}]$, with the latter completion being the ring of convergent power series, i.e.
 \[
-\Z_p\angle{\Tilde{x_1},\dots, \Tilde{x_d}} = \left\{f \in \Z_p[[\Tilde{x_1},\dots,\Tilde{x_d}]] \mid \forall n \geq 0, f + (p^n) \in \Z/p^n\Z[\Tilde{x_1},\dots,\tilde{x_d}] + (p^n) \right\}.
+\Z_p\angle{\Tilde{x_1},\dots, \Tilde{x_d}} = \left\{f \in \Z_p[[\Tilde{x_1},\dots,\Tilde{x_d}]] \mid \forall n \geq 0, f \in \Z[\Tilde{x_1},\dots,\tilde{x_d}] + (p^n) \right\}.
 \]
-By the universal property of completions, as $t$ induces the isomorphism between completion, $t$ also induces a bijection $$\Hom(O(X(\Z_p)_x), \Z_p) \to \Hom(O(X(\Z_p)_x)^{\wedge p}, \Z_p) = \Hom(\Z_p\angle{\Tilde{x_1},\dots,\Tilde{x_d}},\Z_p) = \Z_p^d.$$ Following all the bijections, we indeed get the bijection we wanted.
+By the universal property of completions, as $t$ induces the isomorphism between completions, $t$ also induces a bijection $$\Hom(O(\Tilde{X}_x^p), \Z_p) \to \Hom(\Z_p\angle{\Tilde{x_1},\dots,\Tilde{x_d}},\Z_p) = \Z_p^d.$$ Following all the bijections, we indeed get the bijection we wanted.
 \end{proof}
 
-Note that this construction is functorial, as in the following lemma:
-\begin{lem}
-\label{lem:smoothpointsfunc}
-Given two smooth schemes $X,Y$ over $\Z_p$ and two $\F_p$-points $x\in X(\F_p), y\in Y(\F_p)$, a map $f: Y \to X$ satisfying $f(y) = x$ gives rise to a morphism $\Tilde{Y}_y^p \to \Tilde{X}_x^p$.
-\end{lem}
-\begin{proof}
-\todo{give proof}
-\end{proof}
+\begin{rem}
+\label{rem:smoothpointsfunc}
+Note that this construction is functorial, as in the following sense: given two smooth schemes $X,Y$ over $\Z_p$ and two $\F_p$-points $x\in X(\F_p), y\in Y(\F_p)$, a map $f: Y \to X$ satisfying $f(y) = x$ gives rise to a morphism $\Tilde{Y}_y^p \to \Tilde{X}_x^p$.
+This is a direct consequence of II.7.15 of \citep{hartshorne}.
+\end{rem}
 
-[TODO: add that the map $\Tilde{Y}_y^p(\Z_p) \to \Tilde{X}_x^p(\Z_p)$ is, after choosing parameters, given by convergent power series; are these in general linear modulo $p$?
-And what happens modulo higher powers?]
-
-Finally, we look at the specific case of $X$ being of relative dimension $1$ over $\Z_p$.
-It then turns out that there is additionally a free transitive $\F_p$-action on $X(\Z/p^2\Z)_0$.
-\todo{maybe replace this by an action of the tangent space of $X_{\F_p}$ at $x$}.
-We can parametrise $X(\Z/p^2\Z)_0$ by $t = t_1 : X(\Z/p^2\Z)_0 \to p\Z/p^2\Z$; write $P_{\lambda}$ for the point with $t$-value $\lambda p$.
+\begin{rem}
+\label{rem:cartierlinear}
+We look at the specific case of $X$ being of relative dimension $1$ over $\Z_p$.
+It then turns out that there is additionally a free transitive $\F_p$-action on $X(\Z/p^2\Z)_x$, in the following way.
+We can parametrise $X(\Z/p^2\Z)_x$ by $t = t_1 : X(\Z/p^2\Z)_x \to p\Z/p^2\Z$; write $P_{\lambda}$ for the point with $t$-value $\lambda p$.
 Then as Cartier divisor, the point $P_{\lambda}$ is defined by $t - \lambda p \in O(X_{\Z/p^2\Z})_x$, so $P_{\lambda} + P_{\mu}$ is defined by $(t-\lambda p)(t-\mu p) = t^2 - (\lambda + \mu)tp$, which defines the same Cartier divisor as $P_{\lambda'} + P_{\mu'}$ if and only if $\lambda + \mu = \lambda' + \mu'$.
-So as a Cartier divisor, $P_{\lambda} + P_{\mu}$ is in fact equal to $P_{\lambda'} + P_{\mu'}$.
+In that case, as a Cartier divisor, $P_{\lambda} + P_{\mu}$ is in fact equal to $P_{\lambda'} + P_{\mu'}$.
+\end{rem}
 
@@
 We know that $C(\Z_p)_P$ is in bijection with $\Z_p$, again with the bijection given by evaluating a parameter and dividing by $p$.
-The resulting function $\Z_p \to \Z_p^g$ is linear and non-constant modulo $p$, i.e.
-there are power series $f_1,\dots,f_{g-1} \in \Z_p\angle{z_1,...,z_g}$ such that the image of $C(\Z_p)_P$ is exactly given by $V(f_1,...,f_{g-1})$, and all $f_i$ are linear modulo $p$.
-Another way to think of this, is as $C(\Z/p^2\Z)_P$ being an affine line inside $J(\Z/p^2\Z)_t$.
-\todo{give proof}.
-This uses the functoriality of smooth $\Z_p$-points reducing to a point.
-That $C(\Z/p^2\Z)_P$ is an affine line inside $J(\Z/p^2\Z)_t$ can also be seen more easily, using Lemma~\ref{lem:smoothpointsfunc}.
-% Say something about the f_i defining C(Z_p) in J(Z_p)
+The resulting function $\Z_p \to \Z_p^g$ is linear modulo $p$, i.e.
+by using that $\Z\angle{z_1,\dots,z_g}$ is $p$-adically complete there are power series $f_1,\dots,f_{g-1} \in \Z_p\angle{z_1,\dots,z_g}$ such that the image of $C(\Z_p)_P$ is exactly given by $V(f_1,\dots,f_{g-1})$, and all $f_i$ are linear modulo $p$ as a consequence of \ref{rem:cartierlinear}.Another way to think of this, is as $C(\Z/p^2\Z)_P$ being an affine line inside $J(\Z/p^2\Z)_t$.
+That $C(\Z/p^2\Z)_P$ is an affine line inside $J(\Z/p^2\Z)_t$ can also be seen more easily, using Remark~\ref{rem:smoothpointsfunc}.
 
@@
 Then $f_1,\dots,f_{g-1}$ are just the other parameters at $t$, so they are linear.
+This can be done by picking generators $f_1,\dots,f_{g-1}$ for the ideal defining $\Tilde{C}_P^p$ inside $\Tilde{J}_t^p$.
 \end{rem}
@@
 Let $\kappa: \Z^r \to \Z_p^g$ be the map resulting from the inclusion $J(\Z)_t \to J(\Z_p)_t$.
-Then $\kappa$ turns out to have a special property.
+In this section we will prove that $\kappa$ turns out to have a special property.
 
@@
 \label{thm:kappanice}
-There are uniquely determined $\kappa_1,\dots,\kappa_g \in \Z_p\angle{z_1,...,z_r}$ such that for all $x \in \Z^r$ we have $\kappa(x) = (\kappa_1(x),\dots,\kappa_g(x))$ and the image $\overline{\kappa_i}$ of $\kappa_i$ in $\F_p[z_1,...,z_r]$ has degree at most $1$; furthermore, for $m \in \Z_{>0}$ with $m<p-1$, these $\kappa$ are also of degree at most $m$ modulo $p^m$.
+There are uniquely determined $\kappa_1,\dots,\kappa_g \in \Z_p\angle{z_1,\dots,z_r}$ such that for all $x \in \Z^r$ we have $\kappa(x) = (\kappa_1(x),\dots,\kappa_g(x))$ and the image $\overline{\kappa_i}$ of $\kappa_i$ in $\F_p[z_1,\dots,z_r]$ has degree at most $1$; furthermore, for $m \in \Z_{>0}$ with $m<p-1$, these $\kappa_i$ are also of degree at most $m$ modulo $p^m$.
 \end{thm}
@@
 Let $R$ be a commutative ring, and $x = (x_1,\dots,x_n)$ and sometimes $y,z$ are vectors of variables.
-Then $R[[x]]$ denotes as usual the powerseries in the $x_i$, and $R[[x]]_0$ denotes those power series with constant term $0$.
+Then $R[[x]]$ denotes as usual the ring of formal powerseries in the $x_i$, and $R[[x]]_0$ denotes those power series with constant term $0$.
 With $x = (x_1,\dots,x_n)$ and $y = (y,_1,\dots,y_m$), let $f \in R[[x]]^m$ and assume $f(0) = 0$.
@@
 Let $x,y,z$ be vectors of $n$ variables.
-An $n$-dimensional formal group is an element $F = (F_1,\dots,F_n) \in R[[x,y]]_0^n$ satisfying $F \equiv x + y \mod (x,y)^2$ and $F(F(x,y),z) = F(x,F(y,z))$.
+An $n$-dimensional formal group is an element $F = (F_1,\dots,F_n) \in R[[x,y]]_0^n$ satisfying $F \equiv x + y \bmod (x,y)^2$ and $F(F(x,y),z) = F(x,F(y,z))$.
 If furthermore $F(x,y) = F(y,x)$, this formal group is said to be commutative.
@@
 \begin{exmp}
+\label{exmp:ganformalgroup}
+For any $n$, we can take $F(x,y) = x+ y$, also known as the $n$-dimensional additive formal group.
+\end{exmp}
+\begin{exmp}
 \label{exmp:gmformalgroup}
 Take $n=1$ and $F(x,y) = x + y + xy = (1+x)(1+y)-1$, also known as the multiplicative formal group. This satisfies associativity as $F(F(x,y),z) = (1+x)(1+y)(1+z)-1 = F(x,F(y,z))$.
-\end{exmp}
-\begin{exmp}
-\label{exmp:ganformalgroup}
-For any $n$, we can take $F(x,y) = x+ y$, also known as the $n$-dimensional additive formal group.
 \end{exmp}
@@
 \begin{proof}
-If $F$ is a polynomial, this is a special case of a multivariate version of Hensel's lemma, as in Corrolaire~2 of \cite[III,4.5]{BourbakiCA}, over $R[[x]]$ with maximal ideal $\m = (x)$, as the derivative matrix of $F(x,\iota)$ with respect to $\iota$ is $B$, which is invertible, and $\iota = 0$ gives a solution modulo $\m$.
-Now for $F$ any power series, let $F_j$ be the polynomial consisting of all terms in $F$ of degree at most $j$, and let $\iota_j$ be the unique power series in $R[[x]]_0^n$such that $F_j(x,\iota_j) = 0$.
-Note that both $\iota_j$ and $\iota_{j+1}$ are solutions to $F_j(x,\iota) \equiv 0 \mod \m^j$, so by the uniquess guaranteed by Hensel's lemma used over $R[[x]]/\m^j$, these must be equal.
+If $F$ is a polynomial, this is a special case of a multivariate version of Hensel's lemma, as in Corollaire~2 of \cite[III,4.5]{BourbakiCA}: we work over $R[[x]]$ which is complete with respect to the ideal $\m = (x)$, and the derivative matrix of $F(x,\iota)$ with respect to $\iota$ is $B$, which is invertible, and $\iota = 0$ gives a solution modulo $\m$.
+Now for $F$ any power series, let $F_j$ be the polynomial consisting of all terms in $F$ of degree at most $j$, and let $\iota_j$ be the unique power series in $R[[x]]_0^n$ such that $F_j(x,\iota_j) = 0$.
+Note that both $\iota_j$ and $\iota_{j+1}$ are solutions to $F_j(x,\iota) \equiv 0 \bmod \m^j$, so by the uniquess guaranteed by Hensel's lemma used over $R[[x]]/\m^j$, these must be equal.
 Hence they converge to $\iota \in R[[x]]_0^n$, which is the unique solution of $F(x,\iota(x)) = 0$.
@@
 \label{lem:formalinverse}
-Let $x$ have length $n$. Let $a \in R[[x]]_0^n$ with $a \equiv Px \mod x$ for some matrix $A\in \GL_n(R)$. Then there is a unique $b \in R[[x]]_0^n$ such that $a \circ b = b \circ a = x$.
+Let $x$ have length $n$. Let $a \in R[[x]]_0^n$ with $a \equiv Px \bmod x$ for some matrix $P\in \GL_n(R)$. Then there is a unique $b \in R[[x]]_0^n$ such that $a \circ b = b \circ a = x$.
 \end{cor}
 \begin{proof}
-Let $F(x,y) = x - a(x)$.
+Let $F(x,y) = x - a(y)$.
 This satisfies the constraints of Lemma~\ref{lem:implicitfunction}, so we find a unique $b$ such that $a \circ b = x$.
@@
 So a formal group $F$ does by Lemma~\ref{lem:implicitfunction} indeed have a right inverse $\iota_F$.
-Also, by $F(0,0) = 0$ we have that $F(x,F(\iota_f,0)) = 0$ so $F(\iota_f,0)$ is in fact equal to $\iota_F$; as $\iota_F \equiv -x \mod (x)^2$, it has a formal inverse and hence $F(x,0) = x$, so $0$ is indeed a right unit.
-A standard argument now shows that $\iota_F$ is also a left inverse and $0$ is also a right unit, so $F$ gives $R[[x]]$ the structure of a group object in the category of topological rings; for two continuous morphisms $f_1,f_2$ from $R[[x]]$ to some ring $A$, given by sending $x$ to $a_1,a_2$ respectively, we define $(f_1 \oplus f_2)(x) = F(a_1,a_2)$, and by our considerations this makes $\Hom_{\text{cont}}{R,A}$ into a group, functorially in $A$.
+Also, by $F(0,0) = 0$ we have that $F(x,F(\iota_f,0)) = 0$ so $F(\iota_f,0)$ is in fact equal to $\iota_F$; as $\iota_F \equiv -x \bmod (x)^2$, it has a formal inverse and hence $F(x,0) = x$, so $0$ is indeed a right unit.
+A standard argument now shows that $\iota_F$ is also a left inverse and $0$ is also a right unit, so $F$ gives $R[[x]]$, together with the $(x)$-adic topology, the structure of a group object in the category of topological rings\todo{Bas, je had "category of top.
+rings" gemarkeerd, waarom?}; for two continuous morphisms $f_1,f_2$ from $R[[x]]$ to some ring $A$, given by sending $x$ to $a_1,a_2$ respectively, we define $(f_1 \oplus f_2)(x) = F(a_1,a_2)$, and by our considerations this makes $\Hom_{\text{cont}}(R[[x]],A)$ into a group, functorially in $A$.
 
@@
 By smoothness, after picking parameters, this is isomorphic as topological $\Z_p$-algebras to the ring of power series $\Z_p[[x_1,\dots,x_d]]$.
-This completion naturally gives rise to a formal scheme denoted $\Spf \Hat{O}_{G,e}$; in a categorical notion, this is a functor on finite length $\Z_p$-algebras sending $A$ to $\Hom_{\text{cont}}(\Hat{O}_{G,e},A)$, but we can also think of it as a locally ringed space with $\Spec \Z_p$ as topological space, and sheaf of rings $\Hat{O}_{G,e}$.
+This completion naturally gives rise to a formal scheme denoted $\Spf \Hat{O}_{G,e}$; in a categorical notion, this is a functor on finite length $\Z_p$-algebras sending $A$ to $\Hom_{\text{cont}}(\Hat{O}_{G,e},A)$, but we can also think of it as a locally ringed space with $\Spec \Z_p$ as topological space, and sheaf of rings $\lim_n \Tilde{O_{G,e}/m^n}$ where $m$ is the maximal ideal of $O_{G,e}$.
+The global sections of these sheaf are simply $\Hat{O}_{G,e}$.
 
@@
 for every finite $\Z_p$-algebra $A$ the set $\Hom_{\text{cont}}(\Hat{O}_{G,e},A)$ gets a group structure, functorially in $A$.
-By functoriality, this is the same [TODO: figure out why exactly?
-Probably just Yoneda] as an continuous coproduct $\mu: \Hat{O}_{G,e} \to \left(\Hat{O}_{G,e}\right)^{\Hat{\tensor} 2}$.
-After choosing an isomorphism between $\Hat{O}_{G,e}$ and $\Z_p[[x_1,\dots,x_d]]$, let $F_j \in \Z_p[[x,y]]$ denote $\mu(x_i)$.
+By functoriality, this is the same as an continuous coproduct $\mu: \Hat{O}_{G,e} \to \left(\Hat{O}_{G,e}\right)^{\Hat{\tensor} 2}$.
+After choosing an isomorphism between $\Hat{O}_{G,e}$ and $\Z_p[[x_1,\dots,x_d]]$, let $F_j \in \Z_p[[x,y]]$ denote $\mu(x_j)$.
 Then it is clear that $F_G = (F_1,\dots,F_d)$ is a $d$-dimensional formal group scheme, and commutative if $G$ was commutative.
-\begin{exmp}
-\label{exmp:gmtoformal} \todo{nicely LaTeX Example bla, continued}
+\addtocounter{thm}{-3}
+\begin{exmp}[continued]
+\label{exmp:gmtoformal}
 Take $G = \G_m$ over $\Z_p$, i.e.
@@
 $d\omega_j = 0$.
-A $1$-form $d\omega = \sum_{i=1}^n f_i \diff x_i$ being closed means exactly that $\frac{\partial f_i}{\partial x_j} = \frac{\partial f_j}{\partial x_i}$ for all $i,j$, and then, if $R$ has no torsion, we can formally integrate $\omega$, i.e.
+A $1$-form $d\omega = \sum_{i=1}^n f_i \diff x_i$ being closed means exactly that $\frac{\partial f_i}{\partial x_j} = \frac{\partial f_j}{\partial x_i}$ for all $i,j$.
+From now on, assume $R$ has no torsion; then $R$ imbeds into $\Q \tensor R$ and, we can formally integrate $\omega$, i.e.
 write it as $df$ where $f \in (\Q\tensor R)[[x]]$.
@@
 In particular, we write $\log_i$ for the unique element of $(\Q\tensor R)[[x]]$ such that $d\log_i = \omega_i$.
-Together, these $\log_i$ give an element $\log \in R[[x]]^n$, and by Theorem~1 of \citep{honda70}, this logarithm satisfies $\log(x) = x \mod (x)^2$, and $\log(F(x,y)) = \log(x)+\log(y)$.
-By the first result, $\log$ has an inverse which we will call $\exp$, also given by powerseries in $(\Q\tensor R)[[x]])$, and also satisfying $\exp(x) = x \mod (x)^2$.
-\begin{exmp} \todo{nicely LaTeX Example bla, continued}
+Together, these $\log_i$ give an element $\log \in R[[x]]^n$, and by Theorem~1 of \citep{honda70}, this logarithm satisfies $\log(x) = x \bmod (x)^2$, and $\log(F(x,y)) = \log(x)+\log(y)$.
+By the first result, $\log$ has an inverse which we will call $\exp$, also given by powerseries in $(\Q\tensor R)[[x]]$, and also satisfying $\exp(x) = x \bmod (x)^2$.
+\addtocounter{thm}{-1}
+\begin{exmp}[continued]
 Taking $F$ the multiplicative group as in Example~\ref{exmp:gmformalgroup}, Proposition~1.1 of \citep{honda70} gives us $\omega = \frac{1}{x+1}dx$; as a power series this is $\sum_{j \geq 0} (-x)^j$.
-The formal anti-derivative of this is $\log = \sum_{j \geq 1} \frac{-(-x)^j}{j}$, and Theorem $1$ will tell us what we already know in the context of analysis $\log(x + y + xy) = \log(x)+\log(y)$.
+The formal anti-derivative of this is $\log = \sum_{j \geq 1} \frac{-(-x)^j}{j}dx$, and Theorem $1$ will tell us what we already know in the context of analysis $\log(x + y + xy) = \log(x)+\log(y)$.
 Then analysis will also explicitly tell us what $\exp$ looks like: namely, $\exp(x) = \sum_{j \geq 1} \frac{x^j}{j!}$.
 \end{exmp}
+\addtocounter{thm}{2}
 
@@
 	\item Letting $\oplus$ denote the group structure on $\Z_p^d$ coming from the bijection $G(\Z_p)_0 \to p\Z_p^d \to \Z_p^d$, the map $\log_p$ is a group morphism from $(\Z_p^d,\oplus)$ to $(\Z_p^d,+)$.
-	\item If $p > 2$, the map $\log_{p,i}$ reduces to $x_i$ modulo $p$ and hence $\log_p$ has an inverse $\exp_p$, which is also an element of $\Z_p\angle{x_1,\dots,x_d}$.
+	\item If $p > 2$, the map $\log_{p,i}$ reduces to $x_i$ modulo $p$ and hence $\log_p$ has an inverse $\exp_p$, which is also an element of $\Z_p\angle{x_1,\dots,x_d}_0^d$.
 Then this $\exp_p$ is a two-sided inverse of $\log_p$, and hence $\log_p: \Z_p^d \to \Z_p^d$ is a bijection.
@@
 For purposes of easy estimation, this also means $|I|a_{i,I} \in \Z_p$.
-As we have, with no constraint on $p$, for all $n\geq $ that $c_n\coloneqq p^{n-1}/n$ lies in $\Z_p$ and converges to $0$, this means that \[ \log_{p,i} = \sum_I a_{i,I} p^{|I|-1} x^I = \sum_I |I|a_{i,I} c_{|I|} x^I\] is indeed an element of $\Z_p\angle{x_1,\dots,x_d}^n$, and hence defines a map $\Z_p^d \to \Z_p$.
+As we have, with no constraint on $p$, for all $n\geq 1$ that $c_n\coloneqq p^{n-1}/n$ lies in $\Z_p$ and converges to $0$, this means that \[ \log_{p,i} = \sum_I a_{i,I} p^{|I|-1} x^I = \sum_I |I|a_{i,I} c_{|I|} x^I\] is indeed an element of $\Z_p\angle{x_1,\dots,x_d}^n$, and hence defines a map $\Z_p^d \to \Z_p$.
 Hence all the $\log_{p,i}$ together give a map $\Z_p^d \to \Z_p^d$.
@@
 To study $\log_p$ modulo $p$, we note that if $n\geq 3$, then $p$ actually divides $c_n$, and for $p > 2$ we even have $p|c_2$.
-As $\log_{p,i} = x_i \mod (x)^2$, this means that for $p > 2$ we have \[\log_{p,i} \equiv \sum_{|I| = 1} |I|a_{i,I}c_{|I|} x^I \equiv x_i \bmod p.\]
-Note that as $\log_p \equiv x \mod (x)^2$, by Lemma~\ref{lem:formalinverse} it has an inverse $\exp_p \in \Z_p[[x]]_0^n$.
+As $\log_{p,i} = x_i \bmod (x)^2$, this means that for $p > 2$ we have \[\log_{p,i} \equiv \sum_{|I| = 1} |I|a_{i,I}c_{|I|} x^I \equiv x_i \bmod p.\]
+Note that as $\log_p \equiv x \bmod (x)^2$, by Lemma~\ref{lem:formalinverse} it has an inverse $\exp_p \in \Z_p[[x]]_0^n$.
 Modulo $p$, this $\exp_p$ must be $x$, which lies in $\Z_p\angle{x}_0^n$; as $\Z_p\angle{x}$ is $p$-adically complete, using Hensel this shows $\exp_p$ is indeed in $\Z_p\angle{x}_0^n$.
@@
 As $c_n$ has $p$-adic valuation $n-1$ for $n < p$, and $p$-adic valuation at least $p-2 \geq m$ for $n \geq p$, indeed $\log_p$ has degree at most $m$ modulo $p^m$.
-Then we use induction to prove that $\exp_p$ has degree at most $m$ modulo $p^m$.
-This will follow immediately from the following considerations; firstly, for $f,g,g_m \in \Z/p^m\Z[x]_0^d$ satisfying $f(g(x)) = x \bmod p^{m-1}$, with $f,g$ linear modulo $p$ and $f,g$ having as derivative at $0$ invertible $d\times d$-matrices $C_f,C_g$ we have the formula
+That the same holds immediately for $\exp_p$, follows immediately from the consideration that the set
 \[
-f(g(x) + p^{m-1}g_m(x))+p^{m-1}f_m(g(x)) = f(g(x)) + p^{m-1}(C_f g_m(x))x^m
+S \coloneqq \{f \in \Z/p^n\Z[x]_0^d \mid  f \equiv x \bmod p, \forall m \deg(f \bmod p^m) \leq m\}
 \]
-and as $C_f$ is invertible, there is a unique value of $p^{m-1}g_m$ such that $f((g+p^{m-1}g_m)(x)) = x$, and then $p^{m-1}g_m$ has degree at most $\deg f(g(x))$.
-Secondly, if furthermore we can write $f,g$ in the forms $f = \sum_{i=1}^m p^{i-1}a_i x^i,g = \sum_{i=1}^{m-1} p^{i-1}b_i x^i$ with $p^{i-1}\mid a_i,b_i$, then we have
-\begin{align*}
-f(g(x)) &= \sum_{i=1}^m p^{i-1} a_i g^i \\
-        &= \sum_{i=1}^m p^{i-1} a_i \sum_{I_1,\dots,I_{i}} \prod_{j=1}^i p^{I_j-1} b_{I_j} x^{I_j} \\
-        &= \sum_{i=1}^m \sum_n p^{n-1} x^n \left(\sum_{I_1 + \cdots +I_{i} = n} a_i \prod_{j=1}^i b_{I_j}\right) \\
-\end{align*}
-which is clearly of degree at most $m$.
-In total, there is a unique $\tilde{g} \in \Z/p^m\Z[x]_0^d$ satisfying $\tilde{g} \equiv g \bmod p^{m-1}$ and $f(\tilde{g}(x))=x$, and this $\tilde{g}$ has degree at most $m$.
-This finishes the proof.
-\todo{TODO This is clearly a Hensel like proof, and I would prefer to just outright use Hensels lemma in some way}.
-[Is this doable?
-I think so...
-Maybe multiply $g$ by $p$ and divide coefficients of $f$ by powers of $p$, and use that $\Z_p[[px]]$ is $p$-adically complete.
-Also, try to get rid of the calculation at the end.]
+forms a group under composition, as we will now see. As $\Z_p\angle{x}$ is complete, we know the superset set of $S$
+\[
+T \coloneqq \{f \in \Z/p^n\Z[x]_0^d \mid  f \equiv x \bmod p\}
+\]
+is a group.
+As $S$ is finite and non-empty, all that remains to show is that $S$ is closed under composition.
+We can also characterise $S$ as consisting of images $\overline{f}$ of polynomials $f \in \Z_p[x]_0^d$ such that there is a polynomial $\tilde{f}\in\Z_p[x]_0^d$ with $pf(x) = \tilde{f}(px)$.
+If we then take two elements $\overline{f},\overline{g} \in S$, reductions of $f,g$ respectively with $\tilde{f},\tilde{g}$ such that $pf(x) = \tilde{f}(px), pg(x) = \tilde{g}(px)$, we see that with $h = f\circ g, \tilde{h} = \tilde{f} \circ \tilde{g}$ that $ph(x) = \tilde{h}(px)$ and $h \equiv \overline{f} \circ \overline{g} \bmod p^m$, so indeed $\overline{f} \circ \overline{g}$ is also an element of $S$.
+Hence we see $S$ is indeed a group, and as $\log_p \bmod p^m$ is an element of it, so is $\exp_p \bmod p^m$.
+\todo{Bas, dit is gelukt wat simpeler te maken, geen lelijke berekeningen meer :)}.
 \end{proof}
@@
 
-Hence if we find an upper bound for the cardinality of $Z(\lambda_1,\dots,\lambda_{g-1})$, this is also an upper bound for $C(\Z_p)_P$.
+Hence if we find an upper bound for the cardinality of $Z(\lambda_1,\dots,\lambda_{g-1})$, this is also an upper bound for $C(\Z)_P$.
 There are several, sometimes ad hoc, ways of proving finiteness.
-We let $A$ denote $\Z_p\angle{x_1,\dots,x_r}$ and $I$ the ideal generated by $\lambda_1,\dots,\lambda_{g-1}$.
-Noting that $Z(\lambda_1,\dots,\lambda_{g-1}) = \Hom_{\Z_p}(A/I,\Z_p)$, we can use the following theorem.
+We let $I$ denote the ideal inside $\Z_p\angle{x_1,\dots,x_r}$ generated by $\lambda_1,\dots,\lambda_{g-1}$, and $A$ the quotient $\Z_p\angle{x_1,\dots,x_r}/I$.
+Noting that $Z(\lambda_1,\dots,\lambda_{g-1}) = \Hom_{\Z_p}(A/I,\Z_p)$, we can use the following theorem, the statement and proof of which come from \citep{edixhoven20}.
 
@@
 \label{prop:finedix}
-Let $\overline{A} = A/pA$ and $\overline{I} = I\overline{A}$. Assume $\overline{A}/\overline{I}$ is finite. Then ...% $A$ is the product $\prod_{m \in \MaxSpec(A)} A_m$ and $$\Hom(A/I,\Z_p)$
+Let $\overline{A} = A/pA$ and $\overline{I} = I\overline{A}$.
+Assume $\overline{A}$ is finite.
+Then $\overline{A}$ is the product $\prod_{m \in \MaxSpec(\overline{A})} A_m$, and the sum of $\dim_{\F_p} \overline{A}_m$ over those $m\in \MaxSpec(\overline{A})$ with $\overline{A}/m = \F_p$ is an upper bound for $\Hom(A/I,\Z_p)$.
 \end{prop}
 \begin{proof}
-\todo{give exact statement and proof}
+We start by proving that $A$ is $p$-adically complete. This follows from the more general fact of a quotient
+\todo{give proof}
+\todo{Bas, ik begrijp het bewijs niet helemaal\dots }
 \end{proof}
 
-To utilise this theorem, we only need to calculate the $\lambda_i$ modulo $p$. In our case, of all $\kappa_i$ and $f_i$ being linear modulo $p$, we get as special case the following corrollary.
+To utilise this theorem, we only need to calculate the $\lambda_i$ modulo $p$.
+In our case, of all $\kappa_i$ and $f_i$ being linear modulo $p$, so are the $\lambda_i$, and we get as special case the following corollary.
 \begin{cor}
 \label{cor:finedixlinear}
-If the system of equations $\forall i: \lambda_i \equiv 0 \bmod p$ has respectively no or one solution, there is respectively none or at most one point in $C(\Z)_P$.
+If the linear system of equations $\forall i: \lambda_i \equiv 0 \bmod p$ has respectively no or one solution, there is respectively none or at most one point in $C(\Z)_P$.
 \end{cor}
 
-In general, even if $\overline{A}/\overline{I}$ is not finite, we see $\Hom(A/I,\Z_p)$ factors through $A/(I:p)$ where $(I:p) = \{x \in A \mid \exists k \in \Z_{\geq 0} p^kx \in A\}$.
-Then a higher precision calculation of the $\lambda_i$ can still lead to a succesfull application of Proposition~\ref{prop:finedix}.
+This leads to a now trivial proposition.
+\begin{prop}
+\label{prop:linchabauty}
+If for all points $P \in C(\F_p)$, the linear system of $g-1$ equations defining $U(\Z_p)_P$ in $\overline{J(\Z)_P}$ modulo $p$ has at most one solution, we get the inequality
+\[
+|C(\Z)| \leq |C(\F_p)|.
+\]
+\end{prop}
+
+\begin{rem}
+\label{rem:prob}
+Note that in general a linear system of $n + k$ equations over a vector space of dimension $n$ over a finite field of size $p$ has more than one solution with probability at most $\frac{1}{(p-1)^{k+1}}$.
+By the Hasse-Weil bound, assuming $p = \Omega(g^2)$, and that all linear systems of Proposition~\ref{prop:linchabauty} for all $P \in C(\F_p)$ are independent, we see that the conditions of these propositions have a high condition of being satisfied if $r<g-1$, and may even work for the case $r = g-1$ with probability around $e^{-1}$ for $p$ large enough.
+Hence trying a few small primes should generally be enough.
+\end{rem}
+
+Of note are that this upper bound for $C(\Z)$ does not even depend on the genus, and behaves agreeably when compared to the upper bound in Theorem 5.3 of \citep{poonen12}, which tells us that $|C(\Z)| \leq |C(\F_p)| + 2g-2$ under the much lighter condition of $r < g, p > 2g$ where $p$ is still a prime of good reduction.
+To summarise: in proposition~\ref{prop:linchabauty} we sacrifice consistency for being to able to prove much sharper bounds.
+
+In general, even if $\overline{A}/\overline{I}$ is not finite, we see $\Hom(A/I,\Z_p)$ factors through $A/(I:p)$ where $(I:p) = \{x \in A \mid \exists k \in \Z_{\geq 0}: p^kx \in A\}$.
+Then a higher precision calculation of the $\lambda_i$ can still lead to a succesful application of Proposition~\ref{prop:finedix}.
 
@@
 \section{Complications and improvements}
-\label{section:remarks} \todo{Write everything}
+\label{section:remarks} \todo{Bas, ik ben niet echt groot fan van dit hoofdstuk, voegt het iets toe denk je?}
+In this section, we quickly make some further remarks on how or when to apply the theory we have built up in previous section to real cases.
 \begin{itemize} 
-\item $\overline{J(\Z)_0}$ open in $J(\Z_p)_0$.
-\item Calculations in $J(\Z)$.
-\item According to McCallum\&Poonen, it can be that $J(\Z)_0$ and $C(\Z)_P$ are tangent as $p$-adic manifolds and then finite-precision calculations will never be enough.
-I don't see what's happening there.
-Maybe give an example?
-\item It is possible that $C(\Z_p)_P \cap \overline{J(\Z)_t}$ is bigger than $C(\Z)_P$; give an example. Refer to \citep{Balakrishnan19}.
-\item Explain Mordell-Weil sieve. Maybe "The Mordell-Weil sieve: Proving non-existence of rational points on curves" for a short explanation? Nice to also treat this in the final example.
-\item in general, generators of the Mordell-Weil group are computationally out of reach.
-But, if we only generate a subgroup of $J(\Z)_0$ of index finite and coprime to $p$, then the closure of this in $J(\Z_p)_0$ will be the same.
-This happens in particular if we generate a subgroup of $J(\Z)$ of index finite and coprime to $p|J(\F_p)|$.
-Preferably, find a source for this?
-Bas, do you have a reference for the complexity of such calculations?
-\item Fun case: if $J$ splits up to isogeny as the product of an elliptic curve and an abelian surface of Mordell-Weil rank respectively $2$ and $1$, then we only need two elements of $J(\Z)_0$ to generate $\overline{J(\Z)_0}$ I think.
-\item Multivatiate generalisation of Newton Polygons: Tropical stuff by Rabinoff, Park, Mixed volume calculations to bound number of zeroes. Katz-Rabinoff-ZB.
+\item Even if $r \geq g$, it might still be possible that $\overline{J(\Z)}$ coincidentally has dimension $r'$ smaller than $r$ (for example, if $r > g$); then one can find a rank $r'$ subgroup of $J(\Z)$ with the same closure inside $J(\Z_p)$, and do computations in this subgroup; we can expect this to work if $r' < g$.
+We can even use this to improve our calculations if we already have $r < g$, but $r'$ is even smaller.
+On the other hand, if $J(\Z)$ is open in $J(\Z_p)$, there is no way to apply Chabauty's method to the curve.
+\item Note that in all of the discussion of the previous section, we are calculating upper bounds for the cardinality of $C(\Z_p)_P \cap \overline{J(\Z)_t}$.
+It can and does however happen that this set is strictly bigger than $C(\Z)_P$.
+For example, there might be a $K$-point $Q$ where $K$ is a quadratic field where $p$ splits, such that $Q-b$ is non-$p-$torsion, and then $Q-b$ also lies in the closure of $J(\Z)$.
+We refer to \citep{Balakrishnan19} for further examples and explanations.
+\todo{finish}
+\item An important part of doing these calculations, is working with the Mordell-Weil group $J(\Z)$.
+In general, finding generators of $J(\Z)$ is computationally out of reach, and one may need to assume the BSD conjecture to even find the rank $r$.
+However, note that one does not need to find all of $J(\Z)$; if we can generate a subgroup of $J(\Z)$ of index finite and coprime to $p|J(\F_p)|$, it will have the same closure in $J(\Z_p)$.
+For this, we only need to generate sufficiently many independent points of the Jacobian, and saturate subgroups with respect to some primes.
+Both of these feats are easier than finding all of $J(\Z)$.
+\item Even this method does not work for a certain prime $p$, and neither for some other primes we tried, we can still use parts of the information we have learned.
+For example, maybe the method tells us that we have found all points of $J(\Z)$ stemming from $C(\Z)$ except those in a certain fibre of the map $J(\Z) \to J(\F_p)$.
+We can then aggregate this information for different primes, by looking at the maps $J(\Z) \to \prod_{p \in S} J(\F_p)$ for some set $S$ of primes of good reduction.
+See for example \citep{stoll10} for an introduction to the Mordell-Weil sieve.
 \end{itemize}
@@
 inside $\P(1,g+1,1)$ where $f$ is a monic polynomial of degree $2g+1$ or $2g+2$.
-An alternative way of defining such a curve, and the one we will be using mainly, is as a glueing of two affine charts: $y^2 = f(x)$, and $w^2 = f^{r}(v)$, where $f^{r}(v)$ is the polynomial $v^{2g + 2} f(1/v)$, and a birational map between them is given by $(x,y) \mapsto (\frac{1}{x},\frac{y}{x^{-g-1}})$.
+An alternative way of defining such a curve, and the one we will be using mainly, is as a glueing of two affine charts: $y^2 = f(x)$, and $w^2 = f^{r}(v)$, where $f^{r}(v)$ is the polynomial $v^{2g + 2} f(1/v)$, and a birational map between them is given by $(x,y) \mapsto (\frac{1}{x},\frac{y}{x^{g+1}})$.
 We also have the coordinates $X,Y,Z$ of $\P(1,g+1,1)$, with $x = X/Z, y = Y/Z^{g+1}, v = Z/X, w = Y/X^{g+1}$, but beware; these coordinates do not behave nicely on the origin of the patch $D(Y)$.
@@
 \subsection{Makdisis algorithms}
-Say something about how Makdisis algorithms work (i.e., give an introduction to the terminology) \cite{makdisi04}.
-
-As we are using and adding on an implementation by Mascot \cite{mascot2018}, we briefly introduce his notation. This is a summary of section 2.1 in \cite{mascot2018}.
+We work in the Jacobian using Makdisi's representations for divisors.
+As we are using and adding on to an implementation by Mascot \cite{mascot2018}, we briefly introduce his notation.
+This is a summary of section 2.1 in \cite{mascot2018}.
 
@@
 As explained in Mascot's article, using this representation one can do all relevant computations in $J(k)$; adding, subtracting, finding the zero element, and most importantly: checking equality.
+Important from a computational standpoint is the complexity; as everything is simply linear algebra in spaces of dimensions $O(g)$, the complexity of all these operations, assuming calculations in the ground ring are $O(1)$, are all simply $O(g^\omega)$ where $\omega$ is the matrix constant.
 
@@
 \[
-D(a,b) + D(\frac{f-b^2}{a},b) = (y-h)
+D(a,b) + D\left(\frac{f-b^2}{a},b\right) = (y-h)
 \]
@@
 \end{proof}
+\begin{rem}
+\label{rem:complexityabel} Clearly, the complexity of Algorithm~\ref{alg:abeljacobi} is $O(g^\omega)$.
+For a point in the Jacobian that is represented as $\sum P_i - gb$, this gives an $O(g^{\omega+1})$ algorithm for computing it in Makdisi's representation.
+\end{rem}
 
@@
 \]
-and then it should follow over $\Z_p$ so over $\Z/p^k\Z$. \todo{Give more details, currently talking with Mascot about this.}
+and then it should follow over $\Z_p$ so over $\Z/p^k\Z$.
+\todo{See [Todo]}[TODO:It is not necessarily true that a map that is an isomorphism when tensored with $\F_p$ and $\Q_p$ it is an isomorphism, but that is of course true if the map is between free modules, as I think it is here, right?
+As everything embeds into $\Z_p^n$ by evaluating at points, and submodule of free is free]
 
@@
 For any nice curve $C$ over $\Z$, smooth over $\Z_{(p)}$, with a $\Z$-point $b$, we have a birational map from $C^{(g)}$, the $g$-fold symmetric product of $C$, to $J$, given on points by sending $[(P_1,\dots,P_g)]$ to $[\sum P_i - gb]$.
-This map is \'etale at $[(P_1,\dots,P_g)]$ if $H^0(P_1 + \cdots + P_g)$ has dimension $1$ \todo{find a reference for this}, and if all $P_i$ are distinct, then the map $C^g \to C^{(g)}$ is \'etale at $P_1,\dots,P_g$ as well.
+This map is \'etale at $[(P_1,\dots,P_g)]$ if $H^0(P_1 + \cdots + P_g)$ has dimension $1$ as the fibre of $P_1 + \cdots + P_g -gb$ is exactly $\P H^0(P_1 + \cdots + P_g)$.
+Also, if all $P_i$ are distinct, then the map $C^g \to C^{(g)}$ is \'etale at $P_1,\dots,P_g$ as well.
 Then finding parameters $t_1,\dots,t_g$ at $Q := [\sum_{i=1}^g P_i - gb]$ just comes down to finding parameters at each of the $P_i$.
-In our case of a hyperellptic curve, this is just an easy computation; for a point $(a,b)$ on the first affine chart, we can take $x-a$ if $b$ is non-zero and $y$ if $a$ is zero.
+In our case of a hyperelliptic curve, this is just an easy computation; for a point $(a,b)$ on the first affine chart, we can take $x-a$ if $b$ is non-zero and $y$ if $a$ is zero.
 We can also compute the inverse of the map $C(\Z/p^k\Z)_{P_i} \to p\Z/p^k\Z$; this is just a simple exercise in Hensel lifting.
@@
 
-\todo{Explain how this can be improved in complexity}
+\begin{rem}
+\label{rem:faster}
+We can do this faster at the cost of consistency, by applying another algorithm by Mascot, Algorithm~7 in \cite{mascot18}.
+This algorithm computes a rational map $J \to \P V_2$, dependent on the choice of some specific degree effective divisors, with complexity $O(g^\omega)$.
+Of course, it is trivial to compute parameters in $\P V_2$, but the downside is that the rational map may not need to be defined where we want it to be.
+In that case, one can just take another choice of effective divisors and construct a different rational map; remember that we only need the map to be defined in our residue disc of choice.
+\end{rem}
 
@@
 Then $f$ is uniquely determinable in $O(nm^{n+1})$ by its values on $S^n$.
-\todo{There is a better complexity algorithm I think, at least clearly so for $m=1$}
+\todo{Make the complexity better} There is a better complexity algorithm I think, at least clearly so for $m=1$.
+I have to work on this a bit more.
+For $m = 1$, clearly we only need $n+1$ evaluations.
 \end{lem}
@@
 That means we can explicitly compute $\lambda_i$ modulo $p^m$ for $m < p-1$.
-Using Proposition~\ref{prop:finedix} or another way, we can hope to find an upper bound on the number of common zeroes of the $\lambda_i$, and hence an upper bound on $C(\Z)_P$
+Using Proposition~\ref{prop:finedix} or another way, we can hope to find an upper bound on the number of common zeroes of the $\lambda_i$, and hence an upper bound on $C(\Z)_P$.
 
 \subsection{Complexity}
-\todo{Refer back to complexity of calculations on the Jacobian ($J(\Z)$ and so on)}
+We assume necessary data for the Mordell-Weil group of the Jacobian is given; that is, we have a set of generators for either $J(\Z)$, or just a full rank subgroup of index coprime to $pJ(\F_p)$.
+We also assume that all relevant elements in $J(\Z)$ and $J(\F_p)$ are in the subgroup generated by $C(\Z)$ and $C(\F_p)$.
+Finally, we assume that we can find rational maps $J \to \P V_2$ as in Remark~\ref{rem:faster}.
 
-\todo{Find complexity of operations in the Jacobian performed by Mascots code}
+Then by Remark~\ref{rem:complexityabel} and Lemma~\ref{lem:interpolate}, we can compute $\lambda_i \bmod p$ in $O(rg^{\omega+1})$; then solving the linear system of equations $\forall i \lambda_i \equiv 0 \bmod p$ has complexity lower than that, and hence checking if $|C(\Z)_P|$ is at most $1$ can be done in $O(rg^{\omega+1})$.
+Repeating this for all $\F_p$-points, gives by the Hasse-Weil bound a complexity of $O\left((p + g\sqrt{p})rg^{\omega+1}\right)$.
 
@@
 
-We will first show there is at most one point in the residue disc of $\theta$. \todo{Add computations}
+We will first show there is at most one point in the same residue disc as $\theta$.
+As we already know there is at least one point, namely $\theta$, we can simplify the calculations by looking at the map $j_{\theta}: C \to J$ to be subtraction of $\theta$.
+Letting $\theta_{\mu}$ for $\mu \in \F_p$ denote the deformations of $\theta$ in $C(\Z/p^2\Z)_{\theta}$, with $\theta_\mu \mapsto \mu$ being a parameter at $\theta$, we see the image of $C(\Z/p^2\Z)_\theta$ in $J(\Z/p^2\Z)_0$ is $\{\theta_\mu - \theta \mid \mu \in \F_p\}$.
+Also, identifying $J(\Z)_0$ with $\Z^r$, the image of $J(\Z)_0$ in $J(\Z/p^2\Z)_0$ can be given as a map $\F_p^r \to J(\Z/p^2\Z)_0$.
+Choosing parameters by giving a local chart $J \to \P(V_2)$, we want to exactly show that the two maps $C(\Z/p^2\Z)_\theta \to J(\Z/p^2\Z)_0, \F_p^r \to J(\Z/p^2\Z)_0$ together form a map $\F_p \oplus \F_p^r \to J(\Z_p^2\Z)_0$ with kernel $0$.
+Now that this is a statement in linear algebra, it can be verified easily, and it turns out that indeed the residue disc of $C(\Z)$ containing $\theta$ contains only $\theta$.
 
@@
 
-Bas, what do I do with my code? Do I just paste it in at the end, give a link to the github page, or just not give it all?
+\todo{Bas, what do I do with my code?} Do I just paste it in at the end, give a link to the github page, or just not give it all?
 
 \section{Quadratic Chabauty}
-In this section we attempt to give an introduction to the article~\ref{edixhoven20} aimed to introduce all the players in Chabauty at a slightly slower pace.
-We will omit any proofs.For further reading, see for example \ref{hashimoto20}, an in progress cartoon guide to the article by Edixhoven-Lido.
+\label{section:quadratic}
+In this section we attempt to give an introduction to the article~\citep{edixhoven20} aimed to introduce all the players in Chabauty at a slightly slower pace.
+We will omit any proofs.For further reading, see for example \citep{hashimoto20}, an in progress cartoon guide to the article by Edixhoven-Lido.
 
@@
 We start with explaining the idea over $\Q$; we let $C_\Q$ be a projective, smooth curve over $\Q$ of genus at least $2$, we let $J_\Q$ be its Jacobian.
-We again assume the existence of a rational point $b \in C(\Q)$, and use it to construct an embedding $j_b : C_\Q \to J_\Q$.
+We again assume the existence of a rational point $b \in C_\Q(\Q)$, and use it to construct an embedding $j_b : C_\Q \to J_\Q$.
 We wish to set up a similar situation to classic Chabauty, and for that we introduce the Poincar\'e line bundle and Poincar\'e torsor.
-For this we need $J^\wedge$, the dual of $J$.
-This dual parametrised degree 0 line bundles on $J$, and hence we get a universal degree 0 line bundle $P$ on $J \times J^\wedge$, called the Poincar\'e line bundle $P$, which also satisfies that both $P_{0\times J^\wedge}$ and $P_{J \times 0\}$ are trivial.
+For this we need $J_\Q^\wedge$, the dual of $J_\Q$, which in fact is isomorphic to $J_\Q$, taking as isomorphism for example the principal polarisation $\lambda: J_\Q \to J_\Q^\wedge$.
+This dual parametrised degree $0$ line bundles on $J_\Q$, and hence we get a universal degree $0$ line bundle $P_\Q$ on $J_\Q \times J_\Q^\wedge$, called the Poincar\'e line bundle $P_\Q$, which also satisfies that both $P_{\Q,0\times J_\Q^\wedge}$ and $P_{\Q,J_\Q \times 0}$ are trivial.
 
-\begin{example}
-If $C$ is an elliptic curve then, identifying $C,J$ and $J^{\wedge}$, we get $P = O(\Delta-\[0\} \times E - E \times \{0\})$, indeed with the fibres $P|_{c \times E} \cong O(c-0)$ being exactly the degree $0$ line bundles on $C$ up to isomorphism.
-\end{example}
+\begin{exmp}
+If $C_\Q$ is an elliptic curve then, identifying $C_\Q,J_\Q$ and $J_\Q^{\wedge}$, we get $P_\Q = O(\Delta-\{0\} \times C_\Q - C_\Q \times \{0\})$, indeed with the fibres $P|_{\Q,c \times E_\Q} \cong O(c-0)$ being exactly the degree $0$ line bundles on $C_\Q$ up to isomorphism.
+\end{exmp}
 
-The object we will be working with is the Poincar\'e torsor, the $\G_m$ torsor over $J \times J^\wedge$ defined by \[
-P^\times = \text{Isom}_{J_\Q \times J^\wedge_\Q}(O_{J_\Q \times J^\wedge_\Q},P_\Q);
+The object we will be working with is the Poincar\'e torsor, the $\G_m$ torsor over $J_\Q \times J_\Q^\wedge$ defined by \[
+P_\Q^\times = \text{Isom}_{J_\Q \times J^\wedge_\Q}(O_{J_\Q \times J^\wedge_\Q},P_\Q);
 \] 
@@
 We denote the pullback of $P^\times_\Q$ along this map by $T_\Q$, a $\G_m$-torsor over $J_\Q$.
-This $T$ has dimension $g+1$.
+This $T_\Q$ has dimension $g+1$.
 The general idea of geometric quadratic Chabauty, is to work with the following diagram
-\begin{tikzcd} % https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBoBGAXVJADcBDAGwFcYkQBhAfQB0eBFEAF9S6TLnyEU5CtTpNW7AFK8Bw0SAzY8BIgCZZNBizaIQKvvwAEfPAFt4VpQD0+AdxhQA5jFWCRYtqS+qTEcsaKZgAKrjz28OqBErrSoeEKpiAAKsJynj4IKKAAZgBOEHZIZCA4EEgALEYZ7HxZWIywwABWXABGQokgZRVVNLVIMvIm7D29g8OViJPjiAZTkSAAFHxYUKS2pVwAxjY8R1ilJ8UAlPPli401dUsBQ-cNY88AzK8LSF+fJBrRj0XowRhRcQ6KQgRgwYo4XJCIA
-                                                & T \arrow[d] \arrow[r]                   & P^\times \arrow[d]      \\
+\[\begin{tikzcd} % https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBoBGAXVJADcBDAGwFcYkQBhAfQB0eBFEAF9S6TLnyEU5CtTpNW7AFK8Bw0SAzY8BIgCZZNBizaIQKvvwAEfPAFt4VpQD0+AdxhQA5jFWCRYtqS+qTEcsaKZgAKrjz28OqBErrSoeEKpiAAKsJynj4IKKAAZgBOEHZIZCA4EEgALEYZ7HxZWIywwABWXABGQokgZRVVNLVIMvIm7D29g8OViJPjiAZTkSAAFHxYUKS2pVwAxjY8R1ilJ8UAlPPli401dUsBQ-cNY88AzK8LSF+fJBrRj0XowRhRcQ6KQgRgwYo4XJCIA
+                                                & T_\Q \arrow[d] \arrow[r]                   & P_\Q^\times \arrow[d]      \\
 C_\Q \arrow[ru, "\Tilde{j_b}"] \arrow[r, "j_b"] & J_\Q \arrow[r, "{(\id,\tr_c \circ f)}"] & J_\Q \times J^\wedge_\Q
-\end{tikzcd}
+\end{tikzcd}\]
 where $\Tilde{j_b}$ is a lift of $j_b$.
-This lift will only exist if $j_b^* T$ is a trivial $\G_m$-torsor over $C$; for that, it turns out that we want $f$ to be an element of $\Hom^+(J_\Q,J^\wedge_\Q)$, the group of self dual homomorphism, of trace 0 (where this trace comes from identification with the N\'eron-Severi group); if we do that, it turns out that $j_b^* T$ will correspond to a degree $0$ line bundle on $C_\Q$, and we only need to translate by a constant to make $j_b^* T$ trivial.
+This lift will only exist if $j_b^* T$ is a trivial $\G_m$-torsor over $C_\Q$; for that, it turns out that we want $f$ to be an element of $\Hom^+(J_\Q,J^\wedge_\Q)$, the group of self dual homomorphisms, of trace $0$ (where this trace comes from identification with the N\'eron-Severi group); if we do that, it turns out that $j_b^* T$ will correspond to a degree $0$ line bundle on $C_\Q$, and we only need to translate by a constant to make $j_b^* T$ trivial.
 
-If $f$ itself is already trivial, then $T$ is trivial and this will give no further information, and in general that is the best we can do, as generically, the rank of $\Hom^+(J_\Q,J^\wedge_\Q)$, also called the N\'eron-Severi rank $\rho$, is $1$.\todo{This is true, right?
+If $f$ itself is already $0$, then $T$ is trivial and this will give no further information, and in general that is the best we can do, as generically the rank of $\Hom^+(J_\Q,J^\wedge_\Q)$, also called the N\'eron-Severi rank $\rho$, is $1$.\todo{This is true, right?
 Can't find reference} But in many interesting cases, this rank is non-zero.
-A family of examples is given by modular curves, where the Hecke algebra acts on $\Hom^+(J_\Q,J^\wedge_\Q)$, in which case the N\'eron-Severi rank turns out to be equal to the genus.
-We can then pick a basis $f_1,\dots,f_{\rho-1}$ of the trace $0$ subgroup of $\Hom^+(J_\Q,J^\wedge_\Q)$, and take the product of all the resulting pullbacks over $J$, to get a $g+\rho-1$ dimensional scheme over $J_\Q$ that admits a morphism from $C_\Q$.
+Using the isomorphism $\lambda$, this rank is also the rank of the endomorphism ring of $J_\Q$, and hence a family of examples is given by modular curves, where the endomorphism ring is the Hecke algebra and the N\'eron-Severi rank turns out to be equal to the genus.
 
-For ease of exposition, we will look at the case $\rho \geq 2$ and use a single, non-zero, trace $0$ morphism $f \in \Hom^+(J_\Q,J^\wedge_\Q)$.
-We then would like to intersect the rational points of $T_\Q$ with the $p$-adic points of $C_\Q$, mapped to $T_\Q$ under $\tilde{j_b}$, inside the $p$-adic points of $T$.
-As in the case of classic Chabauty, one can conclude that the $p$-adic points of $T$ form a $p$-adic manifold of dimension $g+1$, but there is a problem with the rational points of $T_\Q$; these are in bijection with $\G_m(\Q) \times J_\Q(\Q)$.
-The latter is a finitely generated group of rank $r$, the Mordell-Weil rank, but the former is an infinitely generated group, and hence we cannot easily upper bound the dimension of $\overline{T(\Q)}$ inside $T(\Q_p)$ \todo{Check that there is a underscore-Q everywhere}
+In general, we can pick a basis $f_1,\dots,f_{\rho-1}$ of the trace $0$ subgroup of $\Hom^+(J_\Q,J^\wedge_\Q)$ and elements $c_1,\dots,c_{\rho-1} \in J_\Q^\wedge$ with $j_b^* (\id,\tr_{c_i} \circ f_i)^* P_{\Q}^\times$ trivial, and take the product of all the resulting pullbacks over $J_\Q$, to get a $\G_m^{\rho-1}$-torsor $T$ over $J_\Q$ that admits a morphism from $C_\Q$.
+
+We then would like to intersect the rational points of $T_\Q$ with the $p$-adic points of $C_\Q$, mapped to $T_\Q$ under $\tilde{j_b}$, inside the $p$-adic points of $T_\Q$.
+As in the case of classic Chabauty, one can conclude that the $p$-adic points of $T_\Q$ form a $p$-adic manifold of dimension $g+\rho-1$, but there is a problem with the rational points of $T_\Q$; these are in bijection with $\G_m(\Q)^{\rho-1} \times J_\Q(\Q)$.
+The latter is a finitely generated group of rank $r$, the Mordell-Weil rank, but the former is an infinitely generated group, and hence we cannot easily upper bound the dimension of $\overline{T_\Q(\Q)}$ inside $T_\Q(\Q_p)$.
 
@@
 We cannot expect $C$ to be smooth over $\Z$, we only ask that $C$ is smooth over $\Z[1/n]$ for some squarefree $n$ consisting of bad primes.
-Hence if we build up the theory correctly, we get that as sets, $T(\Z) = \{\pm1\} \times J(\Q)$, which we might expect to parametrise with $\Z^r$ in some nice way.
-It turns out that this is indeed possible, when restricted to residue discs.
-In sections 4 and 5 of the Edixhoven-Lido paper, they give a rather explicit parametrisation in terms of the structure of $P^\times$.
+We let $J$ be the N\'eron model over $\Z$ of the Jacobian of $C_\Q$, and $J^\wedge$ the N\'eron model of the dual of $J$.
+If we want to keep the essential structure of the Poincar\'e torsor intact, we can only extend to $P \to J \times J^{\wedge 0}$ where $J^{\wedge 0}$ is the connected component of $J^\wedge$ containing $0$; the component group $J/J^{\wedge 0}$ is only supported on $\Z/n\Z$, i.e.
+on the bad primes.
+We let $m\in \Z_{>0}$ be the annihilator of $J/J^{\wedge 0}$.
+We can then make a similar diagram as before
+\[\begin{tikzcd} % https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBoBGAXVJADcBDAGwFcYkQBhAfQB0eBFEAF9S6TLnyEU5CtTpNW7AFK8Bw0SAzY8BIgCZZNBizaIQKvvwAEfPAFt4VpQD0+AdxhQA5jFWCRYtqS+qTEcsaKZgAKrjz28OqBErrSoeEKpiAAKsJynj4IKKAAZgBOEHZIZCA4EEgALEYZ7HxZWIywwABWXABGQokgZRVVNLVIMvIm7D29g8OViJPjiAZTkSAAFHxYUKS2pVwAxjY8R1ilJ8UAlPPli401dUsBQ-cNY88AzK8LSF+fJBrRj0XowRhRcQ6KQgRgwYo4XJCIA
+                                                & T \arrow[d] \arrow[r]                   & P^\times \arrow[d]      \\
+C \arrow[ru, "\Tilde{j_b}", dotted] \arrow[r, "j_b"] & J \arrow[r, "{(\id,\cdot m \circ\tr_c \circ f)}"] & J \times J^{\wedge 0}
+\end{tikzcd}\]
+Where this time $f$ is an 
+There is one problem: the lift of $j_b$ from $C$ to $T$ only exists if $j_b^* T$ is trivial over $C$.
+We know this is true when base changed over $\Q$, and then the lift exists and is unique up to the action of $\Q^\times$.
+For $q$ prime for which $C_q$ has only one component, we can multiply by a suitable power of $q$ to make the fibre of $j_b^* T$ over $p$ trivial, however we cannot always do this if $C_q$ has multiple components.
 
-For
+So instead we cover $C^{\sm}$ with multiple opens $U_i$, obtained by removing for each $q$ dividing $n$ all but one irreducible components.
+As $C(\Z) = C^{\sm}(\Z)$, it is enough to compute $U_i(\Z)$ for every $U_i$.
+Then the map $j_{b,i}: U_i \to J$ does lift as in the following diagram:
+\[\begin{tikzcd} % https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBoBGAXVJADcBDAGwFcYkQBhAfQB0eBFEAF9S6TLnyEU5CtTpNW7AFK8Bw0SAzY8BIgCZZNBizaIQKvvwAEfPAFt4VpQD0+AdxhQA5jFWCRYtqS+qTEcsaKZgAKrjz28OqBErrSoeEKpiAAKsJynj4IKKAAZgBOEHZIZCA4EEgALEYZ7HxZWIywwABWXABGQokgZRVVNLVIMvIm7D29g8OViJPjiAZTkSAAFHxYUKS2pVwAxjY8R1ilJ8UAlPPli401dUsBQ-cNY88AzK8LSF+fJBrRj0XowRhRcQ6KQgRgwYo4XJCIA
+                                                & T \arrow[d] \arrow[r]                   & P^\times \arrow[d]      \\
+U_i \arrow[ru, "\Tilde{j_{b,i}}"] \arrow[r, "j_{b,i}"] & J \arrow[r, "{(\id,\cdot m \circ\tr_c \circ f)}"] & J \times J^{\wedge 0}
+\end{tikzcd}\]
+and we can finalise the summary of quadratic Chabauty.
+Denote $T$ now for the product of all $\rho-1$ such pullbacks for $f$ ranging over a basis of $\Hom(J,J^{\wedge})^+$.
+Taking a specific such $U$ with a lift $\Tilde{j_b}: U \to T$, for every prime $p$, the set $\Tilde{j_{b}}(U(\Z))$ is a subset of the intersection, inside the $p$-adic manifold $T(\Z_p)$, of $\Tilde{j_b}()U(\Z_p)$ and the closure $\overline{T(\Z)}$ of $T(\Z)$.
+As the dimension of $T$ is $g+\rho-1$ (it is a $\G_m^{\rho-1}$-torsor over $J$), we can as in Section~\ref{section:smoothzppoints} see that $T(\Z_p)$ has dimension $g+\rho-1$; and as $T(\Z)$ is a ${\pm 11}^{\rho-1}$-torsor over the group $J(\Z)$ of rank $r$, it will turn out $\overline{T(\Z)}$ has dimension at most $r$.
+As $U(\Z_p)$ has dimension $1$, we can hope that this intersection is be dimension $0$, and hence finite as $T(\Z_p)$ is compact, if $r < g + \rho-1$, hence we have an improvement over classical Chabauty.
+
+This argument can be made explicit when looking at residue discs; in short, just like we could parametrise $J(\Z)_0$ with $\Z^r$ in Section~\ref{section:kappa} where the inclusion $\Z^r \to J(\Z_p)_0 \cong \Z_p^{g}$ is given by convergent power series, it turns out that for $t \in T(\F_p)$ that lift to $T(\Z)$, there is a map $\kappa: \Z^r \to T(\Z_p)_t \cong \Z_p^{g+\rho-1}$ such that $\im \kappa = \overline{T(\Z)}$ and $\kappa$ is given by convergent power series.
+When the parameters at $t$ are chosen nicely, the first $g$ coming from $J$, it turns out that $\kappa_1,\dots,\kappa_g$ are linear modulo $p$, and $\kappa_{g+1},\dots,\kappa_{g+\rho-1}$ are quadratic modulo $p$.
+The fact that these are quadratic is in fact related to this being called quadratic Chabauty; it has to do with $(\id,\cdot m \circ\tr_c \circ f)$ being a quadratic like map, as the product of $\id$ and $m \circ\tr_c \circ f$, two linear maps.
+Also, one can again find equations $g_1,\cdots,g_{r+\rho-2}$for the the image of $U(\Z_p)$ in $T(\Z_p)_t$, which will again be linear modulo $p$.
+
+We end with a proposition we already know; Proposition~\ref{prop:finedix} also holds in our case, and this once again can lead to giving an explicit upper bound for the cardinality of residue discs of $U(\Z)$ using finite precision calculations; repeating these calculations for the multiple opens $U$ and their $\F_p$-points, finally gives an upper bound for $C(\Z)$.
+
 % Computations, and section 7 of the article (line bundles on C x C)
+An important part of making the calculations work, is forming the map $\tilde{j_b}: U \to T$.
+For this we need to be able to explicitly describe the trivialisation of the $\G_m$-torsor $j_b^* T$ restricted to $U$.
+Remember that $j_b^* T$ is also the pullback of $P^\times$ along the map $C \to J \times J^{\wedge 0}$, and this map factors through the diagonal map $C \times C\times C$.
+As described in Section~7 of the paper, it turns out that giving such a map $f: J \to J^{\wedge}$ and $c \in J^\wedge$ with $j_b^* T$ trivial over all opens $U$, is equivalent to giving a line bundle $\Lcal$ on $C \times C$ satisfying the following three properties: $\Lcal$ is rigidified on $\{b\} \times C_\Q$, the fibres of $\pr_2: (C \times C)_\Q \to C_\Q$ are degree $0$, and the pullback $\diag^* \Lcal$ is trivial on $C_\Q$.
+This turns the problem of describing a map $J \to J^\wedge$ in useful terms of th in the sometimes more concrete problem of giving a line bundle on $C \times C$ satisfying some simple conditions.
 
-Maybe treat how the Poincare torsor fits into this context; perhaps give an overview?
-Not sure if I can say enough while keeping it interesting.
-I would like to give a simpler introduction to \citep{edixhoven20}, saying a few things about the similarities and differences with linear Chabauty.
-I am not going to go in much detail, and am not going to do an example.
-Bas, do you think this would be useful?
+These line bundles are crucial in doing actual computations.
+In the example in the Edixhoven-Lido paper, they use an involution of the curve to construct a correct line bundle.
+Right now, the focus is on doing a modular example, $X_0(73)^+$, a genus $2$ curve with endomorphism ring of rank $2$.
+Here, the extra information comes from the Hecke algebra working on the curve, and the problem lies in describing Hecke operators explicitly as correspondences on $C \times C$, and computations with these correspondences over $\Z$.
 

### 2020-06-03 MS.tex
Added probability heuristics and cleaned up todos

@@
 \DeclareMathOperator{\GL}{GL}
+\DeclareMathOperator{\Mat}{Mat}
 \let\S\undefined
@@
 %-----------------------------------------------------------------------------------------------------------------------
-
+\todo{Remove overfull h-box warnings}\todo{Referentie naar een artikel van Balakrishnan en Dogra, en Besser.}
 \section{Introduction}
@@
 
-In this thesis, we look only at the case $g > 1$, It turns out that there are always only finitely many points; this result was originally conjectured by Mordell in 1922 and finally proven by Faltings in 1983.
+In this thesis, we look only at the case $g > 1$.
+It turns out that there are always only finitely many rational points; this result was originally conjectured by Mordell in 1922 and finally proven by Faltings in 1983.
 
 Before it was proven, one of the major partial results was a theorem from Chabauty in 1941, phrased in terms of the rank $r$ of the group of rational points on the Jacobian $J$ of the curve, also called the Mordell-Weil rank, which is finite by the Mordell-Weil theorem.
-Chabauty proved, using $p$-adic methods, that if $r$ is strictly smaller than the genus $g$, then $C$ has only finitely many points.
-Loosely said, this proof and all Chabauty related theorems, rely on choosing a prime $p$ for which $C$ has good reduction, and intersecting $J(\Z)$ with $C(\Z_p)$ inside the bigger $p$-adic manifold $J(\Z_p)$; by properties of $\Z_p$, the subgroup $J(\Z_p)$, generated by $r$ elements, lies within a $p$-adic manifold of dimension at most $r$, and $C(\Z_p)$ is a $1$-dimensional $p$-adic manifold, and hence their intersection is expected to be discrete and -- as $J(\Z_p)$ is compact -- finite.
+Chabauty proved, using $p$-adic methods, that if $r$ is strictly smaller than the genus $g$, then $C$ has only finitely many rational points.
+Loosely said, this proof and all Chabauty related theorems, rely on choosing a prime $p$ for which $C$ has good reduction, and intersecting $J(\Z)$ with $C(\Z_p)$ inside the bigger Lie group $J(\Z_p)$; by properties of $\Z_p$, the subgroup $J(\Z)$, generated by $r$ elements, lies within a Lie subgroup of dimension at most $r$, and $C(\Z_p)$ is a $1$-dimensional $p$-adic manifold, and hence their intersection can be proven to be discrete and -- as $J(\Z_p)$ is compact -- finite.
 
@@
 He interprets working in the Jacobian as dealing with the abelianised fundamental group of the curve $C$, and works with larger, non-abelian quotients of the fundamental group.
-Using quadratic Chabauty, the simplest case of non-abelian Chabauty, Balakrishnan, Dogra, M\"uller, Tuitman and Vonk famously calculated in May of 2019 all rational points of the ``cursed curve'', the modular curve $X_s^+(13)$.
+Using quadratic Chabauty, the simplest case of non-abelian Chabauty, Balakrishnan, Dogra, M\"uller, Tuitman and Vonk in 2017 famously calculated  all rational points of the ``cursed curve'', the modular curve $X_s^+(13)$ \citep{cursedcurve}.
 They use an endomorphism of the Jacobian, and do $p$-adic analysis on $p$-adic local heights to make quadratic Chabauty explicit.
@@
 This upper bound compares favorably with classical Coleman-Chabauty, but unlike classical Coleman-Chabauty, we cannot say in general when the conditions of these propositions hold.
-Heuristics show that generally trying multiple primes $p$ of good reduction will yield good results, and if $r < g-1$ the conditions hold for most primes.
+We develop heuristics that suggest that generally trying multiple primes $p$ of good reduction will yield good results; these heuristics say that the conditional upper bound will hold for a set of primes of density $1$, and if $r < g-1$ can even often (in a set of primes of density $e^{-1}$) be improved to prove there are at most $|C(\Q)|$ rational points\todo{Bas, dit is denk ik de beste samenvatting}.
 The methods used to obtain Proposition~\ref{prop:linchabauty} are also amenable to higher precision calculations.
-We also give a hyperelliptic example with $r = 1, g = 2$, where the bound from Proposition~\ref{lin:chabauty} indeed holds.
+We also give a hyperelliptic example with $r = 1, g = 2$, where the bound from Proposition~\ref{prop:linchabauty} indeed holds.
 
@@
 In Section~\ref{section:intersection}, we put all of this information together, culminating in several methods to possibly compute upper bounds on $\left|C(\Z_p)_P \cap \overline{J(\Z)_t}\right|$ with finite precision calculations.
-
-These methods are not always guaranteed to prove finiteness of $C(\Z)_P$.
-In Section~\ref{section:remarks} we treat several possible complications and improvements, partially with explicit examples.
-We also look at the specific case of calculations modulo $p$, i.e.
-in $J(\Z/p^2\Z)_t$, in which the theory simplifies.
-\todo{Bas, wat vind je van het bestaan van dit hoofdstuk?}
-
-Next, in Section~\ref{section:explicit} we focus on how to perform these calculations happening in the Jacobian.
+We also perform a heuristic analysis to show that a simple calculation of linear algebra modulo $p$ is very likely to result in an upper bound of at most $|C(\F_p)|$ for $|C(\Z)|$, and for $r < g-1$ even in an upper bound of $|C(\Z)|$.
+
+The methods developed in the first four sections are not always guaranteed to prove finiteness of $C(\Z)_P$.
+In Section~\ref{section:remarks} we treat several possible complications and improvements, referring to other work on Chabauty for further reading.
+
+Next, in Section~\ref{section:explicit} we focus on how to perform the calculations happening in the Jacobian.
 Here, we use Makdisi's approach of representing a divisor by a subspace of a large Riemann-Roch space.
-We partially follow the article \citep{mascot2018} by Mascot, and also give an original algorithm for explicitly computing the map $C(\Z_p)_P \to J(\Z_p)_t$ in Makdisi's representation.
+We partially follow the article \citep{mascot18} by Mascot, and also give an original algorithm for explicitly computing the map $C(\Z_p)_P \to J(\Z_p)_t$ in Makdisi's representation.
 
@@
 Here, we aim to introduce all the different objects relevant to geometric quadratic Chabauty; we explain why we have to work over $\Z$ instead of over $\Q$ to make geometric quadratic Chabauty make sense; and we explain some of the problems and solutions that working over $\Z$ gives rise to.
+
+\subsection{Preliminaries}\todo{Bas, dit en het volgende stukje zijn nieuw}
+We expect the readers of this thesis to be familiar with algebraic geometry, e.g.
+master students with a specialisation in algebraic geometry.
+The introduction to geometric quadratic Chabauty in Section~\ref{section:quadratic} contains some terms typically not treated in a master; while knowing them will help put the material in context, this section is meant to be understandible even if that is not the case.
+\todo{Bas, nog een specifieke referentie voor voorkennis die ik op kan nemen, of niet per se?}
+
+\subsection{Acknowledgements}
+I would like to thank my supervisor Bas Edixhoven for his help --- I have learnt a great deal since starting on this thesis, and he helped me do so.
+I would also like to thank my father, for all the support he has shown me.
 
@@
 By shrinking $X$ even more, we may assume as $X$ is smooth that $t = (t_1,\dots,t_d): X \to \A^d_{\Z_p}$ is \'etale.
-Now consider the blowup $\Tilde{X}_x \to X$ of $X$ at $x$, and let $\Tilde{X}_x^p$ be the part where $p$ generates the inverse image of the maximal ideal of $O_{X,x}$.
+Now consider the blowup $\widetilde{X}_x \to X$ of $X$ at $x$, and let $\widetilde{X}_x^p$ be the part where $p$ generates the inverse image of the maximal ideal of $O_{X,x}$.
 Equivalently, that is the part where $t_1,\dots,t_d$ are multiples of $p$, so informally it consists of the points that reduce to $x$ modulo $p$.
 
-There is an explicit description of the map $\Tilde{X}_x^p \to X$; as $t$ is \'etale, the ideal of $X$ defining $x$ is the pullback along $t$ of the ideal of $\A^d_{\Z_p}$ defining the origin $a$ over $\F_p$.
-That means that the blowup $\Tilde{X}_x \to X$ is the pullback of the blowup $\Tilde{\A}^d_{\Z_p,a} \to \A_{\Z_p}^d$.
-Then the part $\Tilde{X}_x^p$ is the pullback of the corresponding part of $\Tilde{\A}^d_{\Z_p,a}$, i.e.
-$\Spec \Z_p[\Tilde{x_1},\dots,\Tilde{x_d}] = \Spec \Z_p[x_1/p,\dots,x_d/p]$ with the morphism $\Z_p[x_1,\dots,x_d] \to \Z_p[\Tilde{x_1},\dots,\tilde{x_d}]$ given by $x_i \mapsto p\Tilde{x_i}$.
-That implies that $\Tilde{X}_x^p$ is $\Spec A[t_1/p,\dots,t_d/p]$, with the map $\Tilde{X}_x^p \to X$ given by the inclusion $A \to \Spec A[t_1/p,\dots,t_d/p]$ (remember that the $t_i$ are elements of $O_X(X) = A$).
+There is an explicit description of the map $\widetilde{X}_x^p \to X$; as $t$ is \'etale, the ideal of $X$ defining $x$ is the pullback along $t$ of the ideal of $\A^d_{\Z_p}$ defining the origin $a$ over $\F_p$.
+That means that the blowup $\widetilde{X}_x \to X$ is the pullback of the blowup $\widetilde{\A}^d_{\Z_p,a} \to \A_{\Z_p}^d$.
+Then the part $\widetilde{X}_x^p$ is the pullback of the corresponding part of $\widetilde{\A}^d_{\Z_p,a}$, i.e.
+$\Spec \Z_p[\widetilde{x_1},\dots,\widetilde{x_d}] = \Spec \Z_p[x_1/p,\dots,x_d/p]$ with the morphism $\Z_p[x_1,\dots,x_d] \to \Z_p[\widetilde{x_1},\dots,\widetilde{x_d}]$ given by $x_i \mapsto p\widetilde{x_i}$.
+That implies that $\widetilde{X}_x^p$ is $\Spec A[t_1/p,\dots,t_d/p]$, with the map $\widetilde{X}_x^p \to X$ given by the inclusion $A \to \Spec A[t_1/p,\dots,t_d/p]$ (remember that the $t_i$ are elements of $O_X(X) = A$).
 
@@
 \begin{lem}
-With $X$ as above, there is a natural bijection $X(\Z_p)_x \to \Tilde{X}_x^p(\Z_p)$,
+With $X$ as above, there is a natural bijection $X(\Z_p)_x \to \widetilde{X}_x^p(\Z_p)$,
 \end{lem}
 \begin{proof}
-Note that by (I,2.4.4) of \cite{ega}, a $\Z_p$ point of a scheme $S$ is just an $\F_p$-point $s$ together with a local morphism $\O_{S,s} \to \Z_p$.
+Note that by (I,2.4.4) of \cite{ega}, a $\Z_p$-point of a scheme $S$ is just an $\F_p$-point $s$ together with a local morphism $\O_{S,s} \to \Z_p$.
 In our case, we find that $X(\Z_p)_x$ is naturally in bijection with $\Hom_{\text{local}}(A_x,\Z_p)$.
@@
 exactly those morphisms that extend to a morphism $A[t_1/p,\dots,t_d/p] \to \Z_p$, i.e.
-a $\Z_p$-point of $\Tilde{X}_x^p$.
+a $\Z_p$-point of $\widetilde{X}_x^p$.
 Hence we find the natural bijection.
@@
 \begin{proof}
-As $t$ is locally of finite type, by (IV,17.6.3) of \cite{ega} we have an isomorphism between the $p$-adic completion $O(\Tilde{X}_x^p)^{\wedge p}$ and the completion $\Z_p\angle{\Tilde{x_1},\dots, \Tilde{x_d}}$ of $\Z_p[\Tilde{x_1},\dots,\Tilde{x_d}]$, with the latter completion being the ring of convergent power series, i.e.
-\[
-\Z_p\angle{\Tilde{x_1},\dots, \Tilde{x_d}} = \left\{f \in \Z_p[[\Tilde{x_1},\dots,\Tilde{x_d}]] \mid \forall n \geq 0, f \in \Z[\Tilde{x_1},\dots,\tilde{x_d}] + (p^n) \right\}.
-\]
-By the universal property of completions, as $t$ induces the isomorphism between completions, $t$ also induces a bijection $$\Hom(O(\Tilde{X}_x^p), \Z_p) \to \Hom(\Z_p\angle{\Tilde{x_1},\dots,\Tilde{x_d}},\Z_p) = \Z_p^d.$$ Following all the bijections, we indeed get the bijection we wanted.
+As $t$ is locally of finite type, by (IV,17.6.3) of \cite{ega} we have an isomorphism between the $p$-adic completion $O(\widetilde{X}_x^p)^{\wedge p}$ and the completion $\Z_p\angle{\widetilde{x_1},\dots, \widetilde{x_d}}$ of $\Z_p[\widetilde{x_1},\dots,\widetilde{x_d}]$, with the latter completion being the ring of convergent power series, i.e.
+\[
+\Z_p\angle{\widetilde{x_1},\dots, \widetilde{x_d}} = \left\{f \in \Z_p[[\widetilde{x_1},\dots,\widetilde{x_d}]] \mid \forall n \geq 0, f \in \Z[\widetilde{x_1},\dots,\widetilde{x_d}] + (p^n) \right\}.
+\]
+By the universal property of completions, as $t$ induces the isomorphism between completions, $t$ also induces a bijection $$\Hom(O(\widetilde{X}_x^p), \Z_p) \to \Hom(\Z_p\angle{\widetilde{x_1},\dots,\widetilde{x_d}},\Z_p) = \Z_p^d.$$ Following all the bijections, we indeed get the bijection we wanted.
 \end{proof}
@@
 \label{rem:smoothpointsfunc}
-Note that this construction is functorial, as in the following sense: given two smooth schemes $X,Y$ over $\Z_p$ and two $\F_p$-points $x\in X(\F_p), y\in Y(\F_p)$, a map $f: Y \to X$ satisfying $f(y) = x$ gives rise to a morphism $\Tilde{Y}_y^p \to \Tilde{X}_x^p$.
+Note that this construction is functorial, as in the following sense: given two smooth schemes $X,Y$ over $\Z_p$ and two $\F_p$-points $x\in X(\F_p)$, $y\in Y(\F_p)$, a map $f: Y \to X$ satisfying $f(y) = x$ gives rise to a morphism $\widetilde{Y}_y^p \to \widetilde{X}_x^p$.
 This is a direct consequence of II.7.15 of \citep{hartshorne}.
+\end{rem}
+
+\todo{Volgend stukje is nieuw, en het stukje erna is iets herschreven}\begin{rem}
+\label{rem:torsortangentspace}
+In actual calculations, we will be focusing on $X(\Z/p^2\Z)_x$.
+This set is a natural torsor of the tangent space $T_x X_{\F_p}$ of $X_{\F_p}$ at $x$, which we will describe here.
+We write $R$ for the local ring $O_{X_{\Z/p^2\Z},x}$ and $\m$ for its maximal ideal, and $\overline{R}$ and $\overline{m}$ for their reductions modulo $p$.
+Then an element in $X(\Z/p^2\Z)_x$ is a local morphism $R \to \Z/p^2\Z$.
+As $R/\m = \F_p$, giving such a local morphism is equivalent to giving a map $\m \to p\Z/p^2\Z$ respecting multiplication and sending $p$ to $p$.
+Such a map factors uniquely through $\m/\m^2 \to p\Z/p^2\Z$.
+We see the set $X(\Z/p^2\Z)_x$ is canonically in bijection with $\F_p$-linear maps $\m/\m^2 \to p\Z/p^2\Z$ sending $p$ to $p$.
+Note that $\m/\m^2$ is a $d+1$-dimensional $\F_p$-vector space, and $\overline{\m}/\overline{\m}^2$ is a $d$-dimensional vector space; the map $\m/\m^2 \to \overline{\m}/\overline{\m}^2$ is dividing out by $p$.
+Denoting ${}^\wedge$ to be $\Hom(\cdot,\F_p)$, the exact sequence
+\[
+0 \to p\Z/p^2\Z \to \m/\m^2 \to \overline{\m}/\overline{\m}^2 \to 0
+\]
+can be dualised to
+\[
+0 \to (\overline{\m}/\overline{\m}^2)^\wedge \to (\m/\m^2)^\wedge \to (p\Z/p^2\Z)^{\wedge} \to 0.
+\]
+As $X(\Z/p^2\Z)_x$ is exactly the subset of $(\m/\m^2)^\wedge$ that gets mapped to $p \mapsto 1 \in (p\Z/p^2\Z)^{\wedge}$, we see this is naturally a torsor under $(\overline{\m}/\overline{\m}^2)^\wedge = T_{x} X_{\F_p}$.
+
+Note that this set does not have any more canonical structure; for example, with $X = \A^1_{\Z_p}$ and $x$ is the $\F_p$-point $1$, the set $X(\Z/p^2\Z)_x$ is $\{1 + pi | i \in \F_p\}$, and we see we cannot upgrade the torsor structure.
+This is due to the fact that even after choosing a parameter at $x$ as a point of $X_{\F_p}$, a lift of such a parameter to $X_{\Z/p^2\Z}$ is not unique, and can in fact differ up to translation.
+This is in contrast to the situation over $\F_p[\varepsilon]/(\varepsilon^2)$, where the $\F_p$-algebra structure gives rise to an isomorphism of $\F_p$-vector spaces between $X(\F_p[\varepsilon]/(\varepsilon^2))$ and $T_x X_{\F_p}$; indeed, this is an alternate definition of the tangent space.
 \end{rem}
@@
 We look at the specific case of $X$ being of relative dimension $1$ over $\Z_p$.
-It then turns out that there is additionally a free transitive $\F_p$-action on $X(\Z/p^2\Z)_x$, in the following way.
+Then the $T_x X_{\F_p}$-torsor structure on $X(\Z/p^2\Z)_x$ translates into something more concrete.
 We can parametrise $X(\Z/p^2\Z)_x$ by $t = t_1 : X(\Z/p^2\Z)_x \to p\Z/p^2\Z$; write $P_{\lambda}$ for the point with $t$-value $\lambda p$.
@@
 The resulting function $\Z_p \to \Z_p^g$ is linear modulo $p$, i.e.
-by using that $\Z\angle{z_1,\dots,z_g}$ is $p$-adically complete there are power series $f_1,\dots,f_{g-1} \in \Z_p\angle{z_1,\dots,z_g}$ such that the image of $C(\Z_p)_P$ is exactly given by $V(f_1,\dots,f_{g-1})$, and all $f_i$ are linear modulo $p$ as a consequence of \ref{rem:cartierlinear}.Another way to think of this, is as $C(\Z/p^2\Z)_P$ being an affine line inside $J(\Z/p^2\Z)_t$.
-That $C(\Z/p^2\Z)_P$ is an affine line inside $J(\Z/p^2\Z)_t$ can also be seen more easily, using Remark~\ref{rem:smoothpointsfunc}.
+by using that $\Z\angle{z_1,\dots,z_g}$ is $p$-adically complete there are power series $f_1,\dots,f_{g-1} \in \Z_p\angle{z_1,\dots,z_g}$ such that the image of $C(\Z_p)_P$ is exactly given by $V(f_1,\dots,f_{g-1})$, and all $f_i$ are linear modulo $p$ as a consequence of Remark \ref{rem:cartierlinear}.
+Another way to think of this, is as $C(\Z/p^2\Z)_P$ being an affine line inside $J(\Z/p^2\Z)_t$.
+That $C(\Z/p^2\Z)_P$ is an affine line inside $J(\Z/p^2\Z)_t$ can also be seen more easily: this map can be identified with the tangent map, using the structure of $X(\Z/p^2\Z)_x$ as a torsor over the tangent space from \ref{rem:cartierlinear}.
 
@@
 \label{rem:fislinear}
-We can pick our parameters right such that $C(\Z_p)_P \to J(\Z_p)_t$ is given by $\Z_p \to \Z_p^g$, mapping $\Z_p$ to the last coordinate.
+We can pick our parameters such that $C(\Z_p)_P \to J(\Z_p)_t$ is given by $\Z_p \to \Z_p^g$, mapping $\Z_p$ to the last coordinate.
 Then $f_1,\dots,f_{g-1}$ are just the other parameters at $t$, so they are linear.
-This can be done by picking generators $f_1,\dots,f_{g-1}$ for the ideal defining $\Tilde{C}_P^p$ inside $\Tilde{J}_t^p$.
+This can be done by picking generators $f_1,\dots,f_{g-1}$ for the ideal defining $\widetilde{C}_P^p$ inside $\widetilde{J}_t^p$.
 \end{rem}
@@
 By assumption, we also know $J(\Z)_t$ is in bijection with $J(\Z)_0$, with the bijection giving by translating with a lift of $t$.
-By Subsection \ref{section:smoothzppoints} we know $J(\Z_p)_t$ is in bijection with $\Z_p^{g}$, with the bijection given by evaluating parameters and dividing by $p$.
+By Section \ref{section:smoothzppoints} we know $J(\Z_p)_t$ is in bijection with $\Z_p^{g}$, with the bijection given by evaluating parameters and dividing by $p$.
 Let $\kappa: \Z^r \to \Z_p^g$ be the map resulting from the inclusion $J(\Z)_t \to J(\Z_p)_t$.
@@
 Then $R[[x]]$ denotes as usual the ring of formal powerseries in the $x_i$, and $R[[x]]_0$ denotes those power series with constant term $0$.
-With $x = (x_1,\dots,x_n)$ and $y = (y,_1,\dots,y_m$), let $f \in R[[x]]^m$ and assume $f(0) = 0$.
-Then for $g \in R[[y]]^k$ for some $k\in\Z_{\geq 0}$, we can compose $g$ and $f$ to get $g\circ f := (g_1(f(x)),\dots,g_k(f(x)))\in R[[x]]]^k$.
-This definition makes sense because $f^i$ converges to $0$, so for any $a \in R^{\Z_{\geq 0}} $ the sum $\sum_i a_i f^i$ always converges.
+With $x = (x_1,\dots,x_n)$ and $y = (y_1,\dots,y_m$), let $f \in R[[x]]^m$ and assume $f(0) = 0$.
+Then for $g \in R[[y]]^k$ for some $k\in\Z_{\geq 0}$, we can compose $g$ and $f$ to get \[g\circ f := (g_1(f(x)),\dots,g_k(f(x)))\in R[[x]]]^k.\] This definition makes sense because $f^i$ converges to $0$, so the infinite sum $g_j(f(x))$ converges.
 
@@
 Let $x,y,z$ be vectors of $n$ variables.
-An $n$-dimensional formal group is an element $F = (F_1,\dots,F_n) \in R[[x,y]]_0^n$ satisfying $F \equiv x + y \bmod (x,y)^2$ and $F(F(x,y),z) = F(x,F(y,z))$.
+An $n$-dimensional formal group is an element $F = (F_1,\dots,F_n)$ of $R[[x,y]]_0^n$ satisfying $F \equiv x + y \bmod (x,y)^2$ and $F(F(x,y),z) = F(x,F(y,z))$.
 If furthermore $F(x,y) = F(y,x)$, this formal group is said to be commutative.
@@
 \label{exmp:gmformalgroup}
-Take $n=1$ and $F(x,y) = x + y + xy = (1+x)(1+y)-1$, also known as the multiplicative formal group. This satisfies associativity as $F(F(x,y),z) = (1+x)(1+y)(1+z)-1 = F(x,F(y,z))$.
+Take $n=1$ and $F(x,y) = x + y + xy = (1+x)(1+y)-1$, also known as the multiplicative formal group, as it is a translation of the natural multiplication on $1 + xR[x]$.
+This satisfies associativity by the formula \[F(F(x,y),z) = (1+x)(1+y)(1+z)-1 = F(x,F(y,z)).\]
 \end{exmp}
-Note there is no mention of an inverse, but the following lemma, a formal version of the implicit function theorem, tells us that the inverse follows automatically from the definitions.
+Note there is no mention of an inverse; the following lemma, a formal version of the implicit function theorem, tells us that the inverse follows automatically from the definitions.
 \begin{lem}
 \label{lem:implicitfunction}
-Let $x,y$ have length $n$. Let $F \in R[[x,y]]_0^n$ such that $F \equiv Ax + By \bmod (x,y)^2$ with $B \in \GL_n(R)$. Then there's a unique $\iota \in R[[x]]_0^n$ such that $F(x,\iota(x)) = 0$. 
+Let $x,y$ be vectors of variables of length $n$.
+Let $F \in R[[x,y]]_0^n$ such that $F \equiv Ax + By \bmod (x,y)^2$ with $A \in \Mat_n(R)$ and $B \in \GL_n(R)$.
+Then there is a unique $\iota \in R[[x]]_0^n$ such that $F(x,\iota(x)) = 0$.
 \end{lem}
@@
 \label{lem:formalinverse}
-Let $x$ have length $n$. Let $a \in R[[x]]_0^n$ with $a \equiv Px \bmod x$ for some matrix $P\in \GL_n(R)$. Then there is a unique $b \in R[[x]]_0^n$ such that $a \circ b = b \circ a = x$.
+Let $x$ have length $n$. Let $a \in R[[x]]_0^n$ with $a \equiv Px \bmod (x)^2$ for some matrix $P\in \GL_n(R)$. Then there is a unique $b \in R[[x]]_0^n$ such that $a \circ b = b \circ a = x$.
 \end{cor}
@@
 Also, by $F(0,0) = 0$ we have that $F(x,F(\iota_f,0)) = 0$ so $F(\iota_f,0)$ is in fact equal to $\iota_F$; as $\iota_F \equiv -x \bmod (x)^2$, it has a formal inverse and hence $F(x,0) = x$, so $0$ is indeed a right unit.
-A standard argument now shows that $\iota_F$ is also a left inverse and $0$ is also a right unit, so $F$ gives $R[[x]]$, together with the $(x)$-adic topology, the structure of a group object in the category of topological rings\todo{Bas, je had "category of top.
-rings" gemarkeerd, waarom?}; for two continuous morphisms $f_1,f_2$ from $R[[x]]$ to some ring $A$, given by sending $x$ to $a_1,a_2$ respectively, we define $(f_1 \oplus f_2)(x) = F(a_1,a_2)$, and by our considerations this makes $\Hom_{\text{cont}}(R[[x]],A)$ into a group, functorially in $A$.
-
-Given a smooth scheme $G$ over $\Z_p$ of relative dimension $d$, together with a $\Z_p$-point $e$, we can look at the completion $\Hat{O}_{G,e}$ along the section $e$.
+A standard argument now shows that $\iota_F$ is also a left inverse and $0$ is also a right unit, so $F$ gives $R[[x]]$, together with the $(x)$-adic topology, the structure of a group object in the category of topological $R$-algebras\todo{Nu zou het goed moeten zijn, toch?
+Als nog steeds niet: werk in de categorie $(S,I)$ waar $S$ compleet is m.r.t.
+$I$}; for two continuous morphisms $f_1,f_2$ from $R[[x]]$ to some ring $A$, given by sending $x$ to $a_1,a_2$ respectively, we define $(f_1 \oplus f_2)(x) = F(a_1,a_2)$, and by our considerations this makes $\Hom_{\text{cont}}(R[[x]],A)$ into a group, functorially in $A$.
+
+Given a smooth scheme $G$ over $\Z_p$ of relative dimension $d$, together with a $\Z_p$-point $e$, we can look at the completion $\widehat{O}_{G,e}$ along the section $e$.
 By smoothness, after picking parameters, this is isomorphic as topological $\Z_p$-algebras to the ring of power series $\Z_p[[x_1,\dots,x_d]]$.
-This completion naturally gives rise to a formal scheme denoted $\Spf \Hat{O}_{G,e}$; in a categorical notion, this is a functor on finite length $\Z_p$-algebras sending $A$ to $\Hom_{\text{cont}}(\Hat{O}_{G,e},A)$, but we can also think of it as a locally ringed space with $\Spec \Z_p$ as topological space, and sheaf of rings $\lim_n \Tilde{O_{G,e}/m^n}$ where $m$ is the maximal ideal of $O_{G,e}$.
-The global sections of these sheaf are simply $\Hat{O}_{G,e}$.
+This completion naturally gives rise to a formal scheme denoted $\Spf \widehat{O}_{G,e}$; in a categorical notion, this is a functor on finite length $\Z_p$-algebras sending $A$ to $\Hom_{\text{cont}}(\widehat{O}_{G,e},A)$, but we can also think of it as a locally ringed space with $\Spec \Z_p$ as topological space, and sheaf of rings $\lim_n \widetilde{O_{G,e}/m^n}$ where $m$ is the ideal of $O_{G,e}$ defining $e$\todo{Is dit de juiste formulering?}.
+The global sections of this sheaf are simply $\widehat{O}_{G,e}$.
 
 If furthermore $G$ is a group scheme over $\Z_p$, then this formal scheme promotes to a formal group scheme, i.e.
-for every finite $\Z_p$-algebra $A$ the set $\Hom_{\text{cont}}(\Hat{O}_{G,e},A)$ gets a group structure, functorially in $A$.
-By functoriality, this is the same as an continuous coproduct $\mu: \Hat{O}_{G,e} \to \left(\Hat{O}_{G,e}\right)^{\Hat{\tensor} 2}$.
-After choosing an isomorphism between $\Hat{O}_{G,e}$ and $\Z_p[[x_1,\dots,x_d]]$, let $F_j \in \Z_p[[x,y]]$ denote $\mu(x_j)$.
+for every finite $\Z_p$-algebra $A$ the set $\Hom_{\text{cont}}(\widehat{O}_{G,e},A)$ gets a group structure, functorially in $A$.
+By functoriality, this is the same as an continuous coproduct $\mu: \widehat{O}_{G,e} \to \left(\widehat{O}_{G,e}\right)^{\widehat{\tensor} 2}$.
+After choosing an isomorphism between $\widehat{O}_{G,e}$ and $\Z_p[[x_1,\dots,x_d]]$, let $F_j \in \Z_p[[x,y]]$ denote $\mu(x_j)$.
 Then it is clear that $F_G = (F_1,\dots,F_d)$ is a $d$-dimensional formal group scheme, and commutative if $G$ was commutative.
@@
 $\Z_p[u,u^{-1}]$.
-Then the zero section $e$ is the map sending $u$ to $1$, and we can identify the completion $\Hat{O}_{G,e}$ with the power series ring $\Z_p[[u-1]] \cong \Z_p[[x]]$, sending $u-1$ to $x$.
+Then the zero section $e$ is the map sending $u$ to $1$, and we can identify the completion $\widehat{O}_{G,e}$ with the power series ring $\Z_p[[u-1]] \cong \Z_p[[x]]$, sending $u-1$ to $x$.
 The group structure on $G$ then gives rise to the coproduct $\Z_p[[u-1]] \to \Z_p[[u-1,v-1]], u \mapsto uv$ so the coproduct on $\Z_p[[x]]$ sends $x$ to $uv-1 = (x+1)(y+1) -1 = x + y + xy$.
@@
 
-This formal group tells us exactly how multiplication works on $G(\Z/p^e\Z)_0$; if we let $t = (t_1,\dots,t_d)$ denote the formal parameters giving the isomorphism $\Hat{O}_{G,e} \to \Z_p[[x_1,\dots,x_d]]$, and we represent a point $P$ in $G(\Z/p^e\Z)_0$ by their parameter values $t(P) \in p\Z/p^e\Z$, then the multiplication $p\Z/p^e\Z \times p\Z/p^e\Z \to p\Z/p^e\Z$ is exactly $F$.
+This formal group tells us exactly how multiplication works on $G(\Z/p^e\Z)_0$; if we let $t = (t_1,\dots,t_d)$ denote the formal parameters giving the isomorphism $\widehat{O}_{G,e} \to \Z_p[[x_1,\dots,x_d]]$, and we represent a point $P$ in $G(\Z/p^e\Z)_0$ by their parameter values $t(P) \in p\Z/p^e\Z$, then the resulting multiplication on $p\Z/p^e\Z$ obtained from the group structure on $G(\Z/p^e\Z)_0$, i.e.
+the map $p\Z/p^e\Z \times p\Z/p^e\Z \to p\Z/p^e\Z$, is exactly evaluating $F$.
 By taking limits, $F$ also gives the multiplication on $G(\Z_p)_0$.
@@
 Taking $F$ the multiplicative group as in Example~\ref{exmp:gmformalgroup}, Proposition~1.1 of \citep{honda70} gives us $\omega = \frac{1}{x+1}dx$; as a power series this is $\sum_{j \geq 0} (-x)^j$.
-The formal anti-derivative of this is $\log = \sum_{j \geq 1} \frac{-(-x)^j}{j}dx$, and Theorem $1$ will tell us what we already know in the context of analysis $\log(x + y + xy) = \log(x)+\log(y)$.
+The formal anti-derivative of this is $\log = \sum_{j \geq 1} \frac{-(-x)^j}{j}dx$ (note this is a translate of the $\log$ from analysis), and Theorem $1$ will tell us what we already know in the context of analysis $\log(x + y + xy) = \log(x)+\log(y)$ (this formula is also a translate of the corresponding formula from analysis).
 Then analysis will also explicitly tell us what $\exp$ looks like: namely, $\exp(x) = \sum_{j \geq 1} \frac{x^j}{j!}$.
@@
 \begin{proof}
-Write $\log_{i} = \sum_{I} a_{i,I} x^I$ and $log_{p,i} = \sum_I a_{i,I} p^{|I|-1} x^I$ where $I$ ranges over the multi indices.
+Write $\log_{i} = \sum_{I} a_{i,I} x^I$ and $\log_{p,i} = \sum_I a_{i,I} p^{|I|-1} x^I$ where $I$ ranges over the multi indices.
 Recall that $a_{i,0} = 0$.
@@
 Hence all the $\log_{p,i}$ together give a map $\Z_p^d \to \Z_p^d$.
-By the equality of power series $\log(F(x,y)) = \log(x)+\log(y)$ from the definition of the logarithm, and the fact that all these powerseries converge on $p\Z_p^d$, this $\log_{p,i}$ is indeed a group morphism from $(\Z_p^d,\oplus)$ to $(\Z_p^d,+)$
+By the equality of power series $\log(F(x,y)) = \log(x)+\log(y)$ from the definition of the logarithm, and the fact that all these powerseries converge on $p\Z_p^d$, this $\log_{p,i}$ is indeed a group morphism from $(\Z_p^d,\oplus)$ to $(\Z_p^d,+)$.
 
@@
 As $\log_{p,i} = x_i \bmod (x)^2$, this means that for $p > 2$ we have \[\log_{p,i} \equiv \sum_{|I| = 1} |I|a_{i,I}c_{|I|} x^I \equiv x_i \bmod p.\]
-Note that as $\log_p \equiv x \bmod (x)^2$, by Lemma~\ref{lem:formalinverse} it has an inverse $\exp_p \in \Z_p[[x]]_0^n$.
+Note that as $\log_p \equiv x \bmod (x)^2$, by Lemma~\ref{lem:formalinverse} it has an inverse $\exp_p$ that a priori lies just in $\Z_p[[x]]_0^n$.
 Modulo $p$, this $\exp_p$ must be $x$, which lies in $\Z_p\angle{x}_0^n$; as $\Z_p\angle{x}$ is $p$-adically complete, using Hensel this shows $\exp_p$ is indeed in $\Z_p\angle{x}_0^n$.
@@
 As $S$ is finite and non-empty, all that remains to show is that $S$ is closed under composition.
-We can also characterise $S$ as consisting of images $\overline{f}$ of polynomials $f \in \Z_p[x]_0^d$ such that there is a polynomial $\tilde{f}\in\Z_p[x]_0^d$ with $pf(x) = \tilde{f}(px)$.
-If we then take two elements $\overline{f},\overline{g} \in S$, reductions of $f,g$ respectively with $\tilde{f},\tilde{g}$ such that $pf(x) = \tilde{f}(px), pg(x) = \tilde{g}(px)$, we see that with $h = f\circ g, \tilde{h} = \tilde{f} \circ \tilde{g}$ that $ph(x) = \tilde{h}(px)$ and $h \equiv \overline{f} \circ \overline{g} \bmod p^m$, so indeed $\overline{f} \circ \overline{g}$ is also an element of $S$.
+We can also characterise $S$ as consisting of images $\overline{f}$ of polynomials $f \in \Z_p[x]_0^d$ such that there is a polynomial $\widetilde{f}\in\Z_p[x]_0^d$ with $pf(x) = \widetilde{f}(px)$.
+If we then take two elements $\overline{f},\overline{g} \in S$, reductions of $f,g$ respectively with $\widetilde{f},\widetilde{g}$ such that $pf(x) = \widetilde{f}(px), pg(x) = \widetilde{g}(px)$, we see that with $h = f\circ g, \widetilde{h} = \widetilde{f} \circ \widetilde{g}$ that $ph(x) = \widetilde{h}(px)$ and $h \equiv \overline{f} \circ \overline{g} \bmod p^m$, so indeed $\overline{f} \circ \overline{g}$ is also an element of $S$.
 Hence we see $S$ is indeed a group, and as $\log_p \bmod p^m$ is an element of it, so is $\exp_p \bmod p^m$.
-\todo{Bas, dit is gelukt wat simpeler te maken, geen lelijke berekeningen meer :)}.
 \end{proof}
@@
 \begin{proof}[Proof of Theorem~\ref{thm:kappanice}]
-Write $\log_p$ for the logarithm corresponding to the formal group corresponding to the The map $\kappa_0: \Z^d \to \Z_p^g$ given by the inclusion $J(\Z)_0$ to $J(\Z_p)_0$ is a group morphism with the group structure on $\Z^d$ being addition and the group structure on $\Z_p^g$, denoted by $\oplus$, given by the bijection with $J(\Z_p)_0$ induced by choosing parameters at $0$, and $\kappa$ is $\kappa_0 \oplus t$.
+Write $\log_p$ for the logarithm corresponding to the formal group corresponding to the map $\kappa_0: \Z^d \to \Z_p^g$ given by the inclusion $J(\Z)_0$ to $J(\Z_p)_0$ is a group morphism with the group structure on $\Z^d$ being addition and the group structure on $\Z_p^g$, denoted by $\oplus$, given by the bijection with $J(\Z_p)_0$ induced by choosing parameters at $0$, and $\kappa$ is $\kappa_0 \oplus t$.
 Then by Lemma~\ref{lem:formallog} the map $\kappa$ factors as in the diagram of groups
@@
 \label{cor:closurejac}
-The map $\kappa$ extends uniquely to a continuous map $\kappa: \Z_p^r \to \Z_p^g$, given by the same power series, and the closure $\overline{J(\Z)_t} \subset J(\Z_p)_t$ is given by the image of $\Z_p^r$ under $\kappa$.
+The map $\kappa: \Z^r \to \Z_p^g$ extends uniquely to a continuous map $\kappa: \Z_p^r \to \Z_p^g$, given by the same power series, and the closure $\overline{J(\Z)_t} \subset J(\Z_p)_t$ is given by the image of $\Z_p^r$ under $\kappa$.
 \end{cor}
@@
 Let $C,J,p,P,t$ be as in the overview, let $\kappa$ be as in Theorem~\ref{thm:kappanice} and let $f_1,\cdots,f_{g-1}$ be as in Subsection~\ref{subsection:czptojzp}.
-Define $\lambda_1 = \kappa^*f_1,\dots,\lambda_{g-1} = \kappa^*f_{g-1}$ to be the pullbacks along $\kappa$ of the $f_i$.
+Define $\lambda_1 = \kappa^*f_1,\dots$, $\lambda_{g-1} = \kappa^*f_{g-1}$ to be the pullbacks along $\kappa$ of the $f_i$.
 Then $\kappa$ induces a surjection from $Z(\lambda_1,\dots,\lambda_{g-1}) \subset \Z_p^r$ to $C(\Z_p)_P \cap \overline{J(\Z)_t}$.
@@
 There are several, sometimes ad hoc, ways of proving finiteness.
+We start by looking simply at calculations modulo $p$.
 We let $I$ denote the ideal inside $\Z_p\angle{x_1,\dots,x_r}$ generated by $\lambda_1,\dots,\lambda_{g-1}$, and $A$ the quotient $\Z_p\angle{x_1,\dots,x_r}/I$.
-Noting that $Z(\lambda_1,\dots,\lambda_{g-1}) = \Hom_{\Z_p}(A/I,\Z_p)$, we can use the following theorem, the statement and proof of which come from \citep{edixhoven20}.
+Noting that $Z(\lambda_1,\dots,\lambda_{g-1}) = \Hom_{\Z_p}(A,\Z_p)$, we can use the following theorem, the statement and proof of which come from \citep{edixhoven20}.
 
@@
 \label{prop:finedix}
-Let $\overline{A} = A/pA$ and $\overline{I} = I\overline{A}$.
+Let $\overline{A} = A/pA$.
 Assume $\overline{A}$ is finite.
-Then $\overline{A}$ is the product $\prod_{m \in \MaxSpec(\overline{A})} A_m$, and the sum of $\dim_{\F_p} \overline{A}_m$ over those $m\in \MaxSpec(\overline{A})$ with $\overline{A}/m = \F_p$ is an upper bound for $\Hom(A/I,\Z_p)$.
+Then $\overline{A}$ is the product $\prod_{m \in \MaxSpec(\overline{A})} A_m$, and the sum of $\dim_{\F_p} \overline{A}_m$ over those $m\in \MaxSpec(\overline{A})$ with $\overline{A}/m = \F_p$ is an upper bound for $\Hom(A,\Z_p)$.
 \end{prop}
 \begin{proof}
-We start by proving that $A$ is $p$-adically complete. This follows from the more general fact of a quotient
-\todo{give proof}
-\todo{Bas, ik begrijp het bewijs niet helemaal\dots }
+We start by proving that $A$ is $p$-adically complete.
+This follows from the following more general fact: let $R$ be a Noetherian ring, and $I,J$ two ideals of $R$ such that $R$ is $J$-adically complete.
+We will then prove that $R/I$ is also $J$-adically complete.
+By Theorem 10.17 of \cite{atiyah}, any module over a complete ring injects into its completion, i.e.
+the map $R/I \to \widehat{R/I}$ is injective.
+Furthermore, as completion is exact, the surjection $R \to R/I$ gives rise to a surjection $R \to \widehat{R/I}$.
+The kernel contains $I$, so the map $R/I \to \widehat{R/I}$ is surjective and hence an isomorphism.
+Then note that $\Z_p\angle{x_1,\dots,x_r}$ is itself the $p$-adic completion of $\Z_p[x_1,\dots,x_r]$ and hence is complete, so $A$ is indeed $p$-adically complete.
+
+Next, we use that $\overline{A}$ is a finite $\Z_p$-module, generated by the image of some finite set $S \subset A$.
+Using the series of exact sequences \[0 \to \overline{A} \xrightarrow{\cdot p^{n-1}} A/p^nA \to A/p^{n-1}A \to 0,\] we see by induction that $S$ indeed generates $A/p^nA$ as a $\Z_p$-module and by completeness, $S$ generates $A$ as well.
+Hence $A$ is a finite rank $\Z_p$-algebra.
+
+Remember that a finite dimension algebra over a field is Artinian, and Artin rings are product of Artin local rings (Theorem 8.7 of \cite{atiyah}).
+So, we can write the $\F_p$-algebra $\overline{A}$ as a product of Artin local rings.
+As idempotents in $\overline{A}$ lift to $A$, we see this factorisation lifts, and we can write $A$ as
+\[
+\prod_{m \in \MaxSpec(\overline{A})} A_m.
+\]
+Then any morphism $A \to \Z_p$ factors through $A_m$.
+If we tensor $A_m$ with $\Q_p$, we see that, after dividing out the nilradical, it is a product of fields.
+Hence $\Hom(A_m,\Z_p)$ is at most $\text{rank}_{\Z_p}(A_m)$, and can be non-empty if and only if $A/m$ is isomorphic to $\F_p$.
+We conclude that the sum of $\dim_{\F_p} \overline{A}_m$ over those $m\in \MaxSpec(\overline{A})$ with $\overline{A}/m = \F_p$ is an upper bound for $\Hom(A,\Z_p)$
 \end{proof}
@@
 To utilise this theorem, we only need to calculate the $\lambda_i$ modulo $p$.
-In our case, of all $\kappa_i$ and $f_i$ being linear modulo $p$, so are the $\lambda_i$, and we get as special case the following corollary.
+In our case, of all $\kappa_i$ and $f_i$ being linear modulo $p$ (as polynomials; they do not necessarily give linear map), so are the $\lambda_i$, and we get as special case the following corollary.
 \begin{cor}
 \label{cor:finedixlinear}
-If the linear system of equations $\forall i: \lambda_i \equiv 0 \bmod p$ has respectively no or one solution, there is respectively none or at most one point in $C(\Z)_P$.
+If the (not necessarily homogenous) linear system of equations $\forall i: \lambda_i \equiv 0 \bmod p$ has respectively no or one solution, there is respectively none or at most one point in $C(\Z)_P$.
 \end{cor}
 
-This leads to a now trivial proposition.
+This leads to a now trivial proposition.\todo{Bas, proposition of theorem?}
 \begin{prop}
 \label{prop:linchabauty}
-If for all points $P \in C(\F_p)$, the linear system of $g-1$ equations defining $U(\Z_p)_P$ in $\overline{J(\Z)_P}$ modulo $p$ has at most one solution, we get the inequality
+If for all points $P \in C(\F_p)$, the linear system of $g-1$ equations modulo $p$ defining $C(\Z_p)_P \subset J(\Z_p)_t$ pulled back to $\overline{J(\Z)_t}$ has at most one solution, we get the inequality
 \[
@@
 
+Of note is that this upper bound for $C(\Z)$ does not even depend on the genus, and behaves agreeably when compared to the upper bound in Theorem 5.3 of \citep{poonen12}, which tells us that $|C(\Z)| \leq |C(\F_p)| + 2g-2$ under the much lighter condition of $r < g, p > 2g$ where $p$ is still a prime of good reduction.
+To summarise: in proposition~\ref{prop:linchabauty} we sacrifice certainty for being to able to prove much sharper bounds.
+However, a simple heuristic analysis shows that the conditions are quite likely to be satisfied, as we shall see in the following lemma and proposition.
+
+\begin{lem}
+\label{lem:probindep}
+Let $\F_p$ be any finite field, let $A$ be a random $(n+k)\times n$ matrix over $\F_p$, and $b$ randomly chosen from $\in \F_p^{n+k}$.
+Then the probability that $Ax=0$ has more than one solution is at most $c_k (p-1)^{-(k+1)}$ and the probability that $Ax=b$ has more than one solution is at most $c_k (p-1)^{-(k+1)} p^{-(k+1)}$ where $c_k = \sum_{\ell = 0}^k \binom{k}{\ell}/(\ell+1)!
+\leq 2^k$.
+\end{lem}
+\begin{proof}
+Let $A_i$ denote the rows of $A$, let the space $V_i$ be the linear span of $A_1,\dots,A_i$ with $V_0 = 0$, and let $E_i$ denote the event that $A_i \in V_{i-1}$.
+Then we see the row space of $A$ can only fail to be $\F_p^n$ if for $k+1$ different indices $i$, the event $E_i$ takes place.
+As clearly $\dim V_i \leq i$, we see that $\P(E_i)$ is at most $p^{i-1-n}$ for $i \leq n$ and at most $p^{-1}$ for $i \geq n$.
+Finally note, that $\P(E_i | E_{j_1} \wedge \cdots \wedge E_{j_\ell}) \leq \P(E_i)$ if all $j_1,\dots,j_\ell$ are smaller than $i$.
+Now we can make the following calculation
+\begin{align*}
+\P(\text{At least } k+1 \text{ of } E_i \text{ occur}) &= \P\left(\bigvee_{1\leq i_1 < \cdots < i_{k+1} \leq n + k} \bigwedge_{j=1}^{k+1} E_{i_j} \right) \\
+&\leq \sum_{1\leq i_1 < \cdots < i_{k+1} \leq n + k} \P\left(\bigwedge_{j=1}^{k+1} E_{i_j}\right) \\
+&\leq \sum_{1\leq i_1 < \cdots < i_{k+1} \leq n + k} \prod_{j=1}^{k+1} \P(E_{i_j}) \\
+&\leq \sum_{1\leq i_1 < \cdots < i_{k+1} \leq n + k} \prod_{j=1}^{k+1} p^{{\min(i_j-1-n,-1)}}.
+\end{align*}
+Then we note that for $\ell = 0,\dots,k$ we have
+\begin{align*}
+\sum_{1\leq i_1 < \cdots < i_{\ell} \leq n}\prod_{j=1}^{\ell} p^{i_j-1-n} &\leq \frac{1}{\ell!} \sum_{1\leq i_1,\dots,i_{\ell} \leq n} \prod_{j=1}^{\ell} p^{i_j-1-n} \\
+&= \frac{1}{\ell!} (\frac{1}{p^n} + \frac{1}{p^{n-1}} + \cdots + \frac{1}{p})^\ell\\
+&\leq \frac{1}{\ell! (p-1)^\ell}.
+\end{align*}
+Now if we partition the sum over all $1\leq i_1 < \cdots < i_{k+1} \leq n + k$ based on how many of the indices lie in $[n+1,n+k]$, we find
+\begin{align*}
+\sum_{\substack{1\leq i_1 < \cdots \\ < i_{k+1} \leq n + k}} \prod_{j=1}^{k+1} p^{{\min(i_j-1-n,-1)}} &= \sum_{m = 0}^{k} \binom{k}{m}p^{-m}\sum_{1\leq i_1 < \cdots < i_{k+1-m} \leq n}\prod_{j=1}^{k+1-m} p^{i_j-1-n}\\
+&\leq \sum_{m = 0}^{k} \binom{k}{m}p^{-m}(p-1)^{-(k+1-m)}/(k+1-m)! \\
+&\leq (p-1)^{-(k+1)} \sum_{\ell = 0}^k \binom{k}{\ell}/(\ell+1)! \\
+& = c_k (p-1)^{-(k+1)}.\\
+\end{align*}
+This shows that the probability of $Ax = 0$ having more than one solution is indeed at most $c_k (p-1)^{-(k+1)}$.
+Furthermore, if $Ax = 0$ has more than one solution, then $\text{rank} A < n$ so there are at most $p^{n-1}$ possible values of $b$ such that $Ax = b$ has multiple solutions, hence the total probability is at most $c_k (p-1)^{-(k+1)} p^{-(k+1)}$.
+\end{proof}
+
+For a generic point $P \in C(\F_p)$, we might assume the linear system modulo $p$ defining $C(\Z_p)_P$ pulled back to $\overline{J(\Z)}$ is completely random, but for point $P \in C(\F_p)$ coming from $\Z$-points, we always know there is at least one solution; and indeed, it turns out that with a translation, one can assume the linear system is homogenous.
+\begin{prop}
+\label{prop:probwork}
+Assume that the map $C(\Z) \to C(\F_p)$ is injective.
+Assume that for points $P \in C(\F_p)$ coming from $C(\Z)$ the linear system modulo $p$ defining $C(\Z_p)_P$ pulled back to $\overline{J(\Z)}$ is a random homogenous linear system, and for all other points, it is a random not necessarily homogenous linear system.
+Assume furthermore that all these linear systems are independently random.
+Then for $p > 4g^2$ the conditions of Proposition~\ref{prop:linchabauty} are not satisfied with probability at most
+\[
+c_{g-1-r}(|C(\Z)|+2)p^{-(g-r)}
+\]
+Hence for $r = g-1$ we expect a subset of primes with density $1$ to show finiteness of $C(\Z)$, and for $r < g-1$ we expect all but a finite number to work.
+These expectations are uniform in $g$ and $|C(\Z)|$.
+\end{prop}
+\begin{proof}
+First note that our linear systems consist of $g-1$ equalities in $r$ variable, i.e.
+we can use Lemma~\ref{lem:probindep} with $k = g-1-r$.
+Let $a$ denote $|C(\Z)|$, and let $b$ denote $|C(\F_p)|-a$.
+Under all our assumptions, the probability of none of the systems having more than one solutions is at least
+\[
+\left(1 - c_k(p-1)^{-(k+1)}\right)^{a} \left(1 - c_k(p-1)^{-(k+1)}p^{-(k+1)}\right)^b.
+\]
+Using the Bernoulli's inequality, this is at least 
+\[
+\left(1- ac_k(p-1)^{-(k+1)}\right)\left(1 - c_k(p-1)^{-(k+1)}p^{-(k+1)}\right)
+\]
+which is itself at least $1 - ac_k(p-1)^{-(k+1)} - bc_k(p-1)^{-(k+1)}p^{-(k+1)}$.
+Using the Hasse-Weil bound, we can make the estimate $b \leq 2p$.
+Then we can lower bound this by $1 - ac_k(p-1)^{-(k+1)} - 2c_k(p-1)^{-(2k+1)}) \geq 1 - c_k(a+2)(p-1)^{-(k+1)}$.
+
+For $r = g-1$ we have $k= 0$, and the probability of one of the conditions not being satisfied is at most $(a+2)/p$, hence we indeed expect an infinite but density $0$ subset of primes to fail.
+For $r < g-1$, we have $k > 0$; as $\sum_{p\text{ prime}} 1/p^2$ converges, one may expect a finite number of primes to fail.
+\end{proof}
 \begin{rem}
-\label{rem:prob}
-Note that in general a linear system of $n + k$ equations over a vector space of dimension $n$ over a finite field of size $p$ has more than one solution with probability at most $\frac{1}{(p-1)^{k+1}}$.
-By the Hasse-Weil bound, assuming $p = \Omega(g^2)$, and that all linear systems of Proposition~\ref{prop:linchabauty} for all $P \in C(\F_p)$ are independent, we see that the conditions of these propositions have a high condition of being satisfied if $r<g-1$, and may even work for the case $r = g-1$ with probability around $e^{-1}$ for $p$ large enough.
-Hence trying a few small primes should generally be enough.
+The author believes that this proposition gives a strong reason to expect the method of only computing modulo $p$ to work in practice; and if it does not, one can just take the next prime.
 \end{rem}
-
-Of note are that this upper bound for $C(\Z)$ does not even depend on the genus, and behaves agreeably when compared to the upper bound in Theorem 5.3 of \citep{poonen12}, which tells us that $|C(\Z)| \leq |C(\F_p)| + 2g-2$ under the much lighter condition of $r < g, p > 2g$ where $p$ is still a prime of good reduction.
-To summarise: in proposition~\ref{prop:linchabauty} we sacrifice consistency for being to able to prove much sharper bounds.
-
-In general, even if $\overline{A}/\overline{I}$ is not finite, we see $\Hom(A/I,\Z_p)$ factors through $A/(I:p)$ where $(I:p) = \{x \in A \mid \exists k \in \Z_{\geq 0}: p^kx \in A\}$.
-Then a higher precision calculation of the $\lambda_i$ can still lead to a succesful application of Proposition~\ref{prop:finedix}.
+\begin{rem}
+Note that if $r=g-1$, as we expect a random $n\times n$-matrix to be invertible, we expect that if the conditions of Proposition~\ref{prop:linchabauty} are satisfied, we generally find an upper bound for $|C(\Z)|$ slightly lower than $|C(\F_p)|$.
+However, a not necessarily inhomogenous linear system of dimension $(n+k)\times n$ is solvable with probability at most $p^{-k}$, as the dimension of the column space is at most $n$.
+Hence for $r = g-2$ we can expect to find an upper bound of about $|C(\Z)|+1$, and with probability about $(1-\frac{1}{p})^{|C(\F_p)|} \approx (1-\frac{1}{p})^p \approx e^{-1}$ \todo{Extra heuristiek!}even the optimal upper bound of $|C(\Z)|$.
+For $r = g-3$, we even expect to find an upper bound of $|C(\Z)|$ for a set of primes of density $1$; and for $r < g-3$, for all but a finite set of primes.
+\end{rem}
+
+Now we briefly discuss what can be done if for a specific prime $p$, the conditions of Proposition~\ref{prop:linchabauty} are not satisfied.
+In general, even if $\overline{A}$ is not finite, we see $\Hom(A,\Z_p)$ factors through $\Z_p\angle{x_1,\dots,x_r}/(I:p)$ where $(I:p)$ is the saturation \[\{x \in \Z_p\angle{x_1,\dots,x_r} \mid \exists k \in \Z_{\geq 0}: p^kx \in I\}\] Then a higher precision calculation of the $\lambda_i$ can still lead to a succesful application of Proposition~\ref{prop:finedix}.
 
@@
 \section{Complications and improvements}
-\label{section:remarks} \todo{Bas, ik ben niet echt groot fan van dit hoofdstuk, voegt het iets toe denk je?}
+\label{section:remarks} \todo{Bas, het is niet alleen werk van anderen, hopelijk is het nu duidelijker}
 In this section, we quickly make some further remarks on how or when to apply the theory we have built up in previous section to real cases.
@@
 We can even use this to improve our calculations if we already have $r < g$, but $r'$ is even smaller.
-On the other hand, if $J(\Z)$ is open in $J(\Z_p)$, there is no way to apply Chabauty's method to the curve.
+On the other hand, if $J(\Z)$ is dense in $J(\Z_p)$, there is no way to apply Chabauty's method to the curve.
 \item Note that in all of the discussion of the previous section, we are calculating upper bounds for the cardinality of $C(\Z_p)_P \cap \overline{J(\Z)_t}$.
-It can and does however happen that this set is strictly bigger than $C(\Z)_P$.
-For example, there might be a $K$-point $Q$ where $K$ is a quadratic field where $p$ splits, such that $Q-b$ is non-$p-$torsion, and then $Q-b$ also lies in the closure of $J(\Z)$.
-We refer to \citep{Balakrishnan19} for further examples and explanations.
-\todo{finish}
+It can and does however happen that this set is strictly bigger than $C(\Z)_P$, as shown in \citep{Balakrishnan19}, where Coleman-Chabauty is used on a whole database of curves.
+They treat several possible cases and examples where the set is bigger.
+For example, there might be a $K$-point $Q$ where $K$ is a quadratic field where $p$ splits, such that $Q-b$ is non-$p$-torsion, and then $Q-b$ also lies in the closure of $J(\Z)$.\todo{Nee, niet echt, hun argument is anders omdat ze Coleman-Chabauty doen}
 \item An important part of doing these calculations, is working with the Mordell-Weil group $J(\Z)$.
@@
 We work in the Jacobian using Makdisi's representations for divisors.
-As we are using and adding on to an implementation by Mascot \cite{mascot2018}, we briefly introduce his notation.
-This is a summary of section 2.1 in \cite{mascot2018}.
+As we are using and adding on to an implementation by Mascot \cite{mascot18}, we briefly introduce his notation.
+This is a summary of section 2.1 in \cite{mascot18}.
 
@@
 \label{lem:poles2d0i+}
-The poles of $F$, as defined in line~\ref{alg:abeljacobi:defF1} or \ref{alg:abeljacobi:defF2}, are exactly $g(\infty_+ + \infty_-) + \infty_+$. 
+The poles of $F$, as defined in line~\ref{alg:abeljacobi:defF1} or \ref{alg:abeljacobi:defF2}, are $g(\infty_+ + \infty_-) + \infty_+$. 
 \end{lem}
@@
 Letting $g^r(v)$ be the polynomial $(f^r(v)-1)/v$, we can rewrite the equation for $C$ to $(w-1)(w+1) = vg^r(v)$.
-As the derivative of $(w-1)(w+1)$ to $w$ doesn't vanish at both of $\infty_\pm$, we see that $v$ is a uniformiser at both these points.
+As the derivative of $(w-1)(w+1)$ to $w$ does not vanish at both of $\infty_\pm$, we see that $v$ is a uniformiser at both these points.
 That means that $v_{\infty_\pm}(x)$, the order of $x$ at $\infty_\pm$, is equal to $-1$.
@@
 \begin{proof}[Algorithm/proof]
-Let $(a,b)$ be the Mumford representation of a divisor $D = D(a,b)$.
+Let $(a,b)$ be the Mumford representation of a divisor $D$.
 Let $\deg a = d \leq g$, and denote $D_{\text{aff}}$ for the affine part of $D$.
-Note that $E-D_0 = D$ for $E = D_0 - D_{\text{aff}} + d\infty_+$ an effective divisor, so $\Lcal(2D_0 - E) = \Lcal(D_0 - D)$ is a Makdisi representation for $[D]$.
+Note that $E-D_0 = D$ for $E = D_0 + D_{\text{aff}} - d\infty_+$, an effective divisor, so $\Lcal(2D_0 - E) = \Lcal(D_0 - D)$ is a Makdisi representation for $[D]$.
 
 Of course, we can rewrite $\Lcal(D_0 -D)$ as 
-\[
-\Lcal((g+1)\infty_- + (g+1+d)\infty_+ - D_{\text{aff}}) = \Lcal(2D_0 - D_{\text{aff}} ) \cap \Lcal((g+1)\infty_- + (g+1+d)\infty_+).
-\]
+\begin{multline*}
+\Lcal((g+1)\infty_- + (g+1+d)\infty_+ - D_{\text{aff}}) \\= \Lcal(2D_0 - D_{\text{aff}} ) \cap \Lcal((g+1)\infty_- + (g+1+d)\infty_+).
+\end{multline*}
 
@@
 and then it should follow over $\Z_p$ so over $\Z/p^k\Z$.
-\todo{See [Todo]}[TODO:It is not necessarily true that a map that is an isomorphism when tensored with $\F_p$ and $\Q_p$ it is an isomorphism, but that is of course true if the map is between free modules, as I think it is here, right?
+\todo{Bas, ik wilde je nog vragen over de [Todo]}[TODO:It is not necessarily true that a map that is an isomorphism when tensored with $\F_p$ and $\Q_p$ it is an isomorphism, but that is of course true if the map is between free modules, as I think it is here, right?
 As everything embeds into $\Z_p^n$ by evaluating at points, and submodule of free is free]
 
-For $\Lcal((g+1)\infty_- + (g+1+d)\infty_+)$, we first inductively calculate $W_n := \Lcal(2D_0 - n\infty_-)$.
-For $W_1$ we have a basis $1,x,\dots,x^{2g+1},y,xy,\dots,x^g y, x^{g+1}y+x^{2g+2}$, and for $n \geq 0$ we have by a simple use of Lemma 2.2 of \citep{makdisi04} that for $1 \leq n \leq g+1$ we have $W_{n} = \{s \in \Lcal(2D_0) \mid s\Lcal(2D_0) \in W_1 \cdot W_{n-1}\}$.
+For $\Lcal((g+1)\infty_- + (g+1+d)\infty_+)$, we first inductively calculate the spaces $W_n := \Lcal(2D_0 - n\infty_-)$.
+For $W_1$ we have a basis $1,x,\dots,x^{2g+1},y,xy,\dots$, $x^g y, x^{g+1}y+x^{2g+2}$, and for $n \geq 0$ we have by a simple use of Lemma 2.2 of \citep{makdisi04} that for $1 \leq n \leq g+1$ we have \[W_{n} = \{s \in \Lcal(2D_0) \mid s\Lcal(2D_0) \in W_1 \cdot W_{n-1}\}\].
 This is a purely linear constraint, hence simple linear algebra allows us to calculate all $W_n$ for $n \leq g+1$.
@@
 \] 
-Once again noting that we can write down an explicit basis for $\Lcal((g+1+d)(\infty_+ + \infty_-))$, this allows us to calculate $\Lcal((g+1)\infty_- + (g+1+d)\infty_+)$ and to finish the computation.
+Once again noting that we can write down an explicit basis for the space $\Lcal((g+1+d)(\infty_+ + \infty_-))$, this allows us to calculate $\Lcal((g+1)\infty_- + (g+1+d)\infty_+)$ and to finish the computation.
 \end{proof}
 
-\subsection{Parameters at $J$}
+\subsection{Parameters at \texorpdfstring{$J$}{J}}
 \label{subs:paramj}
@@
 
-\subsection{Interpolating polynomials}
+\subsection{Interpolating polynomials}\todo{Dit stuk is herschreven}
 \label{subs:interpolate}
-The $\lambda_i$ from are in general not computationally available, as they are power series, but we can approximate them modulo powers of $p$.
+The $\lambda_i$ from Theorem~\ref{thm:final} are in general not computationally available, as they are power series, but we can approximate them modulo powers of $p$.
 For example, we know that the $\lambda_i$ are linear modulo $p$.
 And in particular, if $f_1,\dots,f_{g-1}$ are as in Remark~\ref{rem:fislinear}, then $\lambda_i = \kappa_i$ for $i \leq g-1$, so they are also of degree at most $m$ modulo $p^m$ for $m < p-1$.
-Knowing this, we can compute $\lambda_i$ modulo powers of $p$ by extrapolation, and the following lemma, an immediate consequence of Lagrange interpolation, tells us how.
-\begin{lem}
-\label{lem:interpolate}
-Let $R$ be a ring, and assume operations in $R$ are $O(1)$, $f \in R[x]$ with $x = (x_1,\dots,x_n)$ a polynomial of degree at most $m$, and $S$ a subset of $R$ with $S-S \subset \{0\} \cup R^*$ and $|S| > m$.
-Then $f$ is uniquely determinable in $O(nm^{n+1})$ by its values on $S^n$.
-\todo{Make the complexity better} There is a better complexity algorithm I think, at least clearly so for $m=1$.
-I have to work on this a bit more.
-For $m = 1$, clearly we only need $n+1$ evaluations.
-\end{lem}
-\begin{proof}
-Both uniqueness and construction follow from the case with $n=1$; uniqueness from the fact that the ideals $\{(x-s) \mid s \in S\}$ are pairwise coprime, and the construction is Lagrange interpolation.
-The complexity follows easily from induction on $n$ and the formula for Lagrange interpolation.
-\end{proof}
+Knowing this, we can compute $\lambda_i$ modulo powers of $p$ by interpolation, and the following formula, coming from \cite{salzer}: if $f$ is a polynomial over a ring $R$ of degree $m$ in $n$ variables and $m!$ is a unit in $R$, then we have the equality of polynomials
+\[
+f(x_1,\dots,x_n) = \sum_{i_1 + \cdots + i_n \leq m} f(i_1,\dots,i_n) \binom{m-x_1-\cdots-x_n}{m-i_1-\cdots-i_n} \prod_{j=1}^n \binom{x_j}{i_j}.
+\]
+Note that this formula requires evaluation of $f$ at $\binom{m+n}{n}$ points; this is clearly optimal, as there are $\binom{m+n}{n}$ monomials of degree at most $m$.
+Also note that for $m=1$, the complexity of calculating this formula is simply $O(n)$ applications of $f$, and $O(n)$ calculations in $R$.
 
@@
 Using Proposition~\ref{prop:finedix} or another way, we can hope to find an upper bound on the number of common zeroes of the $\lambda_i$, and hence an upper bound on $C(\Z)_P$.
+
+This formula for interpolation unfortunately does not work for $m \geq p$; then the values of $\lambda_i$ on $\F_p^{n}$ do not determine $\lambda_i$, and one needs to evaluate on extensions on $\F_q^n$ and look for more general interpolation formulas (e.g., Lagrange interpolation).
 
@@
 
-Then by Remark~\ref{rem:complexityabel} and Lemma~\ref{lem:interpolate}, we can compute $\lambda_i \bmod p$ in $O(rg^{\omega+1})$; then solving the linear system of equations $\forall i \lambda_i \equiv 0 \bmod p$ has complexity lower than that, and hence checking if $|C(\Z)_P|$ is at most $1$ can be done in $O(rg^{\omega+1})$.
+Then by Remark~\ref{rem:complexityabel} and Section~\ref{subs:interpolate}, we compute $\lambda_i \bmod p$ in $O(rg^{\omega+1})$; then solving the linear system of equations $\forall i \lambda_i \equiv 0 \bmod p$ has complexity lower than that, and hence checking if $|C(\Z)_P|$ is at most $1$ can be done in $O(rg^{\omega+1})$.
 Repeating this for all $\F_p$-points, gives by the Hasse-Weil bound a complexity of $O\left((p + g\sqrt{p})rg^{\omega+1}\right)$.
@@
 \]
+This curve has genus $2$, and the Mordell-Weil group is isomorphic to $\Z$. This curve is also treated in Example~8.2 of \citep{poonen12}.
+
 We denote the standard involution on this curve by $\sigma$.
@@
 Also, identifying $J(\Z)_0$ with $\Z^r$, the image of $J(\Z)_0$ in $J(\Z/p^2\Z)_0$ can be given as a map $\F_p^r \to J(\Z/p^2\Z)_0$.
-Choosing parameters by giving a local chart $J \to \P(V_2)$, we want to exactly show that the two maps $C(\Z/p^2\Z)_\theta \to J(\Z/p^2\Z)_0, \F_p^r \to J(\Z/p^2\Z)_0$ together form a map $\F_p \oplus \F_p^r \to J(\Z_p^2\Z)_0$ with kernel $0$.
+Choosing parameters by giving a local chart $J \to \P(V_2)$, we want to exactly show that the two maps $C(\Z/p^2\Z)_\theta \to J(\Z/p^2\Z)_0, \F_p^r \to J(\Z/p^2\Z)_0$ together form a map $\F_p \oplus \F_p^r \to J(\Z/p^2\Z)_0$ with kernel $0$.
 Now that this is a statement in linear algebra, it can be verified easily, and it turns out that indeed the residue disc of $C(\Z)$ containing $\theta$ contains only $\theta$.
@@
 
-\todo{Bas, what do I do with my code?} Do I just paste it in at the end, give a link to the github page, or just not give it all?
+Code for the calculations in this section can be found in \citep{spelier2020}.
+\todo{Bas, hiervoor ben ik nu gegaan}
 
@@
 \label{section:quadratic}
-In this section we attempt to give an introduction to the article~\citep{edixhoven20} aimed to introduce all the players in Chabauty at a slightly slower pace.
-We will omit any proofs.For further reading, see for example \citep{hashimoto20}, an in progress cartoon guide to the article by Edixhoven-Lido.
+In this section we attempt to give an introduction to the article~\citep{edixhoven20} aimed to introduce all the players in quadratic Chabauty at a slightly slower pace.
+We will omit any proofs.
+For further reading, see for example \citep{hashimoto20}, an in progress cartoon guide to the article by Edixhoven-Lido.
 
@@
 For this we need $J_\Q^\wedge$, the dual of $J_\Q$, which in fact is isomorphic to $J_\Q$, taking as isomorphism for example the principal polarisation $\lambda: J_\Q \to J_\Q^\wedge$.
-This dual parametrised degree $0$ line bundles on $J_\Q$, and hence we get a universal degree $0$ line bundle $P_\Q$ on $J_\Q \times J_\Q^\wedge$, called the Poincar\'e line bundle $P_\Q$, which also satisfies that both $P_{\Q,0\times J_\Q^\wedge}$ and $P_{\Q,J_\Q \times 0}$ are trivial.
+This dual parametrises line bundles that are algebraically equivalent to $0$ on $J_\Q$, and hence we get a universal such line bundle $P_\Q$ on $J_\Q \times J_\Q^\wedge$, called the Poincar\'e line bundle $P_\Q$, which also satisfies that both $P_{\Q,0\times J_\Q^\wedge}$ and $P_{\Q,J_\Q \times 0}$ are trivial.
 
@@
 
-I don't want to explain the biextension structure. \todo{Bas, do you agree?}
+Furthermore, this Poincar\'e torsor has a nice structure of a biextension; this means we can think think of the fibers $P^\times_{\Q,(x,y)}$ as being a $\G_m$ above the point $x \times y$; this structure then gives multipliction maps \[P^\times_{\Q,(x_1,y)} \times P^\times_{\Q,(x_2,y)} \to P^\times_{\Q,(x_1+x_2,y)}\] and similarly \[P^\times_{\Q,(x,y_1)} \times P^\times_{\Q,(x,y_2)} \to P^\times_{\Q,(x,y_1+y_2)}\]
+This bilinear structure comes from interpreting $J^\wedge$ as $\text{Ext}^1(J,\G_m)$; then $P^\times$ is the universal extension of $J$ by $\G_m$, indexed by $J^\wedge$, and by duality vice versa as well.
 
@@
 \[\begin{tikzcd} % https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBoBGAXVJADcBDAGwFcYkQBhAfQB0eBFEAF9S6TLnyEU5CtTpNW7AFK8Bw0SAzY8BIgCZZNBizaIQKvvwAEfPAFt4VpQD0+AdxhQA5jFWCRYtqS+qTEcsaKZgAKrjz28OqBErrSoeEKpiAAKsJynj4IKKAAZgBOEHZIZCA4EEgALEYZ7HxZWIywwABWXABGQokgZRVVNLVIMvIm7D29g8OViJPjiAZTkSAAFHxYUKS2pVwAxjY8R1ilJ8UAlPPli401dUsBQ-cNY88AzK8LSF+fJBrRj0XowRhRcQ6KQgRgwYo4XJCIA
-                                                & T_\Q \arrow[d] \arrow[r]                   & P_\Q^\times \arrow[d]      \\
-C_\Q \arrow[ru, "\Tilde{j_b}"] \arrow[r, "j_b"] & J_\Q \arrow[r, "{(\id,\tr_c \circ f)}"] & J_\Q \times J^\wedge_\Q
+                                                & T_\Q \arrow[d] \arrow[rr]                   && P_\Q^\times \arrow[d]      \\
+C_\Q \arrow[ru, "\widetilde{j_b}"] \arrow[r, "j_b"] & J_\Q \arrow[rr, "{(\id,\tr_c \circ f)}"] && J_\Q \times J^\wedge_\Q
 \end{tikzcd}\]
-where $\Tilde{j_b}$ is a lift of $j_b$.
-This lift will only exist if $j_b^* T$ is a trivial $\G_m$-torsor over $C_\Q$; for that, it turns out that we want $f$ to be an element of $\Hom^+(J_\Q,J^\wedge_\Q)$, the group of self dual homomorphisms, of trace $0$ (where this trace comes from identification with the N\'eron-Severi group); if we do that, it turns out that $j_b^* T$ will correspond to a degree $0$ line bundle on $C_\Q$, and we only need to translate by a constant to make $j_b^* T$ trivial.
-
-If $f$ itself is already $0$, then $T$ is trivial and this will give no further information, and in general that is the best we can do, as generically the rank of $\Hom^+(J_\Q,J^\wedge_\Q)$, also called the N\'eron-Severi rank $\rho$, is $1$.\todo{This is true, right?
-Can't find reference} But in many interesting cases, this rank is non-zero.
-Using the isomorphism $\lambda$, this rank is also the rank of the endomorphism ring of $J_\Q$, and hence a family of examples is given by modular curves, where the endomorphism ring is the Hecke algebra and the N\'eron-Severi rank turns out to be equal to the genus.
+where $\widetilde{j_b}$ is a lift of $j_b$.
+This lift will only exist if $j_b^* T$ is a trivial $\G_m$-torsor over $C_\Q$; for that, it turns out that we want $f$ to be an element of $\Hom^+(J_\Q,J^\wedge_\Q)_0$, the group of self dual homomorphisms of trace $0$ (where this trace comes from identification with the N\'eron-Severi group); if we do that, it turns out that $j_b^* T$ will correspond to a degree $0$ line bundle on $C_\Q$, and we only need to translate by a constant to make $j_b^* T$ trivial.
+
+If $f$ itself is already $0$, then $T$ is trivial and this will give no further information, and in general that is the best we can do, as generically the rank of $\Hom^+(J_\Q,J^\wedge_\Q)$, also called the N\'eron-Severi rank $\rho$, is $1$.
+But in many interesting cases, this rank is bigger than $1$.
+Using the isomorphism $\lambda$, this rank is also the rank of a certain subgroup of the endomorphism ring of $J_\Q$, and it turns out a family of possible examples is given by modular curves; for example, normalisers of non-split Cartan curves $X_{\text{ns}}^+(\ell)$ have N\'eron-Severi rank equal to the genus, and according to the BSD conjecture Mordell-Weil rank at least equal to the genus.
+\todo{Bas, uiteindelijk heb ik er gewoon dit van gemaakt}.
 
@@
 
-We then would like to intersect the rational points of $T_\Q$ with the $p$-adic points of $C_\Q$, mapped to $T_\Q$ under $\tilde{j_b}$, inside the $p$-adic points of $T_\Q$.
+We then would like to intersect the rational points of $T_\Q$ with the $p$-adic points of $C_\Q$, mapped to $T_\Q$ under $\widetilde{j_b}$, inside the $p$-adic points of $T_\Q$.
 As in the case of classic Chabauty, one can conclude that the $p$-adic points of $T_\Q$ form a $p$-adic manifold of dimension $g+\rho-1$, but there is a problem with the rational points of $T_\Q$; these are in bijection with $\G_m(\Q)^{\rho-1} \times J_\Q(\Q)$.
-The latter is a finitely generated group of rank $r$, the Mordell-Weil rank, but the former is an infinitely generated group, and hence we cannot easily upper bound the dimension of $\overline{T_\Q(\Q)}$ inside $T_\Q(\Q_p)$.
+The latter is a finitely generated group of rank $r$, the Mordell-Weil rank, but the former is an infinitely generated group.
+One can upper bound the dimension of $\overline{T_\Q(\Q)}$ by $r + \rho -1$, but it is clear that this will not lead to an improvement to classic Chabauty.
 
@@
 We let $J$ be the N\'eron model over $\Z$ of the Jacobian of $C_\Q$, and $J^\wedge$ the N\'eron model of the dual of $J$.
-If we want to keep the essential structure of the Poincar\'e torsor intact, we can only extend to $P \to J \times J^{\wedge 0}$ where $J^{\wedge 0}$ is the connected component of $J^\wedge$ containing $0$; the component group $J/J^{\wedge 0}$ is only supported on $\Z/n\Z$, i.e.
+If we want to keep the essential biextension structure of the Poincar\'e torsor intact, we can only extend to $P \to J \times J^{\wedge 0}$ where $J^{\wedge 0}$ is the connected component of $J^\wedge$ containing $0$; the component group $J^\wedge/J^{\wedge 0}$ is only supported on $\Z/n\Z$, i.e.
 on the bad primes.
-We let $m\in \Z_{>0}$ be the annihilator of $J/J^{\wedge 0}$.
+We let $m\in \Z_{>0}$ be the annihilator of $J^\wedge/J^{\wedge 0}$.
 We can then make a similar diagram as before
 \[\begin{tikzcd} % https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBoBGAXVJADcBDAGwFcYkQBhAfQB0eBFEAF9S6TLnyEU5CtTpNW7AFK8Bw0SAzY8BIgCZZNBizaIQKvvwAEfPAFt4VpQD0+AdxhQA5jFWCRYtqS+qTEcsaKZgAKrjz28OqBErrSoeEKpiAAKsJynj4IKKAAZgBOEHZIZCA4EEgALEYZ7HxZWIywwABWXABGQokgZRVVNLVIMvIm7D29g8OViJPjiAZTkSAAFHxYUKS2pVwAxjY8R1ilJ8UAlPPli401dUsBQ-cNY88AzK8LSF+fJBrRj0XowRhRcQ6KQgRgwYo4XJCIA
-                                                & T \arrow[d] \arrow[r]                   & P^\times \arrow[d]      \\
-C \arrow[ru, "\Tilde{j_b}", dotted] \arrow[r, "j_b"] & J \arrow[r, "{(\id,\cdot m \circ\tr_c \circ f)}"] & J \times J^{\wedge 0}
+                                                & T \arrow[d] \arrow[rr]                   && P^\times \arrow[d]      \\
+C \arrow[ru, "\widetilde{j_b}", dotted] \arrow[r, "j_b"] & J \arrow[rr, "{(\id,\cdot m \circ\tr_c \circ f)}"] && J \times J^{\wedge 0}
 \end{tikzcd}\]
-Where this time $f$ is an 
+where this time $f$ is an element of $\Hom^+(J,J^\wedge)$ of trace $0$ and $c \in J^{\wedge}$ such that $j_b^* (\id,\tr_{c_i} \circ f_i)^* P_{\Q}^\times$ is trivial.
+
 There is one problem: the lift of $j_b$ from $C$ to $T$ only exists if $j_b^* T$ is trivial over $C$.
-We know this is true when base changed over $\Q$, and then the lift exists and is unique up to the action of $\Q^\times$.
-For $q$ prime for which $C_q$ has only one component, we can multiply by a suitable power of $q$ to make the fibre of $j_b^* T$ over $p$ trivial, however we cannot always do this if $C_q$ has multiple components.
+We know this is true when base changed over $\Q$, and over $\Q$ the lift exists and is unique up to the action of $\Q^\times$.
+For $q$ prime for which $C_{\F_q}$ has only one component, we can multiply a trivialising section over $C_\Q$ by a suitable power of $q$ to make it a trivialising section over $C_{\Z_{(q)}}$.
+However, we cannot always do this if $C_{\F_q}$ has multiple components.
 
@@
 \[\begin{tikzcd} % https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBoBGAXVJADcBDAGwFcYkQBhAfQB0eBFEAF9S6TLnyEU5CtTpNW7AFK8Bw0SAzY8BIgCZZNBizaIQKvvwAEfPAFt4VpQD0+AdxhQA5jFWCRYtqS+qTEcsaKZgAKrjz28OqBErrSoeEKpiAAKsJynj4IKKAAZgBOEHZIZCA4EEgALEYZ7HxZWIywwABWXABGQokgZRVVNLVIMvIm7D29g8OViJPjiAZTkSAAFHxYUKS2pVwAxjY8R1ilJ8UAlPPli401dUsBQ-cNY88AzK8LSF+fJBrRj0XowRhRcQ6KQgRgwYo4XJCIA
-                                                & T \arrow[d] \arrow[r]                   & P^\times \arrow[d]      \\
-U_i \arrow[ru, "\Tilde{j_{b,i}}"] \arrow[r, "j_{b,i}"] & J \arrow[r, "{(\id,\cdot m \circ\tr_c \circ f)}"] & J \times J^{\wedge 0}
+                                                & T \arrow[d] \arrow[rr]                   && P^\times \arrow[d]      \\
+U_i \arrow[ru, "\widetilde{j_{b,i}}"] \arrow[r, "j_{b,i}"] & J \arrow[rr, "{(\id,\cdot m \circ\tr_c \circ f)}"] && J \times J^{\wedge 0}
 \end{tikzcd}\]
 and we can finalise the summary of quadratic Chabauty.
-Denote $T$ now for the product of all $\rho-1$ such pullbacks for $f$ ranging over a basis of $\Hom(J,J^{\wedge})^+$.
-Taking a specific such $U$ with a lift $\Tilde{j_b}: U \to T$, for every prime $p$, the set $\Tilde{j_{b}}(U(\Z))$ is a subset of the intersection, inside the $p$-adic manifold $T(\Z_p)$, of $\Tilde{j_b}()U(\Z_p)$ and the closure $\overline{T(\Z)}$ of $T(\Z)$.
-As the dimension of $T$ is $g+\rho-1$ (it is a $\G_m^{\rho-1}$-torsor over $J$), we can as in Section~\ref{section:smoothzppoints} see that $T(\Z_p)$ has dimension $g+\rho-1$; and as $T(\Z)$ is a ${\pm 11}^{\rho-1}$-torsor over the group $J(\Z)$ of rank $r$, it will turn out $\overline{T(\Z)}$ has dimension at most $r$.
-As $U(\Z_p)$ has dimension $1$, we can hope that this intersection is be dimension $0$, and hence finite as $T(\Z_p)$ is compact, if $r < g + \rho-1$, hence we have an improvement over classical Chabauty.
-
-This argument can be made explicit when looking at residue discs; in short, just like we could parametrise $J(\Z)_0$ with $\Z^r$ in Section~\ref{section:kappa} where the inclusion $\Z^r \to J(\Z_p)_0 \cong \Z_p^{g}$ is given by convergent power series, it turns out that for $t \in T(\F_p)$ that lift to $T(\Z)$, there is a map $\kappa: \Z^r \to T(\Z_p)_t \cong \Z_p^{g+\rho-1}$ such that $\im \kappa = \overline{T(\Z)}$ and $\kappa$ is given by convergent power series.
+Denote $T$ now for the product of all $\rho-1$ such pullbacks for $f$ ranging over a basis of the trace $0$ submodule of $\Hom^+(J,J^{\wedge})$.
+Taking a specific such $U$ with a lift $\widetilde{j_b}: U \to T$, for every prime $p$, the set $\widetilde{j_{b}}(U(\Z))$ is a subset of the intersection, inside the $p$-adic manifold $T(\Z_p)$, of $\widetilde{j_b}(U(\Z_p))$ and the closure $\overline{T(\Z)}$ of $T(\Z)$.
+As the relative dimension of $T$ over $\Z_p$ is $g+\rho-1$ (it is a $\G_m^{\rho-1}$-torsor over $J$), we can as in Section~\ref{section:smoothzppoints} see that $T(\Z_p)$ has dimension $g+\rho-1$; and as $T(\Z)$ is a $\{\pm 1\}^{\rho-1}$-torsor over the group $J(\Z)$ of rank $r$, it will turn out $\overline{T(\Z)}$ has dimension at most $r$.
+As $U(\Z_p)$ has dimension $1$, we can hope that this intersection is dimension $0$, and hence finite as $T(\Z_p)$ is compact, if $r < g + \rho-1$, hence we have an improvement over classical Chabauty.
+
+This argument can be made explicit when looking at residue discs; in short, just like we could parametrise $J(\Z)_0$ with $\Z^r$ in Section~\ref{section:kappa} where the inclusion $\Z^r \to J(\Z_p)_0 \cong \Z_p^{g}$ is given by convergent power series, it turns out that for $t \in T(\F_p)$ that lift to $T(\Z)$, there is a map $\kappa: \Z^r \to T(\Z_p)_t \cong \Z_p^{g+\rho-1}$ such that $\im \kappa = \overline{T(\Z)_t}$ and $\kappa$ is given by convergent power series.
+This fact is a consequence of the biextension structure of $P^\wedge$; it allows us to quite explicitly move in the Poincar\'e torsor.
+
 When the parameters at $t$ are chosen nicely, the first $g$ coming from $J$, it turns out that $\kappa_1,\dots,\kappa_g$ are linear modulo $p$, and $\kappa_{g+1},\dots,\kappa_{g+\rho-1}$ are quadratic modulo $p$.
-The fact that these are quadratic is in fact related to this being called quadratic Chabauty; it has to do with $(\id,\cdot m \circ\tr_c \circ f)$ being a quadratic like map, as the product of $\id$ and $m \circ\tr_c \circ f$, two linear maps.
-Also, one can again find equations $g_1,\cdots,g_{r+\rho-2}$for the the image of $U(\Z_p)$ in $T(\Z_p)_t$, which will again be linear modulo $p$.
+The fact that these are quadratic is in fact related to this being called quadratic Chabauty; it has to do with the bilinear structure on $P^\times$, that when restricted to the image of $(\id,\cdot m \circ\tr_c \circ f)$ is a quadratic object, as both of $\id$ and $m \circ\tr_c \circ f$ are linear maps.
+This is analogous to how a bilinear form gives a quadratic form when evaluated at the diagonal.
+One can also again find equations $g_1,\cdots,g_{r+\rho-2}$ for the the image of $U(\Z_p)$ in $T(\Z_p)_t$, which will again be linear modulo $p$.
 
@@
 % Computations, and section 7 of the article (line bundles on C x C)
-An important part of making the calculations work, is forming the map $\tilde{j_b}: U \to T$.
+An important part of making the calculations work, is forming the map $\widetilde{j_b}: U \to T$.
 For this we need to be able to explicitly describe the trivialisation of the $\G_m$-torsor $j_b^* T$ restricted to $U$.
-Remember that $j_b^* T$ is also the pullback of $P^\times$ along the map $C \to J \times J^{\wedge 0}$, and this map factors through the diagonal map $C \times C\times C$.
+Remember that $j_b^* T$ is also the pullback of $P^\times$ along the map $C \to J \times J^{\wedge 0}$, and this map factors through the diagonal map $C \to C\times C$.
 As described in Section~7 of the paper, it turns out that giving such a map $f: J \to J^{\wedge}$ and $c \in J^\wedge$ with $j_b^* T$ trivial over all opens $U$, is equivalent to giving a line bundle $\Lcal$ on $C \times C$ satisfying the following three properties: $\Lcal$ is rigidified on $\{b\} \times C_\Q$, the fibres of $\pr_2: (C \times C)_\Q \to C_\Q$ are degree $0$, and the pullback $\diag^* \Lcal$ is trivial on $C_\Q$.
-This turns the problem of describing a map $J \to J^\wedge$ in useful terms of th in the sometimes more concrete problem of giving a line bundle on $C \times C$ satisfying some simple conditions.
+This turns the problem of describing a map $J \to J^\wedge$ in the sometimes more concrete problem of giving a line bundle on $C \times C$ satisfying some simple conditions.
 
@@
 Right now, the focus is on doing a modular example, $X_0(73)^+$, a genus $2$ curve with endomorphism ring of rank $2$.
-Here, the extra information comes from the Hecke algebra working on the curve, and the problem lies in describing Hecke operators explicitly as correspondences on $C \times C$, and computations with these correspondences over $\Z$.
+Here, the extra information comes from the Hecke algebra working on the curve, and the problem at the time of writing lies in describing Hecke operators explicitly as correspondences on $C \times C$, and computations with these correspondences over $\Z$.
 

### 2020-06-10 MS.tex
Replaced citep by cite everywhere, and fixed some typos

@@
 \newcommand{\Q}{\mathbb{Q}}
+\newcommand{\Fcal}{\mathcal{F}}
 \newcommand{\Lcal}{\mathcal{L}}
@@
 Pulling $\omega$ back to $C_{\Z_p}$ and looking at the fibre of reduction to a single $\F_p$-point $P$, one can in certain cases give an upper bound for the number of points in $C(\Z)$ reducing to $P$ based only on finite-precision calculations of $\omega$.
-Most well known is the generic upper bound $|C(\Q)| \leq |C(\F_p)| + 2g-2$ under the conditions $r < g, p > 2g$, as explained in the introductory article \citep{poonen12}.
+Most well known is the generic upper bound $|C(\Q)| \leq |C(\F_p)| + 2g-2$ under the conditions $r < g, p > 2g$, as explained in the introductory article \cite{poonen12}.
 
@@
 He interprets working in the Jacobian as dealing with the abelianised fundamental group of the curve $C$, and works with larger, non-abelian quotients of the fundamental group.
-Using quadratic Chabauty, the simplest case of non-abelian Chabauty, Balakrishnan, Dogra, M\"uller, Tuitman and Vonk in 2017 famously calculated  all rational points of the ``cursed curve'', the modular curve $X_s^+(13)$ \citep{cursedcurve}.
+Using quadratic Chabauty, the simplest case of non-abelian Chabauty, Balakrishnan, Dogra, M\"uller, Tuitman and Vonk in 2017 famously calculated  all rational points of the ``cursed curve'', the modular curve $X_s^+(13)$ \cite{cursedcurve}.
 They use an endomorphism of the Jacobian, and do $p$-adic analysis on $p$-adic local heights to make quadratic Chabauty explicit.
 
-Very recently, Edixhoven and Lido made available a preprint of their article ``Geometric quadratic Chabauty'' \citep{edixhoven20}.
+Very recently, Edixhoven and Lido made available a preprint of their article ``Geometric quadratic Chabauty'' \cite{edixhoven20}.
 Their goal in this article is to make a more geometric approach to effective quadratic Chabauty, by working in a pullback $T$ of the Poincar\'e torsor of the Jacobian.
@@
 Here, we use Makdisi's approach of representing a divisor by a subspace of a large Riemann-Roch space.
-We partially follow the article \citep{mascot18} by Mascot, and also give an original algorithm for explicitly computing the map $C(\Z_p)_P \to J(\Z_p)_t$ in Makdisi's representation.
+We partially follow the article \cite{mascot18} by Mascot, and also give an original algorithm for explicitly computing the map $C(\Z_p)_P \to J(\Z_p)_t$ in Makdisi's representation.
 
@@
 Note that this construction is functorial, as in the following sense: given two smooth schemes $X,Y$ over $\Z_p$ and two $\F_p$-points $x\in X(\F_p)$, $y\in Y(\F_p)$, a map $f: Y \to X$ satisfying $f(y) = x$ gives rise to a morphism $\widetilde{Y}_y^p \to \widetilde{X}_x^p$.
-This is a direct consequence of II.7.15 of \citep{hartshorne}.
+This is a direct consequence of II.7.15 of \cite{hartshorne}.
 \end{rem}
@@
 
-We will prove this using results about formal group as defined in \citep{honda70}.
+We will prove this using results about formal group as defined in \cite{honda70}.
 To be able to use this theory, we first give some results about going from a group scheme over $\Z_p$ to a formal group.
@@
 Now we will look at the theory of formal groups, and how that will help us.
-For a $n$-dimensional formal group $F$ over a ring $R$, Proposition~1.1 of \citep{honda70} gives us a canonical $R$-basis $\omega_1,\dots,\omega_n$ of the right invariant differentials; these are elements of $\bigoplus_{j=1}^n R[[x]] \diff x_j$.
-If the formal group is furthermore commutative, then by Proposition~1.3 of \citep{honda70} these are closed, i.e.
+For a $n$-dimensional formal group $F$ over a ring $R$, Proposition~1.1 of \cite{honda70} gives us a canonical $R$-basis $\omega_1,\dots,\omega_n$ of the right invariant differentials; these are elements of $\bigoplus_{j=1}^n R[[x]] \diff x_j$.
+If the formal group is furthermore commutative, then by Proposition~1.3 of \cite{honda70} these are closed, i.e.
 $d\omega_j = 0$.
@@
 In particular, we write $\log_i$ for the unique element of $(\Q\tensor R)[[x]]$ such that $d\log_i = \omega_i$.
-Together, these $\log_i$ give an element $\log \in R[[x]]^n$, and by Theorem~1 of \citep{honda70}, this logarithm satisfies $\log(x) = x \bmod (x)^2$, and $\log(F(x,y)) = \log(x)+\log(y)$.
+Together, these $\log_i$ give an element $\log \in R[[x]]^n$, and by Theorem~1 of \cite{honda70}, this logarithm satisfies $\log(x) = x \bmod (x)^2$, and $\log(F(x,y)) = \log(x)+\log(y)$.
 By the first result, $\log$ has an inverse which we will call $\exp$, also given by powerseries in $(\Q\tensor R)[[x]]$, and also satisfying $\exp(x) = x \bmod (x)^2$.
@@
 \begin{exmp}[continued]
-Taking $F$ the multiplicative group as in Example~\ref{exmp:gmformalgroup}, Proposition~1.1 of \citep{honda70} gives us $\omega = \frac{1}{x+1}dx$; as a power series this is $\sum_{j \geq 0} (-x)^j$.
+Taking $F$ the multiplicative group as in Example~\ref{exmp:gmformalgroup}, Proposition~1.1 of \cite{honda70} gives us $\omega = \frac{1}{x+1}dx$; as a power series this is $\sum_{j \geq 0} (-x)^j$.
 The formal anti-derivative of this is $\log = \sum_{j \geq 1} \frac{-(-x)^j}{j}dx$ (note this is a translate of the $\log$ from analysis), and Theorem $1$ will tell us what we already know in the context of analysis $\log(x + y + xy) = \log(x)+\log(y)$ (this formula is also a translate of the corresponding formula from analysis).
@@
 We let $I$ denote the ideal inside $\Z_p\angle{x_1,\dots,x_r}$ generated by $\lambda_1,\dots,\lambda_{g-1}$, and $A$ the quotient $\Z_p\angle{x_1,\dots,x_r}/I$.
-Noting that $Z(\lambda_1,\dots,\lambda_{g-1}) = \Hom_{\Z_p}(A,\Z_p)$, we can use the following theorem, the statement and proof of which come from \citep{edixhoven20}.
+Noting that $Z(\lambda_1,\dots,\lambda_{g-1}) = \Hom_{\Z_p}(A,\Z_p)$, we can use the following theorem, the statement and proof of which come from \cite{edixhoven20}.
 
@@
 
-Of note is that this upper bound for $C(\Z)$ does not even depend on the genus, and behaves agreeably when compared to the upper bound in Theorem 5.3 of \citep{poonen12}, which tells us that $|C(\Z)| \leq |C(\F_p)| + 2g-2$ under the much lighter condition of $r < g, p > 2g$ where $p$ is still a prime of good reduction.
+Of note is that this upper bound for $C(\Z)$ does not even depend on the genus, and behaves agreeably when compared to the upper bound in Theorem 5.3 of \cite{poonen12}, which tells us that $|C(\Z)| \leq |C(\F_p)| + 2g-2$ under the much lighter condition of $r < g, p > 2g$ where $p$ is still a prime of good reduction.
 To summarise: in proposition~\ref{prop:linchabauty} we sacrifice certainty for being to able to prove much sharper bounds.
@@
 \item Note that in all of the discussion of the previous section, we are calculating upper bounds for the cardinality of $C(\Z_p)_P \cap \overline{J(\Z)_t}$.
-It can and does however happen that this set is strictly bigger than $C(\Z)_P$, as shown in \citep{Balakrishnan19}, where Coleman-Chabauty is used on a whole database of curves.
+It can and does however happen that this set is strictly bigger than $C(\Z)_P$, as shown in \cite{Balakrishnan19}, where Coleman-Chabauty is used on a whole database of curves.
 They treat several possible cases and examples where the set is bigger.
-For example, there might be a $K$-point $Q$ where $K$ is a quadratic field where $p$ splits, such that $Q-b$ is non-$p$-torsion, and then $Q-b$ also lies in the closure of $J(\Z)$.\todo{Nee, niet echt, hun argument is anders omdat ze Coleman-Chabauty doen}
+For example, there might be a $K$-point $Q$ where $K$ is a quadratic field where $p$ splits, such that $Q-b$ lies in $J(\Z_p)_0$ and is non-$p$-torsion in $J(\Z_p)_0/J(\Z)_0$; then, as $J(\Z_p)$ is isomorphic as continous group to $\Z_p^g$, the point $Q-b$ lies in $\overline{J(\Z)_0}$, and clearly also in $C(\Z_p)$.\todo{Bas, explanation added}
 \item An important part of doing these calculations, is working with the Mordell-Weil group $J(\Z)$.
@@
 We can then aggregate this information for different primes, by looking at the maps $J(\Z) \to \prod_{p \in S} J(\F_p)$ for some set $S$ of primes of good reduction.
-See for example \citep{stoll10} for an introduction to the Mordell-Weil sieve.
+See for example \cite{stoll10} for an introduction to the Mordell-Weil sieve.
 \end{itemize}
@@
 
-We first calculate $\Lcal(2D_0 - D_{\text{aff}})$. Both over $\Q_p$ and over $\F_p$ we have the equality
-\[
-\Lcal(2D_0 - D_{\text{aff}}) = a(x)\Lcal((2g+2-d)(\infty_- + \infty_+)) + (y-b(x))\Lcal((g+1)(\infty_- + \infty_+))
-\]
-and then it should follow over $\Z_p$ so over $\Z/p^k\Z$.
-\todo{Bas, ik wilde je nog vragen over de [Todo]}[TODO:It is not necessarily true that a map that is an isomorphism when tensored with $\F_p$ and $\Q_p$ it is an isomorphism, but that is of course true if the map is between free modules, as I think it is here, right?
-As everything embeds into $\Z_p^n$ by evaluating at points, and submodule of free is free]
+We first calculate $\Lcal(2D_0 - D_{\text{aff}})$. Over $\F_p$ we have the equality
+\[
+\Lcal(2D_0 - D_{\text{aff}}) = a(x)\Lcal((2g+2-d)(\infty_- + \infty_+)) + (y-b(x))\Lcal((g+1)(\infty_- + \infty_+)).
+\]
+Note all these Riemann-Roch spaces are of the form $H^0(C_{\F_p},\Fcal_{\F_p})$ where $\Fcal$ is a sheaf on $C_{\Z_p}$ of degree higher than $2g-2$.
+Hence by Serre duality, $h^{1}(C_y,\Fcal_y)$ is $0$ for all $y \in \Spec \Z_p$.
+Then as the Euler characteristic is constant, also $h^{0}(C_y,\Fcal_y)$ is constant.
+By III.12.9 of \cite{hartshorne}, we see the basechange morphism $H^0(C_{\Z_p},\Fcal_{\Z_p}) \tensor \F_p \to H^0(C_{\F_p},\Fcal_{\F_p})$ is an isomorphism and $H^0(C_{\Z_p},\Fcal_{\Z_p})$ is a free $\Z_p$-module.
+That means this equality also holds over $\Z_p$, and hence over $\Z/p^k\Z$.
+then it should follow over $\Z_p$ so over $\Z/p^k\Z$.
+\todo{Bas, dit is het huidige argument}
 
 For $\Lcal((g+1)\infty_- + (g+1+d)\infty_+)$, we first inductively calculate the spaces $W_n := \Lcal(2D_0 - n\infty_-)$.
-For $W_1$ we have a basis $1,x,\dots,x^{2g+1},y,xy,\dots$, $x^g y, x^{g+1}y+x^{2g+2}$, and for $n \geq 0$ we have by a simple use of Lemma 2.2 of \citep{makdisi04} that for $1 \leq n \leq g+1$ we have \[W_{n} = \{s \in \Lcal(2D_0) \mid s\Lcal(2D_0) \in W_1 \cdot W_{n-1}\}\].
+For $W_1$ we have a basis $1,x,\dots,x^{2g+1},y,xy,\dots$, $x^g y, x^{g+1}y+x^{2g+2}$, and for $n \geq 0$ we have by a simple use of Lemma 2.2 of \cite{makdisi04} that for $1 \leq n \leq g+1$ we have \[W_{n} = \{s \in \Lcal(2D_0) \mid s\Lcal(2D_0) \in W_1 \cdot W_{n-1}\}\].
 This is a purely linear constraint, hence simple linear algebra allows us to calculate all $W_n$ for $n \leq g+1$.
@@
 \]
-This curve has genus $2$, and the Mordell-Weil group is isomorphic to $\Z$. This curve is also treated in Example~8.2 of \citep{poonen12}.
+This curve has genus $2$, and the Mordell-Weil group is isomorphic to $\Z$. This curve is also treated in Example~8.2 of \cite{poonen12}.
 
@@
 
-Code for the calculations in this section can be found in \citep{spelier2020}.
+Code for the calculations in this section can be found in \cite{spelier2020}.
 \todo{Bas, hiervoor ben ik nu gegaan}
@@
 \label{section:quadratic}
-In this section we attempt to give an introduction to the article~\citep{edixhoven20} aimed to introduce all the players in quadratic Chabauty at a slightly slower pace.
+In this section we attempt to give an introduction to the article~\cite{edixhoven20} aimed to introduce all the players in quadratic Chabauty at a slightly slower pace.
 We will omit any proofs.
-For further reading, see for example \citep{hashimoto20}, an in progress cartoon guide to the article by Edixhoven-Lido.
+For further reading, see for example \cite{hashimoto20}, an in progress cartoon guide to the article by Edixhoven-Lido.
 

### 2020-06-11 MS.tex
Fixed most of the last comments by Bas

@@
 %-----------------------------------------------------------------------------------------------------------------------
-\todo{Remove overfull h-box warnings}\todo{Referentie naar een artikel van Balakrishnan en Dogra, en Besser.}
+\todo{Remove overfull h-box warnings}
 \section{Introduction}
@@
 Chabauty proved, using $p$-adic methods, that if $r$ is strictly smaller than the genus $g$, then $C$ has only finitely many rational points.
-Loosely said, this proof and all Chabauty related theorems, rely on choosing a prime $p$ for which $C$ has good reduction, and intersecting $J(\Z)$ with $C(\Z_p)$ inside the bigger Lie group $J(\Z_p)$; by properties of $\Z_p$, the subgroup $J(\Z)$, generated by $r$ elements, lies within a Lie subgroup of dimension at most $r$, and $C(\Z_p)$ is a $1$-dimensional $p$-adic manifold, and hence their intersection can be proven to be discrete and -- as $J(\Z_p)$ is compact -- finite.
+Loosely said, this proof and all Chabauty related theorems, rely on choosing a prime $p$ for which $C$ has good reduction, and intersecting $J(\Z)$ with $C(\Z_p)$ inside the bigger Lie group $J(\Z_p)$; by properties of $\Z_p$, the subgroup $J(\Z)$, up to torsion generated by $r$ elements, lies within a Lie subgroup of dimension at most $r$, and $C(\Z_p)$ is a $1$-dimensional $p$-adic manifold, and hence their intersection can be proven to be discrete and -- as $J(\Z_p)$ is compact -- finite.\todo{Ik moet volgens mij uberhaupt nadenken wat over $\Q,\Q_p,\Z,\Z_p$ moet}
 
@@
 
-This Coleman-Chabauty method has been greatly generalised by Kim to so called non-abelian Chabauty.
+This Coleman-Chabauty method has been greatly generalised by Kim to so called non-abelian Chabauty in \todo{Ref} and \todo{Ref}.
 He interprets working in the Jacobian as dealing with the abelianised fundamental group of the curve $C$, and works with larger, non-abelian quotients of the fundamental group.
-Using quadratic Chabauty, the simplest case of non-abelian Chabauty, Balakrishnan, Dogra, M\"uller, Tuitman and Vonk in 2017 famously calculated  all rational points of the ``cursed curve'', the modular curve $X_s^+(13)$ \cite{cursedcurve}.
+Then the simplest case of non-abelian Chabauty, quadratic Chabauty was developed by Kim, Balakrishnan, Besser Dogran and M\"uller in the series of articles \todo{Ref}, and further extended by Balakrishnan, Dogra, M\"uller, Tuitman and Vonk; in 2017 they famously calculated  all rational points of the ``cursed curve'', the modular curve $X_s^+(13)$ \cite{cursedcurve}.
 They use an endomorphism of the Jacobian, and do $p$-adic analysis on $p$-adic local heights to make quadratic Chabauty explicit.
+Their methods are strong enough to prove finiteness of $C(\Z)$ under the condition of $r < g + \rho - 1$, where $\rho$ is the N\'eron-Severi rank of the Jacobian.
 
@@
 They also abandon the Coleman method for Chabauty; instead they parametrise the map $T(\Z) \to T(\Z_p)$ with power series, and pull back equations for the curve inside $T(\Z_p)$ along this map.
+Again, a necessary condition is $r < g + \rho - 1$.
 
 The purpose of this thesis is to make the work by Edixhoven and Lido more accessible by applying geometric Chabauty to the linear case, i.e.
-when working with $J(\Z)$ and $J(\Z_p)$.
+when working with $J(\Z)$ and $J(\Z_p)$ and assuming $r < g$.
 In this thesis, we go into more detail of what is happening throughout the process, including both theoretical and practical components.
-This new method of applying Chabauty leads to, when working modulo $p$, a conditional upper bound $|C(\Q)| \leq |C(\F_p)|$, as obtained in Proposition~\ref{prop:linchabauty}.
+This new method of applying Chabauty leads to, when working with single digit $p$-adic precision, a conditional upper bound $|C(\Q)| \leq |C(\F_p)|$, as obtained in Proposition~\ref{prop:linchabauty}.
 This upper bound compares favorably with classical Coleman-Chabauty, but unlike classical Coleman-Chabauty, we cannot say in general when the conditions of these propositions hold.
-We develop heuristics that suggest that generally trying multiple primes $p$ of good reduction will yield good results; these heuristics say that the conditional upper bound will hold for a set of primes of density $1$, and if $r < g-1$ can even often (in a set of primes of density $e^{-1}$) be improved to prove there are at most $|C(\Q)|$ rational points\todo{Bas, dit is denk ik de beste samenvatting}.
-The methods used to obtain Proposition~\ref{prop:linchabauty} are also amenable to higher precision calculations.
-We also give a hyperelliptic example with $r = 1, g = 2$, where the bound from Proposition~\ref{prop:linchabauty} indeed holds.
+We develop heuristics that suggest that generally trying multiple primes $p$ of good reduction will yield good results; these heuristics say that the conditional upper bound will hold for a set of primes of density $1$, and if $r < g-1$ can even often (in a set of primes of density at least $e^{-1}$) be improved to prove there are at most $|C(\Q)|$ rational points.
+The methods used to obtain Proposition~\ref{prop:linchabauty} are also amenable to higher precision calculations; indeed, in the case $r = g-1$ this may be necessary to calculate $|C(\Z)|$ exactly.\todo{Over hebben met Bas}
+
+We also give a hyperelliptic example with $r = 1, g = 2$, where the bound from Proposition~\ref{prop:linchabauty} indeed holds, and we are able to compute $C(\Z)$.
 
@@
 We first present the context in which we will perform Chabauty.
-Let $p>2$ be a prime, and $C$ be a scheme over $\Z$, proper, flat, regular with $C$ smooth over $\Z_{(p)}$ and $C_\Q$ of dimension $1$ and geometrically connected, of genus $g \geq 1$ and with the Jacobian $J$ of $C$ having Mordell-Weil rank $r < g$.
+Let $p>2$ be a prime, and $C$ be a scheme over $\Z$, proper, flat, regular with $C$ smooth over $\Z_{(p)}$ and $C_\Q$ of dimension $1$ and geometrically connected, of genus $g \geq 1$ and with the N\'eron model $J$ of the Jacobiano of $C_\Q$ having Mordell-Weil rank $r < g$.
 Assume we have a $\Q$-point $b$ in $C$, or equivalently a $\Z$-point.
@@
 
-Geometric chabauty works by finding an upper bound for the cardinality of $C(\Z)_P$. For this, we use the following diagram.
+Geometric Chabauty works by finding an upper bound for the cardinality of $C(\Z)_P$. For this, we use the following diagram.
 \[
@@
 
-\subsection{Preliminaries}\todo{Bas, dit en het volgende stukje zijn nieuw}
+\subsection{Preliminaries}
 We expect the readers of this thesis to be familiar with algebraic geometry, e.g.
@@
 The introduction to geometric quadratic Chabauty in Section~\ref{section:quadratic} contains some terms typically not treated in a master; while knowing them will help put the material in context, this section is meant to be understandible even if that is not the case.
-\todo{Bas, nog een specifieke referentie voor voorkennis die ik op kan nemen, of niet per se?}
 
@@
 
-\todo{Volgend stukje is nieuw, en het stukje erna is iets herschreven}\begin{rem}
+\begin{rem}
 \label{rem:torsortangentspace}
@@
 Note that this set does not have any more canonical structure; for example, with $X = \A^1_{\Z_p}$ and $x$ is the $\F_p$-point $1$, the set $X(\Z/p^2\Z)_x$ is $\{1 + pi | i \in \F_p\}$, and we see we cannot upgrade the torsor structure.
-This is due to the fact that even after choosing a parameter at $x$ as a point of $X_{\F_p}$, a lift of such a parameter to $X_{\Z/p^2\Z}$ is not unique, and can in fact differ up to translation.
+This is due to the fact that even after choosing a parameter at $x$ as a point of $X_{\F_p}$, a lift of such a parameter to $X_{\Z/p^2\Z}$ is not canonical, and can in fact differ up to translation.
 This is in contrast to the situation over $\F_p[\varepsilon]/(\varepsilon^2)$, where the $\F_p$-algebra structure gives rise to an isomorphism of $\F_p$-vector spaces between $X(\F_p[\varepsilon]/(\varepsilon^2))$ and $T_x X_{\F_p}$; indeed, this is an alternate definition of the tangent space.
@@
 Also, by $F(0,0) = 0$ we have that $F(x,F(\iota_f,0)) = 0$ so $F(\iota_f,0)$ is in fact equal to $\iota_F$; as $\iota_F \equiv -x \bmod (x)^2$, it has a formal inverse and hence $F(x,0) = x$, so $0$ is indeed a right unit.
-A standard argument now shows that $\iota_F$ is also a left inverse and $0$ is also a right unit, so $F$ gives $R[[x]]$, together with the $(x)$-adic topology, the structure of a group object in the category of topological $R$-algebras\todo{Nu zou het goed moeten zijn, toch?
-Als nog steeds niet: werk in de categorie $(S,I)$ waar $S$ compleet is m.r.t.
-$I$}; for two continuous morphisms $f_1,f_2$ from $R[[x]]$ to some ring $A$, given by sending $x$ to $a_1,a_2$ respectively, we define $(f_1 \oplus f_2)(x) = F(a_1,a_2)$, and by our considerations this makes $\Hom_{\text{cont}}(R[[x]],A)$ into a group, functorially in $A$.
+A standard argument now shows that $\iota_F$ is also a left inverse and $0$ is also a right unit, so $F$ gives $(R[[x]],(x))$, together with the $(x)$-adic topology, the structure of a group object in the category of pairs of objects $(A,I)$ where $A$ is a topological $R$-algebra, complete with respect to $I$ with the $I$-adic topology; for two continuous morphisms $f_1,f_2$ from $(R[[x]],(x))$ to $(A,I)$, given by sending $x$ to $a_1,a_2 \in I^n$ respectively, we define $(f_1 \oplus f_2)(x) = F(a_1,a_2)$, and by our considerations this makes $\Hom_((R[[x]],x),(A,I))$ into a group, functorially in $A$.\todo{Nu zou het goed moeten zijn, toch?}
 
@@
 By smoothness, after picking parameters, this is isomorphic as topological $\Z_p$-algebras to the ring of power series $\Z_p[[x_1,\dots,x_d]]$.
-This completion naturally gives rise to a formal scheme denoted $\Spf \widehat{O}_{G,e}$; in a categorical notion, this is a functor on finite length $\Z_p$-algebras sending $A$ to $\Hom_{\text{cont}}(\widehat{O}_{G,e},A)$, but we can also think of it as a locally ringed space with $\Spec \Z_p$ as topological space, and sheaf of rings $\lim_n \widetilde{O_{G,e}/m^n}$ where $m$ is the ideal of $O_{G,e}$ defining $e$\todo{Is dit de juiste formulering?}.
+This completion naturally gives rise to a formal scheme denoted $\Spf \widehat{O}_{G,e}$; in a categorical notion, this is a functor on finite length $\Z_p$-algebras sending $A$ to $\Hom_{\text{cont}}(\widehat{O}_{G,e},A)$, but we can also think of it as a locally ringed space with $\Spec \Z_p$ as topological space, and sheaf of rings $\lim_n \widetilde{O_{G,e}/m^n}$ where $m$ is the ideal of $O_{G,e}$ defining $e$\todo{Over hebben met Bas}.
 The global sections of this sheaf are simply $\widehat{O}_{G,e}$.
@@
 
-This leads to a now trivial proposition.\todo{Bas, proposition of theorem?}
+This leads to a now trivial proposition.
 \begin{prop}
 \label{prop:linchabauty}
-If for all points $P \in C(\F_p)$, the linear system of $g-1$ equations modulo $p$ defining $C(\Z_p)_P \subset J(\Z_p)_t$ pulled back to $\overline{J(\Z)_t}$ has at most one solution, we get the inequality
-\[
-|C(\Z)| \leq |C(\F_p)|.
-\]
+If for all points $P \in C(\F_p)$, the linear system of $g-1$ equations modulo $p$ defining $C(\Z_p)_P \subset J(\Z_p)_t$ pulled back to $\overline{J(\Z)_t}$ has $n_P \leq 1$ solutions, we get the inequality
+\[
+|C(\Z)| \leq \sum_{P \in C(\F_p)} n_P \leq |C(\F_p)|. 
+\]\todo{Over hebben met Bas}
 \end{prop}
@@
 \label{lem:probindep}
-Let $\F_p$ be any finite field, let $A$ be a random $(n+k)\times n$ matrix over $\F_p$, and $b$ randomly chosen from $\in \F_p^{n+k}$.
-Then the probability that $Ax=0$ has more than one solution is at most $c_k (p-1)^{-(k+1)}$ and the probability that $Ax=b$ has more than one solution is at most $c_k (p-1)^{-(k+1)} p^{-(k+1)}$ where $c_k = \sum_{\ell = 0}^k \binom{k}{\ell}/(\ell+1)!
-\leq 2^k$.
+Let $\F_q$ be any finite field, let $A$ be a random $(n+k)\times n$ matrix over $\F_q$, and $b$ randomly chosen from $\F_q^{n+k}$.
+Then the probability that $Ax=0$ has more than one solution is at most $\frac{1}{(p-1)p^k}$ and the probability that $Ax=b$ has more than one solution is at most $\frac{1}{(p-1)p^{2k+1}}$.
 \end{lem}
 \begin{proof}
-Let $A_i$ denote the rows of $A$, let the space $V_i$ be the linear span of $A_1,\dots,A_i$ with $V_0 = 0$, and let $E_i$ denote the event that $A_i \in V_{i-1}$.
-Then we see the row space of $A$ can only fail to be $\F_p^n$ if for $k+1$ different indices $i$, the event $E_i$ takes place.
-As clearly $\dim V_i \leq i$, we see that $\P(E_i)$ is at most $p^{i-1-n}$ for $i \leq n$ and at most $p^{-1}$ for $i \geq n$.
-Finally note, that $\P(E_i | E_{j_1} \wedge \cdots \wedge E_{j_\ell}) \leq \P(E_i)$ if all $j_1,\dots,j_\ell$ are smaller than $i$.
-Now we can make the following calculation
+Let $A_i$ denote the columns of $A$, let the space $V_i$ be the linear span of $A_1,\dots,A_i$ with $V_0 = 0$, and let $E_i$ denote the event that $A_i \in V_{i-1}$.
+Note that $Ax = 0$ has more than one solution if and only if $V_n$ is not $n$-dimensional, i.e.
+if and only if $E_1 \vee \cdots \vee E_n$ holds.
+As clearly for $1\leq i \leq n$ we have $\dim V_{i-1} \leq i-1$, we see that $\P(E_i)$ is at most $p^{i-1-n-k}$.
+We then see
 \begin{align*}
-\P(\text{At least } k+1 \text{ of } E_i \text{ occur}) &= \P\left(\bigvee_{1\leq i_1 < \cdots < i_{k+1} \leq n + k} \bigwedge_{j=1}^{k+1} E_{i_j} \right) \\
-&\leq \sum_{1\leq i_1 < \cdots < i_{k+1} \leq n + k} \P\left(\bigwedge_{j=1}^{k+1} E_{i_j}\right) \\
-&\leq \sum_{1\leq i_1 < \cdots < i_{k+1} \leq n + k} \prod_{j=1}^{k+1} \P(E_{i_j}) \\
-&\leq \sum_{1\leq i_1 < \cdots < i_{k+1} \leq n + k} \prod_{j=1}^{k+1} p^{{\min(i_j-1-n,-1)}}.
+\P(E_1 \vee \cdots \vee E_n) &\leq \sum_{i=1}^n \P(E_i)\\
+&\leq \sum_{i=1}^n p^{i-1-n-k}\\
+&\leq \sum_{i=-\infty}^n p^{i-1-n-k}\\
+&= \frac{1}{(p-1)p^k}
 \end{align*}
-Then we note that for $\ell = 0,\dots,k$ we have
-\begin{align*}
-\sum_{1\leq i_1 < \cdots < i_{\ell} \leq n}\prod_{j=1}^{\ell} p^{i_j-1-n} &\leq \frac{1}{\ell!} \sum_{1\leq i_1,\dots,i_{\ell} \leq n} \prod_{j=1}^{\ell} p^{i_j-1-n} \\
-&= \frac{1}{\ell!} (\frac{1}{p^n} + \frac{1}{p^{n-1}} + \cdots + \frac{1}{p})^\ell\\
-&\leq \frac{1}{\ell! (p-1)^\ell}.
-\end{align*}
-Now if we partition the sum over all $1\leq i_1 < \cdots < i_{k+1} \leq n + k$ based on how many of the indices lie in $[n+1,n+k]$, we find
-\begin{align*}
-\sum_{\substack{1\leq i_1 < \cdots \\ < i_{k+1} \leq n + k}} \prod_{j=1}^{k+1} p^{{\min(i_j-1-n,-1)}} &= \sum_{m = 0}^{k} \binom{k}{m}p^{-m}\sum_{1\leq i_1 < \cdots < i_{k+1-m} \leq n}\prod_{j=1}^{k+1-m} p^{i_j-1-n}\\
-&\leq \sum_{m = 0}^{k} \binom{k}{m}p^{-m}(p-1)^{-(k+1-m)}/(k+1-m)! \\
-&\leq (p-1)^{-(k+1)} \sum_{\ell = 0}^k \binom{k}{\ell}/(\ell+1)! \\
-& = c_k (p-1)^{-(k+1)}.\\
-\end{align*}
-This shows that the probability of $Ax = 0$ having more than one solution is indeed at most $c_k (p-1)^{-(k+1)}$.
-Furthermore, if $Ax = 0$ has more than one solution, then $\text{rank} A < n$ so there are at most $p^{n-1}$ possible values of $b$ such that $Ax = b$ has multiple solutions, hence the total probability is at most $c_k (p-1)^{-(k+1)} p^{-(k+1)}$.
+This shows that the probability of $Ax = 0$ having more than one solution is indeed at most $\frac{1}{(p-1)p^k}$.
+Furthermore, if $Ax = 0$ has more than one solution, then $\text{rank} A < n$ so there are at most $p^{n-1}$ possible values of $b$ such that $Ax = b$ has multiple solutions, hence the total probability is at most $\frac{1}{(p-1)p^{2k+1}}$.
 \end{proof}
-
-For a generic point $P \in C(\F_p)$, we might assume the linear system modulo $p$ defining $C(\Z_p)_P$ pulled back to $\overline{J(\Z)}$ is completely random, but for point $P \in C(\F_p)$ coming from $\Z$-points, we always know there is at least one solution; and indeed, it turns out that with a translation, one can assume the linear system is homogenous.
+\begin{rem}
+Using similar methods, one can show that $\P(E_1 \vee \cdots \vee E_n) \geq \frac{1}{p^{k+1}}$, hence this lemma is asymptotically as sharp as possible.
+\end{rem}\todo{Bas, stelling + bewijs verbeterd en remark toegevoegd}
+
+For a general\todo{general mag wel toch?} point $P \in C(\F_p)$, we might assume the linear system modulo $p$ defining $C(\Z_p)_P$ pulled back to $\overline{J(\Z)}$ is completely random, but for point $P \in C(\F_p)$ coming from $\Z$-points, we always know there is at least one solution; and indeed, it turns out that with a translation, one can assume the linear system is homogenous.
 \begin{prop}
@@
 Assume furthermore that all these linear systems are independently random.
-Then for $p > 4g^2$ the conditions of Proposition~\ref{prop:linchabauty} are not satisfied with probability at most
-\[
-c_{g-1-r}(|C(\Z)|+2)p^{-(g-r)}
+Then for $p > 4g^2,|C(\Z)|$ the conditions of Proposition~\ref{prop:linchabauty} are not satisfied with probability at most
+\[
+(|C(\Z)|+2p^{-g-r-1})(p-1)^{-1}p^{-(g-r-1)}
 \]
@@
 \[
-\left(1 - c_k(p-1)^{-(k+1)}\right)^{a} \left(1 - c_k(p-1)^{-(k+1)}p^{-(k+1)}\right)^b.
-\]
-Using the Bernoulli's inequality, this is at least 
-\[
-\left(1- ac_k(p-1)^{-(k+1)}\right)\left(1 - c_k(p-1)^{-(k+1)}p^{-(k+1)}\right)
-\]
-which is itself at least $1 - ac_k(p-1)^{-(k+1)} - bc_k(p-1)^{-(k+1)}p^{-(k+1)}$.
+\left(1 - \frac{1}{(p-1)p^k}\right)^{a} \left(1 - \frac{1}{(p-1)p^{2k+1}}\right)^b.
+\]
+Using the Bernoulli's inequality and the fact that $\left(1- a\frac{1}{(p-1)p^k}\right)$ and $\left(1 - b\frac{1}{(p-1)p^{2k+1}}\right)$ are positive, this is at least 
+\[
+\left(1- a\frac{1}{(p-1)p^k}\right)\left(1 - b\frac{1}{(p-1)p^{2k+1}}\right)
+\]
+which is itself at least $1 - a\frac{1}{(p-1)p^k} - b\frac{1}{(p-1)p^{2k+1}}$.
 Using the Hasse-Weil bound, we can make the estimate $b \leq 2p$.
-Then we can lower bound this by $1 - ac_k(p-1)^{-(k+1)} - 2c_k(p-1)^{-(2k+1)}) \geq 1 - c_k(a+2)(p-1)^{-(k+1)}$.
+Then we can lower bound this by $1 - a\frac{1}{(p-1)p^k} - 2\frac{1}{(p-1)p^{2k}} \geq 1 - (a+2p^{-k})\frac{1}{(p-1)p^k}$.
 
@@
 \begin{rem}
-Note that if $r=g-1$, as we expect a random $n\times n$-matrix to be invertible, we expect that if the conditions of Proposition~\ref{prop:linchabauty} are satisfied, we generally find an upper bound for $|C(\Z)|$ slightly lower than $|C(\F_p)|$.
-However, a not necessarily inhomogenous linear system of dimension $(n+k)\times n$ is solvable with probability at most $p^{-k}$, as the dimension of the column space is at most $n$.
-Hence for $r = g-2$ we can expect to find an upper bound of about $|C(\Z)|+1$, and with probability about $(1-\frac{1}{p})^{|C(\F_p)|} \approx (1-\frac{1}{p})^p \approx e^{-1}$ \todo{Extra heuristiek!}even the optimal upper bound of $|C(\Z)|$.
+Note that if $r=g-1$, as we expect a random $n\times n$-matrix to be invertible, we expect that if the conditions of Proposition~\ref{prop:linchabauty} are satisfied, we generally find an upper bound for $|C(\Z)|$ slightly lower than $|C(\F_p)|$.\todo{Hopelijk nu minder verwarrend, met de herformulering van de Prop} However, a not necessarily homogenous linear system of dimension $(n+k)\times n$ is solvable with probability at most $p^{-k}$, as the dimension of the column space is at most $n$.
+Hence for $r = g-2$ we can expect to find an upper bound of about $|C(\Z)|+1$, and with probability about $(1-\frac{1}{p})^{|C(\F_p)|} \approx (1-\frac{1}{p})^p \approx e^{-1}$ even the optimal upper bound of $|C(\Z)|$.
 For $r = g-3$, we even expect to find an upper bound of $|C(\Z)|$ for a set of primes of density $1$; and for $r < g-3$, for all but a finite set of primes.
@@
 \section{Complications and improvements}
-\label{section:remarks} \todo{Bas, het is niet alleen werk van anderen, hopelijk is het nu duidelijker}
+\label{section:remarks} \todo{Bas, er staat bij al het werk van anderen een referentie}
 In this section, we quickly make some further remarks on how or when to apply the theory we have built up in previous section to real cases.
@@
 \item Note that in all of the discussion of the previous section, we are calculating upper bounds for the cardinality of $C(\Z_p)_P \cap \overline{J(\Z)_t}$.
-It can and does however happen that this set is strictly bigger than $C(\Z)_P$, as shown in \cite{Balakrishnan19}, where Coleman-Chabauty is used on a whole database of curves.
+It can and does however happen that this set is strictly bigger than $C(\Z)_P$, as shown in \cite{Balakrishnan19}, where Coleman-Chabauty is used on a database of 16997 curves of genus $3$ with Mordell-Weil rank of the Jacobian equal to $1$.
 They treat several possible cases and examples where the set is bigger.
-For example, there might be a $K$-point $Q$ where $K$ is a quadratic field where $p$ splits, such that $Q-b$ lies in $J(\Z_p)_0$ and is non-$p$-torsion in $J(\Z_p)_0/J(\Z)_0$; then, as $J(\Z_p)$ is isomorphic as continous group to $\Z_p^g$, the point $Q-b$ lies in $\overline{J(\Z)_0}$, and clearly also in $C(\Z_p)$.\todo{Bas, explanation added}
+One of the main families they have found can be given in the following way: let $Q$ be a $K$-point $Q$ where $K$ is a quadratic number field where $p$ splits.
+Embedding $K$ into $\Q_p$, assume $Q-b$ lies in $J(\Z_p)_0$ and is torsion of order prime to $p$ in $J(\Z_p)_0/J(\Z)_0$.
+Then, as $J(\Z_p)$ is isomorphic as continous group to $\Z_p^g$, the point $Q-b$ lies in $\overline{J(\Z)_0}$, and clearly also in $C(\Z_p)$.\todo{Bas, even over hebben}
 \item An important part of doing these calculations, is working with the Mordell-Weil group $J(\Z)$.
-In general, finding generators of $J(\Z)$ is computationally out of reach, and one may need to assume the BSD conjecture to even find the rank $r$.
+Finding generators of $J(\Z)$ is as of yet a computationally difficult problem, and one may need to assume the BSD conjecture to even find the rank $r$.
 However, note that one does not need to find all of $J(\Z)$; if we can generate a subgroup of $J(\Z)$ of index finite and coprime to $p|J(\F_p)|$, it will have the same closure in $J(\Z_p)$.
 For this, we only need to generate sufficiently many independent points of the Jacobian, and saturate subgroups with respect to some primes.
-Both of these feats are easier than finding all of $J(\Z)$.
+Both of these tasks are easier than finding all of $J(\Z)$.
 \item Even this method does not work for a certain prime $p$, and neither for some other primes we tried, we can still use parts of the information we have learned.
@@
 we can represent rational functions in $V_5$ by their values in $k^Z$.
-In this representation, we can add, subtract, or, if the degree at infinity is not too large, even multiply rational functions, by respectively adding, subtracting or multiplying the correspondig vectors in $k^Z$.
+In this representation, we can add, subtract, or, if the degree at infinity is not too large, even multiply rational functions, by respectively adding, subtracting or multiplying the corresponding vectors in $k^Z$.
 It is now also possible to represent subspaces of $V_5$ by giving a basis in $k^Z$.
@@
 \]
-Note all these Riemann-Roch spaces are of the form $H^0(C_{\F_p},\Fcal_{\F_p})$ where $\Fcal$ is a sheaf on $C_{\Z_p}$ of degree higher than $2g-2$.
+Note all these Riemann-Roch spaces are of the form $H^0(C_{\F_p},\Fcal_{\F_p})$ where $\Fcal$ is an invertible $O_{C_{\Z_p}}$-module on $C_{\Z_p}$ of degree higher than $2g-2$.
 Hence by Serre duality, $h^{1}(C_y,\Fcal_y)$ is $0$ for all $y \in \Spec \Z_p$.
@@
 then it should follow over $\Z_p$ so over $\Z/p^k\Z$.
-\todo{Bas, dit is het huidige argument}
+\todo{Over hebben met Bas}
 
@@
 
-\subsection{Interpolating polynomials}\todo{Dit stuk is herschreven}
+\subsection{Interpolating polynomials}
 \label{subs:interpolate}
@@
 Code for the calculations in this section can be found in \cite{spelier2020}.
-\todo{Bas, hiervoor ben ik nu gegaan}
 
@@
 we can also describe this in terms of its functor of points; for any scheme $S$ over $J_\Q \times J^\wedge_\Q$, we have that $P^\times_\Q(S)$ is the set of isomorphisms betweeen $O_S$ and $(P_\Q)_S$, with a free, transitive action of $O_S(S)^\times$, i.e.
-a torsor of $O_S(S)^\times$ in the traditional group-theoretic sense (note that this torsor can be empty).
-
-Furthermore, this Poincar\'e torsor has a nice structure of a biextension; this means we can think think of the fibers $P^\times_{\Q,(x,y)}$ as being a $\G_m$ above the point $x \times y$; this structure then gives multipliction maps \[P^\times_{\Q,(x_1,y)} \times P^\times_{\Q,(x_2,y)} \to P^\times_{\Q,(x_1+x_2,y)}\] and similarly \[P^\times_{\Q,(x,y_1)} \times P^\times_{\Q,(x,y_2)} \to P^\times_{\Q,(x,y_1+y_2)}\]
+a pseudotorsor of $O_S(S)^\times$ in the traditional group-theoretic sense (note that this set can be empty).
+
+Furthermore, this Poincar\'e torsor has a nice structure of a biextension; this means we can think think of the fibers $P^\times_{\Q,(x,y)}$ as being a $\G_m$ above the point $x \times y$; this structure then gives multiplication maps \[P^\times_{\Q,(x_1,y)} \times P^\times_{\Q,(x_2,y)} \to P^\times_{\Q,(x_1+x_2,y)}\] and similarly \[P^\times_{\Q,(x,y_1)} \times P^\times_{\Q,(x,y_2)} \to P^\times_{\Q,(x,y_1+y_2)}\]
 This bilinear structure comes from interpreting $J^\wedge$ as $\text{Ext}^1(J,\G_m)$; then $P^\times$ is the universal extension of $J$ by $\G_m$, indexed by $J^\wedge$, and by duality vice versa as well.
@@
 Instead of doing Chabauty in this Poincar\'e torsor, we will look at a pullback of this torsor to a $\G_m$-torsor over $J_\Q$.
-Our first attempt is pulling back along the map $J_\Q$ to $J_\Q \times J^\wedge_\Q$ given as $(\id,\tr_c \circ f)$ where $f: J_\Q \to J^\wedge_\Q$ is a morphism of group schemes.
+Our first attempt is pulling back along the map $J_\Q$ to $J_\Q \times J^\wedge_\Q$ given as $(\id,\tr_c \circ f)$ where $f: J_\Q \to J^\wedge_\Q$ is a morphism of group schemes and $\tr_c: J^\wedge_\Q \to J^\wedge_\Q$ is translation along $c \in J^\wedge_\Q(\Q)$.
 We denote the pullback of $P^\times_\Q$ along this map by $T_\Q$, a $\G_m$-torsor over $J_\Q$.
@@
 
-If $f$ itself is already $0$, then $T$ is trivial and this will give no further information, and in general that is the best we can do, as generically the rank of $\Hom^+(J_\Q,J^\wedge_\Q)$, also called the N\'eron-Severi rank $\rho$, is $1$.
+If $f$ itself is already $0$, then $T$ is trivial and this will give no further information, and most of the times that is the best we can do, as generically the rank of $\Hom^+(J_\Q,J^\wedge_\Q)$, also called the N\'eron-Severi rank $\rho$, is $1$.
 But in many interesting cases, this rank is bigger than $1$.
 Using the isomorphism $\lambda$, this rank is also the rank of a certain subgroup of the endomorphism ring of $J_\Q$, and it turns out a family of possible examples is given by modular curves; for example, normalisers of non-split Cartan curves $X_{\text{ns}}^+(\ell)$ have N\'eron-Severi rank equal to the genus, and according to the BSD conjecture Mordell-Weil rank at least equal to the genus.
-\todo{Bas, uiteindelijk heb ik er gewoon dit van gemaakt}.
 
@@
 
-This argument can be made explicit when looking at residue discs; in short, just like we could parametrise $J(\Z)_0$ with $\Z^r$ in Section~\ref{section:kappa} where the inclusion $\Z^r \to J(\Z_p)_0 \cong \Z_p^{g}$ is given by convergent power series, it turns out that for $t \in T(\F_p)$ that lift to $T(\Z)$, there is a map $\kappa: \Z^r \to T(\Z_p)_t \cong \Z_p^{g+\rho-1}$ such that $\im \kappa = \overline{T(\Z)_t}$ and $\kappa$ is given by convergent power series.
+This argument can be made explicit when looking at residue discs; in short, just like we could parametrise $J(\Z)_0$ with $\Z^r$ in Section~\ref{section:kappa} where the inclusion $\Z^r \to J(\Z_p)_0 \cong \Z_p^{g}$ is given by convergent power series, it turns out that for $t \in T(\F_p)$ that lift to $T(\Z)$, there is a map $\kappa: \Z^r \to T(\Z_p)_t \cong \Z_p^{g+\rho-1}$ such that $\kappa$ is given by convergent power series and extending the domain of $\kappa$ to $\Z_p^r$ we have $\kappa(\Z_p^r) = \overline{T(\Z)_t}$.
 This fact is a consequence of the biextension structure of $P^\wedge$; it allows us to quite explicitly move in the Poincar\'e torsor.
@@
 Remember that $j_b^* T$ is also the pullback of $P^\times$ along the map $C \to J \times J^{\wedge 0}$, and this map factors through the diagonal map $C \to C\times C$.
-As described in Section~7 of the paper, it turns out that giving such a map $f: J \to J^{\wedge}$ and $c \in J^\wedge$ with $j_b^* T$ trivial over all opens $U$, is equivalent to giving a line bundle $\Lcal$ on $C \times C$ satisfying the following three properties: $\Lcal$ is rigidified on $\{b\} \times C_\Q$, the fibres of $\pr_2: (C \times C)_\Q \to C_\Q$ are degree $0$, and the pullback $\diag^* \Lcal$ is trivial on $C_\Q$.
+As described in Section~7 of the paper, it turns out that giving such a map $f: J \to J^{\wedge}$ and $c \in J^\wedge(\Z)$ with $j_b^* T$ trivial over all opens $U$, is equivalent to giving a line bundle $\Lcal$ on $C \times C$ satisfying the following three properties: $\Lcal$ is rigidified on $\{b\} \times C_\Q$, the fibres of $\pr_2: (C \times C)_\Q \to C_\Q$ are degree $0$, and the pullback $\diag^* \Lcal$ is trivial on $C_\Q$.
 This turns the problem of describing a map $J \to J^\wedge$ in the sometimes more concrete problem of giving a line bundle on $C \times C$ satisfying some simple conditions.

### 2023-12-08 MSK.tex
Add defense files

--- 2020-06-11 MS.tex
@@
 \newcommand{\Q}{\mathbb{Q}}
+\newcommand{\va}{\mathbf{a}}
+\newcommand{\vx}{\mathbf{x}}
+\newcommand{\vy}{\mathbf{y}}
+\newcommand{\vz}{\mathbf{z}}
 \newcommand{\Fcal}{\mathcal{F}}
@@
 \DeclareMathOperator{\Mat}{Mat}
+\DeclareMathOperator{\Jac}{Jac}
 \let\S\undefined
@@
 
-\title{A geometric approach to linear and quadratic Chabauty}
+\title{A geometric approach to linear Chabauty}
 \author{Pim Spelier}
@@
 {\LARGE\bf 
-A geometric approach to linear Chabauty
+A geometric approach to linear Chabauty\\
+{\color{red} Over number fields}
 }
 
-\vspace{10em}
+\vspace{8em}
 
@@
 
-\vspace{10em}
+\vspace{8em}
 
@@
 }
-
 \vfill
@@
 \newpage
-\listoftodos
 \tableofcontents
@@
 %-----------------------------------------------------------------------------------------------------------------------
-\todo{Remove overfull h-box warnings}
 \section{Introduction}
 \label{section:intro}
-In mathematics a fundamental problem is solving polynomial equations over the rationals, dating back to Diophantus.
+A fundamental problem in mathematics is solving polynomial equations over the rationals, dating back to Diophantus.
 An important special case in algebraic geometry is that of curves.
-The behavior of the rational points of curves depends enormously on the \textit{genus} $g$ of the curve $C$, a numerical invariant of a curve.
+The behavior of the rational points of curves depends enormously on the \textit{genus} $g$ of the curve, a numerical invariant.
 For $g = 0$, there are either no or infinitely many solutions, and their behavior is well understood.
@@
 
-In this thesis, we look only at the case $g > 1$.
-It turns out that there are always only finitely many rational points; this result was originally conjectured by Mordell in 1922 and finally proven by Faltings in 1983.
-
-Before it was proven, one of the major partial results was a theorem from Chabauty in 1941, phrased in terms of the rank $r$ of the group of rational points on the Jacobian $J$ of the curve, also called the Mordell-Weil rank, which is finite by the Mordell-Weil theorem.
+In this thesis, we look only at the case of a curve $C$ with genus $g > 1$.
+It turns out that there are always only finitely many rational points.
+This result was originally conjectured by Mordell in 1922 and finally proven by Faltings in 1983 in \cite{faltings}.
+
+Before Faltings's theorem was proven, one of the major partial results was a theorem from Chabauty in 1941, phrased in terms of the rank $r$ of the group of rational points on the Jacobian $J$ of the curve, also called the Mordell-Weil rank, which is finite by the Mordell-Weil theorem.
 Chabauty proved, using $p$-adic methods, that if $r$ is strictly smaller than the genus $g$, then $C$ has only finitely many rational points.
-Loosely said, this proof and all Chabauty related theorems, rely on choosing a prime $p$ for which $C$ has good reduction, and intersecting $J(\Z)$ with $C(\Z_p)$ inside the bigger Lie group $J(\Z_p)$; by properties of $\Z_p$, the subgroup $J(\Z)$, up to torsion generated by $r$ elements, lies within a Lie subgroup of dimension at most $r$, and $C(\Z_p)$ is a $1$-dimensional $p$-adic manifold, and hence their intersection can be proven to be discrete and -- as $J(\Z_p)$ is compact -- finite.\todo{Ik moet volgens mij uberhaupt nadenken wat over $\Q,\Q_p,\Z,\Z_p$ moet}
-
-This was later made into an effective argument by Coleman in 1985.
-This was done by finding explicitly, as a power series, a differential form $\omega$ on $J_{\Z_p}$ whose Coleman integral vanishes on $J(\Z)$.
-Pulling $\omega$ back to $C_{\Z_p}$ and looking at the fibre of reduction to a single $\F_p$-point $P$, one can in certain cases give an upper bound for the number of points in $C(\Z)$ reducing to $P$ based only on finite-precision calculations of $\omega$.
-Most well known is the generic upper bound $|C(\Q)| \leq |C(\F_p)| + 2g-2$ under the conditions $r < g, p > 2g$, as explained in the introductory article \cite{poonen12}.
-
-This Coleman-Chabauty method has been greatly generalised by Kim to so called non-abelian Chabauty in \todo{Ref} and \todo{Ref}.
-He interprets working in the Jacobian as dealing with the abelianised fundamental group of the curve $C$, and works with larger, non-abelian quotients of the fundamental group.
-Then the simplest case of non-abelian Chabauty, quadratic Chabauty was developed by Kim, Balakrishnan, Besser Dogran and M\"uller in the series of articles \todo{Ref}, and further extended by Balakrishnan, Dogra, M\"uller, Tuitman and Vonk; in 2017 they famously calculated  all rational points of the ``cursed curve'', the modular curve $X_s^+(13)$ \cite{cursedcurve}.
-They use an endomorphism of the Jacobian, and do $p$-adic analysis on $p$-adic local heights to make quadratic Chabauty explicit.
-Their methods are strong enough to prove finiteness of $C(\Z)$ under the condition of $r < g + \rho - 1$, where $\rho$ is the N\'eron-Severi rank of the Jacobian.
+Loosely said, this proof and all Chabauty related theorems, rely on choosing a prime $p$ for which $C$ has good reduction, and intersecting $J(\Q)$ with $C(\Q_p)$ inside the bigger Lie group $J(\Q_p)$.
+By properties of $\Q_p$, the subgroup $J(\Q)$, up to torsion generated by $r$ elements, lies within a Lie subgroup of dimension at most $r$, and $C(\Q_p)$ is a $1$-dimensional $p$-adic manifold, and hence this intersection can be proven to be discrete and -- as $J(\Q_p)$ is compact -- finite.
+
+This was made into an effective argument by Coleman in 1985.
+This was done by finding explicitly, as a power series, a differential form $\omega$ on $J_{\Q_p}$ whose Coleman integral vanishes on $J(\Q)$.
+Pulling $\omega$ back to $C_{\Q_p}$ and looking at the fibre of reduction to a single $\F_p$-point $P$, one can in certain cases give an upper bound for the number of points in $C(\Q)$ reducing to $P$ based only on finite-precision calculations of $\omega$.
+Most well known is the generic upper bound $|C(\Q)| \leq |C(\F_p)| + 2g-2$ under the conditions $r < g, p > 2g$, as explained in the excellent introductory article \cite{poonen12}.
+
+This Coleman-Chabauty method has been greatly generalised by Kim to so-called non-abelian Chabauty in \cite{kim1} and \cite{kim2}.
+He interprets working in the Jacobian as dealing with the abelianised fundamental group of the curve $C$ and works with larger, non-abelian quotients of the fundamental group.
+Then quadratic Chabauty, the simplest case of non-abelian Chabauty, was developed by Kim, Balakrishnan, Besser, Dogra and M\"uller in the series of articles \cite{qc1},\cite{qc2},\cite{qc3}, and further extended by Balakrishnan, Dogra, M\"uller, Tuitman and Vonk; in 2017 they famously calculated all rational points of the ``cursed curve'', the modular curve $X_s^+(13)$ \cite{cursedcurve}.
+They use an endomorphism of the Jacobian and do $p$-adic analysis on $p$-adic local heights to make quadratic Chabauty explicit.
+Their methods are strong enough to prove finiteness of $C(\Q)$ under the condition of $r < g + \rho - 1$, where $\rho$ is the N\'eron-Severi rank of the Jacobian, even if finding $C(\Q)$ can still be difficult in those cases.
 
 Very recently, Edixhoven and Lido made available a preprint of their article ``Geometric quadratic Chabauty'' \cite{edixhoven20}.
-Their goal in this article is to make a more geometric approach to effective quadratic Chabauty, by working in a pullback $T$ of the Poincar\'e torsor of the Jacobian.
-They also abandon the Coleman method for Chabauty; instead they parametrise the map $T(\Z) \to T(\Z_p)$ with power series, and pull back equations for the curve inside $T(\Z_p)$ along this map.
+Their goal in this article is to create a more geometric approach to effective quadratic Chabauty, by working in a pullback $T$ of the Poincar\'e torsor of the Jacobian spread out over $\Z$.
+They also abandon the Coleman method for Chabauty; instead, they parametrise the map $T(\Z) \to T(\Z_p)$ with power series and pull back equations for the curve inside $T(\Z_p)$ along this map.
 Again, a necessary condition is $r < g + \rho - 1$.
@@
 The purpose of this thesis is to make the work by Edixhoven and Lido more accessible by applying geometric Chabauty to the linear case, i.e.
-when working with $J(\Z)$ and $J(\Z_p)$ and assuming $r < g$.
-In this thesis, we go into more detail of what is happening throughout the process, including both theoretical and practical components.
-This new method of applying Chabauty leads to, when working with single digit $p$-adic precision, a conditional upper bound $|C(\Q)| \leq |C(\F_p)|$, as obtained in Proposition~\ref{prop:linchabauty}.
+when working with $J(\Q)$ and $J(\Q_p)$ and assuming $r < g$.\todo{Add number fields in the introduction} In this thesis, we go into more detail on what is happening throughout the process, including both theoretical and practical components.
+This new method of applying Chabauty leads to, when working with single-digit $p$-adic precision, a conditional upper bound $|C(\Q)| \leq |C(\F_p)|$, as obtained in Proposition~\ref{prop:linchabauty}.
 This upper bound compares favorably with classical Coleman-Chabauty, but unlike classical Coleman-Chabauty, we cannot say in general when the conditions of these propositions hold.
-We develop heuristics that suggest that generally trying multiple primes $p$ of good reduction will yield good results; these heuristics say that the conditional upper bound will hold for a set of primes of density $1$, and if $r < g-1$ can even often (in a set of primes of density at least $e^{-1}$) be improved to prove there are at most $|C(\Q)|$ rational points.
-The methods used to obtain Proposition~\ref{prop:linchabauty} are also amenable to higher precision calculations; indeed, in the case $r = g-1$ this may be necessary to calculate $|C(\Z)|$ exactly.\todo{Over hebben met Bas}
-
-We also give a hyperelliptic example with $r = 1, g = 2$, where the bound from Proposition~\ref{prop:linchabauty} indeed holds, and we are able to compute $C(\Z)$.
+We develop heuristics that suggest that generally, trying multiple primes $p$ of good reduction will yield good results; these heuristics say that the conditional upper bound will hold for a set of primes of density $1$, and if $r < g-1$ the upper bound can even often (in a set of primes of density at least $e^{-1}$) be improved to prove there are at most $|C(\Q)|$ rational points, i.e., finding $C(\Q)$ exactly.
+The methods used to obtain Proposition~\ref{prop:linchabauty} are also amenable to higher precision calculations; indeed, in the case $r = g-1$ one expects to need either higher precision calculations or the Mordell-Weil sieve to calculate $|C(\Q)|$ exactly.
+
+We also give a hyperelliptic example with $r = 1, g = 2$, where the bound from Proposition~\ref{prop:linchabauty} indeed holds, and we are able to compute $C(\Q)$.
 
@@
 We first present the context in which we will perform Chabauty.
-Let $p>2$ be a prime, and $C$ be a scheme over $\Z$, proper, flat, regular with $C$ smooth over $\Z_{(p)}$ and $C_\Q$ of dimension $1$ and geometrically connected, of genus $g \geq 1$ and with the N\'eron model $J$ of the Jacobiano of $C_\Q$ having Mordell-Weil rank $r < g$.
-Assume we have a $\Q$-point $b$ in $C$, or equivalently a $\Z$-point.
+Let $K$ be a number field of degree $d$, and let $v: K \to \Z$ be a finite place.
+Let $\pi$ denote a uniformiser, $q$ the cardinality of the residue field and $p> 2$ its caracteristic\todo{Check when $p,\pi$ is big enough for both Pierre Parent and logarithm}\todo{Decide if we can allow ramification}.
+Let $f$ denote the residue field degree $[\F_q : \F_p]$ and $e$ the ramification $v(p)$.
+We use $O$ to denote the maximal order of $K$, and $O_{(\pi)}$ and $O_{\pi}$ for respectively the localisation and the completion with respect to $\pi$.
+This valuation also gives rise to an embedding of $K$ into an extension $K_{\pi}$ of $\Q_p$ of degree $ef$, with ramification degree $e$ and residue field degree $f$; then $O_\pi$ is simply the ring of integers of $K_{\pi}$.
+
+Let $C_{K}/K$ be a curve (i.e., a proper, smooth, geometrically connected variety of dimension $1$) of genus $g \geq 2$ whose $K$-points we will attempt to find.
+assume we have a scheme $C$ over $O_{(\pi)}$, proper and smooth with generic fibre $C_{K}$; then we immediately have $C_K(K) = C(K) = C(O_{(\pi)})$ by the valuative criterion of properness.
+Let $J$ be the relative Jacobian of $C$ over $O_{(\pi)}$, i.e.
+with fibres $\Jac C_K$ and $\Jac C_{\F_q}$.
+We assume from now on that the Mordell-Weil rank of $J$ is $r \leq d(g-1)$.
+Assume we have a $K$-point $b$ in $C$, or equivalently a $O_{(\pi)}$-point.
 We view $C$ as a subscheme of $J$, using the map $Q \mapsto Q - b$ on points.
-Let $P \in C(\F_p)$ be a point such that $t := P - b \in J(\F_p)$ lies in the image of $J(\Z)$.
+Let $P \in C(\F_q)$ be a point such that $t := P - b \in J(\F_q)$ lies in the image of $J(O_{(\pi)})$.
 
@@
 \begin{exmp}
-If we have a projective variety $X$ over $\Z$, then $X(\Z)$ is in bijection with $X(\Q)$.
-The natural map $X(\Z) \to X(\F_p)$ reduces a point modulo $p$ and for $x \in X(\F_p)$, the set $X(\Z)_x$ consists of the $\Z$-points reducing to $x$.
+If we have a proper variety $X$ over $O_{(\pi)}$, then $X(O_{(\pi)})$ is naturally in bijection with $X(K)$.
+The natural map $X(O_{(\pi)}) \to X(\F_q)$ reduces a point modulo $\pi$ and for $x \in X(\F_q)$, the set $X(O_{(\pi)})_x$ consists of the residue disc of $O_{(\pi)}$-points reducing to $x$.
 \end{exmp}
 
-Geometric Chabauty works by finding an upper bound for the cardinality of $C(\Z)_P$. For this, we use the following diagram.
+Geometric Chabauty works by finding an upper bound for the cardinality of $C(O_{(\pi)})_P$. For this, we use the following diagram.
 \[
 \begin{tikzcd}
-C(\Z)_P \arrow[d] \arrow[r, "a"] & J(\Z)_t \arrow[d] \\
-C(\Z_p)_P \arrow[r]              & J(\Z_p)_t        
+C(O_{(\pi)})_P \arrow[d] \arrow[r] & J(O_{(\pi)})_t \arrow[d] \\
+C(O_\pi)_P \arrow[r]              & J(O_\pi)_t        
 \end{tikzcd}
@@
 where the two vertical maps are inclusions, and the two horizontal maps are subtraction of $b$.
-We will in fact compute upper bounds for the larger set $C(\Z_p)_P \cap \overline{J(\Z)_t}$, where $\overline{J(\Z)_t}$ is the closure of $J(\Z)_t$ in $J(\Z_p)_t$.
-
-In Section~\ref{section:smoothzppoints}, we treat the structure of $C(\Z_p)_P$ and $J(\Z_p)_t$; we will show that, after choosing parameters, they are canonically in bijection with respectively $\Z_p$ and $\Z_p^g$.
-We also discuss the resulting map $\Z_p \to \Z_p^g$.
-
-In Section~\ref{section:kappa} we further look at the map $J(\Z)_t \to J(\Z_p)_t$.
-This is a translation of the group morphism $J(\Z)_0 \to J(\Z_p)_0$ between kernels of reduction; it turns out that for our choice of $p$, the subgroup $J(\Z)_0$ is free of rank $r$.
-We study the properties of the resulting map $\Z^r \to \Z_p^g$, using the theory of formal groups to determine the group structure on $\Z_p^g$ induced by the bijection $J(\Z_p)_t \to \Z_p^g$.
-
-In Section~\ref{section:intersection}, we put all of this information together, culminating in several methods to possibly compute upper bounds on $\left|C(\Z_p)_P \cap \overline{J(\Z)_t}\right|$ with finite precision calculations.
-We also perform a heuristic analysis to show that a simple calculation of linear algebra modulo $p$ is very likely to result in an upper bound of at most $|C(\F_p)|$ for $|C(\Z)|$, and for $r < g-1$ even in an upper bound of $|C(\Z)|$.
-
-The methods developed in the first four sections are not always guaranteed to prove finiteness of $C(\Z)_P$.
+We will in fact compute upper bounds for the larger set $C(O_\pi)_P \cap \overline{J(O_{(\pi)})_t}$, where $\overline{J(O_{(\pi)})_t}$ is the closure of $J(O_{(\pi)})_t$ in $J(O_\pi)_t$.
+
+In Section~\ref{section:smoothzppoints}, we treat the structure of $C(O_\pi)_P$ and $J(O_\pi)_t$; we will show that, after choosing parameters, they are in bijection with respectively $O_\pi$ and $O_\pi^g$.
+We also discuss the resulting map $O_\pi \to O_\pi^g$.{\color{red} and, identifying $O_\pi$ with $\Z_p^{ef}$ as topological groups, the map $\Z_p^{ef} \to \Z_p^{efg}$.
+This latter map is not necessarily well behaved if there is ramification; choosing a $\Z_p$-basis of $O_{\pi}$ appropriately, we will instead look at the well behaved restriction $\Z_p^{f} \to \Z_p^{fg}$.}
+
+In Section~\ref{section:kappa} we further look at the map $J(O_{(\pi)})_t \to J(O_\pi)_t$.
+This is a translation of the group morphism $J(O_{(\pi)})_0 \to J(O_\pi)_0$ between kernels of reduction; it turns out that for our choice of $p$, the subgroup $J(O_{(\pi)})_0$ is free of rank $r$.
+We study the properties of the resulting map $\Z^r \to O_\pi^g$, using the theory of formal groups to determine the group structure on $O_\pi^g$ induced by the bijection $J(O_\pi)_0 \to O_\pi^g$.
+{\color{red} Importantly, we identify $O_\pi$ with $\Z_p^{ef}$ as topological groups; we also look at the resulting map $\Z^r \to \Z_p^{efg}$.
+Again, to control the behavior of this map modulo $p$, we consider the map $\Z^r \to \Z_p^{fg}$.}
+
+In Section~\ref{section:intersection}, we put all of this information together, culminating in several methods to possibly compute upper bounds on $\left|C(O_\pi)_P \cap \overline{J(O_{(\pi)})_t}\right|$ with finite precision calculations if $r \leq f(g-1)$.
+We also perform a heuristic analysis to show that a simple calculation of linear algebra modulo $p$ is very likely to result in an upper bound of at most $|C(\F_q)|$ for $|C(O_{(\pi)})|$, and for $r < f(g-1)$ \todo{check whether this is correct, it should hold.} even in an upper bound of $|C_K(K)|$.
+Hence given only a curve $C_K/K$, the best possible choice of a prime of $K$ is an inert prime
+
+The methods developed in the first four sections are not always guaranteed to prove finiteness of $C(O_{(\pi)})_P$.
 In Section~\ref{section:remarks} we treat several possible complications and improvements, referring to other work on Chabauty for further reading.
@@
 Here, we use Makdisi's approach of representing a divisor by a subspace of a large Riemann-Roch space.
-We partially follow the article \cite{mascot18} by Mascot, and also give an original algorithm for explicitly computing the map $C(\Z_p)_P \to J(\Z_p)_t$ in Makdisi's representation.
-
-We end our discussion of linear geometric Chabauty with an explicit example in Section~\ref{section:example}, a genus $2$ curve whose Jacobian has Mordell-Weil rank $1$.
+We partially follow the article \cite{mascot18} by Mascot, and also give an original algorithm for explicitly computing the map $C(O_{\pi})_P \to J(O_{\pi})_t$ in Makdisi's representation.
+
+We end our discussion of linear geometric Chabauty with an explicit example in Section~\ref{section:example}, a genus $2$ curve over the rationals whose Jacobian has Mordell-Weil rank $1$.
 We use both Magma and Pari/GP to do our calculations, and end up with a complete list of all rational points of the curve.
 
-Finally, we provide an introduction to geometric quadratic Chabauty in Section~\ref{section:quadratic}.
-Here, we aim to introduce all the different objects relevant to geometric quadratic Chabauty; we explain why we have to work over $\Z$ instead of over $\Q$ to make geometric quadratic Chabauty make sense; and we explain some of the problems and solutions that working over $\Z$ gives rise to.
+Finally, we provide an introduction to geometric quadratic Chabauty in Section~\ref{section:quadratic} (working only over the rationals).
+Here, we aim to introduce all the different objects relevant to geometric quadratic Chabauty; we explain why we have to work over $\Z$ instead of over $\Q$ in order for geometric quadratic Chabauty to make sense; and we explain some of the problems and solutions that working over $\Z$ gives rise to.
 
@@
 master students with a specialisation in algebraic geometry.
-The introduction to geometric quadratic Chabauty in Section~\ref{section:quadratic} contains some terms typically not treated in a master; while knowing them will help put the material in context, this section is meant to be understandible even if that is not the case.
+The introduction to geometric quadratic Chabauty in Section~\ref{section:quadratic} contains some terms typically not treated in a master programme; while knowing them will help to put the material in context, this section is meant to be understandable for those that are not familiar with the terminology as well.
 
@@
 \label{section:smoothzppoints}
+{\color{red} Most of this section should still hold in the general number field case; replacing $p$ by $\pi$ when it is an element of $A$ (i.e., a section of $X$) and by $q$ when it is the cardinality of the residue field.
+Only the remark on it being a torsor of the tangent space merits a checking+rewrite.
+This has been done.}
 Let $X/\Z_p$ be a smooth scheme of relative dimension $d$, and let $x \in X(\F_p)$ be a point.
-Then $X(\Z_p)_x$ is in bijection with $\Z_p^d$.
+Then we will show in this section that $X(\Z_p)_x$ is naturally in bijection with $\Z_p^d$.
 This bijection is given by choosing parameters at $x$; evaluating at $X(\Z_p)_x$ gives a bijection with $(p\Z_p)^d$, and then we divide by $p$.
@@
 % Blow up X at x, and look at the part where p generates the maximal ideal
-Assume, by looking at a neighborhood of $x$, that $X = \Spec A$ is affine and that $p,t_1,\dots,t_d$ generate the maximal ideal of $O_{X,x}$ with $t_1,\dots,t_d$ elements of $O_X(X) = A$, also called \textit{parameters} at $x$.
-By shrinking $X$ even more, we may assume as $X$ is smooth that $t = (t_1,\dots,t_d): X \to \A^d_{\Z_p}$ is \'etale.
-Now consider the blowup $\widetilde{X}_x \to X$ of $X$ at $x$, and let $\widetilde{X}_x^p$ be the part where $p$ generates the inverse image of the maximal ideal of $O_{X,x}$.
-Equivalently, that is the part where $t_1,\dots,t_d$ are multiples of $p$, so informally it consists of the points that reduce to $x$ modulo $p$.
+Assume, by looking at a neighborhood of $x$, that $X = \Spec A$ is affine and that $p,t_1,\dots,t_d$ generate the maximal ideal of $\O_{X,x}$ with $t_1,\dots,t_d$ elements of $\O_X(X) = A$, also called \textit{parameters} at $x$.
+By shrinking $X$ even more, we may assume as $X$ is smooth that $t = (t_1,\dots,t_d): X \to \A^d_{\Z_p}$ is \'etale and the fibre of the origin over $\F_p$ consists of just $x$.
+Now consider the blowup $\widetilde{X}_x \to X$ of $X$ at $x$, and let $\widetilde{X}_x^p$ be the open subscheme where $p$ generates the inverse image of the maximal ideal of $\O_{X,x}$.
+Equivalently, that is the part where $t_1,\dots,t_d$ are multiples of $p$, so informally $\widetilde{X}_x^p$ consists of the points that reduce to $x$ modulo $p$.
 
@@
 That means that the blowup $\widetilde{X}_x \to X$ is the pullback of the blowup $\widetilde{\A}^d_{\Z_p,a} \to \A_{\Z_p}^d$.
-Then the part $\widetilde{X}_x^p$ is the pullback of the corresponding part of $\widetilde{\A}^d_{\Z_p,a}$, i.e.
+Then the open subscheme $\widetilde{X}_x^p$ is the pullback of the corresponding subscheme of $\widetilde{\A}^d_{\Z_p,a}$, i.e.
 $\Spec \Z_p[\widetilde{x_1},\dots,\widetilde{x_d}] = \Spec \Z_p[x_1/p,\dots,x_d/p]$ with the morphism $\Z_p[x_1,\dots,x_d] \to \Z_p[\widetilde{x_1},\dots,\widetilde{x_d}]$ given by $x_i \mapsto p\widetilde{x_i}$.
-That implies that $\widetilde{X}_x^p$ is $\Spec A[t_1/p,\dots,t_d/p]$, with the map $\widetilde{X}_x^p \to X$ given by the inclusion $A \to \Spec A[t_1/p,\dots,t_d/p]$ (remember that the $t_i$ are elements of $O_X(X) = A$).
+That implies that $\widetilde{X}_x^p$ is $\Spec A[t_1/p,\dots,t_d/p]$, with the map $\widetilde{X}_x^p \to X$ given by the inclusion $A \to \Spec A[t_1/p,\dots,t_d/p]$ (remember that the $t_i$ are elements of $\O_X(X) = A$).
 
@@
 \begin{lem}
-With $X$ as above, there is a natural bijection $X(\Z_p)_x \to \widetilde{X}_x^p(\Z_p)$,
+There is a natural bijection \[X(\Z_p)_x \to \widetilde{X}_x^p(\Z_p).\]
 \end{lem}
 \begin{proof}
-Note that by (I,2.4.4) of \cite{ega}, a $\Z_p$-point of a scheme $S$ is just an $\F_p$-point $s$ together with a local morphism $\O_{S,s} \to \Z_p$.
+Note that by (I,2.4.4) of \cite{ega}, a $\Z_p$-point of a scheme $S$ is just an $\F_p$-point $s$ together with a local morphism $\\O_{S,s} \to \Z_p$.
 In our case, we find that $X(\Z_p)_x$ is naturally in bijection with $\Hom_{\text{local}}(A_x,\Z_p)$.
-As the maximal ideal of $A_x$ is generated by $p,t_1,\dots,t_d$, the locality property just means that the images of $t_1,\dots,t_d$ are divisible by $p$, i.e.
-exactly those morphisms that extend to a morphism $A[t_1/p,\dots,t_d/p] \to \Z_p$, i.e.
+As the maximal ideal of $A_x$ is generated by $p,t_1,\dots,t_d$, the morphism being local just means that the images of $t_1,\dots,t_d$ are divisible by $p$.
+That exactly gives those morphisms that extend to a morphism $A[t_1/p,\dots,t_d/p] \to \Z_p$, i.e.
 a $\Z_p$-point of $\widetilde{X}_x^p$.
@@
 \begin{lem}
-With $X$ as above, evaluating $t$ at $X(\Z_p)_x$ gives a bijection to $(p\Z_p)^d$.
+Evaluating $t$ at $X(\Z_p)_x$ gives a bijection to $(p\Z_p)^d$.
 \end{lem}
 \begin{proof}
-As $t$ is locally of finite type, by (IV,17.6.3) of \cite{ega} we have an isomorphism between the $p$-adic completion $O(\widetilde{X}_x^p)^{\wedge p}$ and the completion $\Z_p\angle{\widetilde{x_1},\dots, \widetilde{x_d}}$ of $\Z_p[\widetilde{x_1},\dots,\widetilde{x_d}]$, with the latter completion being the ring of convergent power series, i.e.
+As $t$ is locally of finite type, by (IV,17.6.3) of \cite{ega} we have an isomorphism between the $p$-adic completion $\O(\widetilde{X}_x^p)^{\wedge p}$ and the completion $\Z_p\angle{\widetilde{x_1},\dots, \widetilde{x_d}}$ of $\Z_p[\widetilde{x_1},\dots,\widetilde{x_d}]$, with the latter completion being the ring of convergent power series, i.e.
 \[
@@
 \]
-By the universal property of completions, as $t$ induces the isomorphism between completions, $t$ also induces a bijection $$\Hom(O(\widetilde{X}_x^p), \Z_p) \to \Hom(\Z_p\angle{\widetilde{x_1},\dots,\widetilde{x_d}},\Z_p) = \Z_p^d.$$ Following all the bijections, we indeed get the bijection we wanted.
+By the universal property of completions, as $t$ induces the isomorphism between completions, $t$ also induces a bijection $$\Hom(\O(\widetilde{X}_x^p), \Z_p) \to \Hom(\Z_p\angle{\widetilde{x_1},\dots,\widetilde{x_d}},\Z_p) = \Z_p^d.$$ Following all the bijections, we indeed get the bijection we wanted.
 \end{proof}
@@
 \label{rem:smoothpointsfunc}
-Note that this construction is functorial, as in the following sense: given two smooth schemes $X,Y$ over $\Z_p$ and two $\F_p$-points $x\in X(\F_p)$, $y\in Y(\F_p)$, a map $f: Y \to X$ satisfying $f(y) = x$ gives rise to a morphism $\widetilde{Y}_y^p \to \widetilde{X}_x^p$.
-This is a direct consequence of II.7.15 of \cite{hartshorne}.
+Note that this construction is functorial, in the following sense: let $X,Y$ be two smooth schemes over $\Z_p$ and $x\in X(\F_p)$, $y\in Y(\F_p)$ be two $\F_p$-points, and let $f: Y \to X$ be a map satisfying $f(y) = x$.
+Then the inverse image along the map\[\widetilde{Y}_y^p \to Y \to X\] of the ideal sheaf defining $x$ is the ideal generated by $p$.
+Hence by the universal property of blowups (II.7.14 of \cite{hartshorne}), this factors through a unique morphism $\widetilde{Y}_y^p \to \widetilde{X}_x$, landing in $\widetilde{X}_x^p$, i.e.
+we get that there is a unique morphism $\widetilde{f}: \widetilde{Y}_y^p \to \widetilde{X}_x^p$ making the diagram
+\[
+\begin{tikzcd}
+\widetilde{Y}_y^p \arrow[d] \arrow[r,"\widetilde{f}"] & \widetilde{X}_x^p \arrow[d] \\
+Y \arrow[r,"f"]              & X  
+\end{tikzcd}
+\]
+commute.
 \end{rem}
@@
 \label{rem:torsortangentspace}
-In actual calculations, we will be focusing on $X(\Z/p^2\Z)_x$.
-This set is a natural torsor of the tangent space $T_x X_{\F_p}$ of $X_{\F_p}$ at $x$, which we will describe here.
-We write $R$ for the local ring $O_{X_{\Z/p^2\Z},x}$ and $\m$ for its maximal ideal, and $\overline{R}$ and $\overline{m}$ for their reductions modulo $p$.
-Then an element in $X(\Z/p^2\Z)_x$ is a local morphism $R \to \Z/p^2\Z$.
-As $R/\m = \F_p$, giving such a local morphism is equivalent to giving a map $\m \to p\Z/p^2\Z$ respecting multiplication and sending $p$ to $p$.
-Such a map factors uniquely through $\m/\m^2 \to p\Z/p^2\Z$.
-We see the set $X(\Z/p^2\Z)_x$ is canonically in bijection with $\F_p$-linear maps $\m/\m^2 \to p\Z/p^2\Z$ sending $p$ to $p$.
-Note that $\m/\m^2$ is a $d+1$-dimensional $\F_p$-vector space, and $\overline{\m}/\overline{\m}^2$ is a $d$-dimensional vector space; the map $\m/\m^2 \to \overline{\m}/\overline{\m}^2$ is dividing out by $p$.
-Denoting ${}^\wedge$ to be $\Hom(\cdot,\F_p)$, the exact sequence
-\[
-0 \to p\Z/p^2\Z \to \m/\m^2 \to \overline{\m}/\overline{\m}^2 \to 0
+In actual calculations, we will be focusing on $X(S)_x$ where $S = O_\pi/\pi^2 O_\pi$.
+This set is a natural torsor of the tangent space $T_x X_{\F_q}$ of $X_{\F_q}$ at $x$, which we will describe here.
+We write $R$ for the local ring $\O_{X_{S},x}$ and $\m$ for its maximal ideal, and $\overline{R}$ and $\overline{\m}$ for their reductions modulo $\pi$.
+Then an element in $X(S)_x$ is a local morphism $R \to S$.
+As $R/\m = \F_q$, giving such a local morphism is equivalent to giving a map $\m \to \pi S$ respecting multiplication and sending $\pi$ to $\pi$.
+Such a map factors uniquely through $\m/\m^2 \to \pi S$.
+We see that the set $X(\Z/p^2\Z)_x$ is canonically in bijection with $\F_q$-linear maps $\m/\m^2 \to \pi S$ sending $\pi$ to $\pi$.
+Note that $\m/\m^2$ is a $(d+1)$-dimensional $\F_q$-vector space, and $\overline{\m}/\overline{\m}^2$ is a $d$-dimensional $\F_q$-vector space; the map $\m/\m^2 \to \overline{\m}/\overline{\m}^2$ is dividing out by $\pi$.
+Denoting ${}^\wedge$ to be $\Hom(\cdot,\F_q)$, the exact sequence
+\[
+0 \to \pi S \to \m/\m^2 \to \overline{\m}/\overline{\m}^2 \to 0
 \]
@@
 \[
-0 \to (\overline{\m}/\overline{\m}^2)^\wedge \to (\m/\m^2)^\wedge \to (p\Z/p^2\Z)^{\wedge} \to 0.
-\]
-As $X(\Z/p^2\Z)_x$ is exactly the subset of $(\m/\m^2)^\wedge$ that gets mapped to $p \mapsto 1 \in (p\Z/p^2\Z)^{\wedge}$, we see this is naturally a torsor under $(\overline{\m}/\overline{\m}^2)^\wedge = T_{x} X_{\F_p}$.
-
-Note that this set does not have any more canonical structure; for example, with $X = \A^1_{\Z_p}$ and $x$ is the $\F_p$-point $1$, the set $X(\Z/p^2\Z)_x$ is $\{1 + pi | i \in \F_p\}$, and we see we cannot upgrade the torsor structure.
-This is due to the fact that even after choosing a parameter at $x$ as a point of $X_{\F_p}$, a lift of such a parameter to $X_{\Z/p^2\Z}$ is not canonical, and can in fact differ up to translation.
+0 \to (\overline{\m}/\overline{\m}^2)^\wedge \to (\m/\m^2)^\wedge \to (\pi S)^{\wedge} \to 0.
+\]
+As $X(S)_x$ is exactly the subset of $(\m/\m^2)^\wedge$ that gets mapped to the function $p \mapsto 1 \in (\pi S)^{\wedge}$, we see this is naturally a torsor under the tangent space $(\overline{\m}/\overline{\m}^2)^\wedge = T_{x} X_{\F_q}$.
+
+Note that this set does not have any more canonical structure; for example, with $X = \A^1_{\Z_p}$ and $x$ the $\F_p$-point $1$, the set $X(\Z/p^2\Z)_x$ is $\{1 + pi | i \in \F_p\}$, and we see we cannot upgrade the torsor structure.
+This is because even after choosing a parameter at $x$ as a point of $X_{\F_p}$, a lift of such a parameter to $X_{\Z/p^2\Z}$ is not canonical, and can in fact differ up to translation.
 This is in contrast to the situation over $\F_p[\varepsilon]/(\varepsilon^2)$, where the $\F_p$-algebra structure gives rise to an isomorphism of $\F_p$-vector spaces between $X(\F_p[\varepsilon]/(\varepsilon^2))$ and $T_x X_{\F_p}$; indeed, this is an alternate definition of the tangent space.
@@
 Then the $T_x X_{\F_p}$-torsor structure on $X(\Z/p^2\Z)_x$ translates into something more concrete.
-We can parametrise $X(\Z/p^2\Z)_x$ by $t = t_1 : X(\Z/p^2\Z)_x \to p\Z/p^2\Z$; write $P_{\lambda}$ for the point with $t$-value $\lambda p$.
-Then as Cartier divisor, the point $P_{\lambda}$ is defined by $t - \lambda p \in O(X_{\Z/p^2\Z})_x$, so $P_{\lambda} + P_{\mu}$ is defined by $(t-\lambda p)(t-\mu p) = t^2 - (\lambda + \mu)tp$, which defines the same Cartier divisor as $P_{\lambda'} + P_{\mu'}$ if and only if $\lambda + \mu = \lambda' + \mu'$.
+We can parametrise $X(\Z/p^2\Z)_x$ by $t = t_1 $ from $X(\Z/p^2\Z)_x \to p\Z/p^2\Z$; write $P_{\lambda}$ for the point with $t$-value $\lambda p$.
+Then as Cartier divisor, the point $P_{\lambda}$ is defined by $t - \lambda p \in \O_{X_{\Z/p^2\Z},x}$, so $P_{\lambda} + P_{\mu}$ is defined by $(t-\lambda p)(t-\mu p) = t^2 - (\lambda + \mu)tp$, which defines the same Cartier divisor as $P_{\lambda'} + P_{\mu'}$ if and only if $\lambda + \mu = \lambda' + \mu'$.
 In that case, as a Cartier divisor, $P_{\lambda} + P_{\mu}$ is in fact equal to $P_{\lambda'} + P_{\mu'}$.
@@
 \label{subsection:czptojzp}
+Let $p,C$ and $J$ be as defined in the overview.
 We know that $C(\Z_p)_P$ is in bijection with $\Z_p$, again with the bijection given by evaluating a parameter and dividing by $p$.
 The resulting function $\Z_p \to \Z_p^g$ is linear modulo $p$, i.e.
-by using that $\Z\angle{z_1,\dots,z_g}$ is $p$-adically complete there are power series $f_1,\dots,f_{g-1} \in \Z_p\angle{z_1,\dots,z_g}$ such that the image of $C(\Z_p)_P$ is exactly given by $V(f_1,\dots,f_{g-1})$, and all $f_i$ are linear modulo $p$ as a consequence of Remark \ref{rem:cartierlinear}.
+by using that $\Z\angle{z_1,\dots,z_g}$ is $p$-adically complete there are power series $f_1,\dots,f_{g-1} \in \Z_p\angle{z_1,\dots,z_g}$ such that the image of $C(\Z_p)_P$ is exactly given by $Z(f_1,\dots,f_{g-1})$, and all $f_i$ are linear modulo $p$ as a consequence of Remark \ref{rem:cartierlinear}.
 Another way to think of this, is as $C(\Z/p^2\Z)_P$ being an affine line inside $J(\Z/p^2\Z)_t$.
-That $C(\Z/p^2\Z)_P$ is an affine line inside $J(\Z/p^2\Z)_t$ can also be seen more easily: this map can be identified with the tangent map, using the structure of $X(\Z/p^2\Z)_x$ as a torsor over the tangent space from \ref{rem:cartierlinear}.
+That $C(\Z/p^2\Z)_P$ is an affine line inside $J(\Z/p^2\Z)_t$ can also be seen more easily: this map can be identified with the tangent map, using the structure of $X(\Z/p^2\Z)_x$ as a torsor over the tangent space from Remark~\ref{rem:cartierlinear}.
 
@@
 
-\section{From \texorpdfstring{$J(\Z)$}{J(Z)} to \texorpdfstring{$J(\Z_p)$}{J(Z\_p)}}
+\section{From \texorpdfstring{$J(\Z_{(p)})$}{J(Z\_{(p)})} to \texorpdfstring{$J(\Z_p)$}{J(Z\_p)}}
 \label{section:kappa}
-For $p > 2$, we know that the torsion of $J(\Z)$ injects into $J(\F_p)$, by Proposition 2.3 of \cite{pierre2000}.
-Hence for $0 \in J(\F_p)$, we know $J(\Z)_0$ is as a group isomorphic to $\Z^r$ with $r$ the Mordell-Weil rank.
-By assumption, we also know $J(\Z)_t$ is in bijection with $J(\Z)_0$, with the bijection giving by translating with a lift of $t$.
+Let $p,C,J$ be as in the overview.
+As $p > 2$, we know that the torsion of $J(\Z_{(p)})$ injects into $J(\F_p)$, by Proposition 2.3 of \cite{pierre2000}.
+Hence for $0 \in J(\F_p)$, we know $J(\Z_{(p)})_0$ is as a group isomorphic to $\Z^r$ with $r$ the Mordell-Weil rank.
+By assumption, we also know $J(\Z_{(p)})_t$ is in bijection with $J(\Z_{(p)})_0$, with the bijection giving by translating with a lift of $t$.
 By Section \ref{section:smoothzppoints} we know $J(\Z_p)_t$ is in bijection with $\Z_p^{g}$, with the bijection given by evaluating parameters and dividing by $p$.
-Let $\kappa: \Z^r \to \Z_p^g$ be the map resulting from the inclusion $J(\Z)_t \to J(\Z_p)_t$.
+Let $\kappa: \Z^r \to \Z_p^g$ be the map resulting from the inclusion $J(\Z_{(p)})_t \to J(\Z_p)_t$.
 In this section we will prove that $\kappa$ turns out to have a special property.
@@
 \label{thm:kappanice}
-There are uniquely determined $\kappa_1,\dots,\kappa_g \in \Z_p\angle{z_1,\dots,z_r}$ such that for all $x \in \Z^r$ we have $\kappa(x) = (\kappa_1(x),\dots,\kappa_g(x))$ and the image $\overline{\kappa_i}$ of $\kappa_i$ in $\F_p[z_1,\dots,z_r]$ has degree at most $1$; furthermore, for $m \in \Z_{>0}$ with $m<p-1$, these $\kappa_i$ are also of degree at most $m$ modulo $p^m$.
+There are uniquely determined $\kappa_1,\dots,\kappa_g \in \Z_p\angle{z_1,\dots,z_r}$ such that for all $\vx \in \Z^r$ we have $\kappa(\vx) = (\kappa_1(\vx),\dots,\kappa_g(\vx))$ and the image $\overline{\kappa_i}$ of $\kappa_i$ in $\F_p[z_1,\dots,z_r]$ has degree at most $1$; furthermore, for $m \in \Z_{>0}$ with $m<p-1$, these $\kappa_i$ are also of degree at most $m$ modulo $p^m$.
 \end{thm}
 
-We will prove this using results about formal group as defined in \cite{honda70}.
+We will prove this using results about formal groups as defined in \cite{honda70}.
 To be able to use this theory, we first give some results about going from a group scheme over $\Z_p$ to a formal group.
-First we introduce some notation that will be used in this section.
-Let $R$ be a commutative ring, and $x = (x_1,\dots,x_n)$ and sometimes $y,z$ are vectors of variables.
-Then $R[[x]]$ denotes as usual the ring of formal powerseries in the $x_i$, and $R[[x]]_0$ denotes those power series with constant term $0$.
-With $x = (x_1,\dots,x_n)$ and $y = (y_1,\dots,y_m$), let $f \in R[[x]]^m$ and assume $f(0) = 0$.
-Then for $g \in R[[y]]^k$ for some $k\in\Z_{\geq 0}$, we can compose $g$ and $f$ to get \[g\circ f := (g_1(f(x)),\dots,g_k(f(x)))\in R[[x]]]^k.\] This definition makes sense because $f^i$ converges to $0$, so the infinite sum $g_j(f(x))$ converges.
+We introduce some notation that will be used in this section.
+Let $R$ be a commutative ring, and $\vx = (x_1,\dots,x_n)$ and similarly $\vy,\vz$ are vectors of variables.
+Then $R[[\vx]]$ denotes as usual the ring of formal power series in the $x_i$, and $R[[\vx]]_0$ denotes those power series with constant term $0$.
+With $\vx = (x_1,\dots,x_n)$ and $\vy = (y_1,\dots,y_m$), let $f \in R[[\vx]]_0^m$.
+Then for $g \in R[[\vy]]^k$ for some $k\in\Z_{\geq 0}$, we can compose $g$ and $f$ to get \[g\circ f := (g_1(f(\vx)),\dots,g_k(f(\vx)))\in R[[\vx]]^k.\] This definition makes sense because $f^i$ converges to $0$ in the $(\vx)$-adic topology, so the infinite sum $g_j(f(\vx))$ converges.
 
 \subsection{From group schemes to formal groups}
-We first recall the definition of a formal group. For this entire section, $R$ is a ring, and $x,y,z$ are vectors of variables.
+We first recall the definition of a formal group.
 \begin{defn}
@@
 Let $n$ be a non-negative integer.
-Let $x,y,z$ be vectors of $n$ variables.
-An $n$-dimensional formal group is an element $F = (F_1,\dots,F_n)$ of $R[[x,y]]_0^n$ satisfying $F \equiv x + y \bmod (x,y)^2$ and $F(F(x,y),z) = F(x,F(y,z))$.
-If furthermore $F(x,y) = F(y,x)$, this formal group is said to be commutative.
+Let $\vx,\vy,\vz$ be vectors of $n$ variables.
+An $n$-dimensional formal group is an element $F = (F_1,\dots,F_n)$ of $R[[\vx,\vy]]_0^n$ with $F \equiv \vx + \vy \bmod (\vx,\vy)^2$ and $F(F(\vx,\vy),\vz) = F(\vx,F(\vy,\vz))$.
+If furthermore $F(\vx,\vy) = F(\vy,\vx)$, this formal group is said to be commutative.
 \end{defn}
@@
 \label{exmp:ganformalgroup}
-For any $n$, we can take $F(x,y) = x+ y$, also known as the $n$-dimensional additive formal group.
+For any $n$, we can take $F(\vx,\vy) = \vx+ \vy$, also known as the $n$-dimensional additive formal group.
 \end{exmp}
@@
 \end{exmp}
-Note there is no mention of an inverse; the following lemma, a formal version of the implicit function theorem, tells us that the inverse follows automatically from the definitions.
+Note there is no mention of an inverse; the following lemma, a formal version of the implicit function theorem, tells us that the existence and uniqueness of the inverse follows automatically from the definitions.
 \begin{lem}
 \label{lem:implicitfunction}
-Let $x,y$ be vectors of variables of length $n$.
-Let $F \in R[[x,y]]_0^n$ such that $F \equiv Ax + By \bmod (x,y)^2$ with $A \in \Mat_n(R)$ and $B \in \GL_n(R)$.
-Then there is a unique $\iota \in R[[x]]_0^n$ such that $F(x,\iota(x)) = 0$.
+Let $\vx,\vy$ be vectors of variables of length $n$.
+Let $F \in R[[\vx,\vy]]_0^n$ such that $F \equiv A\vx + B\vy \bmod (\vx,\vy)^2$ with $A \in \Mat_n(R)$ and $B \in \GL_n(R)$.
+Then there is a unique $\iota \in R[[\vx]]_0^n$ such that $F(\vx,\iota(\vx)) = 0$.
 \end{lem}
 \begin{proof}
-If $F$ is a polynomial, this is a special case of a multivariate version of Hensel's lemma, as in Corollaire~2 of \cite[III,4.5]{BourbakiCA}: we work over $R[[x]]$ which is complete with respect to the ideal $\m = (x)$, and the derivative matrix of $F(x,\iota)$ with respect to $\iota$ is $B$, which is invertible, and $\iota = 0$ gives a solution modulo $\m$.
-Now for $F$ any power series, let $F_j$ be the polynomial consisting of all terms in $F$ of degree at most $j$, and let $\iota_j$ be the unique power series in $R[[x]]_0^n$ such that $F_j(x,\iota_j) = 0$.
-Note that both $\iota_j$ and $\iota_{j+1}$ are solutions to $F_j(x,\iota) \equiv 0 \bmod \m^j$, so by the uniquess guaranteed by Hensel's lemma used over $R[[x]]/\m^j$, these must be equal.
-Hence they converge to $\iota \in R[[x]]_0^n$, which is the unique solution of $F(x,\iota(x)) = 0$.
+Note that $R[[\vx]]$ is complete with respect to the ideal $\m = (\vx)$, and the derivative matrix of $F(\vx,\iota)$ with respect to $\iota$ is $B$, which is invertible, and $\iota = 0$ gives a solution modulo $\m$.
+If $F$ is a polynomial, this means the existence and uniqueness of $\iota$ follow directly from the multivariate version of Hensel's lemma (Corollaire~2 of \cite[III,4.5]{BourbakiCA}).
+Now for general $F \in R[[\vx,\vy]]_0^n$, let $F_j \in R[\vx,\vy]_0^n$ consist of all terms in $F$ of degree at most $j$, and let $\iota_j$ be the unique power series in $R[[\vx]]_0^n$ such that $F_j(\vx,\iota_j) = 0$.
+Note that both $\iota_j$ and $\iota_{j+1}$ are solutions to $F_j(\vx,\iota) \equiv 0 \bmod \m^j$, so by the uniquess guaranteed by Hensel's lemma used over $R[[\vx]]/\m^j$, these must be equal.
+Hence they converge to $\iota \in R[[\vx]]_0^n$, which is the unique solution of $F(\vx,\iota(\vx)) = 0$.
 \end{proof}
@@
 \label{lem:formalinverse}
-Let $x$ have length $n$. Let $a \in R[[x]]_0^n$ with $a \equiv Px \bmod (x)^2$ for some matrix $P\in \GL_n(R)$. Then there is a unique $b \in R[[x]]_0^n$ such that $a \circ b = b \circ a = x$.
+Let $\vx$ have length $n$. Let $a \in R[[\vx]]_0^n$ with $a \equiv P\vx \bmod (x)^2$ for some matrix $P\in \GL_n(R)$. Then there is a unique $b \in R[[\vx]]_0^n$ such that $a \circ b = b \circ a = x$.
 \end{cor}
 \begin{proof}
-Let $F(x,y) = x - a(y)$.
-This satisfies the constraints of Lemma~\ref{lem:implicitfunction}, so we find a unique $b$ such that $a \circ b = x$.
-Applying Lemma~\ref{lem:implicitfunction} again gives a unique $c$ such that $b \circ c = x$.
+Let $F(\vx,\vy) = \vx - a(\vy)$.
+This satisfies the conditions of Lemma~\ref{lem:implicitfunction}, so we find a unique $b$ such that $a \circ b = \vx$.
+Applying Lemma~\ref{lem:implicitfunction} again gives a unique $c$ such that $b \circ c = \vx$.
 But then $a = a \circ (b \circ c) = (a \circ b) \circ c = c$ shows $a = c$ and hence we are done.
 \end{proof}
-So a formal group $F$ does by Lemma~\ref{lem:implicitfunction} indeed have a right inverse $\iota_F$.
-Also, by $F(0,0) = 0$ we have that $F(x,F(\iota_f,0)) = 0$ so $F(\iota_f,0)$ is in fact equal to $\iota_F$; as $\iota_F \equiv -x \bmod (x)^2$, it has a formal inverse and hence $F(x,0) = x$, so $0$ is indeed a right unit.
-A standard argument now shows that $\iota_F$ is also a left inverse and $0$ is also a right unit, so $F$ gives $(R[[x]],(x))$, together with the $(x)$-adic topology, the structure of a group object in the category of pairs of objects $(A,I)$ where $A$ is a topological $R$-algebra, complete with respect to $I$ with the $I$-adic topology; for two continuous morphisms $f_1,f_2$ from $(R[[x]],(x))$ to $(A,I)$, given by sending $x$ to $a_1,a_2 \in I^n$ respectively, we define $(f_1 \oplus f_2)(x) = F(a_1,a_2)$, and by our considerations this makes $\Hom_((R[[x]],x),(A,I))$ into a group, functorially in $A$.\todo{Nu zou het goed moeten zijn, toch?}
-
-Given a smooth scheme $G$ over $\Z_p$ of relative dimension $d$, together with a $\Z_p$-point $e$, we can look at the completion $\widehat{O}_{G,e}$ along the section $e$.
-By smoothness, after picking parameters, this is isomorphic as topological $\Z_p$-algebras to the ring of power series $\Z_p[[x_1,\dots,x_d]]$.
-This completion naturally gives rise to a formal scheme denoted $\Spf \widehat{O}_{G,e}$; in a categorical notion, this is a functor on finite length $\Z_p$-algebras sending $A$ to $\Hom_{\text{cont}}(\widehat{O}_{G,e},A)$, but we can also think of it as a locally ringed space with $\Spec \Z_p$ as topological space, and sheaf of rings $\lim_n \widetilde{O_{G,e}/m^n}$ where $m$ is the ideal of $O_{G,e}$ defining $e$\todo{Over hebben met Bas}.
-The global sections of this sheaf are simply $\widehat{O}_{G,e}$.
-
-If furthermore $G$ is a group scheme over $\Z_p$, then this formal scheme promotes to a formal group scheme, i.e.
-for every finite $\Z_p$-algebra $A$ the set $\Hom_{\text{cont}}(\widehat{O}_{G,e},A)$ gets a group structure, functorially in $A$.
-By functoriality, this is the same as an continuous coproduct $\mu: \widehat{O}_{G,e} \to \left(\widehat{O}_{G,e}\right)^{\widehat{\tensor} 2}$.
-After choosing an isomorphism between $\widehat{O}_{G,e}$ and $\Z_p[[x_1,\dots,x_d]]$, let $F_j \in \Z_p[[x,y]]$ denote $\mu(x_j)$.
-Then it is clear that $F_G = (F_1,\dots,F_d)$ is a $d$-dimensional formal group scheme, and commutative if $G$ was commutative.
+So a formal group $F$ does have a right inverse $\iota_F$.
+Also, by $F(0,0) = 0$ we have that $F(\vx,F(\iota_F,0)) = 0$ so $F(\iota_F,0)$ is in fact equal to $\iota_F$; as $\iota_F \equiv -\vx \bmod (\vx)^2$, it has a formal inverse and hence $F(\vx,0) = \vx$, so $0$ is indeed a right unit.
+A standard argument now shows that $\iota_F$ is also a left inverse and $0$ is also a right unit, so $F$ is indeed a group law in the following sense.
+We consider the category of pairs of objects $(A,I)$ where $A$ is a topological $R$-algebra, complete with respect to $I$ with the $I$-adic topology.
+We give $(R[[\vx]],(\vx))$, together with the $(\vx)$-adic topology, the structure of a group object in this category for two continuous morphisms $f_1,f_2$ from $(R[[\vx]],(\vx))$ to $(A,I)$, given by sending $\vx$ to $\va_1,\va_2 \in I^n$ respectively, we define $(f_1 \oplus f_2)(x) = F(\va_1,\va_2)$.
+By our considerations, this makes $\Hom((R[[\vx]],(\vx)),(A,I))$ into a group, functorially in $(A,I)$.
+
+Given a smooth scheme $G$ of relative dimension $d$ over a ring $R$, together with a $R$-point $e$, we can look at the completion $\widehat{\O}_{G,e}$ along the section $e$.
+By smoothness, after picking parameters, this is isomorphic as a topological $R$-algebra to the ring of power series $R[[x_1,\dots,x_d]]$.
+This completion naturally gives rise to a formal scheme denoted $\Spf \widehat{\O}_{G,e}$; in a categorical notion, this is a functor on finite length $R$-algebras sending $A$ to $\Hom_{\text{cont}}(\widehat{\O}_{G,e},A)$, but we can also think of it as a locally ringed space with $\Spec R$ as topological space, and sheaf of rings the inverse limits of the sheaf of rings associated to the $R$-algebra $\O_{G,e}/I^n$, where $I$ is the ideal of $\O_{G,e}$ defining $e$.
+The global sections of this sheaf are simply $\widehat{\O}_{G,e}$.
+
+If furthermore $G$ is a group scheme over $R$ and $e$ is the unit section, then this formal scheme promotes to a formal group scheme, i.e.
+for every finite $R$-algebra $A$ the set $\Hom_{\text{cont}}(\widehat{\O}_{G,e},A)$ gets a group structure, functorially in $A$.
+By functoriality, this is the same as an continuous coproduct \[\mu: \widehat{\O}_{G,e} \to \left(\widehat{\O}_{G,e}\right)^{\widehat{\tensor} 2}.\]
+After choosing an isomorphism between $\widehat{\O}_{G,e}$ and $R[[x_1,\dots,x_d]]$, let the power series $F_j \in R[[\vx,\vy]]$ denote $\mu(x_j)$.
+Then it is clear that \[F_G = (F_1,\dots,F_d)\] is a $d$-dimensional formal group scheme, and commutative if $G$ is commutative.
 \addtocounter{thm}{-3}
@@
 \label{exmp:gmtoformal}
-Take $G = \G_m$ over $\Z_p$, i.e.
-$\Z_p[u,u^{-1}]$.
-Then the zero section $e$ is the map sending $u$ to $1$, and we can identify the completion $\widehat{O}_{G,e}$ with the power series ring $\Z_p[[u-1]] \cong \Z_p[[x]]$, sending $u-1$ to $x$.
+Take $G = \G_m = \Spec \Z_p[u,u^{-1}]$ over $\Z_p$.
+Then the zero section $e$ is the map sending $u$ to $1$, and we can identify the completion $\widehat{\O}_{G,e}$ with the power series ring $\Z_p[[u-1]] \cong \Z_p[[x]]$, sending $u-1$ to $x$.
 The group structure on $G$ then gives rise to the coproduct $\Z_p[[u-1]] \to \Z_p[[u-1,v-1]], u \mapsto uv$ so the coproduct on $\Z_p[[x]]$ sends $x$ to $uv-1 = (x+1)(y+1) -1 = x + y + xy$.
@@
 
-This formal group tells us exactly how multiplication works on $G(\Z/p^e\Z)_0$; if we let $t = (t_1,\dots,t_d)$ denote the formal parameters giving the isomorphism $\widehat{O}_{G,e} \to \Z_p[[x_1,\dots,x_d]]$, and we represent a point $P$ in $G(\Z/p^e\Z)_0$ by their parameter values $t(P) \in p\Z/p^e\Z$, then the resulting multiplication on $p\Z/p^e\Z$ obtained from the group structure on $G(\Z/p^e\Z)_0$, i.e.
-the map $p\Z/p^e\Z \times p\Z/p^e\Z \to p\Z/p^e\Z$, is exactly evaluating $F$.
-By taking limits, $F$ also gives the multiplication on $G(\Z_p)_0$.
-
-Now we will look at the theory of formal groups, and how that will help us.
-For a $n$-dimensional formal group $F$ over a ring $R$, Proposition~1.1 of \cite{honda70} gives us a canonical $R$-basis $\omega_1,\dots,\omega_n$ of the right invariant differentials; these are elements of $\bigoplus_{j=1}^n R[[x]] \diff x_j$.
+Note that if $R = \Z_p$, the formal group $F_G$ tells us exactly how multiplication works on $G(\Z/p^e\Z)_0$; if we let $t = (t_1,\dots,t_d)$ denote the formal parameters giving the isomorphism $\widehat{\O}_{G,e} \to \Z_p[[x_1,\dots,x_d]]$, and we represent a point $P$ in $G(\Z/p^e\Z)_0$ by their parameter values $t(P) \in p\Z/p^e\Z$, then the resulting multiplication on $p\Z/p^e\Z$ obtained from the group structure on $G(\Z/p^e\Z)_0$, i.e.
+the map $p\Z/p^e\Z \times p\Z/p^e\Z \to p\Z/p^e\Z$, is exactly evaluating $F_G$.
+By taking limits, $F_G$ also gives the multiplication on $G(\Z_p)_0$.
+
+Now we will look at some standard results on formal groups.
+For an $n$-dimensional formal group $F$ over a ring $R$, Proposition~1.1 of \cite{honda70} gives us a canonical $R$-basis $\omega_1,\dots,\omega_n$ of the right invariant differentials; these are elements of $\bigoplus_{j=1}^n R[[\vx]] \diff x_j$.
 If the formal group is furthermore commutative, then by Proposition~1.3 of \cite{honda70} these are closed, i.e.
 $d\omega_j = 0$.
-A $1$-form $d\omega = \sum_{i=1}^n f_i \diff x_i$ being closed means exactly that $\frac{\partial f_i}{\partial x_j} = \frac{\partial f_j}{\partial x_i}$ for all $i,j$.
+A $1$-form $\omega = \sum_{i=1}^n f_i \diff x_i$ being closed means exactly that $\frac{\partial f_i}{\partial x_j} = \frac{\partial f_j}{\partial x_i}$ for all $i,j$.
 From now on, assume $R$ has no torsion; then $R$ imbeds into $\Q \tensor R$ and, we can formally integrate $\omega$, i.e.
-write it as $df$ where $f \in (\Q\tensor R)[[x]]$.
+write it as $df$ where $f \in (\Q\tensor R)[[\vx]]$.
 We make this unique by demanding that $f(0) = 0$.
-Writing this $f$ as $\sum_{I \in \N^n} a_I x^I$ with $I$ denoting a multi index and $a_I \in \Q\tensor R$, we see that $a_I$, although itself not necessarily lying in $R$, is close: writing $I = (I_1,\dots,I_n)$ we see that for all $j$ we must have $I_j a_I \in R$ as $f_j = \frac{\partial f}{\partial x_j} \in R[[x]]$.
-
-In particular, we write $\log_i$ for the unique element of $(\Q\tensor R)[[x]]$ such that $d\log_i = \omega_i$.
-Together, these $\log_i$ give an element $\log \in R[[x]]^n$, and by Theorem~1 of \cite{honda70}, this logarithm satisfies $\log(x) = x \bmod (x)^2$, and $\log(F(x,y)) = \log(x)+\log(y)$.
-By the first result, $\log$ has an inverse which we will call $\exp$, also given by powerseries in $(\Q\tensor R)[[x]]$, and also satisfying $\exp(x) = x \bmod (x)^2$.
+Writing this $f$ as $\sum_{I \in \N^n} a_I x^I$ with $I$ denoting a multi index and $a_I \in \Q\tensor R$, we see that $a_I$, although itself not necessarily lying in $R$, is close: writing $I = (I_1,\dots,I_n)$ we see that for all $j$ we must have $I_j a_I \in R$ as $f_j = \frac{\partial f}{\partial x_j} \in R[[\vx]]$.
+
+In particular, we write $\log_i$ for the unique element of $(\Q\tensor R)[[\vx]]_0$ such that $d\log_i = \omega_i$.
+Together, these $\log_i$ give an element $\log \in (\Q\tensor R)[[\vx]]_0^n$, and by Theorem~1 of \cite{honda70}, this logarithm satisfies $\log(\vx) = \vx \bmod (\vx)^2$, and $\log(F(\vx,\vy)) = \log(\vx)+\log(\vy)$.
+By the first result, $\log$ has an inverse which we will call $\exp$, also given by power series in $(\Q\tensor R)[[\vx]]_0^n$, and also satisfying $\exp(\vx) = \vx \bmod (\vx)^2$.
 \addtocounter{thm}{-1}
 \begin{exmp}[continued]
-Taking $F$ the multiplicative group as in Example~\ref{exmp:gmformalgroup}, Proposition~1.1 of \cite{honda70} gives us $\omega = \frac{1}{x+1}dx$; as a power series this is $\sum_{j \geq 0} (-x)^j$.
-The formal anti-derivative of this is $\log = \sum_{j \geq 1} \frac{-(-x)^j}{j}dx$ (note this is a translate of the $\log$ from analysis), and Theorem $1$ will tell us what we already know in the context of analysis $\log(x + y + xy) = \log(x)+\log(y)$ (this formula is also a translate of the corresponding formula from analysis).
-Then analysis will also explicitly tell us what $\exp$ looks like: namely, $\exp(x) = \sum_{j \geq 1} \frac{x^j}{j!}$.
+Taking $F$ again the multiplicative formal group as in Example~\ref{exmp:gmformalgroup}, Proposition~1.1 of \cite{honda70} gives us $\omega = \frac{1}{x+1}$; as a power series this is $\sum_{j \geq 0} (-x)^j$.
+The formal anti-derivative of this is \[\log = \sum_{j \geq 1} \frac{-(-x)^j}{j}dx\] (note this is a translate of the $\log$ from analysis), and Theorem~$1$ of \cite{honda70} will tell us what we already know in the context of analysis, namely the formula $\log(x + y + xy) = \log(x)+\log(y)$ (this formula is also a translate of the corresponding formula from analysis).
+Then analysis will also explicitly tell us what $\exp$ looks like: $\exp(x) = \sum_{j \geq 1} \frac{x^j}{j!}$.
 \end{exmp}
@@
 Now we will see how we can use this formal logarithm in our case of the formal group $F_G$ stemming from a $d$-dimensional smooth group scheme $G/\Z_p$.
-Recall that we have a bijection $G(\Z_p)_0 \to p\Z_p^d \to \Z_p^d$ given by evaluating at parameters $t = (t_1,\dots,t_d)$ and then dividing by $p$; furthermore, recall that the group structure on $G(\Z_p)_0$ is the same as the group structure defined by $F_G$ on $p\Z_p^d$.
-Let $\log \in \Z_p[[x]]^d$ denote the logarithm corresponding to $F_G$, and let $\log_p$ denote the power series $\log(px)/p = (\log_1(px)/p,\dots,\log_d(px)/p)$.
+Recall from Section~\ref{section:smoothzppoints} that we have a bijection $G(\Z_p)_0 \to p\Z_p^d \to \Z_p^d$ given by evaluating at parameters $t = (t_1,\dots,t_d)$ and then dividing by $p$; furthermore, recall that the group structure on $G(\Z_p)_0$ is the same as the group structure defined by $F_G$ on $p\Z_p^d$.
+Let $\log \in \Z_p[[\vx]]^d$ denote the logarithm corresponding to $F_G$, and let $\log_p$ denote the power series \[\log(p\vx)/p = (\log_1(p\vx)/p,\dots,\log_d(p\vx)/p).\]
 We then have the following little lemma to bridge the gap between power series and maps.
@@
 \label{lem:formallog}
-With notation as above, we have the following statements about $\log_p$:
+With notation as above, we have the following statements about $\log_p$, the first two of which also hold for $p=2$:
 \begin{enumerate}
@@
 Then this $\exp_p$ is a two-sided inverse of $\log_p$, and hence $\log_p: \Z_p^d \to \Z_p^d$ is a bijection.
-	\item Let $m \in \Z_{>0}$. For $p > m+1$, the map $\log_p$ and $\exp_p$ are of degree at most $m$ modulo $p^m$.
+	\item Let $m \in \Z_{>0}$. For $p > m+1$, the maps $\log_p$ and $\exp_p$ are of degree at most $m$ modulo $p^m$.
 \end{enumerate} 
@@
 \begin{proof}
-Write $\log_{i} = \sum_{I} a_{i,I} x^I$ and $\log_{p,i} = \sum_I a_{i,I} p^{|I|-1} x^I$ where $I$ ranges over the multi indices.
+Write $\log_{i} = \sum_{I} a_{i,I} \vx^I$ and $\log_{p,i} = \sum_I a_{i,I} p^{|I|-1} \vx^I$ where $I$ ranges over the multi indices, and $|I| = \sum_{i=1}^d I_i$.
 Recall that $a_{i,0} = 0$.
@@
 For purposes of easy estimation, this also means $|I|a_{i,I} \in \Z_p$.
-As we have, with no constraint on $p$, for all $n\geq 1$ that $c_n\coloneqq p^{n-1}/n$ lies in $\Z_p$ and converges to $0$, this means that \[ \log_{p,i} = \sum_I a_{i,I} p^{|I|-1} x^I = \sum_I |I|a_{i,I} c_{|I|} x^I\] is indeed an element of $\Z_p\angle{x_1,\dots,x_d}^n$, and hence defines a map $\Z_p^d \to \Z_p$.
+As we have, with no constraint on $p$, for all $n\geq 1$ that $c_n\coloneqq p^{n-1}/n$ lies in $\Z_p$ and converges to $0$, this means that \[ \log_{p,i} = \sum_I a_{i,I} p^{|I|-1} \vx^I = \sum_I |I|a_{i,I} c_{|I|} \vx^I\] is indeed an element of $\Z_p\angle{x_1,\dots,x_d}^n$, and hence defines a map $\Z_p^d \to \Z_p$.
 Hence all the $\log_{p,i}$ together give a map $\Z_p^d \to \Z_p^d$.
-By the equality of power series $\log(F(x,y)) = \log(x)+\log(y)$ from the definition of the logarithm, and the fact that all these powerseries converge on $p\Z_p^d$, this $\log_{p,i}$ is indeed a group morphism from $(\Z_p^d,\oplus)$ to $(\Z_p^d,+)$.
+By the equality of power series $\log(F(\vx,\vy)) = \log(\vx)+\log(\vy)$ from the definition of the logarithm, and the fact that all these power series converge on $p\Z_p^d$, this $\log_{p,i}$ is indeed a group morphism from $(\Z_p^d,\oplus)$ to $(\Z_p^d,+)$.
 
 To study $\log_p$ modulo $p$, we note that if $n\geq 3$, then $p$ actually divides $c_n$, and for $p > 2$ we even have $p|c_2$.
-As $\log_{p,i} = x_i \bmod (x)^2$, this means that for $p > 2$ we have \[\log_{p,i} \equiv \sum_{|I| = 1} |I|a_{i,I}c_{|I|} x^I \equiv x_i \bmod p.\]
-Note that as $\log_p \equiv x \bmod (x)^2$, by Lemma~\ref{lem:formalinverse} it has an inverse $\exp_p$ that a priori lies just in $\Z_p[[x]]_0^n$.
-Modulo $p$, this $\exp_p$ must be $x$, which lies in $\Z_p\angle{x}_0^n$; as $\Z_p\angle{x}$ is $p$-adically complete, using Hensel this shows $\exp_p$ is indeed in $\Z_p\angle{x}_0^n$.
+As $\log_{p,i} = x_i \bmod (\vx)^2$, this means that for $p > 2$ we have \[\log_{p,i} \equiv \sum_{|I| = 1} |I|a_{i,I}c_{|I|} x^I \equiv x_i \bmod p.\]
+Note that as $\log_p \equiv \vx \bmod (\vx)^2$, by Lemma~\ref{lem:formalinverse} it has an inverse $\exp_p$ that a priori lies just in $\Z_p[[\vx]]_0^n$.
+Modulo $p$, this $\exp_p$ must be $x$, which lies in $\Z_p\angle{\vx}_0^n$; as $\Z_p\angle{\vx}$ is $p$-adically complete, using Hensel's lemma this shows $\exp_p$ is indeed in $\Z_p\angle{\vx}_0^n$.
 
@@
 As $c_n$ has $p$-adic valuation $n-1$ for $n < p$, and $p$-adic valuation at least $p-2 \geq m$ for $n \geq p$, indeed $\log_p$ has degree at most $m$ modulo $p^m$.
-That the same holds immediately for $\exp_p$, follows immediately from the consideration that the set
-\[
-S \coloneqq \{f \in \Z/p^n\Z[x]_0^d \mid  f \equiv x \bmod p, \forall m \deg(f \bmod p^m) \leq m\}
-\]
-forms a group under composition, as we will now see. As $\Z_p\angle{x}$ is complete, we know the superset set of $S$
-\[
-T \coloneqq \{f \in \Z/p^n\Z[x]_0^d \mid  f \equiv x \bmod p\}
+That the same holds for $\exp_p$, follows immediately from the consideration that the set
+\[
+S \coloneqq \{f \in \Z/p^n\Z[\vx]_0^d \mid  f \equiv \vx \bmod p, \forall m \deg(f \bmod p^m) \leq m\}
+\]
+forms a group under composition, as we will now see. As $\Z_p\angle{\vx}$ is complete, we know the superset of $S$
+\[
+T \coloneqq \{f \in \Z/p^n\Z[\vx]_0^d \mid  f \equiv \vx \bmod p\}
 \]
@@
 As $S$ is finite and non-empty, all that remains to show is that $S$ is closed under composition.
-We can also characterise $S$ as consisting of images $\overline{f}$ of polynomials $f \in \Z_p[x]_0^d$ such that there is a polynomial $\widetilde{f}\in\Z_p[x]_0^d$ with $pf(x) = \widetilde{f}(px)$.
-If we then take two elements $\overline{f},\overline{g} \in S$, reductions of $f,g$ respectively with $\widetilde{f},\widetilde{g}$ such that $pf(x) = \widetilde{f}(px), pg(x) = \widetilde{g}(px)$, we see that with $h = f\circ g, \widetilde{h} = \widetilde{f} \circ \widetilde{g}$ that $ph(x) = \widetilde{h}(px)$ and $h \equiv \overline{f} \circ \overline{g} \bmod p^m$, so indeed $\overline{f} \circ \overline{g}$ is also an element of $S$.
+We can also characterise $S$ as consisting of images $\overline{f}$ of polynomials $f \in \Z_p[\vx]_0^d$ such that there is a polynomial $\widetilde{f}\in\Z_p[\vx]_0^d$ with $pf(\vx) = \widetilde{f}(p\vx)$.
+If we then take two elements $\overline{f},\overline{g} \in S$, reductions of $f,g$ respectively with $\widetilde{f},\widetilde{g}$ such that $pf(\vx) = \widetilde{f}(p\vx), pg(\vx) = \widetilde{g}(p\vx)$, we see that with $h = f\circ g, \widetilde{h} = \widetilde{f} \circ \widetilde{g}$ that $ph(\vx) = \widetilde{h}(p\vx)$ and $\overline{h} \equiv \overline{f} \circ \overline{g} \bmod p^m$, so indeed $\overline{f} \circ \overline{g}$ is also an element of $S$.
 Hence we see $S$ is indeed a group, and as $\log_p \bmod p^m$ is an element of it, so is $\exp_p \bmod p^m$.
@@
 \begin{proof}[Proof of Theorem~\ref{thm:kappanice}]
-Write $\log_p$ for the logarithm corresponding to the formal group corresponding to the map $\kappa_0: \Z^d \to \Z_p^g$ given by the inclusion $J(\Z)_0$ to $J(\Z_p)_0$ is a group morphism with the group structure on $\Z^d$ being addition and the group structure on $\Z_p^g$, denoted by $\oplus$, given by the bijection with $J(\Z_p)_0$ induced by choosing parameters at $0$, and $\kappa$ is $\kappa_0 \oplus t$.
+Write $\log$ for the logarithm corresponding to the formal group of $J$ and $\log_p$ for $\log(p\vx)/p$ and $\exp_p$ for its inverse.
+Note that the map $\kappa_0: \Z^d \to \Z_p^g$ given by the inclusion $J(\Z_{(p)})_0$ to $J(\Z_p)_0$ is a group morphism with the group structure on $\Z^d$ being addition and the group structure on $\Z_p^g$, denoted by $\oplus$, given by the bijection with $J(\Z_p)_0$ induced by choosing parameters at $0$, and $\kappa$ is $\kappa_0 \oplus t$.
 Then by Lemma~\ref{lem:formallog} the map $\kappa$ factors as in the diagram of groups
@@
 \]
-Then the arrow $\log_p \circ \kappa$ is just a linear map, and $\exp_p$ is a convergent power series that is of degree at most $m$ modulo $p^m$ for $m < p-1$, so their composite $\kappa$ is also a convergent power series of degree at most $m$ modulo $p^m$ for $m < p-1$
+Then the arrow $\log_p \circ \kappa$ is just a linear map, and $\exp_p$ is a convergent power series that is of degree at most $m$ modulo $p^m$ for $m < p-1$, so their composite $\kappa$ is also a convergent power series of degree at most $m$ modulo $p^m$ for $m < p-1$.
 \end{proof}
@@
 \label{cor:closurejac}
-The map $\kappa: \Z^r \to \Z_p^g$ extends uniquely to a continuous map $\kappa: \Z_p^r \to \Z_p^g$, given by the same power series, and the closure $\overline{J(\Z)_t} \subset J(\Z_p)_t$ is given by the image of $\Z_p^r$ under $\kappa$.
+The map $\kappa: \Z^r \to \Z_p^g$ extends uniquely to a continuous map $\kappa: \Z_p^r \to \Z_p^g$, given by the same power series, and the closure $\overline{J(\Z_{(p)})_t} \subset J(\Z_p)_t$ is given by the image of $\Z_p^r$ under $\kappa$.
 \end{cor}
@@
 \label{section:intersection}
-Clearly, as subsets of $J(\Z_p)_t$, we have the inclusion $C(\Z)_P \subset C(\Z_p)_P \cap \overline{J(\Z)_t}$.
-The theory we have built so far enables the following method, which is in sharp contrast with Colemans method; instead of pulling back equations for $\overline{J(\Z)_t}$ to $C(\Z_p)_P$, we pull back equations for $C(\Z_p)_P$ to $\overline{J(\Z)_t}$ to arrive at the following theorem.
+Let $p,C$ and $J$ be as defined in the overview. Clearly, as per the diagram \[
+\begin{tikzcd}
+C(\Z_{(p)})_P \arrow[d] \arrow[r] & J(\Z_{(p)})_t \arrow[d] \\
+C(\Z_p)_P \arrow[r]              & J(\Z_p)_t        
+\end{tikzcd}
+\]
+we have, as subsets of $J(\Z_p)_t$, the inclusion \[C(\Z_{(p)})_P \subset C(\Z_p)_P \cap \overline{J(\Z_{(p)})_t}.\]
+The theory we have built so far enables the following method, which is in sharp contrast with Colemans method; instead of pulling back equations for $\overline{J(\Z_{(p)})_t}$ to $C(\Z_p)_P$, we pull back equations for $C(\Z_p)_P$ to $\overline{J(\Z_{(p)})_t}$ to arrive at the following theorem.
 \begin{thm}
 \label{thm:final}
-Let $C,J,p,P,t$ be as in the overview, let $\kappa$ be as in Theorem~\ref{thm:kappanice} and let $f_1,\cdots,f_{g-1}$ be as in Subsection~\ref{subsection:czptojzp}.
-Define $\lambda_1 = \kappa^*f_1,\dots$, $\lambda_{g-1} = \kappa^*f_{g-1}$ to be the pullbacks along $\kappa$ of the $f_i$.
-Then $\kappa$ induces a surjection from $Z(\lambda_1,\dots,\lambda_{g-1}) \subset \Z_p^r$ to $C(\Z_p)_P \cap \overline{J(\Z)_t}$.
+Let $C,J,p,P\in C(\F_p),t\in J(\F_p)$ be as in the overview, let $\kappa: \Z_p^r \to \Z_p^g$ be as in Theorem~\ref{thm:kappanice} and let $f_1,\cdots,f_{g-1} \in \Z_p\angle{x_1,\dots,x_g}$ be as in Subsection~\ref{subsection:czptojzp}.
+Define \[\lambda_1 = \kappa^*f_1,\dots,\lambda_{g-1} = \kappa^*f_{g-1}\] to be the pullbacks along $\kappa$ of the $f_i$.
+Then $\kappa$ induces a surjection from $Z(\lambda_1,\dots,\lambda_{g-1}) \subset \Z_p^r$ to $C(\Z_p)_P \cap \overline{J(\Z_{(p)})_t}$.
 \end{thm}
 
-Hence if we find an upper bound for the cardinality of $Z(\lambda_1,\dots,\lambda_{g-1})$, this is also an upper bound for $C(\Z)_P$.
+Hence if we find an upper bound for the cardinality of $Z(\lambda_1,\dots,\lambda_{g-1})$, this is also an upper bound for $C(\Z_{(p)})_P$.
 There are several, sometimes ad hoc, ways of proving finiteness.
@@
 We let $I$ denote the ideal inside $\Z_p\angle{x_1,\dots,x_r}$ generated by $\lambda_1,\dots,\lambda_{g-1}$, and $A$ the quotient $\Z_p\angle{x_1,\dots,x_r}/I$.
-Noting that $Z(\lambda_1,\dots,\lambda_{g-1}) = \Hom_{\Z_p}(A,\Z_p)$, we can use the following theorem, the statement and proof of which come from \cite{edixhoven20}.
+Noting that $Z(\lambda_1,\dots,\lambda_{g-1})$ is then exactly $\Hom_{\Z_p}(A,\Z_p)$, we can use the following theorem, the statement and proof of which come from Theorem~4.12 of \cite{edixhoven20}.
 
@@
 The kernel contains $I$, so the map $R/I \to \widehat{R/I}$ is surjective and hence an isomorphism.
-Then note that $\Z_p\angle{x_1,\dots,x_r}$ is itself the $p$-adic completion of $\Z_p[x_1,\dots,x_r]$ and hence is complete, so $A$ is indeed $p$-adically complete.
+Then we observe that $\Z_p\angle{x_1,\dots,x_r}$ is itself the $p$-adic completion of $\Z_p[x_1,\dots,x_r]$ and hence is complete, so $A$ is indeed $p$-adically complete.
 
@@
 
-Remember that a finite dimension algebra over a field is Artinian, and Artin rings are product of Artin local rings (Theorem 8.7 of \cite{atiyah}).
+Remember that a finite-dimensional algebra over a field is Artinian, and Artin rings are products of Artin local rings (Theorem 8.7 of \cite{atiyah}).
 So, we can write the $\F_p$-algebra $\overline{A}$ as a product of Artin local rings.
-As idempotents in $\overline{A}$ lift to $A$, we see this factorisation lifts, and we can write $A$ as
-\[
-\prod_{m \in \MaxSpec(\overline{A})} A_m.
-\]
-Then any morphism $A \to \Z_p$ factors through $A_m$.
+As idempotents in $\overline{A}$ lift to $A$, we see this factorisation lifts, and we can decompose $A$ as
+\[
+A = \prod_{m \in \MaxSpec(\overline{A})} A_m.
+\]
+Then any morphism $A \to \Z_p$ factors through one of the $A_m$.
 If we tensor $A_m$ with $\Q_p$, we see that, after dividing out the nilradical, it is a product of fields.
-Hence $\Hom(A_m,\Z_p)$ is at most $\text{rank}_{\Z_p}(A_m)$, and can be non-empty if and only if $A/m$ is isomorphic to $\F_p$.
+Hence $\Hom(A_m,\Z_p)$ is of cardinality at most $\text{rank}_{\Z_p}(A_m)$, and can be non-empty if and only if $A/m$ is isomorphic to $\F_p$.
 We conclude that the sum of $\dim_{\F_p} \overline{A}_m$ over those $m\in \MaxSpec(\overline{A})$ with $\overline{A}/m = \F_p$ is an upper bound for $\Hom(A,\Z_p)$
@@
 To utilise this theorem, we only need to calculate the $\lambda_i$ modulo $p$.
-In our case, of all $\kappa_i$ and $f_i$ being linear modulo $p$ (as polynomials; they do not necessarily give linear map), so are the $\lambda_i$, and we get as special case the following corollary.
+In our case, as all $\kappa_i$ and $f_i$ being linear modulo $p$ (as polynomials; they do not necessarily give linear maps), so are the $\lambda_i$, and we get as a special case the following corollary.
 \begin{cor}
 \label{cor:finedixlinear}
-If the (not necessarily homogenous) linear system of equations $\forall i: \lambda_i \equiv 0 \bmod p$ has respectively no or one solution, there is respectively none or at most one point in $C(\Z)_P$.
+If the (not necessarily homogeneous) linear system of equations $\forall i: \lambda_i \equiv 0 \bmod p$ has respectively no or one solution, there is respectively none or at most one point in $C(\Z_{(p)})_P$.
 \end{cor}
@@
 \label{prop:linchabauty}
-If for all points $P \in C(\F_p)$, the linear system of $g-1$ equations modulo $p$ defining $C(\Z_p)_P \subset J(\Z_p)_t$ pulled back to $\overline{J(\Z)_t}$ has $n_P \leq 1$ solutions, we get the inequality
-\[
-|C(\Z)| \leq \sum_{P \in C(\F_p)} n_P \leq |C(\F_p)|. 
-\]\todo{Over hebben met Bas}
+If for all points $P \in C(\F_p)$, the linear system of $g-1$ equations modulo $p$ defining $C(\Z_p)_P \subset J(\Z_p)_t$ pulled back to $\overline{J(\Z_{(p)})_t}$ has $n_P \leq 1$ solutions, we get the inequality
+\[
+|C_{\Q}(\Q)| = |C(\Z_{(p)})| \leq \sum_{P \in C(\F_p)} n_P \leq |C(\F_p)|. 
+\]
 \end{prop}
 
-Of note is that this upper bound for $C(\Z)$ does not even depend on the genus, and behaves agreeably when compared to the upper bound in Theorem 5.3 of \cite{poonen12}, which tells us that $|C(\Z)| \leq |C(\F_p)| + 2g-2$ under the much lighter condition of $r < g, p > 2g$ where $p$ is still a prime of good reduction.
-To summarise: in proposition~\ref{prop:linchabauty} we sacrifice certainty for being to able to prove much sharper bounds.
-However, a simple heuristic analysis shows that the conditions are quite likely to be satisfied, as we shall see in the following lemma and proposition.
+Of note is that this upper bound for $|C(\Z_{(p)})|$ does not even depend on the genus, and behaves agreeably when compared to the upper bound in Theorem 5.3 of \cite{poonen12}, which tells us that $|C(\Z_{(p)})| \leq |C(\F_p)| + 2g-2$ under the much lighter condition of $r < g, p > 2g$ where $p$ is still a prime of good reduction.
+To summarise: in Proposition~\ref{prop:linchabauty} we sacrifice certainty for being able to prove much sharper bounds.
+However, the loss of certainty is not too great; a simple heuristic analysis shows that the conditions are quite likely to be satisfied, as we shall see in the following lemma and proposition.
 
@@
 Let $\F_q$ be any finite field, let $A$ be a random $(n+k)\times n$ matrix over $\F_q$, and $b$ randomly chosen from $\F_q^{n+k}$.
-Then the probability that $Ax=0$ has more than one solution is at most $\frac{1}{(p-1)p^k}$ and the probability that $Ax=b$ has more than one solution is at most $\frac{1}{(p-1)p^{2k+1}}$.
+Then the probability that $Ax=0$ has more than one solution is at most $\frac{1}{(q-1)q^k}$ and the probability that $Ax=b$ has more than one solution is at most $\frac{1}{(q-1)q^{2k+1}}$.
 \end{lem}
@@
 if and only if $E_1 \vee \cdots \vee E_n$ holds.
-As clearly for $1\leq i \leq n$ we have $\dim V_{i-1} \leq i-1$, we see that $\P(E_i)$ is at most $p^{i-1-n-k}$.
+As clearly for $1\leq i \leq n$ we have $\dim V_{i-1} \leq i-1$, we see that $\P(E_i)$, the probability of $E_i$ occurring,  is at most $q^{i-1-n-k}$.
 We then see
@@
 \P(E_1 \vee \cdots \vee E_n) &\leq \sum_{i=1}^n \P(E_i)\\
-&\leq \sum_{i=1}^n p^{i-1-n-k}\\
-&\leq \sum_{i=-\infty}^n p^{i-1-n-k}\\
-&= \frac{1}{(p-1)p^k}
+&\leq \sum_{i=1}^n q^{i-1-n-k}\\
+&\leq \sum_{i=-\infty}^n q^{i-1-n-k}\\
+&= \frac{1}{(q-1)q^k}.
 \end{align*}
-This shows that the probability of $Ax = 0$ having more than one solution is indeed at most $\frac{1}{(p-1)p^k}$.
-Furthermore, if $Ax = 0$ has more than one solution, then $\text{rank} A < n$ so there are at most $p^{n-1}$ possible values of $b$ such that $Ax = b$ has multiple solutions, hence the total probability is at most $\frac{1}{(p-1)p^{2k+1}}$.
+This shows that the probability of $Ax = 0$ having more than one solution is indeed at most $\frac{1}{(q-1)q^k}$.
+Furthermore, if $Ax = 0$ has more than one solution, then $\text{rank} A < n$ so there are at most $q^{n-1}$ possible values of $b$ such that $Ax = b$ has multiple solutions, hence the total probability is at most $\frac{1}{(q-1)q^{2k+1}}$.
 \end{proof}
 \begin{rem}
-Using similar methods, one can show that $\P(E_1 \vee \cdots \vee E_n) \geq \frac{1}{p^{k+1}}$, hence this lemma is asymptotically as sharp as possible.
-\end{rem}\todo{Bas, stelling + bewijs verbeterd en remark toegevoegd}
-
-For a general\todo{general mag wel toch?} point $P \in C(\F_p)$, we might assume the linear system modulo $p$ defining $C(\Z_p)_P$ pulled back to $\overline{J(\Z)}$ is completely random, but for point $P \in C(\F_p)$ coming from $\Z$-points, we always know there is at least one solution; and indeed, it turns out that with a translation, one can assume the linear system is homogenous.
+Using similar methods, one can show that $\P(E_1 \vee \cdots \vee E_n)$ is at least $\frac{1}{q^{k+1}}$, hence this lemma is asymptotically as sharp as possible.
+\end{rem}
+
+We now want to use this lemma to say something about the number of solutions to the linear systems of Proposition~\ref{prop:linchabauty}.
+Note that for a point $P \in C(\F_p)$ coming from a $\Z_{(p)}$-point, we always know there is at least one solution to the linear system; and indeed, it turns out that with a translation, one can assume the linear system is homogeneous.
+For all other points of $C(\F_p)$, we might assume the linear system modulo $p$ defining $C(\Z_p)_P$ pulled back to $\overline{J(\Z_{(p)})}$ is completely random.
+This motivates the assumptions of the following heuristic.
 \begin{prop}
 \label{prop:probwork}
-Assume that the map $C(\Z) \to C(\F_p)$ is injective.
-Assume that for points $P \in C(\F_p)$ coming from $C(\Z)$ the linear system modulo $p$ defining $C(\Z_p)_P$ pulled back to $\overline{J(\Z)}$ is a random homogenous linear system, and for all other points, it is a random not necessarily homogenous linear system.
+Assume that the map $C(\Z_{(p)}) \to C(\F_p)$ is injective.
+Assume that for points $P \in C(\F_p)$ coming from $C(\Z_{(p)})$ the linear system modulo $p$ defining $C(\Z_p)_P$ pulled back to $\overline{J(\Z_{(p)})_t}$ is a random homogeneous linear system, and for all other points, it is a random not-necessarily-homogeneous linear system.
 Assume furthermore that all these linear systems are independently random.
-Then for $p > 4g^2,|C(\Z)|$ the conditions of Proposition~\ref{prop:linchabauty} are not satisfied with probability at most
-\[
-(|C(\Z)|+2p^{-g-r-1})(p-1)^{-1}p^{-(g-r-1)}
-\]
-Hence for $r = g-1$ we expect a subset of primes with density $1$ to show finiteness of $C(\Z)$, and for $r < g-1$ we expect all but a finite number to work.
-These expectations are uniform in $g$ and $|C(\Z)|$.
+Then for $p$ bigger than both $4g^2$ and $|C(\Z_{(p)})|$ the conditions of Proposition~\ref{prop:linchabauty} are not satisfied with probability at most
+\[
+(|C(\Z_{(p)})|+2p^{-(g-r-1)})(p-1)^{-1}p^{-(g-r-1)}.
+\]
+Hence for $r = g-1$ we expect a subset of primes with density $1$ to show finiteness of $C_\Q(\Q) = C(\Z_{(p)})$, and for $r < g-1$ we expect all but a finite number to work.
+These expectations are uniform in $g$ and $|C(\Q)|$.
 \end{prop}
 \begin{proof}
-First note that our linear systems consist of $g-1$ equalities in $r$ variable, i.e.
+First note that our linear systems consist of $g-1$ equalities in $r$ variables, i.e.
 we can use Lemma~\ref{lem:probindep} with $k = g-1-r$.
-Let $a$ denote $|C(\Z)|$, and let $b$ denote $|C(\F_p)|-a$.
+Let $a$ denote $|C(\Z_{(p)})|$, and let $b$ denote $|C(\F_p)|-a$.
 Under all our assumptions, the probability of none of the systems having more than one solutions is at least
@@
 \]
-Using the Bernoulli's inequality and the fact that $\left(1- a\frac{1}{(p-1)p^k}\right)$ and $\left(1 - b\frac{1}{(p-1)p^{2k+1}}\right)$ are positive, this is at least 
+Using Bernoulli's inequality and the fact that $1- a\frac{1}{(p-1)p^k}$ and $1 - b\frac{1}{(p-1)p^{2k+1}}$ are positive, this is at least 
 \[
@@
 Using the Hasse-Weil bound, we can make the estimate $b \leq 2p$.
-Then we can lower bound this by $1 - a\frac{1}{(p-1)p^k} - 2\frac{1}{(p-1)p^{2k}} \geq 1 - (a+2p^{-k})\frac{1}{(p-1)p^k}$.
-
-For $r = g-1$ we have $k= 0$, and the probability of one of the conditions not being satisfied is at most $(a+2)/p$, hence we indeed expect an infinite but density $0$ subset of primes to fail.
+Then we can lower bound this by \[1 - a\frac{1}{(p-1)p^k} - 2\frac{1}{(p-1)p^{2k}} \geq 1 - (a+2p^{-k})\frac{1}{(p-1)p^k}.\]
+
+For $r = g-1$ we have $k= 0$, and the probability of one of the conditions not being satisfied is at most $(a+2)/(p-1)$, hence we indeed expect an infinite but density $0$ subset of primes to fail.
 For $r < g-1$, we have $k > 0$; as $\sum_{p\text{ prime}} 1/p^2$ converges, one may expect a finite number of primes to fail.
@@
 \begin{rem}
-Note that if $r=g-1$, as we expect a random $n\times n$-matrix to be invertible, we expect that if the conditions of Proposition~\ref{prop:linchabauty} are satisfied, we generally find an upper bound for $|C(\Z)|$ slightly lower than $|C(\F_p)|$.\todo{Hopelijk nu minder verwarrend, met de herformulering van de Prop} However, a not necessarily homogenous linear system of dimension $(n+k)\times n$ is solvable with probability at most $p^{-k}$, as the dimension of the column space is at most $n$.
-Hence for $r = g-2$ we can expect to find an upper bound of about $|C(\Z)|+1$, and with probability about $(1-\frac{1}{p})^{|C(\F_p)|} \approx (1-\frac{1}{p})^p \approx e^{-1}$ even the optimal upper bound of $|C(\Z)|$.
-For $r = g-3$, we even expect to find an upper bound of $|C(\Z)|$ for a set of primes of density $1$; and for $r < g-3$, for all but a finite set of primes.
+Consider the case $r=g-1$.
+As we expect a random $n\times n$-matrix to be invertible, we expect that if the conditions of Proposition~\ref{prop:linchabauty} are satisfied, we generally find an upper bound for $|C(\Q)|$ slightly lower than $|C(\F_p)|$.
+However, a not-necessarily-homogeneous linear system of dimension $(n+k)\times n$ is solvable with probability at most $p^{-k}$, as the dimension of the column space is at most $n$.
+Hence for $r = g-2$ we can expect to find an upper bound for $|C(\Q)|$ of approximately $|C(\Q)|+1$, and with probability approximately $(1-\frac{1}{p})^{|C(\F_p)|} \approx (1-\frac{1}{p})^p \approx e^{-1}$ even the optimal upper bound of $|C(\Q)|$.
+For $r = g-3$, we even expect to find an upper bound of $|C(\Q)|$ for a set of primes of density $1$; and for $r < g-3$, for all but a finite set of primes.
 \end{rem}
@@
 Now we briefly discuss what can be done if for a specific prime $p$, the conditions of Proposition~\ref{prop:linchabauty} are not satisfied.
-In general, even if $\overline{A}$ is not finite, we see $\Hom(A,\Z_p)$ factors through $\Z_p\angle{x_1,\dots,x_r}/(I:p)$ where $(I:p)$ is the saturation \[\{x \in \Z_p\angle{x_1,\dots,x_r} \mid \exists k \in \Z_{\geq 0}: p^kx \in I\}\] Then a higher precision calculation of the $\lambda_i$ can still lead to a succesful application of Proposition~\ref{prop:finedix}.
+In general, even if $\overline{A}$ is not finite, we see $\Hom(A,\Z_p)$ factors through $\Z_p\angle{x_1,\dots,x_r}/(I:p)$ where $(I:p)$ is the saturation \[\{x \in \Z_p\angle{x_1,\dots,x_r} \mid \exists k \in \Z_{\geq 0}: p^kx \in I\}.\]
+Then a higher precision calculation of the $\lambda_i$ can still lead to a succesful application of Proposition~\ref{prop:finedix}.
 
 Another specific case is that of $r = 1$.
-In that case, we can use finite precision approximations of $\lambda_1$ to deduce information about its Newton polygon, and use that to bound the number of zeroes in $\Z_p$.
-We can even adapt this method if $r$ is bigger than $1$; sometimes it might be possible to use the implicit function theorem for powerseries, Lemma~\ref{lem:implicitfunction}, to write one of the variables as a power series in the other variables, and then substitute it in the other equations.
+In that case, we can use finite-precision approximations of $\lambda_1$ to deduce information about its Newton polygon and use that to bound the number of zeroes in $\Z_p$.
+We can even adapt this method if $r$ is bigger than $1$; sometimes it might be possible to use the implicit function theorem for power series, Lemma~\ref{lem:implicitfunction}, to write one of the variables as a power series in the other variables, and then substitute it in the other equations.
 
 \begin{exmp}
-If $r = g-1 = 2$ and $\lambda_1 \equiv px-py,\lambda_2 \equiv x+y+pxy \bmod p^2$, neither Proposition~\ref{prop:finedix} nor Newton polygons are instantly applicable.
-However, substituting $y = -x +px^2 \bmod p^2$ into the first equation gives $2p(x-x^2) = 0 \bmod p^2$, or $x-x^2 = 0\bmod p$.
-Now both Proposition~\ref{prop:finedix} and Newton polygons give an upper bound of $2$ for $C(\Z)_P$.
+If $r = g-1 = 2$ and \[\lambda_1 \equiv px-py,\lambda_2 \equiv x+y+pxy \bmod p^2,\] neither Proposition~\ref{prop:finedix} nor Newton polygons are instantly applicable.
+However, substituting $y = -x +px^2 \bmod p^2$ into the first equation gives the equation $2p(x-x^2) = 0 \bmod p^2$, or $x-x^2 = 0\bmod p$.
+Now both Proposition~\ref{prop:finedix} and Newton polygons give an upper bound of $2$ for $C(\Z_{(p)})_P$.
 \end{exmp}
@@
 \section{Complications and improvements}
-\label{section:remarks} \todo{Bas, er staat bij al het werk van anderen een referentie}
-In this section, we quickly make some further remarks on how or when to apply the theory we have built up in previous section to real cases.
+\label{section:remarks}
+In this section, we quickly make some further remarks on how or when to apply the theory we have built up in previous sections to real cases.
 \begin{itemize} 
-\item Even if $r \geq g$, it might still be possible that $\overline{J(\Z)}$ coincidentally has dimension $r'$ smaller than $r$ (for example, if $r > g$); then one can find a rank $r'$ subgroup of $J(\Z)$ with the same closure inside $J(\Z_p)$, and do computations in this subgroup; we can expect this to work if $r' < g$.
+\item Even if $r \geq g$, it might still be possible that $\overline{J(\Z_{(p)})}$ coincidentally has dimension $r'$ smaller than $r$ (for example, if $r > g$); then one can find a rank $r'$ subgroup of $J(\Z_{(p)})$ with the same closure inside $J(\Z_p)$, and do computations in this subgroup; we can expect this to work if $r' < g$.
 We can even use this to improve our calculations if we already have $r < g$, but $r'$ is even smaller.
-On the other hand, if $J(\Z)$ is dense in $J(\Z_p)$, there is no way to apply Chabauty's method to the curve.
-\item Note that in all of the discussion of the previous section, we are calculating upper bounds for the cardinality of $C(\Z_p)_P \cap \overline{J(\Z)_t}$.
-It can and does however happen that this set is strictly bigger than $C(\Z)_P$, as shown in \cite{Balakrishnan19}, where Coleman-Chabauty is used on a database of 16997 curves of genus $3$ with Mordell-Weil rank of the Jacobian equal to $1$.
+On the other hand, if $J(\Z_{(p)})$ is dense in $J(\Z_p)$, there is no way to apply Chabauty's method to the curve.
+\item Note that in all of the discussion of the previous section, we are calculating upper bounds for the cardinality of $C(\Z_p)_P \cap \overline{J(\Z_{(p)})_t}$.
+It can and does however happen that this set is strictly bigger than $C(\Z_{(p)})_P$, as shown in \cite{Balakrishnan19}, where Coleman-Chabauty is used on a database of 16997 curves of genus $3$ with Mordell-Weil rank of the Jacobian equal to $1$.
 They treat several possible cases and examples where the set is bigger.
-One of the main families they have found can be given in the following way: let $Q$ be a $K$-point $Q$ where $K$ is a quadratic number field where $p$ splits.
-Embedding $K$ into $\Q_p$, assume $Q-b$ lies in $J(\Z_p)_0$ and is torsion of order prime to $p$ in $J(\Z_p)_0/J(\Z)_0$.
-Then, as $J(\Z_p)$ is isomorphic as continous group to $\Z_p^g$, the point $Q-b$ lies in $\overline{J(\Z)_0}$, and clearly also in $C(\Z_p)$.\todo{Bas, even over hebben}
-\item An important part of doing these calculations, is working with the Mordell-Weil group $J(\Z)$.
-Finding generators of $J(\Z)$ is as of yet a computationally difficult problem, and one may need to assume the BSD conjecture to even find the rank $r$.
-However, note that one does not need to find all of $J(\Z)$; if we can generate a subgroup of $J(\Z)$ of index finite and coprime to $p|J(\F_p)|$, it will have the same closure in $J(\Z_p)$.
-For this, we only need to generate sufficiently many independent points of the Jacobian, and saturate subgroups with respect to some primes.
-Both of these tasks are easier than finding all of $J(\Z)$.
-\item Even this method does not work for a certain prime $p$, and neither for some other primes we tried, we can still use parts of the information we have learned.
-For example, maybe the method tells us that we have found all points of $J(\Z)$ stemming from $C(\Z)$ except those in a certain fibre of the map $J(\Z) \to J(\F_p)$.
-We can then aggregate this information for different primes, by looking at the maps $J(\Z) \to \prod_{p \in S} J(\F_p)$ for some set $S$ of primes of good reduction.
-See for example \cite{stoll10} for an introduction to the Mordell-Weil sieve.
+One of the main families they have found can be given in the following way: let $Q$ be a $K$-point where $K$ is a quadratic number field where $p$ splits.
+Embedding $K$ into $\Q_p$, assume $Q-b$ lies in $J(\Z_p)_0$ and is torsion of order coprime to $p$ in $J(\Z_p)_0/J(\Z_{(p)})_0$.
+Then, as $J(\Z_p)$ is isomorphic as continuous group to $\Z_p^g$, the point $Q-b$ lies in $\overline{J(\Z_{(p)})_0}$, and clearly also in $C(\Z_p)$.
+\item An important part of doing these calculations is working with the Mordell-Weil group $J(\Z_{(p)}) \cong J(\Q)$.
+Finding generators of $J(\Q)$ is as of yet a computationally difficult problem, and one may need to assume the Birch-Swinnerton-Dyer conjecture to even find the rank $r$.
+However, note that one does not need to find all of $J(\Q)$; if we can generate a subgroup of $J(\Q)$ of index finite and coprime to $p|J(\F_p)|$, it will have the same closure in $J(\Z_p)$.
+For this, we only need to generate sufficiently many independent points of the Jacobian and saturate subgroups with respect to some primes.
+Both of these tasks are easier than finding all of $J(\Q)$.
+\item Even if this method does not work for a certain prime $p$, and neither for some other primes we tried, we can still use parts of the information we have gathered.
+For example, maybe the method tells us that we have found all points of $J(\Z_{(p)})$ stemming from $C(\Z_{(p)})$ except those in a certain fibre of the map $J(\Z_{(p)}) \to J(\F_p)$.
+We can then aggregate this information for different primes, choosing a smooth model of $C$ over for example $\Z[1/n]$ and lifting $J$ as well, by looking at the maps $J(\Z[1/n]) \to \prod_{p \in S} J(\F_p)$ for some set $S$ of primes of good reduction for $C_{\Q}$ not dividing $n$.
+This method is called the Mordell-Weil sieve, see for example \cite{stoll10} for an introduction.
 \end{itemize}
@@
 \label{section:explicit}
-We now assume that $C$ is hyperelliptic, i.e. given by the degree $2g+2$ homogenisation of an equation of the form
+We now assume that our curve $C$ is hyperelliptic, i.e. given by the degree $2g+2$ homogenisation of an equation of the form
 \[
@@
 \]
-inside $\P(1,g+1,1)$ where $f$ is a monic polynomial of degree $2g+1$ or $2g+2$.
+inside the weighted projective space $\P(1,g+1,1)$ where $f$ is a monic polynomial of degree $2g+1$ or $2g+2$.
 An alternative way of defining such a curve, and the one we will be using mainly, is as a glueing of two affine charts: $y^2 = f(x)$, and $w^2 = f^{r}(v)$, where $f^{r}(v)$ is the polynomial $v^{2g + 2} f(1/v)$, and a birational map between them is given by $(x,y) \mapsto (\frac{1}{x},\frac{y}{x^{g+1}})$.
-We also have the coordinates $X,Y,Z$ of $\P(1,g+1,1)$, with $x = X/Z, y = Y/Z^{g+1}, v = Z/X, w = Y/X^{g+1}$, but beware; these coordinates do not behave nicely on the origin of the patch $D(Y)$.
+We also have the coordinates $X,Y,Z$ of $\P(1,g+1,1)$, with \[x = X/Z, y = Y/Z^{g+1}, v = Z/X, w = Y/X^{g+1},\] but beware; these coordinates do not behave nicely on the origin of the patch given by $Y \neq 0$.
 We mainly use the first chart; we call any point that lies on it an affine point of $C$.
@@
 
-\subsection{Makdisis algorithms}
+\subsection{Makdisi's algorithms}
 We work in the Jacobian using Makdisi's representations for divisors.
 As we are using and adding on to an implementation by Mascot \cite{mascot18}, we briefly introduce his notation.
-This is a summary of section 2.1 in \cite{mascot18}.
+This is a summary of Section~2.1 in \cite{mascot18}.
 
@@
 \]
-We pick $D_0$ an effective divisor of degree $d_0 \geq 2g+1$; in the case of hyperelliptic curves, this will be $(g+1)(\infty_+ + \infty_-)$.
+We pick an effective divisor $D_0$ of degree $d_0 \geq 2g+1$; in the case of hyperelliptic curves, we will choose $(g+1)(\infty_+ + \infty_-)$.
 We set $V_n = \Lcal(nD_0)$.
@@
 we can represent rational functions in $V_5$ by their values in $k^Z$.
-In this representation, we can add, subtract, or, if the degree at infinity is not too large, even multiply rational functions, by respectively adding, subtracting or multiplying the corresponding vectors in $k^Z$.
+In this representation, we can add, subtract, or, if the degree at infinity is not too large, even multiply rational functions, by respectively adding, subtracting, or multiplying the corresponding vectors in $k^Z$.
 It is now also possible to represent subspaces of $V_5$ by giving a basis in $k^Z$.
-(Instead of passing to an extension of $k$, one could also evaluate functions on infinitesemal neighborhoods of $k$-points, i.e.
+(Instead of passing to an extension of $k$, one could also evaluate functions on infinitesimal neighborhoods of $k$-points, i.e.
 compute Taylor expansions near those points.)
@@
 As explained in Mascot's article, using this representation one can do all relevant computations in $J(k)$; adding, subtracting, finding the zero element, and most importantly: checking equality.
-Important from a computational standpoint is the complexity; as everything is simply linear algebra in spaces of dimensions $O(g)$, the complexity of all these operations, assuming calculations in the ground ring are $O(1)$, are all simply $O(g^\omega)$ where $\omega$ is the matrix constant.
+Important from a computational standpoint is the complexity, which we write down in big O notation.
+As everything is simply linear algebra in spaces of dimensions $O(g)$, the complexity of all these operations, assuming calculations in the ground ring are $O(1)$, are all simply $O(g^\omega)$ where $\omega$ is the matrix constant.
 
@@
 However, for Chabauty we want to compute inside $J(\Z/p^e\Z)$.
-Luckily, Mascots code takes care of this too, by passing from vector spaces over $\F_p$ to free $R$-submodules of $R^n$ with $R = \Z/p^e\Z$; in fact, all submodules of $R^n$ we will be seeing are free.
+Luckily, Mascot's code takes care of this too, by passing from vector spaces over $\F_p$ to free $R$-submodules of $R^n$ with $R = \Z/p^e\Z$; in fact, all submodules of $R^n$ we will be seeing are free.
 That means all these submodules will have good reduction, i.e.
 they will remain free and of the same rank after tensoring with $\F_p$.
-If the maps between such modules also have good reduction, then all kernels, images, et cetera will also have these properties, and can first be calculated modulo $p$ using linear algebra and then by Hensel lifting modulo higher powers of $p$.
+If the maps between such modules also have good reduction, then all kernels, images, et cetera will also have these properties, and can first be calculated modulo $p$ using linear algebra, and then Hensel lifted modulo higher powers of $p$.
 
@@
 As said before, we need $n_Z$ affine points that are distinct modulo $p$, so we passed from $\F_p$ to an extension of $\F_q$.
-The corresponding notion of an extension of $\Z/p^e\Z$ is given by taking an irreducible polynomial $\overline{T} \in \F_p[t]$ with $\F_q \cong \F_p[t]/\overline{T}$, arbitrarily lifting $\overline{T}$ to a polynomial $T \in \Z/p^e\Z$, and looking at $R = \Z/p^e\Z[t]/T$.
+The corresponding notion of an extension of $\Z/p^e\Z$ is given by taking an irreducible polynomial $\overline{T} \in \F_p[t]$ with $\F_q \cong \F_p[t]/\overline{T}$, arbitrarily lifting $\overline{T}$ to a polynomial $T \in \Z/p^e\Z[t]$, and looking at $R = (\Z/p^e\Z[t])/T$.
 Again, we will only be looking at free submodules of $R^n$, so we can again do normal linear algebra over $R \tensor \F_p = \F_q$, and using Hensel to lift.
@@
 Now that we can do computations with elements in the Jacobian over $\Z/p^2\Z$, it only remains to construct elements in the Jacobian.
-Explicitly, we want to go from a degree zero divisor to an element in Mascots representation.
-Most of the times these divisors are sums of points over the ring we are working with, but sometimes they are given as a Mumford representation.
+Explicitly, we want to go from a degree zero divisor to an element in Mascot's representation.
+Most of the time these divisors are sums of points over the ring we are working with, but sometimes they are given as a so-called Mumford representation.
 \begin{defn}
@@
 \item the polynomial $a$ is monic of degree at most $g+1$;
-\item the polynomial $a$ divides $f - h^2$.
+\item the polynomial $a$ divides $b^2 - f$.
 \end{enumerate}
@@
 \[
-D(a,b) + D\left(\frac{f-b^2}{a},b\right) = (y-h)
-\]
-meaning that with additional calculations of the behaviour of $(y-h)$ at infinity we can express $[D(a,b)]$ in the Jacobian in terms of $D(\frac{f-b^2}{a},b)$, and if $\deg a$ is strictly bigger than $g+1$, the degree of $\frac{f-b^2}{a}$ is at most $\deg a -2$.
+D(a,b) + D\left(\frac{f-b^2}{a},b\right) = (y-b)
+\]
+meaning that with additional calculations of the behaviour of $(y-b)$ at infinity we can express $[D(a,b)]$ in the Jacobian in terms of $D(\frac{f-b^2}{a},b)$, and if $\deg a$ is strictly bigger than $g+1$, the degree of $\frac{f-b^2}{a}$ is at most $\deg a -2$.
 \end{rem}
 
-We will treat both how to explicitly compute the Abel-Jacobi embedding and divisors in Mumford represenation in Makdisi's representation for the Jacobian. We start with the Abel-Jacobi embedding 
+We will treat how to explicitly compute both the Abel-Jacobi embedding and divisors in Mumford representation in Makdisi's representation for the Jacobian. We start with the Abel-Jacobi embedding 
 \begin{align*}
@@
 \end{prop}
-Before this proof, we start with a quick lemma.
+Before proving this proposition, we start with a quick lemma.
 \begin{lem}
@@
 First note that by Riemann-Roch, the dimension of $\Lcal(D_0)$ is $g + 3$, and we also have by the proof of the previous lemma that $1,x,\dots,x^{g+1},y$ all lie in $\Lcal(D_0)$ and hence form a basis, so we can indeed find $B$ as in line~\ref{alg:abeljacobi:basisLD0}.
-Note that by Lemma~\ref{lem:poles2d0i+} the element $b_{g+4}$ lies in $\Lcal(D_0 + \infty_+)$ but not in $\Lcal(D_0)$, so as adding a point to a divisor causes the the dimension to increase by at most $1$, we have by that $b_1,\dots,b_{g+4}$ is a basis for $\Lcal(D_0 + \infty_+)$; that it is in fact a basis is evident as this argument tells us it is a basis when tensored with $\F_p$.
+Note that by Lemma~\ref{lem:poles2d0i+} the element $b_{g+4}$ lies in $\Lcal(D_0 + \infty_+)$ but not in $\Lcal(D_0)$, so as adding a point to a divisor causes the the dimension to increase by at most $1$, we have that $b_1,\dots,b_{g+4}$ is a basis for $\Lcal(D_0 + \infty_+)$; that it is in fact a basis is evident as this argument tells us it is a basis when tensored with $\F_p$.
 
@@
 Furthermore we have the equality of divisors $P-\infty_+ = E - D_0$ where $E = P + D_0 - \infty_+ \geq 0$, so $\Lcal(D_0 + \infty_+ - P)$ is as a subspace of $V_2$ equal to $\Lcal(2D_0 - E)$.
-This last term is in fact in Mascots representation, so this represents $P-\infty_+$ in the Jacobian.
+This last term is in fact in Mascot's representation, so this represents $P-\infty_+$ in the Jacobian.
 \end{proof}
@@
 We first calculate $\Lcal(2D_0 - D_{\text{aff}})$. Over $\F_p$ we have the equality
-\[
-\Lcal(2D_0 - D_{\text{aff}}) = a(x)\Lcal((2g+2-d)(\infty_- + \infty_+)) + (y-b(x))\Lcal((g+1)(\infty_- + \infty_+)).
-\]
-Note all these Riemann-Roch spaces are of the form $H^0(C_{\F_p},\Fcal_{\F_p})$ where $\Fcal$ is an invertible $O_{C_{\Z_p}}$-module on $C_{\Z_p}$ of degree higher than $2g-2$.
-Hence by Serre duality, $h^{1}(C_y,\Fcal_y)$ is $0$ for all $y \in \Spec \Z_p$.
-Then as the Euler characteristic is constant, also $h^{0}(C_y,\Fcal_y)$ is constant.
-By III.12.9 of \cite{hartshorne}, we see the basechange morphism $H^0(C_{\Z_p},\Fcal_{\Z_p}) \tensor \F_p \to H^0(C_{\F_p},\Fcal_{\F_p})$ is an isomorphism and $H^0(C_{\Z_p},\Fcal_{\Z_p})$ is a free $\Z_p$-module.
-That means this equality also holds over $\Z_p$, and hence over $\Z/p^k\Z$.
-then it should follow over $\Z_p$ so over $\Z/p^k\Z$.
-\todo{Over hebben met Bas}
+\begin{multline*}
+\Lcal(2D_0 - D_{\text{aff}}) \\= a(x)\Lcal((2g+2-d)(\infty_- + \infty_+)) + (y-b(x))\Lcal((g+1)(\infty_- + \infty_+)).
+\end{multline*}
+Note all these Riemann-Roch spaces are of the form $H^0(C_{\F_p},\Fcal_{\F_p})$ where $\Fcal$ is an invertible $\O_{C_{\Z/p^k\Z}}$-module on $C_{\Z/p^k\Z}$ of degree higher than $2g-2$.
+Hence by Serre duality, $h^{1}(C_{\F_p},\Fcal_{\F_p}) = 0$.
+That means the base change map
+\[H^1(C_{\Z/p^k\Z},\Fcal) \tensor \F_p \to H^1(C_{\F_p},\Fcal_{\F_p}) = 0\]
+is surjective, and by Theorem~III.12.11 of \cite{hartshorne} an isomorphism.
+Because $H^1(C_{\Z/p^k\Z},\Fcal)$ is a $\Z/p^k\Z$-module, this means it is $0$.
+Hence we can use Theorem~III.12.11b of \cite{hartshorne} to conclude that the base change map
+\[H^0(C_{\Z/p^k\Z},\Fcal) \tensor \F_p \to H^0(C_{\F_p},\Fcal_{\F_p})\]
+is also an isomorphism, and $H^0(C_{\Z/p^k\Z},\Fcal)$ is a free $\Z/p^k\Z$-module. That means the equality 
+\begin{multline*}
+\Lcal(2D_0 - D_{\text{aff}}) \\= a(x)\Lcal((2g+2-d)(\infty_- + \infty_+)) + (y-b(x))\Lcal((g+1)(\infty_- + \infty_+)).
+\end{multline*}
+also holds over $\Z/p^k\Z$.
+Note that both the Riemann-Roch spaces on the right hand side can be easily calculated, as they are generated by the monomials in $x,y$ of the right order at $\infty_{\pm}$.
 
 For $\Lcal((g+1)\infty_- + (g+1+d)\infty_+)$, we first inductively calculate the spaces $W_n := \Lcal(2D_0 - n\infty_-)$.
-For $W_1$ we have a basis $1,x,\dots,x^{2g+1},y,xy,\dots$, $x^g y, x^{g+1}y+x^{2g+2}$, and for $n \geq 0$ we have by a simple use of Lemma 2.2 of \cite{makdisi04} that for $1 \leq n \leq g+1$ we have \[W_{n} = \{s \in \Lcal(2D_0) \mid s\Lcal(2D_0) \in W_1 \cdot W_{n-1}\}\].
-This is a purely linear constraint, hence simple linear algebra allows us to calculate all $W_n$ for $n \leq g+1$.
-Finally, we have
+For $W_1$ we have a basis \[1,x,\dots,x^{2g+1},y,xy,\dots,x^g y, x^{g+1}y+x^{2g+2}\], and for $n \geq 0$ we have by a simple use of Lemma 2.2 of \cite{makdisi04} that for $1 \leq n \leq g+1$ we have \[W_{n} = \{s \in \Lcal(2D_0) \mid s\Lcal(2D_0) \in W_1 \cdot W_{n-1}\}.\]
+This is a purely linear constraint, hence simple linear algebra allows us to calculate all $W_n$ for $n \leq g+1$. Finally, we have
 \[
@@
 \] 
-Once again noting that we can write down an explicit basis for the space $\Lcal((g+1+d)(\infty_+ + \infty_-))$, this allows us to calculate $\Lcal((g+1)\infty_- + (g+1+d)\infty_+)$ and to finish the computation.
+Once again noting that we can write down an explicit basis for the space $\Lcal((g+1+d)(\infty_+ + \infty_-))$, we can now calculate $\Lcal((g+1)\infty_- + (g+1+d)\infty_+)$ and finish the computation.
 \end{proof}
@@
 Being able to calculate in the Jacobian, we can move on to the final ingredient for explicit computations: parameters at points of $J$.
-For any nice curve $C$ over $\Z$, smooth over $\Z_{(p)}$, with a $\Z$-point $b$, we have a birational map from $C^{(g)}$, the $g$-fold symmetric product of $C$, to $J$, given on points by sending $[(P_1,\dots,P_g)]$ to $[\sum P_i - gb]$.
-This map is \'etale at $[(P_1,\dots,P_g)]$ if $H^0(P_1 + \cdots + P_g)$ has dimension $1$ as the fibre of $P_1 + \cdots + P_g -gb$ is exactly $\P H^0(P_1 + \cdots + P_g)$.
+For any proper, smooth curve $C$ over $\Z_{(p)}$, with a $\Z_{(p)}$-point $b$, we have a birational map from $C^{(g)}$, the $g$-fold symmetric product of $C$, to $J$, given on points by sending $[(P_1,\dots,P_g)]$ to $[\sum P_i - gb]$.
+This map is \'etale at $[(P_1,\dots,P_g)]$ if $\Lcal(P_1 + \cdots + P_g)$ has dimension $1$ as the fibre of $P_1 + \cdots + P_g -gb$ is exactly $\P \Lcal(P_1 + \cdots + P_g)$.
 Also, if all $P_i$ are distinct, then the map $C^g \to C^{(g)}$ is \'etale at $P_1,\dots,P_g$ as well.
@@
 Of course, it is trivial to compute parameters in $\P V_2$, but the downside is that the rational map may not need to be defined where we want it to be.
-In that case, one can just take another choice of effective divisors and construct a different rational map; remember that we only need the map to be defined in our residue disc of choice.
+In that case, one can just make another choice of effective divisors and construct a different rational map; remember that we only need the map to be defined in our residue disc of choice.
 \end{rem}
@@
 
-Note that evaluating $\lambda_i$ at a point in $J(\Z)_t$ comes down to calculating the value of a parameter at that point, and this is something we can do.
+Note that evaluating $\lambda_i$ at a point in $J(\Z_{(p)})_t$ comes down to calculating the value of a parameter at that point, and this is something we can do.
 That means we can explicitly compute $\lambda_i$ modulo $p^m$ for $m < p-1$.
-Using Proposition~\ref{prop:finedix} or another way, we can hope to find an upper bound on the number of common zeroes of the $\lambda_i$, and hence an upper bound on $C(\Z)_P$.
+Using Proposition~\ref{prop:finedix} or another way, we can hope to find an upper bound on the number of common zeroes of the $\lambda_i$, and hence an upper bound on $C(\Z_{(p)})_P$.
 
@@
 \subsection{Complexity}
-We assume necessary data for the Mordell-Weil group of the Jacobian is given; that is, we have a set of generators for either $J(\Z)$, or just a full rank subgroup of index coprime to $pJ(\F_p)$.
-We also assume that all relevant elements in $J(\Z)$ and $J(\F_p)$ are in the subgroup generated by $C(\Z)$ and $C(\F_p)$.
+We assume necessary data for the Mordell-Weil group of the Jacobian is given; that is, we have a set of generators for either $J(\Z_{(p)})$, or just a full rank subgroup of index coprime to $pJ(\F_p)$.
+We also assume that all relevant elements in $J(\Z_{(p)})$ and $J(\F_p)$ are in the subgroup generated by $C(\Z_{(p)})$ and $C(\F_p)$.
 Finally, we assume that we can find rational maps $J \to \P V_2$ as in Remark~\ref{rem:faster}.
 
-Then by Remark~\ref{rem:complexityabel} and Section~\ref{subs:interpolate}, we compute $\lambda_i \bmod p$ in $O(rg^{\omega+1})$; then solving the linear system of equations $\forall i \lambda_i \equiv 0 \bmod p$ has complexity lower than that, and hence checking if $|C(\Z)_P|$ is at most $1$ can be done in $O(rg^{\omega+1})$.
+Then by Remark~\ref{rem:complexityabel} and Section~\ref{subs:interpolate}, we compute $\lambda_i \bmod p$ in $O(rg^{\omega+1})$; then solving the linear system of equations $\forall i \lambda_i \equiv 0 \bmod p$ has complexity lower than that, and hence checking if $|C(\Z_{(p)})_P|$ is at most $1$ can be done in $O(rg^{\omega+1})$.
 Repeating this for all $\F_p$-points, gives by the Hasse-Weil bound a complexity of $O\left((p + g\sqrt{p})rg^{\omega+1}\right)$.
@@
 \label{section:example}
-We treat the hyperelliptic curve $C$ with first affine chart given by
+We treat the hyperelliptic curve $C_\Q/\Q$ with first affine chart given by
 \[
@@
 It has six known rational points $\infty_+,\infty_- = \sigma(\infty_+)$ and $\theta = (0,1),\sigma(\theta),\eta=(-3,1),\sigma(\eta)$.
-We take $p = 5$.
+We take $p = 5$, and use the same equation for the model $C$ over $\Z_{(5)}$.
 It turns out that $C(\F_5)$ has seven points; the reductions of the rational points, and $(1,0)$.
-Again taking the map $C \to J$ to be subtraction of $\infty_+$ on points, all seven points in $C(\F_5)$ lie in the image of $J(\Z)$.
+Again taking the map $C \to J$ to be subtraction of $\infty_+$ on points, all seven points in $C(\F_5)$ lie in the image of $J(\Z_{(p)})$.
 
@@
 Letting $\theta_{\mu}$ for $\mu \in \F_p$ denote the deformations of $\theta$ in $C(\Z/p^2\Z)_{\theta}$, with $\theta_\mu \mapsto \mu$ being a parameter at $\theta$, we see the image of $C(\Z/p^2\Z)_\theta$ in $J(\Z/p^2\Z)_0$ is $\{\theta_\mu - \theta \mid \mu \in \F_p\}$.
-Also, identifying $J(\Z)_0$ with $\Z^r$, the image of $J(\Z)_0$ in $J(\Z/p^2\Z)_0$ can be given as a map $\F_p^r \to J(\Z/p^2\Z)_0$.
+Also, identifying $J(\Z_{(p)})_0$ with $\Z^r$, the image of $J(\Z_{(p)})_0$ in $J(\Z/p^2\Z)_0$ can be given as a map $\F_p^r \to J(\Z/p^2\Z)_0$.
 Choosing parameters by giving a local chart $J \to \P(V_2)$, we want to exactly show that the two maps $C(\Z/p^2\Z)_\theta \to J(\Z/p^2\Z)_0, \F_p^r \to J(\Z/p^2\Z)_0$ together form a map $\F_p \oplus \F_p^r \to J(\Z/p^2\Z)_0$ with kernel $0$.
-Now that this is a statement in linear algebra, it can be verified easily, and it turns out that indeed the residue disc of $C(\Z)$ containing $\theta$ contains only $\theta$.
+Now that this is a statement in linear algebra, it can be verified easily, and it turns out that indeed the residue disc of $C(\Z_{(p)})$ containing $\theta$ contains only $\theta$.
 
 Similarly, it follows that all points in $C(\F_5)$ lift to at most one $\Z$-point.
-Noting that the group generated by $\sigma$ acts on $C(\Z)$ and has no fixed points, this means $|C(\Z)| \leq 6$ so our list of rational points is complete.
+Noting that the group generated by $\sigma$ acts on $C(\Z_{(p)})$ and has no fixed points, this means $|C(\Z_{(p)})| \leq 6$ so our list of rational points is complete.
 
@@
 \label{section:quadratic}
-In this section we attempt to give an introduction to the article~\cite{edixhoven20} aimed to introduce all the players in quadratic Chabauty at a slightly slower pace.
-We will omit any proofs.
-For further reading, see for example \cite{hashimoto20}, an in progress cartoon guide to the article by Edixhoven-Lido.
+In this section, we attempt to give an introduction to the article~\cite{edixhoven20} aimed to introduce all the players in quadratic Chabauty at a slightly slower pace.
+We will omit all proofs.
+For further reading, see for example \cite{hashimoto20}, an in-progress cartoon guide to the article by Edixhoven and Lido.
 
 % Explain all diagrams over Q
-We start with explaining the idea over $\Q$; we let $C_\Q$ be a projective, smooth curve over $\Q$ of genus at least $2$, we let $J_\Q$ be its Jacobian.
-We again assume the existence of a rational point $b \in C_\Q(\Q)$, and use it to construct an embedding $j_b : C_\Q \to J_\Q$.
-We wish to set up a similar situation to classic Chabauty, and for that we introduce the Poincar\'e line bundle and Poincar\'e torsor.
-For this we need $J_\Q^\wedge$, the dual of $J_\Q$, which in fact is isomorphic to $J_\Q$, taking as isomorphism for example the principal polarisation $\lambda: J_\Q \to J_\Q^\wedge$.
-This dual parametrises line bundles that are algebraically equivalent to $0$ on $J_\Q$, and hence we get a universal such line bundle $P_\Q$ on $J_\Q \times J_\Q^\wedge$, called the Poincar\'e line bundle $P_\Q$, which also satisfies that both $P_{\Q,0\times J_\Q^\wedge}$ and $P_{\Q,J_\Q \times 0}$ are trivial.
+We start by explaining the idea over $\Q$; we let $C_\Q$ be a projective, smooth curve over $\Q$ of genus at least $2$, we let $J_\Q$ be its Jacobian.
+We again assume the existence of a rational point $b \in C_\Q(\Q)$ and use it to construct an embedding $j_b : C_\Q \to J_\Q$.
+We wish to set up a similar situation to classic Chabauty, and for that, we introduce the Poincar\'e line bundle and Poincar\'e torsor.
+For this, we need $J_\Q^\wedge$, the dual of $J_\Q$, which is in fact isomorphic to $J_\Q$, taking as isomorphism for example the principal polarisation $\lambda: J_\Q \to J_\Q^\wedge$.
+This dual parametrises line bundles that are algebraically equivalent to $0$ on $J_\Q$, and hence we get a universal such line bundle $P_\Q$ on $J_\Q \times J_\Q^\wedge$, called the Poincar\'e line bundle $P_\Q$, which also satisfies that both $P_{\Q}|_{0\times J_\Q^\wedge}$ and $P_{\Q}|_{J_\Q \times 0}$ are trivial.
 
 \begin{exmp}
-If $C_\Q$ is an elliptic curve then, identifying $C_\Q,J_\Q$ and $J_\Q^{\wedge}$, we get $P_\Q = O(\Delta-\{0\} \times C_\Q - C_\Q \times \{0\})$, indeed with the fibres $P|_{\Q,c \times E_\Q} \cong O(c-0)$ being exactly the degree $0$ line bundles on $C_\Q$ up to isomorphism.
+If $C_\Q$ is an elliptic curve then, identifying $C_\Q,J_\Q$ and $J_\Q^{\wedge}$, we get $P_\Q = \O(\Delta-\{0\} \times C_\Q - C_\Q \times \{0\})$, with the fibres $P_\Q|_{,c \times C_\Q} \cong \O(c-0)$ being exactly the degree $0$ line bundles on $C_\Q$ up to isomorphism.
 \end{exmp}
@@
 The object we will be working with is the Poincar\'e torsor, the $\G_m$ torsor over $J_\Q \times J_\Q^\wedge$ defined by \[
-P_\Q^\times = \text{Isom}_{J_\Q \times J^\wedge_\Q}(O_{J_\Q \times J^\wedge_\Q},P_\Q);
-\] 
-we can also describe this in terms of its functor of points; for any scheme $S$ over $J_\Q \times J^\wedge_\Q$, we have that $P^\times_\Q(S)$ is the set of isomorphisms betweeen $O_S$ and $(P_\Q)_S$, with a free, transitive action of $O_S(S)^\times$, i.e.
-a pseudotorsor of $O_S(S)^\times$ in the traditional group-theoretic sense (note that this set can be empty).
-
-Furthermore, this Poincar\'e torsor has a nice structure of a biextension; this means we can think think of the fibers $P^\times_{\Q,(x,y)}$ as being a $\G_m$ above the point $x \times y$; this structure then gives multiplication maps \[P^\times_{\Q,(x_1,y)} \times P^\times_{\Q,(x_2,y)} \to P^\times_{\Q,(x_1+x_2,y)}\] and similarly \[P^\times_{\Q,(x,y_1)} \times P^\times_{\Q,(x,y_2)} \to P^\times_{\Q,(x,y_1+y_2)}\]
-This bilinear structure comes from interpreting $J^\wedge$ as $\text{Ext}^1(J,\G_m)$; then $P^\times$ is the universal extension of $J$ by $\G_m$, indexed by $J^\wedge$, and by duality vice versa as well.
+P_\Q^\times = \text{Isom}_{J_\Q \times J^\wedge_\Q}(\O_{J_\Q \times J^\wedge_\Q},P_\Q).
+\] 
+We can also describe this in terms of its functor of points; for any scheme $S$ over $J_\Q \times J^\wedge_\Q$, we have that $P^\times_\Q(S)$ is the set of isomorphisms between $\O_S$ and $(P_\Q)_S$, with a free, transitive action of $\O_S(S)^\times$, i.e.
+a pseudotorsor of $\O_S(S)^\times$ in the traditional group-theoretic sense (note that this set can be empty).
+
+Furthermore, this Poincar\'e torsor has a nice structure of a biextension; this means we can think of the fibres $P^\times_{\Q,(x,y)}$ as being a $\G_m$ above the point $x \times y$; this structure then gives multiplication maps \[P^\times_{\Q,(x_1,y)} \times P^\times_{\Q,(x_2,y)} \to P^\times_{\Q,(x_1+x_2,y)}\] and similarly \[P^\times_{\Q,(x,y_1)} \times P^\times_{\Q,(x,y_2)} \to P^\times_{\Q,(x,y_1+y_2)}.\]
+This bilinear structure comes from interpreting $J_\Q^\wedge$ as $\text{Ext}^1(J_\Q,\G_m)$; then $P_\Q^\times$ is the universal extension of $J_\Q$ by $\G_m$, indexed by $J_\Q^\wedge$, and by duality vice versa as well.
 
@@
 
-If $f$ itself is already $0$, then $T$ is trivial and this will give no further information, and most of the times that is the best we can do, as generically the rank of $\Hom^+(J_\Q,J^\wedge_\Q)$, also called the N\'eron-Severi rank $\rho$, is $1$.
+If $f$ itself is already $0$, then $T$ is trivial and this will give no further information, and most of the time that is the best we can do, as generically the rank of $\Hom^+(J_\Q,J^\wedge_\Q)$, also called the N\'eron-Severi rank $\rho$, is $1$.
 But in many interesting cases, this rank is bigger than $1$.
-Using the isomorphism $\lambda$, this rank is also the rank of a certain subgroup of the endomorphism ring of $J_\Q$, and it turns out a family of possible examples is given by modular curves; for example, normalisers of non-split Cartan curves $X_{\text{ns}}^+(\ell)$ have N\'eron-Severi rank equal to the genus, and according to the BSD conjecture Mordell-Weil rank at least equal to the genus.
+Using the isomorphism $\lambda$, this rank is also the rank of a certain subgroup of the endomorphism ring of $J_\Q$, and it turns out a family of possible examples is given by modular curves; for example, normalisers of non-split Cartan curves $X_{\text{ns}}^+(\ell)$ have N\'eron-Severi rank equal to the genus, and, according to the BSD conjecture, Mordell-Weil rank at least equal to the genus.
 
@@
 To combat this problem, the crucial insight is that while $\Q^\times$ is infinitely generated, $\Z^\times$ is finite, so we set everything to work over $\Z$ instead of over $\Q$.
-Our curve is now a surface $C$, of relative dimension $1$ over $\Z$, proper, flat and regular with generic fiber $C_\Q$.
+Our curve is now a surface $C$, of relative dimension $1$ over $\Z$, proper, flat and regular with generic fibre $C_\Q$.
 We cannot expect $C$ to be smooth over $\Z$, we only ask that $C$ is smooth over $\Z[1/n]$ for some squarefree $n$ consisting of bad primes.
@@
 % Computations, and section 7 of the article (line bundles on C x C)
-An important part of making the calculations work, is forming the map $\widetilde{j_b}: U \to T$.
-For this we need to be able to explicitly describe the trivialisation of the $\G_m$-torsor $j_b^* T$ restricted to $U$.
+An important part of making the calculations work is forming the map $\widetilde{j_b}: U \to T$.
+For this, we need to be able to explicitly describe the trivialisation of the $\G_m$-torsor $j_b^* T$ restricted to $U$.
 Remember that $j_b^* T$ is also the pullback of $P^\times$ along the map $C \to J \times J^{\wedge 0}$, and this map factors through the diagonal map $C \to C\times C$.
-As described in Section~7 of the paper, it turns out that giving such a map $f: J \to J^{\wedge}$ and $c \in J^\wedge(\Z)$ with $j_b^* T$ trivial over all opens $U$, is equivalent to giving a line bundle $\Lcal$ on $C \times C$ satisfying the following three properties: $\Lcal$ is rigidified on $\{b\} \times C_\Q$, the fibres of $\pr_2: (C \times C)_\Q \to C_\Q$ are degree $0$, and the pullback $\diag^* \Lcal$ is trivial on $C_\Q$.
+As described in Section~7 of the paper, it turns out that giving such a map $f: J \to J^{\wedge}$ and $c \in J^\wedge(\Z)$ with $j_b^* T$ trivial over all opens $U$ is equivalent to giving a line bundle $\Lcal$ on $C \times C$ satisfying the following three properties: $\Lcal$ is rigidified on $\{b\} \times C_\Q$, the fibres of $\pr_2: (C \times C)_\Q \to C_\Q$ are degree $0$, and the pullback $\diag^* \Lcal$ is trivial on $C_\Q$.
 This turns the problem of describing a map $J \to J^\wedge$ in the sometimes more concrete problem of giving a line bundle on $C \times C$ satisfying some simple conditions.

### 2023-12-08 ScientificTalk.tex
Add defense files

\documentclass[15pt]{beamer}
\usepackage[T1]{fontenc}
\usepackage{multicol}
\usepackage{ragged2e}   %new code
\usepackage[utf8]{inputenc}
\usepackage[brazil]{varioref}
\usepackage[square,sort,comma,super,authoryear]{natbib}
\usepackage{xmpmulti}
\usepackage{epsfig}
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{ru,graphicx,hyperref,url} % 
\usepackage{amsthm}
\usepackage{eucal}
\usepackage{amssymb}
%\usepackage{mdsymbol}
\usepackage{mathrsfs}
\usepackage{dsfont}
%\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{tikz,tikz-cd}
\usepackage{wrapfig,lipsum,booktabs}
\usepackage{caption}
\usepackage[ruled,linesnumbered]{algorithm2e}
\usepackage[all]{nowidow}

%\usepackage{hyperref}
\usepackage{amstext} % for \text macro
\usepackage{array}   % for \newcolumntype macro
\usepackage{mathtools}

% Enable colored hyperlinks
\hypersetup{colorlinks=true}

% The following three lines are for crossmarks & checkmarks
\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

\newcommand{\den}{\mathop{\mathgroup\symoperators den}\nolimits}
\newcommand{\ggd}{\mathop{\mathgroup\symoperators ggd}\nolimits}
\newcommand{\des}{\text{d.e.s.d.a.\ }}
%\newcommand{\opg}{\text{d.e.s.d.a.\ }}
\newcommand{\blokje}{\hfill $\Box$\\}
%Om je bewijs of je antwoord af te sluiten.
\newcommand{\header}[1]{\vspace{0.5cm}\framebox[\linewidth]{\textsc{Exercise #1}}\\}
\newcommand{\deel}[1]{\textbf{#1)}\ }
\newcommand{\macht}[1]{\mathcal{P}(#1)}
\newcommand{\entier}[1]{\left\lfloor #1 \right\rfloor}
\newcommand{\A}{\mathbb{A}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\G}{\mathbb{G}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\vx}{\mathbf{x}}
\newcommand{\vy}{\mathbf{y}}
\newcommand{\vz}{\mathbf{z}}
\newcommand{\Fcal}{\mathcal{F}}
\newcommand{\Lcal}{\mathcal{L}}
\renewcommand{\O}{\mathcal{O}}
\renewcommand{\P}{\mathbb{P}}
\newcommand{\Pcal}{\mathcal{P}}
\newcommand{\NP}{\mathcal{NP}}
\newcommand{\NPC}{\mathcal{NPC}}
\newcommand{\F}{\mathbb{F}}
\renewcommand{\angle}[1]{\hspace{-2pt}\left\langle #1 \right\rangle}
\newcommand*\diff{\mathop{}\!\mathrm{d}}
\newcommand{\rad}{\text{rad}}
\newcommand{\x}{x}
\newcommand{\m}{\mathfrak{m}}
\newcommand{\tensor}{\otimes}
\newcommand{\Ring}{\textbf{Rings}}
\newcommand{\Sets}{\textbf{Sets}}

\DeclareMathOperator{\mon}{mon}
\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\Gal}{Gal}
\DeclareMathOperator{\End}{End}
\DeclareMathOperator{\sgn}{sgn}
\DeclareMathOperator{\trdeg}{trdeg}
\DeclareMathOperator{\rk}{rk}
\DeclareMathOperator{\Fun}{Fun}
\DeclareMathOperator{\im}{im}
\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\sm}{sm}
\DeclareMathOperator{\pr}{pr}
\DeclareMathOperator{\diag}{diag}
\DeclareMathOperator{\Spec}{Spec}
\DeclareMathOperator{\MaxSpec}{MaxSpec}
\DeclareMathOperator{\Spf}{Spf}
\DeclareMathOperator{\sep}{sep}
\DeclareMathOperator{\Ann}{Ann}
\DeclareMathOperator{\GL}{GL}
\DeclareMathOperator{\Mat}{Mat}
\DeclareMathOperator{\Jac}{Jac}
\let\S\undefined
\DeclareMathOperator{\S}{S}
\let\div\undefined
\DeclareMathOperator{\div}{div}

\addtobeamertemplate{block begin}{}{\justifying}
\setbeamertemplate{section in toc}[sections numbered]
\AtBeginSection[]
{
  \begin{frame}{Table of Contents}
  \begin{multicols}{2}
      \tableofcontents[currentsection]
    \end{multicols}
  \end{frame}

}

% The title of the presentation:
%  - first a short version which is visible at the bottom of each slide;
%  - second the full title shown on the title slide;

\title[Geometric linear Chabauty]{Geometric linear Chabauty}

% Optional: a subtitle to be dispalyed on the title slide
% \subtitle{Show where you're from}

% The author(s) of the presentation:
%  - again first a short version to be displayed at the bottom;
%  - next the full list of authors, which may include contact information;
\author[Pim Spelier]{
  Pim Spelier\\\medskip
  {\small {spelier.pim@gmail.com}
  }}

% The institute:
%  - to start the name of the university as displayed on the top of each slide
%    this can be adjusted such that you can also create a Dutch version
%  - next the institute information as displayed on the title slide
\institute[Leiden University]{
  Mathematical Institute \\
  }

% Add a date and possibly the name of the event to the slides
%  - again first a short version to be shown at the bottom of each slide
%  - second the full date and event name for the title slide
\date{\today}

\begin{document}

\begin{frame}
  \titlepage
\end{frame}

%\begin{frame}{Table of Contents}
%    \begin{multicols}{2}
%    \tableofcontents
%    \end{multicols}
%\end{frame}

% Section titles are shown in at the top of the slides with the current section 
% highlighted. Note that the number of sections determines the size of the top 
% bar, and hence the university name and logo. If you do not add any sections 
% they will not be visible.
\section{Introduction}
\begin{frame}
    \frametitle{Introduction}
    \framesubtitle{Problem}
    \begin{block}{Problem}
        Let $C_\Q$ a proper, smooth, geometrically connected curve over $\Q$ of genus $g \geq 2$. Find $C_\Q(\Q)$.
    \end{block}
\end{frame}

\begin{frame}
    \frametitle{Introduction}
    \framesubtitle{Classical solutions}
    $C_\Q$ a proper, smooth, geometrically connected curve over $\Q$ of genus $g \geq 2$.
    \begin{block}{Faltings's theorem (1983)} 
        $C_\Q(\Q)$ is finite.
    \end{block}\pause
    \begin{itemize}[<+->]
	\item This is not effective.
	\item Can be made effective by Chabauty.
	\end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Introduction}
    \framesubtitle{Chabauty}
    $C_\Q$ a proper, smooth, geometrically connected curve over $\Q$ of genus $g \geq 2$.\\
    Let $J_\Q$ be the Jacobian of $C_\Q$, $p$ a prime of good reduction, $r$ the rank of Mordell-Weil group $J_\Q(\Q)$, $b\in C_\Q(\Q)$ and $j_b: C_\Q \to J_\Q$ subtracting $b$ on points.\\ \pause
    \[
\begin{tikzcd}[ampersand replacement=\&]
C_\Q(\Q) \arrow[d] \arrow[r] \& J_\Q(\Q) \arrow[d] \\
C_\Q(\Q_p) \arrow[r]              \& J_\Q(\Q_p)        
\end{tikzcd}
\]
\vspace{50pt}
\end{frame}

\begin{frame}
    \frametitle{Introduction}
    \framesubtitle{Chabauty}
    $C_\Q$ a proper, smooth, geometrically connected curve over $\Q$ of genus $g \geq 2$.\\
    Let $J_\Q$ be the Jacobian of $C_\Q$, $p$ a prime of good reduction, $r$ the rank of Mordell-Weil group $J_\Q(\Q)$, $b\in C_\Q(\Q)$ and $j_b: C_\Q \to J_\Q$ subtracting $b$ on points.\\ 
    \[
\begin{tikzcd}[ampersand replacement=\&]
\& C_\Q(\Q) \arrow[d] \arrow[r] \& \overline{J_\Q(\Q)} \arrow[d] \arrow[r, no head] \& \dim r\\
\dim 1 \arrow[r, no head] \& C_\Q(\Q_p) \arrow[r]              \& J_\Q(\Q_p)   \arrow[r, no head]  \& \dim g   
\end{tikzcd}
\]\pause
    \begin{block}{Definition}
        Let $C_\Q(\Q_p)_1 = C_\Q(\Q_p) \cap \overline{J_\Q(\Q)} \supset C_\Q(\Q)$.
    \end{block}\pause
\end{frame}

\begin{frame}
    \frametitle{Introduction}
    \framesubtitle{Chabauty}
    $C_\Q(\Q_p)_1 = C_\Q(\Q_p) \cap \overline{J_\Q(\Q)}$.
    \begin{block}{Chabauty's theorem (1941)}
        If $r < g$, then $C_\Q(\Q_p)_1$ is finite (and hence so is $C_\Q(\Q)$).
    \end{block}\pause
    Classically, Coleman-Chabauty (1985): find $1$-forms on $J_{\Q_p}$ whose Coleman integral vanish on the Mordell-Weil group $J_{\Q}(\Q)$, and pull back to $C_\Q$ to make effective.
\end{frame}

\begin{frame}
    \frametitle{Recent developments}
    \framesubtitle{Kim-Chabauty and quadratic Chabauty}
    \begin{itemize}[<+->]
        \item Coleman has been generalised by Kim (2009), by replacing $J_\Q$ with Selmer variety.
        \item Gives infinite chain\[ C_\Q(\Q_p)_1 \supset C_\Q(\Q_p)_2 \supset \cdots \supset C_\Q(\Q).\]
        \item Quadratic Chabauty focuses on $C_\Q(\Q_p)_2$, which is finite if $r < g + \rho - 1$ where $\rho$ is the N\'eron-Severi rank of $J_\Q$
        \item Used by Balakrishnan, Dogra, M\"uller, Tuitman, Vonk (2019) to calculate rational points of $X_s(13)$.
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Recent developments}
    \framesubtitle{Geometric quadratic Chabauty}
    Edixhoven and Lido replace $J_\Q$ by $T$, another geometric object, and spread out over $\Z$.\\\pause
    In contrast with Coleman-Chabauty, pull back equations for $C(\Z_p)$ inside $T(\Z_p)$ to $T(\Z)$. \\\pause
    Question: what happens when we pull apply this to $J$, the linear case?\\\pause
    Aim of thesis: describe what happens in the linear case +  heuristics + how to implement + example.
\end{frame}

\section{Setting and strategy}
\begin{frame}
    \frametitle{Setting}
    $C/\Z_{(p)}$ proper, smooth curve with generic fibre $C_\Q$, with $p > 2$.\\\pause
    $J/\Z_{(p)}$ relative Jacobian, with embedding $j_b: C \to J$, subtracting $b \in C(\Z_{(p)})$.\\\pause
    $P \in C(\F_p)$ with $t = P - b \in J(\F_p)$ lifting to a $\Z_{(p)}$-point.\\\pause
    Consider the diagram of residue discs:\[
    \begin{tikzcd}[ampersand replacement=\&]
        C(\Z_{(p)})_P \arrow[d] \arrow[r] \& J(\Z_{(p)})_t \arrow[d] \\
        C(\Z_p)_P \arrow[r]              \& J(\Z_p)_t        
    \end{tikzcd} \]
\end{frame}

\begin{frame}
    \frametitle{Strategy}
    \[
    \begin{tikzcd}[ampersand replacement=\&]
        C(\Z_{(p)})_P \arrow[d] \arrow[r] \& J(\Z_{(p)})_t \arrow[d] \\
        C(\Z_p)_P \arrow[r]              \& J(\Z_p)_t        
    \end{tikzcd} \]
    Strategy:
    \begin{itemize}[<+->]
        \item Describe $C(\Z_p)_P$ and $J(\Z_p)_t$
        \item Describe the inclusion $C(\Z_p)_P \to J(\Z_p)_t  $
        \item Describe the map $\kappa: J(\Z_{(p)})_t \to J(\Z_p)_t$
    \end{itemize}
\end{frame}

\section{Method}
\begin{frame}
    \frametitle{$\Z_p$-points in a residue disc}
    Let $X$ be a smooth $\Z_p$-scheme of relative dimension $n$. Let $x \in X(\F_p)$.\\\pause
    Then $O_{X,x}$ has maximal ideal generated by $p$ and parameters $t_1,\dots,t_n$.
    \begin{block}{Fact (generalisation of Hensel's Lemma)}
    Evaluating $t = (t_1,\dots,t_n)$  gives a bijection $X(\Z_p)_x \to p\Z_p^n$.
    \end{block}\pause
    Dividing by $p$ gives $X(\Z_p)_x \xrightarrow{~} \Z_p^n$.
\end{frame}

\begin{frame}
    \frametitle{Abel-Jacobi map $C \to J$}
    Hence $C(\Z_p)_P \to J(\Z_p)_t$ induces a map $\Z_p \to \Z_p^g$.
    \begin{definition}
    The ring $\Z_p\angle{x_1,\dots,x_n}$ consists of those elements of $\Z_p[[x_1,\dots,x_n]]$ converging on all of $\Z_p^n$.
    \end{definition}
    \begin{block}{Fact}
    There are $f_1,\dots,f_{g-1} \in \Z_p\angle{x_1,\dots,x_{g}}$ whose zero-set cut out the image of $\Z_p \to \Z_p^g$. These are linear modulo $p$ and when the parameters are chosen correctly, are linear.
    \end{block}\pause
\end{frame}

\begin{frame}
    \frametitle{Inclusion Mordell-Weil group $J(\Z_{(p)})$}
    What about $J(\Z_{(p)})_0 \to J(\Z_p)_0$? This is $\kappa: (\Z^r,+) \to (\Z_p^g,\oplus)$.\\\pause
    Group structure on $J(\Z_p)_0 \cong p\Z_p^g$ given by formal group $F \in \Z_p[[\vx,\vy]]^g$.\pause
    This induces a formal logarithm.
\end{frame}

\begin{frame}
    \frametitle{Logarithm}
    \begin{block}{Proposition}
    The formal logarithm for the formal group corresponding to $J(\Z_p)_0$ induces an isomorphism $\log_p: J(\Z_p)_0 = (\Z_p^g,\oplus) \to (\Z_p^g,+)$ with inverse $\exp_p$, with both $\exp_p,\log_p \in \Z_p\angle{x_1,\dots,x_{g}}^g$ linear mod $p$ (and also well behaved mod higher powers).
    \end{block}\pause
    \begin{block}{Theorem}
    The map $\kappa: \Z^r \to \Z_p^g$ is given by $g$ convergent power series, linear mod $p$, and can hence be extended to $\kappa: \Z_p^r \to \Z_p^g$ with $\im \kappa = \overline{J(\Z_{(p)})_0}$
    \end{block}\pause
    Proof:\[
    \begin{tikzcd}[ampersand replacement=\&]
{(\Z^d,+)} \arrow[rr, "\kappa"] \arrow[rd, "\log_p \circ \kappa"] \&                                   \& {(\Z_p^g,\oplus)} \\
                                                                  \& {(\Z_p^g,+)} \arrow[ru, "\exp_p"] \&                  
\end{tikzcd}\]
\end{frame}

\begin{frame}
    \frametitle{Final theorems}
    \begin{definition}
        Let $\lambda_1,\dots,\lambda_{g-1} = \kappa^* f_1,\dots,\kappa^* f_{g-1} \in \Z_p\angle{x_1,\dots,x_r}$, i.e. the pullback to $\overline{J(\Z_{(p)})_P}$ of the equations defining $C(\Z_p)_P$ inside $J(\Z_p)_t$. Then $Z(\lambda_1,\dots,\lambda_{g-1}) \subset \Z_p^r$ surjects onto $C(\Z_p)_{1,P} = C(\Z_p)_P \cap \overline{J(\Z_{(p)})_t}$. \pause I.e., with $A = \Z_p\angle{x_1,\dots,x_r}/(\lambda_1,\dots,\lambda_{g-1})$, then $|C(\Z_{(p)})_P| \leq |\Hom(A,\Z_p)| = |Z(\lambda_1,\dots,\lambda_{g-1})|$
    \end{definition}\pause
    \begin{block}{Proposition (Edixhoven-Lido)}
    If \[\overline{A} = \F_p[x_1,\dots,x_r]/(\overline{\lambda_1},\dots,\overline{\lambda_{g-1}})\] is finite, then $|\Hom(A,\Z_p)| \leq |\dim_{\F_p} \overline{A}|$
    \end{block}\pause
    Proof: $A$ is complete.\\\pause
    Important: our $\lambda_i$ are linear mod $p$.
\end{frame}

\begin{frame}{Final theorems}
    \begin{definition}
        Let $\lambda_1,\dots,\lambda_{g-1} = \kappa^* f_1,\dots,\kappa^* f_{g-1} \in \Z_p\angle{x_1,\dots,x_r}$, i.e. the pullback to $\overline{J(\Z_{(p)})_P}$ of the equations defining $C(\Z_p)_P$ inside $J(\Z_p)_t$. Then $Z(\lambda_1,\dots,\lambda_{g-1}) \subset \Z_p^r$ surjects onto $C(\Z_p)_{1,P} = C(\Z_p)_P \cap \overline{J(\Z_{(p)})_t}$. I.e., with $A = \Z_p\angle{x_1,\dots,x_r}/(\lambda_1,\dots,\lambda_{g-1})$, then $|C(\Z_{(p)})_P| \leq |\Hom(A,\Z_p)| = |Z(\lambda_1,\dots,\lambda_{g-1})|$
    \end{definition}
    \begin{block}{Proposition (Single digit precision geometric linear Chabauty)}
    If for all points $P \in C(\F_p)$, the linear system $\overline{\lambda_1}=\dots=\overline{\lambda_n} = 0$ defining $C(\Z_p)_P \subset J(\Z_p)_t$ pulled back to $\overline{J(\Z_{(p)})_t}$ has $n_P \leq 1$ solutions, we get the inequality
    \[
    |C_{\Q}(\Q)| = |C(\Z_{(p)})| \leq \sum_{P \in C(\F_p)} n_P \leq |C(\F_p)|. 
    \]
    \end{block}
\end{frame}

\section{Heuristics}
\begin{frame}
    \frametitle{Modelling}
    Recall: for each point $P$ in $C(\F_p)$, we have an affine linear system of $g-1$ equations $\overline{\lambda_i} = 0$ in $r$ variables.\\\pause
    Note: $\F_p[x_1,\dots,x_r]/(\overline{\lambda_1},\dots,\overline{\lambda_{g-1}})$ is finite $\Leftrightarrow \overline{\lambda_1} = \cdots = \overline{\lambda_{g-1}} = 0$ has 0 or 1 solution.\\\pause
    If $P$ comes from a $\Z_{(p)}$ point, we model as random homogenous.\\\pause
    Otherwise we assume it to be model as affine.\\\pause
    Question: under these assumptions, what is the probability that our method gives a (good) upper bound?
\end{frame}

\begin{frame}
    \frametitle{Random linear system}
    \begin{block}{Lemma}
    Let $A \in \Mat_{(n+k)\times n}(\F_q)$ be random. Then the probability of $A$ having non-trivial kernel is at most $\frac{1}{(p-1)p^k}$
    \end{block}\pause
    \begin{proof}
    Denote the columns by $A_0,\cdots,A_{n-1}$, let $V_i = \angle{A_0,\dots,A_{i-1}}$ and denote $E_i$ for the event $A_i \in V_i$. Then 
    \begin{align*}
    \P(\ker A \not= 0) &= \P(E_0 \vee \cdots \vee E_{n-1}) \\
                       &\leq \sum_{i=0}^{n-1} \P(E_i) \\
                       &\leq \sum_{i=0}^{n-1} p^{i-(n+k)} \\
                       &\leq \frac{1}{(p-1)p^k}.
    \end{align*}
    \end{proof}
\end{frame}

\begin{frame}
    \frametitle{Heuristic}
    \begin{block}{Lemma}
    Let $A \in \Mat_{(n+k)\times n}(\F_q)$ be random. Then the probability of $A$ having non-trivial kernel is at most $\frac{1}{(p-1)p^k}$
    \end{block}
    \begin{block}{Proposition}
    Under all of our assumptions (+ some technical assumptions), single-digit-precision calculations don't work with probability at most\[
    (|C(\Z_{(p)})|+2p^{-(g-r-1)})(p-1)^{-1}p^{-(g-r-1)}.
    \]
    \end{block}\pause
    \begin{block}{Corollary}
    We expect our method to work for a set of primes with density $1$; if $r < g-1$, for all but finitely many primes.
    For $r < g-1$, we expect to find with probability at least $1/e$ the clearly optimal upper bound of $|C(\Z_{(p)})|$ for $|C(\Z_{(p)})|$.
    \end{block}
\end{frame}

\section{Implementation}
\begin{frame}
    \frametitle{Implementation}
    \framesubtitle{General remarks}
    Parameters at $C$: easy.\\ \pause
    Parameters at $J$: use birationality with $C^{(g)}$.\\ \pause
    Problem: we need to easily represent elements of $J(\Z/p^2\Z)$\\\pause
    Solution: Makdisi's representation
\end{frame}

\begin{frame}
    \frametitle{Implementation}
    \framesubtitle{Makdisi's representation}
    Let $k$ be a field, and $C/k$ a curve.\\\pause
    Let $D_0$ be an effective divisor of degree $d_0 \geq 2g+1$.\\\pause
    Let $V = \Lcal(5D_0)$. Let $S$ be a set of points of size $\geq 5d_0 + 1$ on $C$ not meeting $D_0$, and note $V \hookrightarrow k^S$. \\\pause
    Let $[x] \in J(k)$, pick $E\geq 0$ with $[x] = [D_0 - E]$, and represent $[x]$ by $\Lcal(2D_0 - E) \subset V \subset k^S$.\\\pause
    This is non-unique, but equality can be tested. \\\pause
    Also addition, subtraction, $\dots$. All linear algebra inside $V \subset k^S$.\\\pause
    For $k = \F_p$ this lifts easily to $\Z/p^2\Z$; everything is a free $\Z/p^2\Z$-module inside $(\Z/p^2\Z)^S$, hence still just linear algebra.\\\pause
    Hence all operations in $O(g^\omega) $ where $\omega = 2.37...$.
\end{frame}

\begin{frame}    
    \frametitle{Implementation}
    \framesubtitle{Complexity}
    \begin{block}{Proposition}
        If $C$ is hyperelliptic, the Abel-Jacobi map $C \to J$ can be computed in $O(g^\omega)$.
    \end{block}\pause

    \begin{block}{Proposition}
    	Assume we have a set of $r$ elements of $J(\Z_{(p)})$ that generate a subgroup of index finite and coprime to $p|J(\F_p)|$ (+ other technical assumptions). Then the complexity of executing single-digit-precision geometric linear Chabauty on hyperelliptic curves is $O(|C(\F_p)|rg^{\omega+1})$.
    \end{block}\pause
\end{frame}

\begin{frame}
    \frametitle{Example}
    \begin{block}{Example}
        \[C\colon y^2 = x^6 + 8x^5 + 22x^4 + 22x^3 + 5x^2 + 6x + 1\]
        with $g = 2, r = 1$ and $|C_\Q(\Q)_{\text{known}}| = 6$. Choose $p = 5$. We find $|C(\Z_{(5)})| \leq 7$. By the hyperelliptic involution having two fixed points, $|C_\Q(\Q)|$ is even and hence $C_\Q(\Q)_{\text{known}} = C_\Q(\Q)$.
    \end{block}
\end{frame}

\end{document}

### 2023-12-08 art.tex
Add defense files

--- 2023-12-08 MSK.tex
@@
 {\Large\bf 
-P.\ Spelier
+P.\ Spelier, M.Sc\\
+prof. dr. S.J. Edixhoven
 }
 
-\vspace{1em}
+{\sc 
+Leiden University, Mathematical Institute\\
+}
+
+\vspace{2em}
 
 {\LARGE\bf 
-A geometric approach to linear Chabauty\\
-{\color{red} Over number fields}
+A geometric approach to linear Chabauty
 } 
-
-\vspace{8em}
-
-{\large\bf 
-Master thesis
-}
-
-\vspace{1em}
+\vspace{2em}
 
@@
 
-\vspace{8em}
-
-{\large\bf
-\begin{tabular}{ll}
-Thesis supervisor: & prof. dr. S.J. Edixhoven\\
-\end{tabular}
-}
-\vfill
-
-\includegraphics{ulzegel_blauw}\\
-
-\vspace{2em}
-
-{\large\bf 
-Leiden University\\
-Mathematical Institute\\
-}
-
 \end{center}
-\thispagestyle{empty}
-\newpage
+
+\listoftodos
+\todo{Bas, zou je wellicht een bewijs kunnen schrijven dat onder de voorwaarde $r < g$ (ik weet niet of er nog andere nodig zijn) de verzameling gedefinieerd in Theorem~\ref{thm:final} altijd eindig is?
+Dat lijkt me fijn, en misschien geeft het zelfs een algoritme dat voor elke kromme een bovengrens kan geven?}
+%-----------------------------------------------------------------------------------------------------------------------
+
+\todo{First try of abstract}
+Given a curve of genus at least $2$, it is known by Faltings's Theorem (1983) that the curve has only finitely many rational points.
+Finding the set of rational points can still be a difficult problem.
+Chabauty (1941) already proved the special case of Faltings's Theorem where the Mordell-Weil rank of the Jacobian is less than the genus, by intersecting the $p$-adic points of the curve with the Mordell-Weil group inside the $p$-adic points of the Jacobian, and Coleman (1985) gave a way to make this effective, by introducing Coleman integrals.
+This article aims to make Chabauty's method effective in a different, purely geometric way.
+An important part of this is working with finite precision; we will in particular focus on working modulo $p$, and will develop several heuristics, and also calculate the complexity of our algorithms.
+
 \tableofcontents
-\newpage
-
-%-----------------------------------------------------------------------------------------------------------------------
-\section{Introduction}
+
+\section{Old introduction} \todo{Put a bit of the introduction, and some of the references/results in the new introduction}
 \label{section:intro}
@@
 For $g = 0$, there are either no or infinitely many solutions, and their behavior is well understood.
-For $g = 1$, we get either no point or an elliptic curve, whose set of rational points forms an often infinite group.
-
-In this thesis, we look only at the case of a curve $C$ with genus $g > 1$.
+For $g = 1$, we get either no point or an elliptic curve, whose set of rational points forms a finitely generated abelian group.
+
+In this article, we look only at the case of a curve $C$ with genus $g > 1$.
 It turns out that there are always only finitely many rational points.
@@
 
-Before Faltings's theorem was proven, one of the major partial results was a theorem from Chabauty in 1941, phrased in terms of the rank $r$ of the group of rational points on the Jacobian $J$ of the curve, also called the Mordell-Weil rank, which is finite by the Mordell-Weil theorem.
+Before Faltings's theorem was proven, one of the major partial results was a theorem from Chabauty in 1941, phrased in terms of the rank $r$ of the group of rational points on the Jacobian $J$ of the curve, also called the Mordell-Weil rank; this rank is finite by the Mordell-Weil theorem.
 Chabauty proved, using $p$-adic methods, that if $r$ is strictly smaller than the genus $g$, then $C$ has only finitely many rational points.
-Loosely said, this proof and all Chabauty related theorems, rely on choosing a prime $p$ for which $C$ has good reduction, and intersecting $J(\Q)$ with $C(\Q_p)$ inside the bigger Lie group $J(\Q_p)$.
+Loosely said, this proof and all Chabauty-related theorems, rely on choosing a prime $p$ for which $C$ has good reduction, and intersecting $J(\Q)$ with $C(\Q_p)$ inside the bigger Lie group $J(\Q_p)$.
 By properties of $\Q_p$, the subgroup $J(\Q)$, up to torsion generated by $r$ elements, lies within a Lie subgroup of dimension at most $r$, and $C(\Q_p)$ is a $1$-dimensional $p$-adic manifold, and hence this intersection can be proven to be discrete and -- as $J(\Q_p)$ is compact -- finite.
@@
 
-The purpose of this thesis is to make the work by Edixhoven and Lido more accessible by applying geometric Chabauty to the linear case, i.e.
-when working with $J(\Q)$ and $J(\Q_p)$ and assuming $r < g$.\todo{Add number fields in the introduction} In this thesis, we go into more detail on what is happening throughout the process, including both theoretical and practical components.
+The purpose of this article is to make the work by Edixhoven and Lido more accessible by applying geometric Chabauty to the linear case, i.e.
+when working with $J(\Q)$ and $J(\Q_p)$ and assuming $r < g$.
+In this article, we go into more detail on what is happening throughout the process, including both theoretical and practical components.
 This new method of applying Chabauty leads to, when working with single-digit $p$-adic precision, a conditional upper bound $|C(\Q)| \leq |C(\F_p)|$, as obtained in Proposition~\ref{prop:linchabauty}.
@@
 
-\subsection{Overview}
+\section{Introduction}\todo{Maybe give a bit more context (Faltings, Chabauty, Coleman, McCallum-Poonen, Edixhoven-Lido)?
+Not sure what I want to put in and what not.}\todo{Verwijzen naar dat Sachi en ik eraan werken om de connectie tussen Coleman en geometric duidelijker te maken.}
 We first present the context in which we will perform Chabauty.
-Let $K$ be a number field of degree $d$, and let $v: K \to \Z$ be a finite place.
-Let $\pi$ denote a uniformiser, $q$ the cardinality of the residue field and $p> 2$ its caracteristic\todo{Check when $p,\pi$ is big enough for both Pierre Parent and logarithm}\todo{Decide if we can allow ramification}.
-Let $f$ denote the residue field degree $[\F_q : \F_p]$ and $e$ the ramification $v(p)$.
-We use $O$ to denote the maximal order of $K$, and $O_{(\pi)}$ and $O_{\pi}$ for respectively the localisation and the completion with respect to $\pi$.
-This valuation also gives rise to an embedding of $K$ into an extension $K_{\pi}$ of $\Q_p$ of degree $ef$, with ramification degree $e$ and residue field degree $f$; then $O_\pi$ is simply the ring of integers of $K_{\pi}$.
-
-Let $C_{K}/K$ be a curve (i.e., a proper, smooth, geometrically connected variety of dimension $1$) of genus $g \geq 2$ whose $K$-points we will attempt to find.
-assume we have a scheme $C$ over $O_{(\pi)}$, proper and smooth with generic fibre $C_{K}$; then we immediately have $C_K(K) = C(K) = C(O_{(\pi)})$ by the valuative criterion of properness.
-Let $J$ be the relative Jacobian of $C$ over $O_{(\pi)}$, i.e.
-with fibres $\Jac C_K$ and $\Jac C_{\F_q}$.
-We assume from now on that the Mordell-Weil rank of $J$ is $r \leq d(g-1)$.
-Assume we have a $K$-point $b$ in $C$, or equivalently a $O_{(\pi)}$-point.
+Let $C_{\Q}/\Q$ be a curve (i.e., a proper, smooth, geometrically connected variety of dimension~$1$) of genus $g \geq 2$ whose $\Q$-points we will attempt to find.
+Let $p>2$ be a prime, and assume we have a scheme $C$ over $\Z_{(p)}$, proper and smooth with generic fibre $C_{\Q}$; then we immediately have $C_\Q(\Q) = C(\Q) = C(\Z_{(p)})$ by the valuative criterion of properness.
+Let $J$ be the relative Jacobian of $C$ over $\Z_{(p)}$, i.e.
+with fibres $\Jac C_\Q$ and $\Jac C_{\F_p}$.
+We assume from now on that the Mordell-Weil rank of $J$ is $r < g$.
+Assume we have a $\Q$-point $b$ in $C$, or equivalently a $\Z_{(p)}$-point.
 We view $C$ as a subscheme of $J$, using the map $Q \mapsto Q - b$ on points.
-Let $P \in C(\F_q)$ be a point such that $t := P - b \in J(\F_q)$ lies in the image of $J(O_{(\pi)})$.
+Let $P \in C(\F_p)$ be a point such that $t := P - b \in J(\F_p)$ lies in the image of $J(\Z_{(p)})$.
 
@@
 \begin{exmp}
-If we have a proper variety $X$ over $O_{(\pi)}$, then $X(O_{(\pi)})$ is naturally in bijection with $X(K)$.
-The natural map $X(O_{(\pi)}) \to X(\F_q)$ reduces a point modulo $\pi$ and for $x \in X(\F_q)$, the set $X(O_{(\pi)})_x$ consists of the residue disc of $O_{(\pi)}$-points reducing to $x$.
+If we have a proper variety $X$ over $\Z_{(p)}$, then $X(\Z_{(p)})$ is naturally in bijection with $X(\Q)$.
+The natural map $X(\Z_{(p)}) \to X(\F_p)$ reduces a point modulo $p$ and for $x \in X(\F_p)$, the set $X(\Z_{(p)})_x$ consists of the residue disc of $\Z_{(p)}$-points reducing to $x$.
 \end{exmp}
 
-Geometric Chabauty works by finding an upper bound for the cardinality of $C(O_{(\pi)})_P$. For this, we use the following diagram.
+Geometric Chabauty works by finding an upper bound for the cardinality of $C(\Z_{(p)})_P$. For this, we use the following diagram.
 \[
 \begin{tikzcd}
-C(O_{(\pi)})_P \arrow[d] \arrow[r] & J(O_{(\pi)})_t \arrow[d] \\
-C(O_\pi)_P \arrow[r]              & J(O_\pi)_t        
+C(\Z_{(p)})_P \arrow[d] \arrow[r] & J(\Z_{(p)})_t \arrow[d] \\
+C(\Z_p)_P \arrow[r]              & J(\Z_p)_t        
 \end{tikzcd}
@@
 where the two vertical maps are inclusions, and the two horizontal maps are subtraction of $b$.
-We will in fact compute upper bounds for the larger set $C(O_\pi)_P \cap \overline{J(O_{(\pi)})_t}$, where $\overline{J(O_{(\pi)})_t}$ is the closure of $J(O_{(\pi)})_t$ in $J(O_\pi)_t$.
-
-In Section~\ref{section:smoothzppoints}, we treat the structure of $C(O_\pi)_P$ and $J(O_\pi)_t$; we will show that, after choosing parameters, they are in bijection with respectively $O_\pi$ and $O_\pi^g$.
-We also discuss the resulting map $O_\pi \to O_\pi^g$.{\color{red} and, identifying $O_\pi$ with $\Z_p^{ef}$ as topological groups, the map $\Z_p^{ef} \to \Z_p^{efg}$.
-This latter map is not necessarily well behaved if there is ramification; choosing a $\Z_p$-basis of $O_{\pi}$ appropriately, we will instead look at the well behaved restriction $\Z_p^{f} \to \Z_p^{fg}$.}
-
-In Section~\ref{section:kappa} we further look at the map $J(O_{(\pi)})_t \to J(O_\pi)_t$.
-This is a translation of the group morphism $J(O_{(\pi)})_0 \to J(O_\pi)_0$ between kernels of reduction; it turns out that for our choice of $p$, the subgroup $J(O_{(\pi)})_0$ is free of rank $r$.
-We study the properties of the resulting map $\Z^r \to O_\pi^g$, using the theory of formal groups to determine the group structure on $O_\pi^g$ induced by the bijection $J(O_\pi)_0 \to O_\pi^g$.
-{\color{red} Importantly, we identify $O_\pi$ with $\Z_p^{ef}$ as topological groups; we also look at the resulting map $\Z^r \to \Z_p^{efg}$.
-Again, to control the behavior of this map modulo $p$, we consider the map $\Z^r \to \Z_p^{fg}$.}
-
-In Section~\ref{section:intersection}, we put all of this information together, culminating in several methods to possibly compute upper bounds on $\left|C(O_\pi)_P \cap \overline{J(O_{(\pi)})_t}\right|$ with finite precision calculations if $r \leq f(g-1)$.
-We also perform a heuristic analysis to show that a simple calculation of linear algebra modulo $p$ is very likely to result in an upper bound of at most $|C(\F_q)|$ for $|C(O_{(\pi)})|$, and for $r < f(g-1)$ \todo{check whether this is correct, it should hold.} even in an upper bound of $|C_K(K)|$.
-Hence given only a curve $C_K/K$, the best possible choice of a prime of $K$ is an inert prime
-
-The methods developed in the first four sections are not always guaranteed to prove finiteness of $C(O_{(\pi)})_P$.
+We will in fact compute upper bounds for the larger set $C(\Z_p)_P \cap \overline{J(\Z_{(p)})_t}$, where $\overline{J(\Z_{(p)})_t}$ is the closure of $J(\Z_{(p)})_t$ in $J(\Z_p)_t$.
+
+In goemetric Chabauty, in contrast to Coleman-Chabauty (as explained in \cite{poonen12}), we give equations for the curve inside the Jacobian, and pull those back to the Mordell-Weil group.
+The main result is Theorem~\ref{thm:final}, which in the case of working modulo $p$ specialises to Proposition~\ref{prop:linchabauty}.
+This proposition gives a conditional upper bound on $|C(\Q)|$ of at most $|C(\F_p)|$.
+This behaves comparably with Theorem~5.3 of \cite{poonen12}, which gives an upper bound of $|C(\F_p)| + 2g-2$, albeit under less strict conditions.
+
+It turns out that, when working modulo $p$, the situation becomes linear algebra; we give some heuristics about how often the conditions of Proposition~\ref{prop:linchabauty} are satisfied, and what the upper bound will be in Proposition~\ref{prop:probwork} and Remark~\ref{rem:probwork}.
+In particular, we expect that our method will give an upper bound on $|C(\Q)|$ for all $p$ in a set of density $1$, and for $r \leq g-2$ will even lead to the optimal upper bound of $|C(\Q)|$ in a set of density at least $e^{-1}$ (with both results having refinements for even smaller $r$).
+
+In this article, we also focus on explicit algorithms and computations.
+Assuming all relevant computations in the Mordell-Weil group have been done (finding the rank, a set of generators, and other data), in Section~\ref{section:explicit} we give an $O((p+g\sqrt{p})rg^{4})$ algorithm for executing the calculations needed in Proposition~\ref{prop:linchabauty}, and we implement and run this in Pari/GP.
+
+\subsection{Overview}
+In Section~\ref{section:smoothzppoints}, we treat the structure of $C(\Z_p)_P$ and $J(\Z_p)_t$; we will show that, after choosing parameters, they are in bijection with respectively $\Z_p$ and $\Z_p^g$.
+We also discuss the resulting map $\Z_p \to \Z_p^g$.
+
+In Section~\ref{section:kappa} we further look at the map $J(\Z_{(p)})_t \to J(\Z_p)_t$.
+This is a translation of the group morphism $J(\Z_{(p)})_0 \to J(\Z_p)_0$ between kernels of reduction; it turns out that for our choice of $p$, the subgroup $J(\Z_{(p)})_0$ is free of rank $r$.
+We study the properties of the resulting map $\Z^r \to \Z_p^g$, using the theory of formal groups to determine the group structure on $\Z_p^g$ induced by the bijection $J(\Z_p)_0 \to \Z_p^g$.
+
+In Section~\ref{section:intersection}, we put all of this information together, culminating in several methods to possibly compute upper bounds on $\left|C(\Z_p)_P \cap \overline{J(\Z_{(p)})_t}\right|$ with finite precision calculations.
+We also perform a heuristic analysis to show that a simple calculation of linear algebra modulo $p$ is very likely to result in an upper bound of at most $|C(\F_p)|$ for $|C(\Z_{(p)})|$, and for $r < g-1$ even in an upper bound of $|C(\Q)|$.
+
+The methods developed in the first four sections are not always guaranteed to prove finiteness of $C(\Z_{(p)})_P$.
 In Section~\ref{section:remarks} we treat several possible complications and improvements, referring to other work on Chabauty for further reading.
@@
 Here, we use Makdisi's approach of representing a divisor by a subspace of a large Riemann-Roch space.
-We partially follow the article \cite{mascot18} by Mascot, and also give an original algorithm for explicitly computing the map $C(O_{\pi})_P \to J(O_{\pi})_t$ in Makdisi's representation.
-
-We end our discussion of linear geometric Chabauty with an explicit example in Section~\ref{section:example}, a genus $2$ curve over the rationals whose Jacobian has Mordell-Weil rank $1$.
+We partially follow the article \cite{mascot18} by Mascot, and also give an algorithm for explicitly computing the map $C(\Z_p)_P \to J(\Z_p)_t$ in Makdisi's representation.
+
+We end our discussion of linear geometric Chabauty with an explicit example in Section~\ref{section:example}, a genus $2$ curve whose Jacobian has Mordell-Weil rank $1$.
 We use both Magma and Pari/GP to do our calculations, and end up with a complete list of all rational points of the curve.
-
-Finally, we provide an introduction to geometric quadratic Chabauty in Section~\ref{section:quadratic} (working only over the rationals).
-Here, we aim to introduce all the different objects relevant to geometric quadratic Chabauty; we explain why we have to work over $\Z$ instead of over $\Q$ in order for geometric quadratic Chabauty to make sense; and we explain some of the problems and solutions that working over $\Z$ gives rise to.
-
-\subsection{Preliminaries}
-We expect the readers of this thesis to be familiar with algebraic geometry, e.g.
-master students with a specialisation in algebraic geometry.
-The introduction to geometric quadratic Chabauty in Section~\ref{section:quadratic} contains some terms typically not treated in a master programme; while knowing them will help to put the material in context, this section is meant to be understandable for those that are not familiar with the terminology as well.
-
-\subsection{Acknowledgements}
-I would like to thank my supervisor Bas Edixhoven for his help --- I have learnt a great deal since starting on this thesis, and he helped me do so.
-I would also like to thank my father, for all the support he has shown me.
 
@@
 \label{section:smoothzppoints}
-{\color{red} Most of this section should still hold in the general number field case; replacing $p$ by $\pi$ when it is an element of $A$ (i.e., a section of $X$) and by $q$ when it is the cardinality of the residue field.
-Only the remark on it being a torsor of the tangent space merits a checking+rewrite.
-This has been done.}
 Let $X/\Z_p$ be a smooth scheme of relative dimension $d$, and let $x \in X(\F_p)$ be a point.
-Then we will show in this section that $X(\Z_p)_x$ is naturally in bijection with $\Z_p^d$.
+Then we will show in this section that $X(\Z_p)_x$ is, up to a single choice, naturally in bijection with $\Z_p^d$.
 This bijection is given by choosing parameters at $x$; evaluating at $X(\Z_p)_x$ gives a bijection with $(p\Z_p)^d$, and then we divide by $p$.
@@
 \begin{proof}
-Note that by (I,2.4.4) of \cite{ega}, a $\Z_p$-point of a scheme $S$ is just an $\F_p$-point $s$ together with a local morphism $\\O_{S,s} \to \Z_p$.
+Note that by (I,2.4.4) of \cite{ega}, a $\Z_p$-point of a scheme $S$ is just an $\F_p$-point $s$ together with a local morphism $\O_{S,s} \to \Z_p$.
 In our case, we find that $X(\Z_p)_x$ is naturally in bijection with $\Hom_{\text{local}}(A_x,\Z_p)$.
@@
 \label{rem:torsortangentspace}
-In actual calculations, we will be focusing on $X(S)_x$ where $S = O_\pi/\pi^2 O_\pi$.
-This set is a natural torsor of the tangent space $T_x X_{\F_q}$ of $X_{\F_q}$ at $x$, which we will describe here.
-We write $R$ for the local ring $\O_{X_{S},x}$ and $\m$ for its maximal ideal, and $\overline{R}$ and $\overline{\m}$ for their reductions modulo $\pi$.
-Then an element in $X(S)_x$ is a local morphism $R \to S$.
-As $R/\m = \F_q$, giving such a local morphism is equivalent to giving a map $\m \to \pi S$ respecting multiplication and sending $\pi$ to $\pi$.
-Such a map factors uniquely through $\m/\m^2 \to \pi S$.
-We see that the set $X(\Z/p^2\Z)_x$ is canonically in bijection with $\F_q$-linear maps $\m/\m^2 \to \pi S$ sending $\pi$ to $\pi$.
-Note that $\m/\m^2$ is a $(d+1)$-dimensional $\F_q$-vector space, and $\overline{\m}/\overline{\m}^2$ is a $d$-dimensional $\F_q$-vector space; the map $\m/\m^2 \to \overline{\m}/\overline{\m}^2$ is dividing out by $\pi$.
-Denoting ${}^\wedge$ to be $\Hom(\cdot,\F_q)$, the exact sequence
-\[
-0 \to \pi S \to \m/\m^2 \to \overline{\m}/\overline{\m}^2 \to 0
+In actual calculations, we will be focusing on $X(\Z/p^2\Z)_x$.
+This set is a natural torsor of the tangent space $T_x X_{\F_p}$ of $X_{\F_p}$ at $x$, which we will describe here.
+We write $R$ for the local ring $\O_{X_{\Z/p^2\Z},x}$ and $\m$ for its maximal ideal, and $\overline{R}$ and $\overline{\m}$ for their reductions modulo $p$.
+Then an element in $X(\Z/p^2\Z)_x$ is a local morphism $R \to \Z/p^2\Z$.
+As $R/\m = \F_p$, giving such a local morphism is equivalent to giving a map $\m \to p\Z/p^2\Z$ respecting multiplication and sending $p$ to $p$.
+Such a map factors uniquely through $\m/\m^2 \to p\Z/p^2\Z$.
+We see that the set $X(\Z/p^2\Z)_x$ is canonically in bijection with $\F_p$-linear maps $\m/\m^2 \to p\Z/p^2\Z$ sending $p$ to $p$.
+Note that $\m/\m^2$ is a $(d+1)$-dimensional $\F_p$-vector space, and $\overline{\m}/\overline{\m}^2$ is a $d$-dimensional $\F_p$-vector space; the map $\m/\m^2 \to \overline{\m}/\overline{\m}^2$ is dividing out by $p$.
+Denoting ${}^\wedge$ to be $\Hom(\cdot,\F_p)$, the exact sequence
+\[
+0 \to p\Z/p^2\Z \to \m/\m^2 \to \overline{\m}/\overline{\m}^2 \to 0
 \]
@@
 \[
-0 \to (\overline{\m}/\overline{\m}^2)^\wedge \to (\m/\m^2)^\wedge \to (\pi S)^{\wedge} \to 0.
-\]
-As $X(S)_x$ is exactly the subset of $(\m/\m^2)^\wedge$ that gets mapped to the function $p \mapsto 1 \in (\pi S)^{\wedge}$, we see this is naturally a torsor under the tangent space $(\overline{\m}/\overline{\m}^2)^\wedge = T_{x} X_{\F_q}$.
+0 \to (\overline{\m}/\overline{\m}^2)^\wedge \to (\m/\m^2)^\wedge \to (p\Z/p^2\Z)^{\wedge} \to 0.
+\]
+As $X(\Z/p^2\Z)_x$ is exactly the subset of $(\m/\m^2)^\wedge$ that gets mapped to the function $p \mapsto 1 \in (p\Z/p^2\Z)^{\wedge}$, we see this is naturally a torsor under the tangent space $(\overline{\m}/\overline{\m}^2)^\wedge = T_{x} X_{\F_p}$.
 
@@
 \label{rem:cartierlinear}
-We look at the specific case of $X$ being of relative dimension $1$ over $\Z_p$.
+We look at the specific case of $X$ being of relative dimension~$1$ over $\Z_p$.
 Then the $T_x X_{\F_p}$-torsor structure on $X(\Z/p^2\Z)_x$ translates into something more concrete.
 We can parametrise $X(\Z/p^2\Z)_x$ by $t = t_1 $ from $X(\Z/p^2\Z)_x \to p\Z/p^2\Z$; write $P_{\lambda}$ for the point with $t$-value $\lambda p$.
-Then as Cartier divisor, the point $P_{\lambda}$ is defined by $t - \lambda p \in \O_{X_{\Z/p^2\Z},x}$, so $P_{\lambda} + P_{\mu}$ is defined by $(t-\lambda p)(t-\mu p) = t^2 - (\lambda + \mu)tp$, which defines the same Cartier divisor as $P_{\lambda'} + P_{\mu'}$ if and only if $\lambda + \mu = \lambda' + \mu'$.
+Then as a Cartier divisor, the point $P_{\lambda}$ is defined by $t - \lambda p \in \O_{X_{\Z/p^2\Z},x}$, so $P_{\lambda} + P_{\mu}$ is defined by $(t-\lambda p)(t-\mu p) = t^2 - (\lambda + \mu)tp$, which defines the same Cartier divisor as $P_{\lambda'} + P_{\mu'}$ if and only if $\lambda + \mu = \lambda' + \mu'$.
 In that case, as a Cartier divisor, $P_{\lambda} + P_{\mu}$ is in fact equal to $P_{\lambda'} + P_{\mu'}$.
@@
 \label{subsection:czptojzp}
-Let $p,C$ and $J$ be as defined in the overview.
+Let $p$, $C$ and $J$ be as defined in the overview.
 We know that $C(\Z_p)_P$ is in bijection with $\Z_p$, again with the bijection given by evaluating a parameter and dividing by $p$.
@@
 \section{From \texorpdfstring{$J(\Z_{(p)})$}{J(Z\_{(p)})} to \texorpdfstring{$J(\Z_p)$}{J(Z\_p)}}
-\label{section:kappa}
+\label{section:kappa}\todo{Try to find a reference for this section.
+Maybe try "Lie groups and Lie algebras" by Serre.
+It seems to almost be folklore, couldn't find a reference by googling.
+And I can't even find my result on exp and log mod powers of p.}
 Let $p,C,J$ be as in the overview.
@@
 We introduce some notation that will be used in this section.
-Let $R$ be a commutative ring, and $\vx = (x_1,\dots,x_n)$ and similarly $\vy,\vz$ are vectors of variables.
+Let $R$ be a commutative ring, and let $\vx = (x_1,\dots,x_n)$ and $\vy = (y_1,\dots,y_m)$ be vectors of variables.
 Then $R[[\vx]]$ denotes as usual the ring of formal power series in the $x_i$, and $R[[\vx]]_0$ denotes those power series with constant term $0$.
@@
 \end{defn}
-\begin{exmp}
+\begin{exmp}\todo{If I can't find a reference, at least remove this examples.}
 \label{exmp:ganformalgroup}
@@
 By smoothness, after picking parameters, this is isomorphic as a topological $R$-algebra to the ring of power series $R[[x_1,\dots,x_d]]$.
-This completion naturally gives rise to a formal scheme denoted $\Spf \widehat{\O}_{G,e}$; in a categorical notion, this is a functor on finite length $R$-algebras sending $A$ to $\Hom_{\text{cont}}(\widehat{\O}_{G,e},A)$, but we can also think of it as a locally ringed space with $\Spec R$ as topological space, and sheaf of rings the inverse limits of the sheaf of rings associated to the $R$-algebra $\O_{G,e}/I^n$, where $I$ is the ideal of $\O_{G,e}$ defining $e$.
+This completion naturally gives rise to a formal scheme denoted $\Spf \widehat{\O}_{G,e}$; in a categorical view, this is a functor on finite length $R$-algebras sending $A$ to $\Hom_{\text{cont}}(\widehat{\O}_{G,e},A)$, but we can also think of it as a locally ringed space with $\Spec R$ as topological space, and sheaf of rings the inverse limits of the sheaf of rings associated to the $R$-algebra $\O_{G,e}/I^n$, where $I$ is the ideal of $\O_{G,e}$ defining $e$.
 The global sections of this sheaf are simply $\widehat{\O}_{G,e}$.
@@
 After choosing an isomorphism between $\widehat{\O}_{G,e}$ and $R[[x_1,\dots,x_d]]$, let the power series $F_j \in R[[\vx,\vy]]$ denote $\mu(x_j)$.
-Then it is clear that \[F_G = (F_1,\dots,F_d)\] is a $d$-dimensional formal group scheme, and commutative if $G$ is commutative.
+Then it is clear that \[F_G = (F_1,\dots,F_d)\] is a $d$-dimensional formal group scheme, and is commutative if $G$ is commutative.
 \addtocounter{thm}{-3}
@@
 A $1$-form $\omega = \sum_{i=1}^n f_i \diff x_i$ being closed means exactly that $\frac{\partial f_i}{\partial x_j} = \frac{\partial f_j}{\partial x_i}$ for all $i,j$.
-From now on, assume $R$ has no torsion; then $R$ imbeds into $\Q \tensor R$ and, we can formally integrate $\omega$, i.e.
+From now on, assume $R$ has no torsion; then $R$ embeds into $\Q \tensor R$ and, we can formally integrate $\omega$, i.e.
 write it as $df$ where $f \in (\Q\tensor R)[[\vx]]$.
 We make this unique by demanding that $f(0) = 0$.
-Writing this $f$ as $\sum_{I \in \N^n} a_I x^I$ with $I$ denoting a multi index and $a_I \in \Q\tensor R$, we see that $a_I$, although itself not necessarily lying in $R$, is close: writing $I = (I_1,\dots,I_n)$ we see that for all $j$ we must have $I_j a_I \in R$ as $f_j = \frac{\partial f}{\partial x_j} \in R[[\vx]]$.
+Writing this $f$ as $\sum_{I \in \N^n} a_I x^I$ with $I$ denoting a multi-index and $a_I \in \Q\tensor R$, we see that $a_I$, although itself not necessarily lying in $R$, is close: writing $I = (I_1,\dots,I_n)$ we see that for all $j$ we must have $I_j a_I \in R$ as $f_j = \frac{\partial f}{\partial x_j} \in R[[\vx]]$.
 
@@
 \begin{exmp}[continued]
-Taking $F$ again the multiplicative formal group as in Example~\ref{exmp:gmformalgroup}, Proposition~1.1 of \cite{honda70} gives us $\omega = \frac{1}{x+1}$; as a power series this is $\sum_{j \geq 0} (-x)^j$.
-The formal anti-derivative of this is \[\log = \sum_{j \geq 1} \frac{-(-x)^j}{j}dx\] (note this is a translate of the $\log$ from analysis), and Theorem~$1$ of \cite{honda70} will tell us what we already know in the context of analysis, namely the formula $\log(x + y + xy) = \log(x)+\log(y)$ (this formula is also a translate of the corresponding formula from analysis).
+Taking $F$ again the multiplicative formal group as in Example~\ref{exmp:gmformalgroup}, Proposition~1.1 of \cite{honda70} gives us $\omega = \frac{1}{x+1}dx$; as a power series this is $\sum_{j \geq 0} (-x)^jdx$.
+The formal anti-derivative of this is \[\log = \sum_{j \geq 1} \frac{-(-x)^j}{j}\] (note this is a translate of the $\log$ from analysis), and Theorem~$1$ of \cite{honda70} will tell us what we already know in the context of analysis, namely the formula $\log(x + y + xy) = \log(x)+\log(y)$ (this formula is also a translate of the corresponding formula from analysis).
 Then analysis will also explicitly tell us what $\exp$ looks like: $\exp(x) = \sum_{j \geq 1} \frac{x^j}{j!}$.
@@
 we have, as subsets of $J(\Z_p)_t$, the inclusion \[C(\Z_{(p)})_P \subset C(\Z_p)_P \cap \overline{J(\Z_{(p)})_t}.\]
-The theory we have built so far enables the following method, which is in sharp contrast with Colemans method; instead of pulling back equations for $\overline{J(\Z_{(p)})_t}$ to $C(\Z_p)_P$, we pull back equations for $C(\Z_p)_P$ to $\overline{J(\Z_{(p)})_t}$ to arrive at the following theorem.
+The theory we have built so far enables the following method, which is in sharp contrast with Coleman's method; instead of pulling back equations for $\overline{J(\Z_{(p)})_t}$ to $C(\Z_p)_P$, we pull back equations for $C(\Z_p)_P$ to $\overline{J(\Z_{(p)})_t}$ to arrive at the following theorem.
 \begin{thm}
@@
 
-Of note is that this upper bound for $|C(\Z_{(p)})|$ does not even depend on the genus, and behaves agreeably when compared to the upper bound in Theorem 5.3 of \cite{poonen12}, which tells us that $|C(\Z_{(p)})| \leq |C(\F_p)| + 2g-2$ under the much lighter condition of $r < g, p > 2g$ where $p$ is still a prime of good reduction.
+Of note is that this upper bound for $|C(\Z_{(p)})|$ behaves agreeably when compared to the upper bound in Theorem 5.3 of \cite{poonen12}, which tells us that $|C(\Z_{(p)})| \leq |C(\F_p)| + 2g-2$ under the much lighter condition of $r < g, p > 2g$ where $p$ is still a prime of good reduction.
 To summarise: in Proposition~\ref{prop:linchabauty} we sacrifice certainty for being able to prove much sharper bounds.
@@
 \begin{rem}
+\label{rem:probwork}
 Consider the case $r=g-1$.
@@
 Finding generators of $J(\Q)$ is as of yet a computationally difficult problem, and one may need to assume the Birch-Swinnerton-Dyer conjecture to even find the rank $r$.
-However, note that one does not need to find all of $J(\Q)$; if we can generate a subgroup of $J(\Q)$ of index finite and coprime to $p|J(\F_p)|$, it will have the same closure in $J(\Z_p)$.
+However, when one knows the rank, one does not necessarily need to find generators $J(\Q)$; if we can generate a subgroup of $J(\Q)$ of index finite and coprime to $p|J(\F_p)|$, it will have the same closure in $J(\Z_p)$.
 For this, we only need to generate sufficiently many independent points of the Jacobian and saturate subgroups with respect to some primes.
@@
 
-\section{Implementations of linear Chabauty}
+\section{Implementations of linear Chabauty}\todo{Try to make this a bit more condensed.}
 \label{section:explicit}
@@
 An alternative way of defining such a curve, and the one we will be using mainly, is as a glueing of two affine charts: $y^2 = f(x)$, and $w^2 = f^{r}(v)$, where $f^{r}(v)$ is the polynomial $v^{2g + 2} f(1/v)$, and a birational map between them is given by $(x,y) \mapsto (\frac{1}{x},\frac{y}{x^{g+1}})$.
-We also have the coordinates $X,Y,Z$ of $\P(1,g+1,1)$, with \[x = X/Z, y = Y/Z^{g+1}, v = Z/X, w = Y/X^{g+1},\] but beware; these coordinates do not behave nicely on the origin of the patch given by $Y \neq 0$.
+We also have the coordinates $X,Y,Z$ of $\P(1,g+1,1)$, with \[x = X/Z, y = Y/Z^{g+1}, v = Z/X, w = Y/X^{g+1},\] but beware; $\P(1,g+1,1)$ is not smooth and hence these coordinates do not behave nicely on all of $\P(1,g+1,1)$.
 We mainly use the first chart; we call any point that lies on it an affine point of $C$.
-We will treat the case that $f$ has degree $2g+2$ (this can be done by translating $f$ until the constant coefficient is non-zero, and then looking at $f^r$).
+Again for ease of exposition, we will treat the case that $f$ is monic of degree $2g+2$ (in general, one can demand $f$ has degree $2g+2$ by translating $f$ until the constant coefficient is non-zero, and then looking at $f^r$).
 In that case, near the line at infinity $C$ looks like $Y^2 = X^{2g+2}$, i.e.
@@
 
-As explained in Mascot's article, using this representation one can do all relevant computations in $J(k)$; adding, subtracting, finding the zero element, and most importantly: checking equality.
+As explained in Mascot's article, using this representation one can do all relevant computations in $J(k)$; adding, subtracting, finding the zero element, and very importantly: checking equality.
 Important from a computational standpoint is the complexity, which we write down in big O notation.
-As everything is simply linear algebra in spaces of dimensions $O(g)$, the complexity of all these operations, assuming calculations in the ground ring are $O(1)$, are all simply $O(g^\omega)$ where $\omega$ is the matrix constant.
+As everything is simply linear algebra in spaces of dimensions $O(g)$, the complexity of all these operations, assuming calculations in the ground ring are $O(1)$, are all simply $O(g^\omega)$ where $\omega$ is the exponent of matrix multiplication.
 
@@
 The final trick we need is extensions of $\Z/p^e\Z$.
-As said before, we need $n_Z$ affine points that are distinct modulo $p$, so we passed from $\F_p$ to an extension of $\F_q$.
+As said before, we need $n_Z$ affine points that are distinct modulo $p$, so we passed from $\F_p$ to an extension $\F_q$.
 The corresponding notion of an extension of $\Z/p^e\Z$ is given by taking an irreducible polynomial $\overline{T} \in \F_p[t]$ with $\F_q \cong \F_p[t]/\overline{T}$, arbitrarily lifting $\overline{T}$ to a polynomial $T \in \Z/p^e\Z[t]$, and looking at $R = (\Z/p^e\Z[t])/T$.
@@
 Let $C$ be any (hyper)elliptic curve given by $y^2 = f(x)$ with $f$ of degree $2g+2$ where $g$ is the genus of $C$.
-A Mumford representation is a pair $(a,b)$ with $a,b$ polynomials in $x$, representing the degree $0$ divisor $D(a,b)$ on $C$, given on the first affine chart by the equation $a(x) = 0, y = b(x)$ and on the line at infinity by $-\deg a\infty_+$.
+A Mumford representation is a pair $(a,b)$ with $a,b$ polynomials in $x$, representing the degree $0$ divisor $D(a,b)$ on $C$, given on the first affine chart by the equation $a(x) = 0, y = b(x)$ and on the line at infinity by $(-\deg a)\infty_+$.
 Such a pair $a,b$ is required to satisfy that
@@
 \subsection{Complexity}
-We assume necessary data for the Mordell-Weil group of the Jacobian is given; that is, we have a set of generators for either $J(\Z_{(p)})$, or just a full rank subgroup of index coprime to $pJ(\F_p)$.
+We assume necessary data for the Mordell-Weil group of the Jacobian is given; that is, we have a set of generators for either $J(\Z_{(p)})$, or just a full rank subgroup of index coprime to $p|J(\F_p)|$.
 We also assume that all relevant elements in $J(\Z_{(p)})$ and $J(\F_p)$ are in the subgroup generated by $C(\Z_{(p)})$ and $C(\F_p)$.
@@
 
-\section{Quadratic Chabauty}
-\label{section:quadratic}
-In this section, we attempt to give an introduction to the article~\cite{edixhoven20} aimed to introduce all the players in quadratic Chabauty at a slightly slower pace.
-We will omit all proofs.
-For further reading, see for example \cite{hashimoto20}, an in-progress cartoon guide to the article by Edixhoven and Lido.
-
-% Explain all diagrams over Q
-We start by explaining the idea over $\Q$; we let $C_\Q$ be a projective, smooth curve over $\Q$ of genus at least $2$, we let $J_\Q$ be its Jacobian.
-We again assume the existence of a rational point $b \in C_\Q(\Q)$ and use it to construct an embedding $j_b : C_\Q \to J_\Q$.
-We wish to set up a similar situation to classic Chabauty, and for that, we introduce the Poincar\'e line bundle and Poincar\'e torsor.
-For this, we need $J_\Q^\wedge$, the dual of $J_\Q$, which is in fact isomorphic to $J_\Q$, taking as isomorphism for example the principal polarisation $\lambda: J_\Q \to J_\Q^\wedge$.
-This dual parametrises line bundles that are algebraically equivalent to $0$ on $J_\Q$, and hence we get a universal such line bundle $P_\Q$ on $J_\Q \times J_\Q^\wedge$, called the Poincar\'e line bundle $P_\Q$, which also satisfies that both $P_{\Q}|_{0\times J_\Q^\wedge}$ and $P_{\Q}|_{J_\Q \times 0}$ are trivial.
-
-\begin{exmp}
-If $C_\Q$ is an elliptic curve then, identifying $C_\Q,J_\Q$ and $J_\Q^{\wedge}$, we get $P_\Q = \O(\Delta-\{0\} \times C_\Q - C_\Q \times \{0\})$, with the fibres $P_\Q|_{,c \times C_\Q} \cong \O(c-0)$ being exactly the degree $0$ line bundles on $C_\Q$ up to isomorphism.
-\end{exmp}
-
-The object we will be working with is the Poincar\'e torsor, the $\G_m$ torsor over $J_\Q \times J_\Q^\wedge$ defined by \[
-P_\Q^\times = \text{Isom}_{J_\Q \times J^\wedge_\Q}(\O_{J_\Q \times J^\wedge_\Q},P_\Q).
-\] 
-We can also describe this in terms of its functor of points; for any scheme $S$ over $J_\Q \times J^\wedge_\Q$, we have that $P^\times_\Q(S)$ is the set of isomorphisms between $\O_S$ and $(P_\Q)_S$, with a free, transitive action of $\O_S(S)^\times$, i.e.
-a pseudotorsor of $\O_S(S)^\times$ in the traditional group-theoretic sense (note that this set can be empty).
-
-Furthermore, this Poincar\'e torsor has a nice structure of a biextension; this means we can think of the fibres $P^\times_{\Q,(x,y)}$ as being a $\G_m$ above the point $x \times y$; this structure then gives multiplication maps \[P^\times_{\Q,(x_1,y)} \times P^\times_{\Q,(x_2,y)} \to P^\times_{\Q,(x_1+x_2,y)}\] and similarly \[P^\times_{\Q,(x,y_1)} \times P^\times_{\Q,(x,y_2)} \to P^\times_{\Q,(x,y_1+y_2)}.\]
-This bilinear structure comes from interpreting $J_\Q^\wedge$ as $\text{Ext}^1(J_\Q,\G_m)$; then $P_\Q^\times$ is the universal extension of $J_\Q$ by $\G_m$, indexed by $J_\Q^\wedge$, and by duality vice versa as well.
-
-Instead of doing Chabauty in this Poincar\'e torsor, we will look at a pullback of this torsor to a $\G_m$-torsor over $J_\Q$.
-Our first attempt is pulling back along the map $J_\Q$ to $J_\Q \times J^\wedge_\Q$ given as $(\id,\tr_c \circ f)$ where $f: J_\Q \to J^\wedge_\Q$ is a morphism of group schemes and $\tr_c: J^\wedge_\Q \to J^\wedge_\Q$ is translation along $c \in J^\wedge_\Q(\Q)$.
-We denote the pullback of $P^\times_\Q$ along this map by $T_\Q$, a $\G_m$-torsor over $J_\Q$.
-This $T_\Q$ has dimension $g+1$.
-The general idea of geometric quadratic Chabauty, is to work with the following diagram
-\[\begin{tikzcd} % https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBoBGAXVJADcBDAGwFcYkQBhAfQB0eBFEAF9S6TLnyEU5CtTpNW7AFK8Bw0SAzY8BIgCZZNBizaIQKvvwAEfPAFt4VpQD0+AdxhQA5jFWCRYtqS+qTEcsaKZgAKrjz28OqBErrSoeEKpiAAKsJynj4IKKAAZgBOEHZIZCA4EEgALEYZ7HxZWIywwABWXABGQokgZRVVNLVIMvIm7D29g8OViJPjiAZTkSAAFHxYUKS2pVwAxjY8R1ilJ8UAlPPli401dUsBQ-cNY88AzK8LSF+fJBrRj0XowRhRcQ6KQgRgwYo4XJCIA
-                                                & T_\Q \arrow[d] \arrow[rr]                   && P_\Q^\times \arrow[d]      \\
-C_\Q \arrow[ru, "\widetilde{j_b}"] \arrow[r, "j_b"] & J_\Q \arrow[rr, "{(\id,\tr_c \circ f)}"] && J_\Q \times J^\wedge_\Q
-\end{tikzcd}\]
-where $\widetilde{j_b}$ is a lift of $j_b$.
-This lift will only exist if $j_b^* T$ is a trivial $\G_m$-torsor over $C_\Q$; for that, it turns out that we want $f$ to be an element of $\Hom^+(J_\Q,J^\wedge_\Q)_0$, the group of self dual homomorphisms of trace $0$ (where this trace comes from identification with the N\'eron-Severi group); if we do that, it turns out that $j_b^* T$ will correspond to a degree $0$ line bundle on $C_\Q$, and we only need to translate by a constant to make $j_b^* T$ trivial.
-
-If $f$ itself is already $0$, then $T$ is trivial and this will give no further information, and most of the time that is the best we can do, as generically the rank of $\Hom^+(J_\Q,J^\wedge_\Q)$, also called the N\'eron-Severi rank $\rho$, is $1$.
-But in many interesting cases, this rank is bigger than $1$.
-Using the isomorphism $\lambda$, this rank is also the rank of a certain subgroup of the endomorphism ring of $J_\Q$, and it turns out a family of possible examples is given by modular curves; for example, normalisers of non-split Cartan curves $X_{\text{ns}}^+(\ell)$ have N\'eron-Severi rank equal to the genus, and, according to the BSD conjecture, Mordell-Weil rank at least equal to the genus.
-
-In general, we can pick a basis $f_1,\dots,f_{\rho-1}$ of the trace $0$ subgroup of $\Hom^+(J_\Q,J^\wedge_\Q)$ and elements $c_1,\dots,c_{\rho-1} \in J_\Q^\wedge$ with $j_b^* (\id,\tr_{c_i} \circ f_i)^* P_{\Q}^\times$ trivial, and take the product of all the resulting pullbacks over $J_\Q$, to get a $\G_m^{\rho-1}$-torsor $T$ over $J_\Q$ that admits a morphism from $C_\Q$.
-
-We then would like to intersect the rational points of $T_\Q$ with the $p$-adic points of $C_\Q$, mapped to $T_\Q$ under $\widetilde{j_b}$, inside the $p$-adic points of $T_\Q$.
-As in the case of classic Chabauty, one can conclude that the $p$-adic points of $T_\Q$ form a $p$-adic manifold of dimension $g+\rho-1$, but there is a problem with the rational points of $T_\Q$; these are in bijection with $\G_m(\Q)^{\rho-1} \times J_\Q(\Q)$.
-The latter is a finitely generated group of rank $r$, the Mordell-Weil rank, but the former is an infinitely generated group.
-One can upper bound the dimension of $\overline{T_\Q(\Q)}$ by $r + \rho -1$, but it is clear that this will not lead to an improvement to classic Chabauty.
-
-% Spread out over Z, explain general process and some difficulties
-To combat this problem, the crucial insight is that while $\Q^\times$ is infinitely generated, $\Z^\times$ is finite, so we set everything to work over $\Z$ instead of over $\Q$.
-Our curve is now a surface $C$, of relative dimension $1$ over $\Z$, proper, flat and regular with generic fibre $C_\Q$.
-We cannot expect $C$ to be smooth over $\Z$, we only ask that $C$ is smooth over $\Z[1/n]$ for some squarefree $n$ consisting of bad primes.
-We let $J$ be the N\'eron model over $\Z$ of the Jacobian of $C_\Q$, and $J^\wedge$ the N\'eron model of the dual of $J$.
-If we want to keep the essential biextension structure of the Poincar\'e torsor intact, we can only extend to $P \to J \times J^{\wedge 0}$ where $J^{\wedge 0}$ is the connected component of $J^\wedge$ containing $0$; the component group $J^\wedge/J^{\wedge 0}$ is only supported on $\Z/n\Z$, i.e.
-on the bad primes.
-We let $m\in \Z_{>0}$ be the annihilator of $J^\wedge/J^{\wedge 0}$.
-We can then make a similar diagram as before
-\[\begin{tikzcd} % https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBoBGAXVJADcBDAGwFcYkQBhAfQB0eBFEAF9S6TLnyEU5CtTpNW7AFK8Bw0SAzY8BIgCZZNBizaIQKvvwAEfPAFt4VpQD0+AdxhQA5jFWCRYtqS+qTEcsaKZgAKrjz28OqBErrSoeEKpiAAKsJynj4IKKAAZgBOEHZIZCA4EEgALEYZ7HxZWIywwABWXABGQokgZRVVNLVIMvIm7D29g8OViJPjiAZTkSAAFHxYUKS2pVwAxjY8R1ilJ8UAlPPli401dUsBQ-cNY88AzK8LSF+fJBrRj0XowRhRcQ6KQgRgwYo4XJCIA
-                                                & T \arrow[d] \arrow[rr]                   && P^\times \arrow[d]      \\
-C \arrow[ru, "\widetilde{j_b}", dotted] \arrow[r, "j_b"] & J \arrow[rr, "{(\id,\cdot m \circ\tr_c \circ f)}"] && J \times J^{\wedge 0}
-\end{tikzcd}\]
-where this time $f$ is an element of $\Hom^+(J,J^\wedge)$ of trace $0$ and $c \in J^{\wedge}$ such that $j_b^* (\id,\tr_{c_i} \circ f_i)^* P_{\Q}^\times$ is trivial.
-
-There is one problem: the lift of $j_b$ from $C$ to $T$ only exists if $j_b^* T$ is trivial over $C$.
-We know this is true when base changed over $\Q$, and over $\Q$ the lift exists and is unique up to the action of $\Q^\times$.
-For $q$ prime for which $C_{\F_q}$ has only one component, we can multiply a trivialising section over $C_\Q$ by a suitable power of $q$ to make it a trivialising section over $C_{\Z_{(q)}}$.
-However, we cannot always do this if $C_{\F_q}$ has multiple components.
-
-So instead we cover $C^{\sm}$ with multiple opens $U_i$, obtained by removing for each $q$ dividing $n$ all but one irreducible components.
-As $C(\Z) = C^{\sm}(\Z)$, it is enough to compute $U_i(\Z)$ for every $U_i$.
-Then the map $j_{b,i}: U_i \to J$ does lift as in the following diagram:
-\[\begin{tikzcd} % https://tikzcd.yichuanshen.de/#N4Igdg9gJgpgziAXAbVABwnAlgFyxMJZABgBoBGAXVJADcBDAGwFcYkQBhAfQB0eBFEAF9S6TLnyEU5CtTpNW7AFK8Bw0SAzY8BIgCZZNBizaIQKvvwAEfPAFt4VpQD0+AdxhQA5jFWCRYtqS+qTEcsaKZgAKrjz28OqBErrSoeEKpiAAKsJynj4IKKAAZgBOEHZIZCA4EEgALEYZ7HxZWIywwABWXABGQokgZRVVNLVIMvIm7D29g8OViJPjiAZTkSAAFHxYUKS2pVwAxjY8R1ilJ8UAlPPli401dUsBQ-cNY88AzK8LSF+fJBrRj0XowRhRcQ6KQgRgwYo4XJCIA
-                                                & T \arrow[d] \arrow[rr]                   && P^\times \arrow[d]      \\
-U_i \arrow[ru, "\widetilde{j_{b,i}}"] \arrow[r, "j_{b,i}"] & J \arrow[rr, "{(\id,\cdot m \circ\tr_c \circ f)}"] && J \times J^{\wedge 0}
-\end{tikzcd}\]
-and we can finalise the summary of quadratic Chabauty.
-Denote $T$ now for the product of all $\rho-1$ such pullbacks for $f$ ranging over a basis of the trace $0$ submodule of $\Hom^+(J,J^{\wedge})$.
-Taking a specific such $U$ with a lift $\widetilde{j_b}: U \to T$, for every prime $p$, the set $\widetilde{j_{b}}(U(\Z))$ is a subset of the intersection, inside the $p$-adic manifold $T(\Z_p)$, of $\widetilde{j_b}(U(\Z_p))$ and the closure $\overline{T(\Z)}$ of $T(\Z)$.
-As the relative dimension of $T$ over $\Z_p$ is $g+\rho-1$ (it is a $\G_m^{\rho-1}$-torsor over $J$), we can as in Section~\ref{section:smoothzppoints} see that $T(\Z_p)$ has dimension $g+\rho-1$; and as $T(\Z)$ is a $\{\pm 1\}^{\rho-1}$-torsor over the group $J(\Z)$ of rank $r$, it will turn out $\overline{T(\Z)}$ has dimension at most $r$.
-As $U(\Z_p)$ has dimension $1$, we can hope that this intersection is dimension $0$, and hence finite as $T(\Z_p)$ is compact, if $r < g + \rho-1$, hence we have an improvement over classical Chabauty.
-
-This argument can be made explicit when looking at residue discs; in short, just like we could parametrise $J(\Z)_0$ with $\Z^r$ in Section~\ref{section:kappa} where the inclusion $\Z^r \to J(\Z_p)_0 \cong \Z_p^{g}$ is given by convergent power series, it turns out that for $t \in T(\F_p)$ that lift to $T(\Z)$, there is a map $\kappa: \Z^r \to T(\Z_p)_t \cong \Z_p^{g+\rho-1}$ such that $\kappa$ is given by convergent power series and extending the domain of $\kappa$ to $\Z_p^r$ we have $\kappa(\Z_p^r) = \overline{T(\Z)_t}$.
-This fact is a consequence of the biextension structure of $P^\wedge$; it allows us to quite explicitly move in the Poincar\'e torsor.
-
-When the parameters at $t$ are chosen nicely, the first $g$ coming from $J$, it turns out that $\kappa_1,\dots,\kappa_g$ are linear modulo $p$, and $\kappa_{g+1},\dots,\kappa_{g+\rho-1}$ are quadratic modulo $p$.
-The fact that these are quadratic is in fact related to this being called quadratic Chabauty; it has to do with the bilinear structure on $P^\times$, that when restricted to the image of $(\id,\cdot m \circ\tr_c \circ f)$ is a quadratic object, as both of $\id$ and $m \circ\tr_c \circ f$ are linear maps.
-This is analogous to how a bilinear form gives a quadratic form when evaluated at the diagonal.
-One can also again find equations $g_1,\cdots,g_{r+\rho-2}$ for the the image of $U(\Z_p)$ in $T(\Z_p)_t$, which will again be linear modulo $p$.
-
-We end with a proposition we already know; Proposition~\ref{prop:finedix} also holds in our case, and this once again can lead to giving an explicit upper bound for the cardinality of residue discs of $U(\Z)$ using finite precision calculations; repeating these calculations for the multiple opens $U$ and their $\F_p$-points, finally gives an upper bound for $C(\Z)$.
-
-% Computations, and section 7 of the article (line bundles on C x C)
-An important part of making the calculations work is forming the map $\widetilde{j_b}: U \to T$.
-For this, we need to be able to explicitly describe the trivialisation of the $\G_m$-torsor $j_b^* T$ restricted to $U$.
-Remember that $j_b^* T$ is also the pullback of $P^\times$ along the map $C \to J \times J^{\wedge 0}$, and this map factors through the diagonal map $C \to C\times C$.
-As described in Section~7 of the paper, it turns out that giving such a map $f: J \to J^{\wedge}$ and $c \in J^\wedge(\Z)$ with $j_b^* T$ trivial over all opens $U$ is equivalent to giving a line bundle $\Lcal$ on $C \times C$ satisfying the following three properties: $\Lcal$ is rigidified on $\{b\} \times C_\Q$, the fibres of $\pr_2: (C \times C)_\Q \to C_\Q$ are degree $0$, and the pullback $\diag^* \Lcal$ is trivial on $C_\Q$.
-This turns the problem of describing a map $J \to J^\wedge$ in the sometimes more concrete problem of giving a line bundle on $C \times C$ satisfying some simple conditions.
-
-These line bundles are crucial in doing actual computations.
-In the example in the Edixhoven-Lido paper, they use an involution of the curve to construct a correct line bundle.
-Right now, the focus is on doing a modular example, $X_0(73)^+$, a genus $2$ curve with endomorphism ring of rank $2$.
-Here, the extra information comes from the Hecke algebra working on the curve, and the problem at the time of writing lies in describing Hecke operators explicitly as correspondences on $C \times C$, and computations with these correspondences over $\Z$.
-
 \newpage

### 2023-12-08 artcompile.sh

@@ -1,0 +1,4 @@
+pdflatex art.tex
+bibtex art.aux
+pdflatex art.tex
+pdflatex art.tex

### 2023-12-08 pres.sh

@@ -1,0 +1,1 @@
+pdflatex --shell-escape Defense.tex
